### 2015-10-26 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
Isabelle Document added

%
\begin{isabellebody}%
\def\isabellecontext{TheoryOfAbstractObjectsV{\isadigit{1}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isamarkupsection{Introduction%
}
\isamarkuptrue%
%
\begin{isamarkuptext}%
This work significantly adapts and extends the embedding presented in \cite{J23}; say more ...%
\end{isamarkuptext}%
\isamarkuptrue%
%
\isamarkupsection{Preliminaries%
}
\isamarkuptrue%
\isacommand{typedecl}\isamarkupfalse%
\ i\isanewline
%
\isamarkupcmt{the type possible worlds; the formalism explicitly encodes Kripke style semantics%
}
\isanewline
\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ io\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}i\ {\isasymRightarrow}\ bool{\isacharparenright}{\isachardoublequoteclose}\ \isanewline
%
\isamarkupcmt{modal logic formulas (or propositional formulas) are essentially of this type: predicates on%
}
\isanewline
%
\isamarkupcmt{worlds%
}
\isanewline
\isanewline
\isacommand{typedecl}\isamarkupfalse%
\ e\isanewline
%
\isamarkupcmt{the raw type of entities/objects (abstract or ordinary)%
}
\isanewline
\isanewline
\isacommand{datatype}\isamarkupfalse%
\ {\isacharprime}a\ opt\ {\isacharequal}\ Error\ {\isacharprime}a\ {\isacharbar}\ Term\ {\isacharprime}a\ {\isacharbar}\ Form\ {\isacharprime}a\ {\isacharbar}\ PropForm\ {\isacharprime}a\isanewline
\isanewline
\isanewline
\isacommand{consts}\isamarkupfalse%
\ cw\ {\isacharcolon}{\isacharcolon}\ i\ \isanewline
%
\isamarkupcmt{some fixed current world%
}
\isanewline
\isanewline
\isacommand{consts}\isamarkupfalse%
\ dE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isachardoublequoteclose}\ dIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isachardoublequoteclose}\ dEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dEEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isacharequal}{\isachargreater}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dEEEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isacharequal}{\isachargreater}e{\isacharequal}{\isachargreater}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dA{\isacharcolon}{\isacharcolon}{\isacharprime}a\isanewline
%
\isamarkupcmt{some fixed dummy symbols; we anyway assume that the domains are on-empty%
}
\isanewline
%
\isamarkupcmt{needed as dummy object in some cases below%
}
%
\begin{isamarkuptext}%
We consider an arbitrary but fixed accessibility relation r%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{consts}\isamarkupfalse%
\ r\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharparenleft}i{\isasymRightarrow}i{\isasymRightarrow}bool{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Meta-logical predicates.%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ isWff\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isWff\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Error\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ True{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ isForm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isForm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Form\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ isPropForm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isPropForm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ isTerm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isTerm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Term\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ isError\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isError\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Error\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ valid\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
\ \ \ \ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymforall}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ Form\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymforall}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ satifiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
\ \ \ \ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ Form\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ countersatifiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ \ case\ {\isasymphi}\ of\ \isanewline
\ \ \ \ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymexists}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ Form\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymexists}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ invalid\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
\ \ \ \ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymforall}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ Form\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymforall}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}%
\isamarkupsection{Encoding of the language%
}
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ {\isasymA}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt\ {\isasymRightarrow}\ io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymA}\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
\ \ \ \ Form\ {\isasympsi}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasympsi}\ cw{\isacharparenright}\isanewline
\ \ {\isacharbar}\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasympsi}\ cw{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
\begin{isamarkuptext}%
actuality operator; \isa{{\isasymphi}} is evaluated wrt the current world; Error is passed on%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ Enc{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharless}x{\isasymcirc}P{\isachargreater}\ {\isasymequiv}\ case\ {\isacharparenleft}x{\isacharcomma}P{\isacharparenright}\ of\ \isanewline
\ \ \ \ {\isacharparenleft}Term\ y{\isacharcomma}Term\ Q{\isacharparenright}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isacharparenright}\ w{\isacharparenright}\ \ \ \isanewline
\ \ {\isacharbar}\ {\isacharparenleft}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharparenright}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
\begin{isamarkuptext}%
\isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymPi}\isactrlsup {\isadigit{1}}} will be written here as \isa{{\isacharless}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymcirc}{\isasymPi}\isactrlsup {\isadigit{1}}{\isachargreater}}; \isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymPi}\isactrlsup {\isadigit{1}}} is a Form; Error is passed on%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ Exe{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharless}P{\isasymbullet}x{\isachargreater}\ {\isasymequiv}\ case\ {\isacharparenleft}P{\isacharcomma}x{\isacharparenright}\ of\ \isanewline
\ \ \ \ {\isacharparenleft}Term\ Q{\isacharcomma}Term\ y{\isacharparenright}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isacharparenright}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
\begin{isamarkuptext}%
\isa{{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{1}}}  will be written here as \isa{{\isacharless}{\isasymPi}\isactrlsup {\isadigit{2}}{\isasymbullet}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isachargreater}}; \isa{{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{1}}} is a PropForm; Error is passed on%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ Exe{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharless}P{\isasymbullet}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isachargreater}\ {\isasymequiv}\ case\ {\isacharparenleft}P{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharparenright}\ of\ \isanewline
\ \ \ \ {\isacharparenleft}Term\ Q{\isacharcomma}Term\ y{\isadigit{1}}{\isacharcomma}Term\ y{\isadigit{2}}{\isacharparenright}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isadigit{1}}\ y{\isadigit{2}}{\isacharparenright}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
\begin{isamarkuptext}%
\isa{{\isasymPi}\isactrlsup {\isadigit{2}}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{2}}}   will be written here as \isa{{\isacharless}{\isasymPi}\isactrlsup {\isadigit{2}}{\isasymbullet}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{2}}{\isachargreater}}; \isa{{\isasymPi}\isactrlsup {\isadigit{2}}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{2}}} is a PropForm; Error is passed on%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ Exe{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharless}P{\isasymbullet}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isachargreater}\ {\isasymequiv}\ case\ {\isacharparenleft}P{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isacharparenright}\ of\ \isanewline
\ \ \ \ {\isacharparenleft}Term\ Q{\isacharcomma}Term\ y{\isadigit{1}}{\isacharcomma}Term\ y{\isadigit{2}}{\isacharcomma}Term\ y{\isadigit{3}}{\isacharparenright}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isadigit{1}}\ y{\isadigit{2}}\ y{\isadigit{3}}{\isacharparenright}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
\begin{isamarkuptext}%
\isa{{\isasymPi}\isactrlsup {\isadigit{3}}\isactrlsub {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{2}}{\isasymkappa}\isactrlsub {\isadigit{3}}}  will be written here as \isa{{\isacharless}{\isasymPi}\isactrlsup {\isadigit{2}}{\isasymbullet}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{2}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{3}}{\isachargreater}}; \isa{{\isasymPi}\isactrlsup {\isadigit{3}}\isactrlsub {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{2}}{\isasymkappa}\isactrlsub {\isadigit{3}}} is a PropForm; Error is passed on; 
we could, of course, introduce further operators: Exe4, Exe5, etc.%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ z{\isacharunderscore}not{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymnot}\isactrlsup z\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
\ \ \ \ Form\ {\isasympsi}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymnot}\ {\isasympsi}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymnot}\ {\isasympsi}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
\begin{isamarkuptext}%
negation operator; \isa{{\isasymnot}\isactrlsup z\ {\isasymphi}} inherits its type from \isa{{\isasymphi}} if \isa{{\isasymphi}} is Form or PropForm; 
Error is passed on%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ z{\isacharunderscore}implies{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\ {\isasymrightarrow}\isactrlsup z\ {\isasympsi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymphi}{\isacharcomma}{\isasympsi}{\isacharparenright}\ of\ \isanewline
\ \ \ \ {\isacharparenleft}PropForm\ {\isasymalpha}{\isacharcomma}PropForm\ {\isasymbeta}{\isacharparenright}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharparenleft}Form\ {\isasymalpha}{\isacharcomma}Form\ {\isasymbeta}{\isacharparenright}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
\begin{isamarkuptext}%
implication operator; \isa{{\isasymphi}\ {\isasymrightarrow}\isactrlsup z\ {\isasympsi}} returns returns a PropForm if both are PropForms, Form if both are Forms,
otherwise it returns Error%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ z{\isacharunderscore}forall{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymforall}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ dA{\isacharparenright}\ of\isanewline
\ \ \ \ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ Form\ {\isasymphi}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ Form\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
\begin{isamarkuptext}%
universal quantification; \isa{{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} inherits its kind (Form or PropForm) from \isa{{\isasymphi}}; Error is passed on
\isa{{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} is mapped to \isa{{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}x{\isachardot}{\isasymphi}xw{\isacharparenright}} as expected%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ z{\isacharunderscore}box{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymbox}\isactrlsup r\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
\ \ \ \ Form\ {\isasympsi}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}v{\isachardot}\ {\isacharparenleft}r\ w\ v{\isacharparenright}\ {\isasymlongrightarrow}\ {\isasympsi}\ v{\isacharparenright}\isanewline
\ \ {\isacharbar}\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}v{\isachardot}\ {\isacharparenleft}r\ w\ v{\isacharparenright}\ {\isasymlongrightarrow}\ {\isasympsi}\ v{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
\begin{isamarkuptext}%
box operator; \isa{{\isasymbox}\isactrlsup r\ {\isasymphi}} inherits its type (Form or PropForm) from \isa{{\isasymphi}}; Error is passed on%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ lam{\isadigit{0}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlambda}\isactrlsup {\isadigit{0}}\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
\ \ \ \ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ PropForm\ {\isasympsi}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
\begin{isamarkuptext}%
0-arity lambda abstraction; \isa{{\isasymlambda}\isactrlsup {\isadigit{0}}\ {\isasymphi}} returns PropForm \isa{{\isasymphi}} if \isa{{\isasymphi}} is a PropForm, otherwise Error%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ lam{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlambda}\isactrlsup {\isadigit{1}}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ dE{\isacharparenright}\ of\isanewline
\ \ \ \ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ Term\ {\isacharparenleft}{\isasymlambda}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ {\isasymphi}{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ {\isacharparenleft}{\isasymlambda}x{\isachardot}\ dIO{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
1-arity lambda abstraction; \isa{{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} returns Term \isa{{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} if \isa{{\isasymphi}} is a PropForm, 
otherwise Error%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ lam{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlambda}\isactrlsup {\isadigit{2}}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ dE\ dE{\isacharparenright}\ of\isanewline
\ \ \ \ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ Term\ {\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x\ y{\isacharparenright}\ of\ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ {\isasymphi}{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ {\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ dIO{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
2-arity lambda abstraction; \isa{{\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}} returns Term \isa{{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}} if \isa{{\isasymphi}} is a PropForm, 
otherwise Error%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ lam{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlambda}\isactrlsup {\isadigit{3}}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ dE\ dE\ dE{\isacharparenright}\ of\isanewline
\ \ \ \ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ Term\ {\isacharparenleft}{\isasymlambda}x\ y\ z{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x\ y\ z{\isacharparenright}\ of\ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ {\isasymphi}{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ {\isacharparenleft}{\isasymlambda}x\ y\ z{\isachardot}\ dIO{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
3-arity lambda abstraction; \isa{{\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}xyz{\isachardot}{\isasymphi}{\isacharparenright}} returns Term \isa{{\isacharparenleft}{\isasymlambda}xyz{\isachardot}{\isasymphi}{\isacharparenright}} if \isa{{\isasymphi}} is a PropForm, 
otherwise Error; we could, of course, introduce further operators: \isa{{\isasymlambda}\isactrlsup {\isadigit{4}}}, \isa{{\isasymlambda}\isactrlsup {\isadigit{5}}}, etc.%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ that{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}e\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymepsilon}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ dE{\isacharparenright}\ of\isanewline
\ \ \ \ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ Term\ {\isacharparenleft}THE\ x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ cw{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dE{\isachardoublequoteclose}%
\begin{isamarkuptext}%
that operator; that \isa{{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} returns Term \isa{{\isacharparenleft}THE\ x{\isachardot}\ {\isasymphi}\ x\ cw{\isacharparenright}}, that is the inbuilt THE 
operator is used and evaluation is wrt to the current world cw; moreover, application of that 
is allowed if \isa{{\isacharparenleft}{\isasymPhi}\ sRE{\isacharparenright}} is a PropForm, otherwise Error is passed on for some someRawEntity%
\end{isamarkuptext}%
\isamarkuptrue%
%
\isamarkupsection{Further logical connectives%
}
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ z{\isacharunderscore}and{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\ {\isasymand}\isactrlsup z\ {\isasympsi}\ {\isasymequiv}\ {\isasymnot}\isactrlsup z{\isacharparenleft}{\isasymphi}\ {\isasymrightarrow}\isactrlsup z\ {\isasymnot}\isactrlsup z{\isasympsi}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ z{\isacharunderscore}or{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\ {\isasymor}\isactrlsup z\ {\isasympsi}\ {\isasymequiv}\ {\isacharparenleft}{\isasymnot}\isactrlsup z{\isasymphi}\ {\isasymrightarrow}\isactrlsup z\ {\isasympsi}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ z{\isacharunderscore}equiv{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\ {\isasymequiv}\isactrlsup z\ {\isasympsi}\ {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\ {\isasymrightarrow}\isactrlsup z\ {\isasympsi}{\isacharparenright}\ {\isasymand}\isactrlsup z\ {\isacharparenleft}{\isasympsi}\ {\isasymrightarrow}\isactrlsup z\ {\isasymphi}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ z{\isacharunderscore}exists{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymexists}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ dA{\isacharparenright}\ of\isanewline
\ \ \ \ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymexists}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ Form\ {\isasymphi}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymexists}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ Form\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\isanewline
\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ z{\isacharunderscore}dia{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymdiamond}\isactrlsup r\ {\isasymphi}\ {\isasymequiv}\ {\isasymnot}\isactrlsup z\ {\isasymbox}\isactrlsup r\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isasymphi}{\isacharparenright}{\isachardoublequoteclose}%
\isamarkupsection{Some shorthands for the constructors%
}
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ mkPropForm\ {\isacharcolon}{\isacharcolon}\ \ {\isachardoublequoteopen}io{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharcomma}p{\isacharcomma}\ {\isasymequiv}\ PropForm\ p{\isachardoublequoteclose}\ \isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ mkForm\ {\isacharcolon}{\isacharcolon}\ \ {\isachardoublequoteopen}io{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharsemicolon}p{\isacharsemicolon}\ {\isasymequiv}\ Form\ p{\isachardoublequoteclose}\ \isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ mkTerm\ {\isacharcolon}{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isachardot}t{\isachardot}\ {\isasymequiv}\ Term\ t{\isachardoublequoteclose}%
\isamarkupsection{Some basic tests%
}
\isamarkuptrue%
%
\begin{isamarkuptext}%
An example signature; entities and relations%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{consts}\isamarkupfalse%
\ a{\isacharunderscore}{\isadigit{0}}\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}e{\isachardoublequoteclose}\ \isacommand{abbreviation}\isamarkupfalse%
\ a\ \ \isakeyword{where}\ {\isachardoublequoteopen}a\ {\isasymequiv}\ {\isachardot}a{\isacharunderscore}{\isadigit{0}}{\isachardot}{\isachardoublequoteclose}\isanewline
\isacommand{consts}\isamarkupfalse%
\ b{\isacharunderscore}{\isadigit{0}}\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}e{\isachardoublequoteclose}\ \isacommand{abbreviation}\isamarkupfalse%
\ b\ \ \isakeyword{where}\ {\isachardoublequoteopen}b\ {\isasymequiv}\ {\isachardot}b{\isacharunderscore}{\isadigit{0}}{\isachardot}{\isachardoublequoteclose}\isanewline
\isacommand{consts}\isamarkupfalse%
\ c{\isacharunderscore}{\isadigit{0}}\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}e{\isachardoublequoteclose}\ \isacommand{abbreviation}\isamarkupfalse%
\ c\ \ \isakeyword{where}\ {\isachardoublequoteopen}c\ {\isasymequiv}\ {\isachardot}c{\isacharunderscore}{\isadigit{0}}{\isachardot}{\isachardoublequoteclose}\isanewline
\isanewline
\isacommand{consts}\isamarkupfalse%
\ R{\isacharunderscore}{\isadigit{0}}\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io{\isachardoublequoteclose}\ \ \isacommand{abbreviation}\isamarkupfalse%
\ R{\isadigit{0}}\ \ \isakeyword{where}\ {\isachardoublequoteopen}R{\isadigit{0}}\ {\isasymequiv}\ {\isachardot}R{\isacharunderscore}{\isadigit{0}}{\isachardot}{\isachardoublequoteclose}\isanewline
\isacommand{consts}\isamarkupfalse%
\ R{\isacharunderscore}{\isadigit{1}}\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}e{\isasymRightarrow}io{\isachardoublequoteclose}\ \isacommand{abbreviation}\isamarkupfalse%
\ R{\isadigit{1}}\ \ \isakeyword{where}\ {\isachardoublequoteopen}R{\isadigit{1}}\ {\isasymequiv}\ {\isachardot}R{\isacharunderscore}{\isadigit{1}}{\isachardot}{\isachardoublequoteclose}\isanewline
\isacommand{consts}\isamarkupfalse%
\ R{\isacharunderscore}{\isadigit{2}}\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}e{\isasymRightarrow}e{\isasymRightarrow}io{\isachardoublequoteclose}\ \isacommand{abbreviation}\isamarkupfalse%
\ R{\isadigit{2}}\ \ \isakeyword{where}\ {\isachardoublequoteopen}R{\isadigit{2}}\ {\isasymequiv}\ {\isachardot}R{\isacharunderscore}{\isadigit{2}}{\isachardot}{\isachardoublequoteclose}\isanewline
\isacommand{consts}\isamarkupfalse%
\ R{\isacharunderscore}{\isadigit{3}}\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isachardoublequoteclose}\ \ \isacommand{abbreviation}\isamarkupfalse%
\ R{\isadigit{3}}\ \ \isakeyword{where}\ {\isachardoublequoteopen}R{\isadigit{3}}\ {\isasymequiv}\ {\isachardot}R{\isacharunderscore}{\isadigit{3}}{\isachardot}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Testing some term and formula constructions%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharless}R{\isadigit{1}}{\isasymbullet}a{\isachargreater}{\isacharbrackright}{\isachardoublequoteclose}\ \isacommand{nitpick}\isamarkupfalse%
%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}isPropForm\ {\isacharless}R{\isadigit{1}}{\isasymbullet}a{\isachargreater}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharless}R{\isadigit{1}}{\isasymbullet}a{\isachargreater}\ {\isacharequal}\ X{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharless}a{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharbrackright}{\isachardoublequoteclose}\ \isacommand{nitpick}\isamarkupfalse%
%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}isPropForm\ {\isacharless}a{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}isForm\ {\isacharless}a{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharless}a{\isasymcirc}R{\isadigit{1}}{\isachargreater}\ {\isacharequal}\ X{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharless}{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isasymbullet}a{\isachargreater}{\isacharbrackright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharless}{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isasymbullet}a{\isachargreater}\ {\isacharequal}\ X{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isasymnot}\ isWff\ {\isacharparenleft}{\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharless}{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}{\isasymbullet}a{\isachargreater}{\isacharbrackright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharless}{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}{\isasymbullet}a{\isachargreater}\ {\isacharequal}\ X{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}{\isachardot}R{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}R{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isacharless}{\isachardot}R{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}{\isachardot}R{\isachardot}{\isachargreater}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isasymforall}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isacharless}{\isachardot}R{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}{\isachardot}R{\isachardot}{\isachargreater}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isamarkupsection{Get the priorities right%
}
\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymchi}{\isacharcomma}\ {\isasymequiv}\ {\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymchi}{\isacharcomma}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymchi}{\isacharcomma}\ {\isasymequiv}\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharparenleft}{\isacharcomma}{\isasympsi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymchi}{\isacharcomma}{\isacharparenright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\ \isacommand{nitpick}\isamarkupfalse%
%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}\ {\isasymequiv}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}\ {\isasymequiv}\isactrlsup z\ {\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}\ {\isasymequiv}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharparenleft}{\isacharcomma}{\isasympsi}{\isacharcomma}\ {\isasymequiv}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\ \isacommand{nitpick}\isamarkupfalse%
%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isamarkupsection{E!, O!, A! and =E%
}
\isamarkuptrue%
\isacommand{consts}\isamarkupfalse%
\ E{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Distinguished 1-place Relation Constant: E! (read: ‘being concrete’ or ‘concreteness’)%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ z{\isacharunderscore}ordinary{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}O\isactrlsup {\isacharbang}\ {\isasymequiv}\ {\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymdiamond}\isactrlsup r\ {\isacharless}{\isachardot}E{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Being ordinary is being possibly concrete.%
\end{isamarkuptext}%
\isamarkuptrue%
%
\begin{isamarkuptext}%
Question: is the term above a Form or a PropForm?%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ z{\isacharunderscore}abstract{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}A\isactrlsup {\isacharbang}\ {\isasymequiv}\ {\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymnot}\isactrlsup z\ {\isasymdiamond}\isactrlsup r\ {\isacharless}{\isachardot}E{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Being abstract is not possibly being concrete.%
\end{isamarkuptext}%
\isamarkuptrue%
%
\begin{isamarkuptext}%
Question: is the term above a Form or a PropForm?%
\end{isamarkuptext}%
\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ z{\isacharunderscore}identity{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharequal}\isactrlsub e\isactrlsup z\ {\isasymequiv}\ \isanewline
\ \ {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isacharless}O\isactrlsup {\isacharbang}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymand}\isactrlsup z\ {\isacharless}O\isactrlsup {\isacharbang}{\isasymbullet}{\isachardot}y{\isachardot}{\isachargreater}{\isacharparenright}\ {\isasymand}\isactrlsup z\ {\isasymbox}\isactrlsup r\ {\isacharparenleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharless}{\isachardot}F{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymequiv}\isactrlsup z\ {\isacharless}{\isachardot}F{\isachardot}{\isasymbullet}{\isachardot}y{\isachardot}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ z{\isacharunderscore}identityE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isacharparenright}{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}x\ {\isacharequal}\isactrlsub E\ y\ {\isasymequiv}\ {\isacharparenleft}Exe{\isadigit{2}}\ {\isacharequal}\isactrlsub e\isactrlsup z\ x\ y{\isacharparenright}{\isachardoublequoteclose}%
\isamarkupsection{Some further examples%
}
\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymexists}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isacharparenleft}{\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}{\isachardot}R{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
\ auto%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymforall}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isacharparenleft}{\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}{\isachardot}R{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\ \isacommand{nitpick}\isamarkupfalse%
%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}a\ {\isacharequal}\isactrlsub E\ a{\isacharbrackright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\ \isacommand{nitpick}\isamarkupfalse%
%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharless}O\isactrlsup {\isacharbang}{\isasymbullet}a{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ a\ {\isacharequal}\isactrlsub E\ a{\isacharbrackright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharless}{\isachardot}F{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymequiv}\isactrlsup z\ {\isacharless}{\isachardot}F{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharless}O\isactrlsup {\isacharbang}{\isasymbullet}a{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isachardot}x{\isachardot}\ {\isacharequal}\isactrlsub E\ a{\isacharparenright}{\isasymbullet}a{\isachargreater}{\isacharbrackright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymexists}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharless}a{\isasymcirc}{\isachardot}F{\isachardot}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
\ auto%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}isWff\ {\isacharcomma}{\isacharparenleft}{\isasymlambda}w{\isachardot}\ True{\isacharparenright}{\isacharcomma}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymexists}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharcomma}F{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
\ auto%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymexists}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharsemicolon}F{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{apply}\isamarkupfalse%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
\ auto\isanewline
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
\end{isabellebody}%
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "root"
%%% End:

### 2015-10-27 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
Suggestions by Ed Zalta inserted

@@
 \begin{isamarkuptext}%
-This work significantly adapts and extends the embedding presented in \cite{J23}; say more ...%
+This work is related to \cite{J23}, which is significantly extends ...%
 \end{isamarkuptext}%
@@
 \isanewline
-\isanewline
 \isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
@@
 %
-\isamarkupcmt{modal logic formulas (or propositional formulas) are essentially of this type: predicates on%
-}
-\isanewline
-%
-\isamarkupcmt{worlds%
-}
-\isanewline
+\isamarkupcmt{formulas are essentially of this type%
+}
+\isanewline
+%
+\isamarkupcmt{predicates on worlds%
+}
 \isanewline
@@
 \isanewline
-\isanewline
 \isacommand{datatype}\isamarkupfalse%
@@
 %
-\isamarkupcmt{some fixed current world%
-}
-\isanewline
+\isamarkupcmt{the distinguished actual world%
+}
 \isanewline
@@
 %
-\isamarkupcmt{some fixed dummy symbols; we anyway assume that the domains are on-empty%
+\isamarkupcmt{some fixed dummy symbols; we anyway assume that the domains are non-empty%
 }
@@
 \begin{isamarkuptext}%
-We consider an arbitrary but fixed accessibility relation r%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{consts}\isamarkupfalse%
-\ r\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharparenleft}i{\isasymRightarrow}i{\isasymRightarrow}bool{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
 Meta-logical predicates.%
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ isWff\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isWff\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Error\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ True{\isachardoublequoteclose}\isanewline
+\ isWff\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isWff\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Error\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}\ Term\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}{\isacharunderscore}\ {\isasymRightarrow}\ True{\isachardoublequoteclose}\isanewline
 \isacommand{abbreviation}\isamarkupfalse%
@@
 \ z{\isacharunderscore}box{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymbox}\isactrlsup r\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
-\ \ \ \ Form\ {\isasympsi}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}v{\isachardot}\ {\isacharparenleft}r\ w\ v{\isacharparenright}\ {\isasymlongrightarrow}\ {\isasympsi}\ v{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}v{\isachardot}\ {\isacharparenleft}r\ w\ v{\isacharparenright}\ {\isasymlongrightarrow}\ {\isasympsi}\ v{\isacharparenright}\isanewline
+\ \ \ \ Form\ {\isasympsi}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}v{\isachardot}\ {\isasympsi}\ v{\isacharparenright}\isanewline
+\ \ {\isacharbar}\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}v{\isachardot}\ {\isasympsi}\ v{\isacharparenright}\isanewline
 \ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
 \begin{isamarkuptext}%
-box operator; \isa{{\isasymbox}\isactrlsup r\ {\isasymphi}} inherits its type (Form or PropForm) from \isa{{\isasymphi}}; Error is passed on%
+box operator; \isa{{\isasymbox}\ {\isasymphi}} inherits its type (Form or PropForm) from \isa{{\isasymphi}}; Error is passed on.
+Note that the \isa{{\isasymbox}}-operator is defined here without an accessibility relation; this is ok since we assume logic S5.%
 \end{isamarkuptext}%
@@
 \ z{\isacharunderscore}dia{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymdiamond}\isactrlsup r\ {\isasymphi}\ {\isasymequiv}\ {\isasymnot}\isactrlsup z\ {\isasymbox}\isactrlsup r\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isasymphi}{\isacharparenright}{\isachardoublequoteclose}%
-\isamarkupsection{Some shorthands for the constructors%
+\isamarkupsection{Some shortcuts for the constructors%
 }
@@
 \begin{isamarkuptext}%
-An example signature; entities and relations%
+Example signature; entities and relations%
 \end{isamarkuptext}%
@@
 \begin{isamarkuptext}%
-Testing some term and formula constructions%
+Testing term and formula constructions%
 \end{isamarkuptext}%
@@
 %
-\isamarkupsection{Get the priorities right%
+\isamarkupsection{Are the priorities set correctly?%
 }
@@
 \begin{isamarkuptext}%
-Distinguished 1-place Relation Constant: E! (read: ‘being concrete’ or ‘concreteness’)%
+Distinguished 1-place relation constant: E! (read: ‘being concrete’ or ‘concreteness’)%
 \end{isamarkuptext}%
@@
 \isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Question: is the term above a Form or a PropForm?%
-\end{isamarkuptext}%
-\isamarkuptrue%
 \isacommand{abbreviation}\isamarkupfalse%
@@
 Being abstract is not possibly being concrete.%
-\end{isamarkuptext}%
-\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Question: is the term above a Form or a PropForm?%
 \end{isamarkuptext}%
@@
 \ z{\isacharunderscore}identityE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isacharparenright}{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}x\ {\isacharequal}\isactrlsub E\ y\ {\isasymequiv}\ {\isacharparenleft}Exe{\isadigit{2}}\ {\isacharequal}\isactrlsub e\isactrlsup z\ x\ y{\isacharparenright}{\isachardoublequoteclose}%
-\isamarkupsection{Some further examples%
+\isamarkupsection{Further test examples%
 }

### 2015-11-03 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
some further tests

@@
 \isacommand{consts}\isamarkupfalse%
-\ dE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isachardoublequoteclose}\ dIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isachardoublequoteclose}\ dEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dEEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isacharequal}{\isachargreater}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dEEEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isacharequal}{\isachargreater}e{\isacharequal}{\isachargreater}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dA{\isacharcolon}{\isacharcolon}{\isacharprime}a\isanewline
+\ dE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isachardoublequoteclose}\ dIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isachardoublequoteclose}\ dEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dEEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isasymRightarrow}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dEEEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dA{\isacharcolon}{\isacharcolon}{\isacharprime}a\isanewline
 %
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ satifiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+\ satisfiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
 \ \ \ \ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}box{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymbox}\isactrlsup r\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+\ z{\isacharunderscore}box{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymbox}\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
 \ \ \ \ Form\ {\isasympsi}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}v{\isachardot}\ {\isasympsi}\ v{\isacharparenright}\isanewline
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}dia{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymdiamond}\isactrlsup r\ {\isasymphi}\ {\isasymequiv}\ {\isasymnot}\isactrlsup z\ {\isasymbox}\isactrlsup r\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isasymphi}{\isacharparenright}{\isachardoublequoteclose}%
+\ z{\isacharunderscore}dia{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymdiamond}\ {\isasymphi}\ {\isasymequiv}\ {\isasymnot}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isasymphi}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
 \isamarkupsection{Some shortcuts for the constructors%
@@
 \isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Verifying Modal Logic Principles%
+\end{isamarkuptext}%
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Necessitation holds%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ necessitation{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isasymforall}{\isasymphi}{\isachardot}\ {\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}\ {\isasymlongrightarrow}\ {\isacharbrackleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ necessitation{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isasymforall}{\isasymphi}{\isachardot}\ {\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}\ {\isasymlongrightarrow}\ {\isacharbrackleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Modal Collapse does not hold%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ modalCollapse{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isasymforall}{\isasymphi}{\isachardot}\ {\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ modalCollapse{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isasymforall}{\isasymphi}{\isachardot}\ {\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Verifying S5 Principles%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}M{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}M{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}B{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}B{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}D{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}D{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}A{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}A{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}B{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}B{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}C{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ metis%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}C{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ metis%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}D{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}D{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
 %
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}ordinary{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}O\isactrlsup {\isacharbang}\ {\isasymequiv}\ {\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymdiamond}\isactrlsup r\ {\isacharless}{\isachardot}E{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isachardoublequoteclose}%
+\ z{\isacharunderscore}ordinary{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}O\isactrlsup {\isacharbang}\ {\isasymequiv}\ {\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymdiamond}\ {\isacharless}{\isachardot}E{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isachardoublequoteclose}%
 \begin{isamarkuptext}%
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}abstract{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}A\isactrlsup {\isacharbang}\ {\isasymequiv}\ {\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymnot}\isactrlsup z\ {\isasymdiamond}\isactrlsup r\ {\isacharless}{\isachardot}E{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isachardoublequoteclose}%
+\ z{\isacharunderscore}abstract{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}A\isactrlsup {\isacharbang}\ {\isasymequiv}\ {\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymnot}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharless}{\isachardot}E{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
 \begin{isamarkuptext}%
@@
 \ z{\isacharunderscore}identity{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharequal}\isactrlsub e\isactrlsup z\ {\isasymequiv}\ \isanewline
-\ \ {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isacharless}O\isactrlsup {\isacharbang}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymand}\isactrlsup z\ {\isacharless}O\isactrlsup {\isacharbang}{\isasymbullet}{\isachardot}y{\isachardot}{\isachargreater}{\isacharparenright}\ {\isasymand}\isactrlsup z\ {\isasymbox}\isactrlsup r\ {\isacharparenleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharless}{\isachardot}F{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymequiv}\isactrlsup z\ {\isacharless}{\isachardot}F{\isachardot}{\isasymbullet}{\isachardot}y{\isachardot}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isacharless}O\isactrlsup {\isacharbang}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymand}\isactrlsup z\ {\isacharless}O\isactrlsup {\isacharbang}{\isasymbullet}{\isachardot}y{\isachardot}{\isachargreater}{\isacharparenright}\ {\isasymand}\isactrlsup z\ {\isasymbox}\ {\isacharparenleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharless}{\isachardot}F{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymequiv}\isactrlsup z\ {\isacharless}{\isachardot}F{\isachardot}{\isasymbullet}{\isachardot}y{\isachardot}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
 \isanewline

### 2015-11-03 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
further additions

--- 2015-10-27 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ isWff\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isWff\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Error\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}\ Term\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}{\isacharunderscore}\ {\isasymRightarrow}\ True{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ isForm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isForm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Form\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ isPropForm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isPropForm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ isTerm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isTerm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Term\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ isError\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isError\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Error\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
+\ isWff\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isWff\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Error\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}\ Term\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}{\isacharunderscore}\ {\isasymRightarrow}\ True{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ isForm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isForm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Form\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ isPropForm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isPropForm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ isTerm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isTerm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Term\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ isError\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isError\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Error\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
 \isacommand{abbreviation}\isamarkupfalse%
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ countersatifiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ \ case\ {\isasymphi}\ of\ \isanewline
+\ countersatisfiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ \ case\ {\isasymphi}\ of\ \isanewline
 \ \ \ \ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymexists}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ mkTerm\ {\isacharcolon}{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isachardot}t{\isachardot}\ {\isasymequiv}\ Term\ t{\isachardoublequoteclose}%
-\isamarkupsection{Some basic tests%
-}
-\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Example signature; entities and relations%
-\end{isamarkuptext}%
+\ mkTerm\ {\isacharcolon}{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isachardot}t{\isachardot}\ {\isasymequiv}\ Term\ t{\isachardoublequoteclose}\ \isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ mkError\ {\isacharcolon}{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharasterisk}t{\isacharasterisk}\ {\isasymequiv}\ Term\ t{\isachardoublequoteclose}%
+\isamarkupsection{Some Basic Tests%
+}
+\isamarkuptrue%
+%
+\isamarkupsubsection{Meta-Logic%
+}
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymforall}{\isasymphi}{\isachardot}\ {\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isacharparenright}\ {\isasymlongleftrightarrow}\ {\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymforall}{\isasymphi}{\isachardot}\ {\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isacharparenright}\ {\isasymlongleftrightarrow}\ {\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsubsection{Verifying Modal Logic Principles%
+}
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Necessitation holds%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ necessitation{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}\ {\isasymlongrightarrow}\ {\isacharbrackleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ necessitation{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}\ {\isasymlongrightarrow}\ {\isacharbrackleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Modal Collapse does not hold%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ modalCollapse{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ modalCollapse{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsubsection{S5 Principles%
+}
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}T{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}T{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}B{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}B{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}D{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}D{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}A{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}A{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}B{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}B{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}C{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}C{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}D{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}D{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsubsection{Validity, Satisfiabilty, Countersatisfiability and Invalidity%
+}
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}\ {\isasymlongleftrightarrow}\ {\isasymnot}\ {\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymlongleftrightarrow}\ {\isasymnot}\ {\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}\ {\isasymlongleftrightarrow}\ {\isasymnot}\ {\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymlongleftrightarrow}\ {\isasymnot}\ {\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+For Terms and Error objects these correspondences do not apply%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isachardot}{\isasymphi}{\isachardot}{\isacharbrackright}\ {\isasymlongleftrightarrow}\ {\isasymnot}\ {\isacharbrackleft}{\isachardot}{\isasymphi}{\isachardot}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t{\isachardoublequoteclose}\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isachardot}{\isasymphi}{\isachardot}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymlongleftrightarrow}\ {\isasymnot}\ {\isacharbrackleft}{\isachardot}{\isasymphi}{\isachardot}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v{\isachardoublequoteclose}\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharasterisk}{\isasymphi}{\isacharasterisk}{\isacharbrackright}\ {\isasymlongleftrightarrow}\ {\isasymnot}\ {\isacharbrackleft}{\isacharasterisk}{\isasymphi}{\isacharasterisk}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t{\isachardoublequoteclose}\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharasterisk}{\isasymphi}{\isacharasterisk}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymlongleftrightarrow}\ {\isasymnot}\ {\isacharbrackleft}{\isacharasterisk}{\isasymphi}{\isacharasterisk}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v{\isachardoublequoteclose}\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsubsection{Example signature; entities and relations%
+}
 \isamarkuptrue%
@@
 \isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
 %
@@
 \isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
 %
@@
 \isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}%
+\ simp%
 \endisatagproof
@@
 \isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ simp\ \isacommand{by}\isamarkupfalse%
 \ auto%
@@
 \isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymexists}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharcomma}F{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymexists}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{by}\isamarkupfalse%
 \ auto%
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymexists}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharsemicolon}F{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
-\ auto\isanewline
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymexists}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsection{Axioms%
+}
+\isamarkuptrue%
+%
+\isamarkupsubsection{Axioms for Negations and Conditionals%
+}
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isacharcomma}{\isasympsi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymchi}{\isacharcomma}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymchi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isacharsemicolon}{\isasympsi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasymchi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isacharparenleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasympsi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasymchi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isasymnot}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isasymnot}\isactrlsup z\ {\isacharsemicolon}{\isasympsi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasympsi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsubsection{Axioms of Identity%
+}
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+todo%
+\end{isamarkuptext}%
+\isamarkuptrue%
+%
+\isamarkupsubsection{Axioms of Quantification%
+}
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+todo%
+\end{isamarkuptext}%
+\isamarkuptrue%
+%
+\isamarkupsubsection{Axioms of Actuality%
+}
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymequiv}\isactrlsup z\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharparenleft}{\isasymA}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymequiv}\isactrlsup z\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharparenleft}{\isasymA}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}\ {\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}\ {\isasymequiv}\isactrlsup z\ {\isacharparenleft}{\isasymA}\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isasymA}\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}\ {\isacharparenleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasympsi}{\isacharsemicolon}{\isacharparenright}\ {\isasymequiv}\isactrlsup z\ {\isacharparenleft}{\isasymA}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isasymA}\ {\isacharsemicolon}{\isasympsi}{\isacharsemicolon}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymA}\ {\isacharparenleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}\ {\isasymequiv}\isactrlsup z\ {\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymA}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymA}\ {\isacharparenleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}\ {\isasymequiv}\isactrlsup z\ {\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymA}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymequiv}\isactrlsup z\ {\isasymA}\ {\isacharparenleft}{\isasymA}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymequiv}\isactrlsup z\ {\isasymA}\ {\isacharparenleft}{\isasymA}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsubsection{Axioms of Necessity%
+}
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \ \ \ \ \isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharparenleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \ \ \ \ \isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharparenleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \ \ \ \ \ \ \ \ \isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharparenleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+The following needs to be an axiom; it does not follow for free: it is possible that there 
+are contingently concrete individuals and it is possible that there are not:%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{axiomatization}\isamarkupfalse%
+\ \isakeyword{where}\isanewline
+\ \ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymexists}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}{\isachardot}E{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymand}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharless}{\isachardot}E{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ {\isasymand}\isactrlsup z\ {\isasymdiamond}\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharparenleft}{\isasymexists}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}{\isachardot}E{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymand}\isactrlsup z\ {\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharless}{\isachardot}E{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isamarkupsubsection{Axioms of Necessity and Actuality%
+}
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharparenleft}{\isasymA}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharparenleft}{\isasymA}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymequiv}\isactrlsup z\ {\isacharparenleft}{\isasymA}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymequiv}\isactrlsup z\ {\isacharparenleft}{\isasymA}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+\isanewline
+\isanewline
+\isanewline
 %

### 2015-12-10 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
latest syntax improvements: binder notation and various improvements

--- 2015-10-27 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
@@
 \begin{isamarkuptext}%
-This work is related to \cite{J23}, which is significantly extends ...%
+We present a formalisation and partial automation of an initial part of the (third authors)
+ Principia Metaphysica \cite{zalta:_princ_metap} in Isabelle/HOL \cite{Isabelle}.
+
+ The Principia Metaphysica, which is based on and extends the Theory of Abstract 
+ Objects \cite{zalta83:_abstr_objec}, 
+ employs a modal relational type theory as logical foundation. Arguments
+ defending this choice against a modal functional type theory 
+ have been presented before \cite{zalta11:_relat_versus_funct_found_logic}.
+ In a nutshell, the situation is this: functional type theory comes with strong 
+ comprehension principles, which, in the context of the Theory of Abstract Objects, 
+ have paradoxical implications. When starting off with a relational foundation, however, 
+ weaker comprehension principles are provided, and these obstacles can be avoided.
+
+ Isabelle/HOL is a proof assistant based on a functional type theory, 
+ more precisely, Church's theory of types \cite{Church40}. Recently, it has been shown 
+ that Church's type theory can be elegantly utilized as a meta-logic to encode and 
+ automate various quantified non-classical logics, including modal functional type 
+ theory \cite{J23,C40}. This work has subsequently been employed in a case study in
+ computational metaphysics, in which different variants of Kurt Gödel's ontological 
+ argument \cite{ECAI} were verified (respectively, falsified).
+
+ The motivating research questions for the work presented below include:
+ \begin{itemize} 
+ \item Can functional type theory, despite the problems as pointed by Zalta and Oppenheimer, 
+  be utilized to encode the Theory of Abstract Objects when following the embeddings approach?
+ \item How elegant and user-friendly is the resulting formalization? In other
+  words, to what extend can Isabelle's  user interface be facilitated to hide 
+  unpleasant technicalities of the (extended) embedding from the user?
+ \item How far can automation be pushed in the approach? How much user interaction can
+  be avoided in the formalization of the (first part) of the Principia Metaphysica? 
+ \item Can the consistency of the theory be validated with the available automated 
+  reasoning tools?
+ \item Can the reasoners eventually even contribute some new knowledge? 
+ \ldots
+ \end{itemize}%
+\end{isamarkuptext}%
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+The encoding of modal functional type theory in functional type theory as explored in 
+ previous work \cite{J23,C40} is simple: modal logic formulas are identified with certain functional 
+ type theory formulas of predicate type \isa{io}. Possible worlds are explicitly represented by 
+ terms of type  \isa{i}. A modal logic \isa{{\isasymphi}} formula holds for a world \isa{w} if and 
+ only if the application \isa{{\isasymphi}\ w} evaluates to true. The definition of the propositional modal logic 
+ connectives is then straightforward and it simply realizes the standard translation as a set of equations 
+ in functional type theory. The approach has been successfully extended for quantifiers. A crucial 
+ aspect thereby is that in simple type theory quantifiers can be treated
+ as ordinary logical connectives. No extra binding mechanism is needed since the already existing 
+ lambda binding mechanism can be elegantly utilized.
+
+ The challenge in this work is to appropriately 'restrict' this embedding for modal relational type theory.
+  \begin{figure}[t]
+ \includegraphics[height=5.5cm]{ModalRelationalTypeTheory.png}\includegraphics[height=4.5cm]{ModalRelationalTypeTheory2.png}
+ \caption{Grammar of Modal Relational Type Theory. \label{mmrt}
+ Note that two kinds of (complex) formulas are introduced: ones that may have encoding subformulas and ones that don’t.
+ The latter are designated as propositional formulas, the former ones simply as formulas. }
+ \end{figure}
+
+ To achieve this  we provide means to explicitly represents and maintain information and constraints on the 
+ syntactical structure of modal relational type theory, in particular, we provide means to distinguish 
+ between propositional formulas, formulas, terms and erreneous (disallowed) formations. 
+ This clearly creates some technical overhead. However, we exploit facilities in Isabelle/HOL's user 
+ interface, and other means, to hide most of these technicalities from the user in applications.%
 \end{isamarkuptext}%
@@
 }
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+We start out with some type declarations and type abbreviations. 
+ Our formalism explicitly encodes Kripke style semantics. Hence, we introduce a 
+ distinguished type \isa{i} to represent the set of possible worlds. 
+ Consequently, terms of this type denote possible worlds. 
+ Moreover, modal logic formulas are associated in our approach with
+ predicates (resp. sets) on possible worlds. Hence, modal logic formulas have
+ type \isa{{\isacharparenleft}i\ {\isasymRightarrow}\ bool{\isacharparenright}}. To make our representation in the remainder more concise
+ we abbreviate this type as \isa{io}.%
+\end{isamarkuptext}%
 \isamarkuptrue%
@@
 \ i\isanewline
-%
-\isamarkupcmt{the type possible worlds; the formalism explicitly encodes Kripke style semantics%
-}
-\isanewline
 \isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
-\ io\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}i\ {\isasymRightarrow}\ bool{\isacharparenright}{\isachardoublequoteclose}\ \isanewline
-%
-\isamarkupcmt{formulas are essentially of this type%
-}
-\isanewline
-%
-\isamarkupcmt{predicates on worlds%
-}
-\isanewline
+\ io\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}i\ {\isasymRightarrow}\ bool{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+Entities in the abstract theory of types are represented in our formalism by the
+ type \isa{e}. We call this the raw type of entities resp. objects. Later 
+ on we will introduce means to distinguish between abstract and ordinary entities.%
+\end{isamarkuptext}%
+\isamarkuptrue%
 \isacommand{typedecl}\isamarkupfalse%
-\ e\isanewline
-%
-\isamarkupcmt{the raw type of entities/objects (abstract or ordinary)%
-}
-\isanewline
+\ e%
+\begin{isamarkuptext}%
+To explicitly model the syntactical restrictions of modal relational type theory we introduce a 
+ datatype \isa{{\isacharprime}a\ opt} based on four constructors:
+ \isa{ERR\ {\isacharprime}a} (identifies erroneous term constructions), \isa{P\ {\isacharprime}a} (identifies 
+ propositional formulas), \isa{F\ {\isacharprime}a} (identifies  formulas), and \isa{T\ {\isacharprime}a} (identifies 
+ terms, such as lambda abstractions). The embeddings approach will be suitably adapted below so that 
+ for each language expression (in the embedded modal relational type theory) the respective datatype 
+ is identified and appropriately propagated. The encapsulated expressions (the polymorphic type \isa{{\isacharprime}a} 
+ will be instantiated below) realize the actual modeling of the logic embedding analogous 
+ to previous work for modal functional type theory.%
+\end{isamarkuptext}%
+\isamarkuptrue%
 \isacommand{datatype}\isamarkupfalse%
-\ {\isacharprime}a\ opt\ {\isacharequal}\ Error\ {\isacharprime}a\ {\isacharbar}\ Term\ {\isacharprime}a\ {\isacharbar}\ Form\ {\isacharprime}a\ {\isacharbar}\ PropForm\ {\isacharprime}a\isanewline
-\isanewline
-\isanewline
+\ {\isacharprime}a\ opt\ {\isacharequal}\ ERR\ {\isacharprime}a\ {\isacharbar}\ P\ {\isacharprime}a\ {\isacharbar}\ F\ {\isacharprime}a\ {\isacharbar}\ T\ {\isacharprime}a%
+\begin{isamarkuptext}%
+The following operators support a concise and elegant superscript annotation with these
+ four syntactical categories for our language constructs.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ mkP{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup P{\isachardoublequoteclose}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup P\ {\isasymequiv}\ P\ {\isasymphi}{\isachardoublequoteclose}\ \isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ mkF{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup F{\isachardoublequoteclose}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup F\ {\isasymequiv}\ F\ {\isasymphi}{\isachardoublequoteclose}\ \isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ mkT{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup T{\isachardoublequoteclose}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup T\ {\isasymequiv}\ T\ {\isasymphi}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ mkE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup E{\isachardoublequoteclose}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup E\ {\isasymequiv}\ ERR\ {\isasymphi}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+Some language constructs in the theory of abstract types, e.g. the actuality operator  
+ \isa{{\isasymA}} ("it is actually the case that"), refer to a (fixed) given world. To model such a 
+ global world reference we introduce a
+ constant symbol (name) \isa{cw} of world type \isa{i}. Moreover, for technical reasons, 
+ which will be clarified below, we introduce further (dummy) constant symbols for various domains. Since
+ we assume that all domains are non-empty, introducing these constant symbols is obviously not harmful.%
+\end{isamarkuptext}%
+\isamarkuptrue%
 \isacommand{consts}\isamarkupfalse%
 \ cw\ {\isacharcolon}{\isacharcolon}\ i\ \isanewline
-%
-\isamarkupcmt{the distinguished actual world%
-}
-\isanewline
 \isacommand{consts}\isamarkupfalse%
-\ dE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isachardoublequoteclose}\ dIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isachardoublequoteclose}\ dEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dEEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isacharequal}{\isachargreater}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dEEEIO{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isacharequal}{\isachargreater}e{\isacharequal}{\isachargreater}e{\isasymRightarrow}io{\isachardoublequoteclose}\ dA{\isacharcolon}{\isacharcolon}{\isacharprime}a\isanewline
-%
-\isamarkupcmt{some fixed dummy symbols; we anyway assume that the domains are non-empty%
-}
-\isanewline
-%
-\isamarkupcmt{needed as dummy object in some cases below%
-}
-%
-\begin{isamarkuptext}%
-Meta-logical predicates.%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ isWff\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isWff\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Error\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}\ Term\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}{\isacharunderscore}\ {\isasymRightarrow}\ True{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ isForm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isForm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Form\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ isPropForm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isPropForm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ isTerm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isTerm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Term\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ isError\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isError\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Error\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ valid\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
-\ \ \ \ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymforall}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ Form\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymforall}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ satifiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
-\ \ \ \ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ Form\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ countersatifiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ \ case\ {\isasymphi}\ of\ \isanewline
-\ \ \ \ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymexists}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ Form\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymexists}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ invalid\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
-\ \ \ \ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymforall}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ Form\ {\isasympsi}\ {\isasymRightarrow}\ {\isasymforall}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}%
-\isamarkupsection{Encoding of the language%
-}
+\ de{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isachardoublequoteclose}\ dio{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isachardoublequoteclose}\ da{\isacharcolon}{\isacharcolon}{\isacharprime}a%
+\isamarkupsection{Embedding of Modal Relational Type Theory%
+}
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+The language constructs of modal relational type theory are introduced step by step.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+The actuality operator \isa{{\isasymA}} when applied to a formula or propositional formula 
+ \isa{{\isasymphi}} evaluates \isa{{\isasymphi}} wrt the fixed given world \isa{cw}. 
+ The compound expression \isa{{\isasymA}\ {\isasymphi}} inherits its syntactical category  (\isa{Form} or
+ \isa{PropForm}) from \isa{{\isasymphi}}. If the syntactical catagory of  \isa{{\isasymphi}} is 
+ \isa{Error} or \isa{Term}, then the syntactical catagory of \isa{{\isasymA}\ {\isasymphi}} 
+ is \isa{Error} and a dummy entity of appropriate type is returned. This illustrates the very 
+ idea of our explicit structure and constraints and this scheme will repeated below
+ for all the other language constructs of modal relational type theory.%
+\end{isamarkuptext}%
 \isamarkuptrue%
@@
 \ {\isasymA}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt\ {\isasymRightarrow}\ io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymA}\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
-\ \ \ \ Form\ {\isasympsi}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasympsi}\ cw{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasympsi}\ cw{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-actuality operator; \isa{{\isasymphi}} is evaluated wrt the current world; Error is passed on%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ Enc{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharless}x{\isasymcirc}P{\isachargreater}\ {\isasymequiv}\ case\ {\isacharparenleft}x{\isacharcomma}P{\isacharparenright}\ of\ \isanewline
-\ \ \ \ {\isacharparenleft}Term\ y{\isacharcomma}Term\ Q{\isacharparenright}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isacharparenright}\ w{\isacharparenright}\ \ \ \isanewline
-\ \ {\isacharbar}\ {\isacharparenleft}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharparenright}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-\isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymPi}\isactrlsup {\isadigit{1}}} will be written here as \isa{{\isacharless}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymcirc}{\isasymPi}\isactrlsup {\isadigit{1}}{\isachargreater}}; \isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymPi}\isactrlsup {\isadigit{1}}} is a Form; Error is passed on%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ Exe{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharless}P{\isasymbullet}x{\isachargreater}\ {\isasymequiv}\ case\ {\isacharparenleft}P{\isacharcomma}x{\isacharparenright}\ of\ \isanewline
-\ \ \ \ {\isacharparenleft}Term\ Q{\isacharcomma}Term\ y{\isacharparenright}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isacharparenright}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-\isa{{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{1}}}  will be written here as \isa{{\isacharless}{\isasymPi}\isactrlsup {\isadigit{2}}{\isasymbullet}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isachargreater}}; \isa{{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{1}}} is a PropForm; Error is passed on%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ Exe{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharless}P{\isasymbullet}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isachargreater}\ {\isasymequiv}\ case\ {\isacharparenleft}P{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharparenright}\ of\ \isanewline
-\ \ \ \ {\isacharparenleft}Term\ Q{\isacharcomma}Term\ y{\isadigit{1}}{\isacharcomma}Term\ y{\isadigit{2}}{\isacharparenright}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isadigit{1}}\ y{\isadigit{2}}{\isacharparenright}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-\isa{{\isasymPi}\isactrlsup {\isadigit{2}}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{2}}}   will be written here as \isa{{\isacharless}{\isasymPi}\isactrlsup {\isadigit{2}}{\isasymbullet}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{2}}{\isachargreater}}; \isa{{\isasymPi}\isactrlsup {\isadigit{2}}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{2}}} is a PropForm; Error is passed on%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ Exe{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharless}P{\isasymbullet}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isachargreater}\ {\isasymequiv}\ case\ {\isacharparenleft}P{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isacharparenright}\ of\ \isanewline
-\ \ \ \ {\isacharparenleft}Term\ Q{\isacharcomma}Term\ y{\isadigit{1}}{\isacharcomma}Term\ y{\isadigit{2}}{\isacharcomma}Term\ y{\isadigit{3}}{\isacharparenright}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isadigit{1}}\ y{\isadigit{2}}\ y{\isadigit{3}}{\isacharparenright}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-\isa{{\isasymPi}\isactrlsup {\isadigit{3}}\isactrlsub {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{2}}{\isasymkappa}\isactrlsub {\isadigit{3}}}  will be written here as \isa{{\isacharless}{\isasymPi}\isactrlsup {\isadigit{2}}{\isasymbullet}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{2}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{3}}{\isachargreater}}; \isa{{\isasymPi}\isactrlsup {\isadigit{3}}\isactrlsub {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{2}}{\isasymkappa}\isactrlsub {\isadigit{3}}} is a PropForm; Error is passed on;
-we could, of course, introduce further operators: Exe4, Exe5, etc.%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}not{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymnot}\isactrlsup z\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
-\ \ \ \ Form\ {\isasympsi}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymnot}\ {\isasympsi}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymnot}\ {\isasympsi}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-negation operator; \isa{{\isasymnot}\isactrlsup z\ {\isasymphi}} inherits its type from \isa{{\isasymphi}} if \isa{{\isasymphi}} is Form or PropForm; 
-Error is passed on%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}implies{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\ {\isasymrightarrow}\isactrlsup z\ {\isasympsi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymphi}{\isacharcomma}{\isasympsi}{\isacharparenright}\ of\ \isanewline
-\ \ \ \ {\isacharparenleft}PropForm\ {\isasymalpha}{\isacharcomma}PropForm\ {\isasymbeta}{\isacharparenright}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharparenleft}Form\ {\isasymalpha}{\isacharcomma}Form\ {\isasymbeta}{\isacharparenright}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-implication operator; \isa{{\isasymphi}\ {\isasymrightarrow}\isactrlsup z\ {\isasympsi}} returns returns a PropForm if both are PropForms, Form if both are Forms,
-otherwise it returns Error%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}forall{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymforall}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ dA{\isacharparenright}\ of\isanewline
-\ \ \ \ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ Form\ {\isasymphi}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ Form\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-universal quantification; \isa{{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} inherits its kind (Form or PropForm) from \isa{{\isasymphi}}; Error is passed on
-\isa{{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} is mapped to \isa{{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}x{\isachardot}{\isasymphi}xw{\isacharparenright}} as expected%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}box{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymbox}\isactrlsup r\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
-\ \ \ \ Form\ {\isasympsi}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}v{\isachardot}\ {\isasympsi}\ v{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}v{\isachardot}\ {\isasympsi}\ v{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-box operator; \isa{{\isasymbox}\ {\isasymphi}} inherits its type (Form or PropForm) from \isa{{\isasymphi}}; Error is passed on.
-Note that the \isa{{\isasymbox}}-operator is defined here without an accessibility relation; this is ok since we assume logic S5.%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ lam{\isadigit{0}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlambda}\isactrlsup {\isadigit{0}}\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
-\ \ \ \ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ PropForm\ {\isasympsi}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-0-arity lambda abstraction; \isa{{\isasymlambda}\isactrlsup {\isadigit{0}}\ {\isasymphi}} returns PropForm \isa{{\isasymphi}} if \isa{{\isasymphi}} is a PropForm, otherwise Error%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ lam{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlambda}\isactrlsup {\isadigit{1}}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ dE{\isacharparenright}\ of\isanewline
-\ \ \ \ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ Term\ {\isacharparenleft}{\isasymlambda}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ {\isasymphi}{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ {\isacharparenleft}{\isasymlambda}x{\isachardot}\ dIO{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-1-arity lambda abstraction; \isa{{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} returns Term \isa{{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} if \isa{{\isasymphi}} is a PropForm,
-otherwise Error%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ lam{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlambda}\isactrlsup {\isadigit{2}}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ dE\ dE{\isacharparenright}\ of\isanewline
-\ \ \ \ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ Term\ {\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x\ y{\isacharparenright}\ of\ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ {\isasymphi}{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ {\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ dIO{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-2-arity lambda abstraction; \isa{{\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}} returns Term \isa{{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}} if \isa{{\isasymphi}} is a PropForm,
-otherwise Error%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ lam{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlambda}\isactrlsup {\isadigit{3}}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ dE\ dE\ dE{\isacharparenright}\ of\isanewline
-\ \ \ \ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ Term\ {\isacharparenleft}{\isasymlambda}x\ y\ z{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x\ y\ z{\isacharparenright}\ of\ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ {\isasymphi}{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ {\isacharparenleft}{\isasymlambda}x\ y\ z{\isachardot}\ dIO{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-3-arity lambda abstraction; \isa{{\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}xyz{\isachardot}{\isasymphi}{\isacharparenright}} returns Term \isa{{\isacharparenleft}{\isasymlambda}xyz{\isachardot}{\isasymphi}{\isacharparenright}} if \isa{{\isasymphi}} is a PropForm,
-otherwise Error; we could, of course, introduce further operators: \isa{{\isasymlambda}\isactrlsup {\isadigit{4}}}, \isa{{\isasymlambda}\isactrlsup {\isadigit{5}}}, etc.%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ that{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}e\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymepsilon}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ dE{\isacharparenright}\ of\isanewline
-\ \ \ \ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ Term\ {\isacharparenleft}THE\ x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ cw{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dE{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-that operator; that \isa{{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} returns Term \isa{{\isacharparenleft}THE\ x{\isachardot}\ {\isasymphi}\ x\ cw{\isacharparenright}}, that is the inbuilt THE
-operator is used and evaluation is wrt to the current world cw; moreover, application of that 
-is allowed if \isa{{\isacharparenleft}{\isasymPhi}\ sRE{\isacharparenright}} is a PropForm, otherwise Error is passed on for some someRawEntity%
-\end{isamarkuptext}%
-\isamarkuptrue%
-%
-\isamarkupsection{Further logical connectives%
-}
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}and{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\ {\isasymand}\isactrlsup z\ {\isasympsi}\ {\isasymequiv}\ {\isasymnot}\isactrlsup z{\isacharparenleft}{\isasymphi}\ {\isasymrightarrow}\isactrlsup z\ {\isasymnot}\isactrlsup z{\isasympsi}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}or{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\ {\isasymor}\isactrlsup z\ {\isasympsi}\ {\isasymequiv}\ {\isacharparenleft}{\isasymnot}\isactrlsup z{\isasymphi}\ {\isasymrightarrow}\isactrlsup z\ {\isasympsi}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}equiv{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\ {\isasymequiv}\isactrlsup z\ {\isasympsi}\ {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\ {\isasymrightarrow}\isactrlsup z\ {\isasympsi}{\isacharparenright}\ {\isasymand}\isactrlsup z\ {\isacharparenleft}{\isasympsi}\ {\isasymrightarrow}\isactrlsup z\ {\isasymphi}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}exists{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymexists}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ dA{\isacharparenright}\ of\isanewline
-\ \ \ \ PropForm\ {\isasymphi}\ {\isasymRightarrow}\ PropForm\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymexists}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ Form\ {\isasymphi}\ {\isasymRightarrow}\ Form\ {\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymexists}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ Form\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\isanewline
-\ \ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ Error\ dIO{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}dia{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymdiamond}\isactrlsup r\ {\isasymphi}\ {\isasymequiv}\ {\isasymnot}\isactrlsup z\ {\isasymbox}\isactrlsup r\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isasymphi}{\isacharparenright}{\isachardoublequoteclose}%
-\isamarkupsection{Some shortcuts for the constructors%
-}
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ mkPropForm\ {\isacharcolon}{\isacharcolon}\ \ {\isachardoublequoteopen}io{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharcomma}p{\isacharcomma}\ {\isasymequiv}\ PropForm\ p{\isachardoublequoteclose}\ \isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ mkForm\ {\isacharcolon}{\isacharcolon}\ \ {\isachardoublequoteopen}io{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharsemicolon}p{\isacharsemicolon}\ {\isasymequiv}\ Form\ p{\isachardoublequoteclose}\ \isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ mkTerm\ {\isacharcolon}{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isachardot}t{\isachardot}\ {\isasymequiv}\ Term\ t{\isachardoublequoteclose}%
-\isamarkupsection{Some basic tests%
-}
-\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Example signature; entities and relations%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{consts}\isamarkupfalse%
-\ a{\isacharunderscore}{\isadigit{0}}\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}e{\isachardoublequoteclose}\ \isacommand{abbreviation}\isamarkupfalse%
-\ a\ \ \isakeyword{where}\ {\isachardoublequoteopen}a\ {\isasymequiv}\ {\isachardot}a{\isacharunderscore}{\isadigit{0}}{\isachardot}{\isachardoublequoteclose}\isanewline
-\isacommand{consts}\isamarkupfalse%
-\ b{\isacharunderscore}{\isadigit{0}}\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}e{\isachardoublequoteclose}\ \isacommand{abbreviation}\isamarkupfalse%
-\ b\ \ \isakeyword{where}\ {\isachardoublequoteopen}b\ {\isasymequiv}\ {\isachardot}b{\isacharunderscore}{\isadigit{0}}{\isachardot}{\isachardoublequoteclose}\isanewline
-\isacommand{consts}\isamarkupfalse%
-\ c{\isacharunderscore}{\isadigit{0}}\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}e{\isachardoublequoteclose}\ \isacommand{abbreviation}\isamarkupfalse%
-\ c\ \ \isakeyword{where}\ {\isachardoublequoteopen}c\ {\isasymequiv}\ {\isachardot}c{\isacharunderscore}{\isadigit{0}}{\isachardot}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{consts}\isamarkupfalse%
-\ R{\isacharunderscore}{\isadigit{0}}\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io{\isachardoublequoteclose}\ \ \isacommand{abbreviation}\isamarkupfalse%
-\ R{\isadigit{0}}\ \ \isakeyword{where}\ {\isachardoublequoteopen}R{\isadigit{0}}\ {\isasymequiv}\ {\isachardot}R{\isacharunderscore}{\isadigit{0}}{\isachardot}{\isachardoublequoteclose}\isanewline
-\isacommand{consts}\isamarkupfalse%
-\ R{\isacharunderscore}{\isadigit{1}}\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}e{\isasymRightarrow}io{\isachardoublequoteclose}\ \isacommand{abbreviation}\isamarkupfalse%
-\ R{\isadigit{1}}\ \ \isakeyword{where}\ {\isachardoublequoteopen}R{\isadigit{1}}\ {\isasymequiv}\ {\isachardot}R{\isacharunderscore}{\isadigit{1}}{\isachardot}{\isachardoublequoteclose}\isanewline
-\isacommand{consts}\isamarkupfalse%
-\ R{\isacharunderscore}{\isadigit{2}}\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}e{\isasymRightarrow}e{\isasymRightarrow}io{\isachardoublequoteclose}\ \isacommand{abbreviation}\isamarkupfalse%
-\ R{\isadigit{2}}\ \ \isakeyword{where}\ {\isachardoublequoteopen}R{\isadigit{2}}\ {\isasymequiv}\ {\isachardot}R{\isacharunderscore}{\isadigit{2}}{\isachardot}{\isachardoublequoteclose}\isanewline
-\isacommand{consts}\isamarkupfalse%
-\ R{\isacharunderscore}{\isadigit{3}}\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isachardoublequoteclose}\ \ \isacommand{abbreviation}\isamarkupfalse%
-\ R{\isadigit{3}}\ \ \isakeyword{where}\ {\isachardoublequoteopen}R{\isadigit{3}}\ {\isasymequiv}\ {\isachardot}R{\isacharunderscore}{\isadigit{3}}{\isachardot}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-Testing term and formula constructions%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharless}R{\isadigit{1}}{\isasymbullet}a{\isachargreater}{\isacharbrackright}{\isachardoublequoteclose}\ \isacommand{nitpick}\isamarkupfalse%
+\ \ \ \ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasympsi}\ cw{\isacharparenright}\ {\isacharbar}\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasympsi}\ cw{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+The Principia Metaphysica distinguishes between encoding and exemplifying, ... say more ...
+
+ Encoding \isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymPi}\isactrlsup {\isadigit{1}}} is noted here as \isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymcdot}{\isasymPi}\isactrlsup {\isadigit{1}}}.
+ Encoding yields formulas and never propositional formulas. In the embedding encoding 
+ is identified with predicate application.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ Enc{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}{\isasymlbrace}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrbrace}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlbrace}x{\isacharcomma}{\isasymPhi}{\isasymrbrace}\ {\isasymequiv}\ case\ {\isacharparenleft}x{\isacharcomma}{\isasymPhi}{\isacharparenright}\ of\ \isanewline
+\ \ \ \ {\isacharparenleft}T{\isacharparenleft}y{\isacharparenright}{\isacharcomma}T{\isacharparenleft}Q{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+Exemplifying formulas \isa{{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{1}}} are noted here as \isa{{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymbullet}{\isasymkappa}\isactrlsub {\isadigit{1}}}.
+ Exemplification yields propositional formulas and never formulas. In the embedding exemplification 
+ is identified with predicate application, just as encoding.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ Exe{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isacharparenright}\ of\ \isanewline
+\ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+The Principia Metaphysica supports $n$-ary exemplification constructions. For pragmatical 
+ reasons we consider here the cases only for $n\leq 3$.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ Exe{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharparenright}\ of\ \isanewline
+\ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{1}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{2}}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isadigit{1}}\ y{\isadigit{2}}{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ Exe{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isacharparenright}\ of\ \isanewline
+\ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{1}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{2}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{3}}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isadigit{1}}\ y{\isadigit{2}}\ y{\isadigit{3}}{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+Formations with negation and implication are supported for both, formulas  and propositional
+ formulas, and their embeddings are straightforward.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ not{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymnot}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+\ \ \ \ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}{\isacharparenright}\ {\isacharbar}\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\ \ \isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ implies{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymrightarrow}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{1}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymphi}{\isacharcomma}{\isasympsi}{\isacharparenright}\ of\ \isanewline
+\ \ \ \ {\isacharparenleft}F{\isacharparenleft}{\isasymalpha}{\isacharparenright}{\isacharcomma}F{\isacharparenleft}{\isasymbeta}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharparenleft}P{\isacharparenleft}{\isasymalpha}{\isacharparenright}{\isacharcomma}P{\isacharparenleft}{\isasymbeta}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+Also universal quantification \isa{\isactrlbold {\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} (first-order and higher-order) is supported 
+ for formulas  and propositional formulas. Following previous work the embedding maps 
+ \isa{\isactrlbold {\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} to \isa{{\isacharparenleft}{\isasymlambda}w{\isachardot}\isactrlbold {\isasymforall}x{\isachardot}{\isasymphi}w{\isacharparenright}}.
+Note that \isa{\isactrlbold {\isasymforall}} is introduced as logical connective
+ based on the existing \isa{{\isasymlambda}}-binder. To improve presentation in the remainder we additional
+ introduce binder notation \isa{\isactrlbold {\isasymforall}x{\isachardot}{\isasymphi}} as syntactic sugar for \isa{\isactrlbold {\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}}.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ forall{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ da{\isacharparenright}\ of\isanewline
+\ \ \ \ F{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ forallBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymforall}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+The modal \isa{\isactrlbold {\isasymbox}} operator is introduced here for logic S5. Since in an equivalence class
+ of possible worlds each world is reachable from any other world, the guarding accessibility clause
+ in the usual definition of the \isa{\isactrlbold {\isasymbox}} operator can be omitted. This is convenient and should also
+ ease theorem proving. In Section \ref{sec:S5} we will actually demonstrate that the expected S5 properties
+ are validated by our modeling of \isa{\isactrlbold {\isasymbox}}.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ box{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymbox}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymbox}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+\ \ \ \ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}v{\isachardot}\ {\isasympsi}\ v{\isacharparenright}\ {\isacharbar}\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}v{\isachardot}\ {\isasympsi}\ v{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+n-ary lambda abstraction \isa{{\isasymlambda}\isactrlsup {\isadigit{0}}{\isacharcomma}{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharcomma}{\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}{\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}}, for $n\geq 0$, is supported in the Principia
+ Metaphysica only for propositional formulas. ... say more about \isa{{\isasymlambda}\isactrlsup {\isadigit{0}}} ... Their embedding is 
+ straightforward: \isa{{\isasymlambda}\isactrlsup {\isadigit{0}}} is mapped to identity and \isa{{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharcomma}{\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}{\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}} are mapped to n-ary
+ lambda abstractions, that is, \isa{{\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}} is e.g.
+mapped to \isa{{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}}.
+ For pragmatical reasons we restrict ourselves here to the cases where $n\leq 0$.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ lam{\isadigit{0}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR\ dio{\isachardoublequoteclose}\ \ \isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ lam{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}{\isasymPhi}{\isacharparenright}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline
+\ \ \ \ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}{\isasymlambda}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasymphi}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}{\isasymlambda}x{\isachardot}\ dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ lam{\isadigit{1}}Binder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ lam{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de\ de{\isacharparenright}\ of\isanewline
+\ \ \ \ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x\ y{\isacharparenright}\ of\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasymphi}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ lam{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de\ de\ de{\isacharparenright}\ of\isanewline
+\ \ \ \ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}{\isasymlambda}x\ y\ z{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x\ y\ z{\isacharparenright}\ of\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasymphi}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}{\isasymlambda}x\ y\ z{\isachardot}\ dio{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+The Principia Metaphysica supports rigid definite descriptions. Our definition maps
+ \isa{{\isasymiota}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} to \isa{{\isacharparenleft}THE\ x{\isachardot}\ {\isasymphi}\ cw{\isacharparenright}}, that is Isabelle's inbuilt description operator THE
+ is utilized and evaluation is rigidly carried out with respect to the current world \isa{cw}.
+ Moreover, application of that is allowed only if the body of \isa{{\isasymPhi}}, computed by clause 
+ \isa{{\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}}, is a propositional formula. In this case a term is returned and otherwise error 
+ reported (for dummy entity \isa{de}).%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ that{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}e\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}{\isasymiota}{\isachardoublequoteclose}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymiota}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline
+\ \ \ \ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}THE\ x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ cw{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}de{\isacharparenright}{\isachardoublequoteclose}%
+\isamarkupsection{Further Logical Connectives%
+}
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Further logical connectives can be defined as usual. For existential quantification we here
+ prefer a native introduction, even though a definition based on \isa{\isactrlbold {\isasymnot}} and \isa{\isactrlbold {\isasymforall}} is also
+ possible (but syntactically not more elegant). For pragmatic reasons it eventually makes sense to 
+ to prefer native introductions for all connectives.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ conj{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymand}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{3}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlbold {\isasymand}{\isasympsi}\ {\isasymequiv}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isasymphi}\isactrlbold {\isasymrightarrow}\isactrlbold {\isasymnot}{\isasympsi}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ or{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymor}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{2}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlbold {\isasymor}{\isasympsi}\ {\isasymequiv}\ \isactrlbold {\isasymnot}{\isasymphi}\isactrlbold {\isasymrightarrow}{\isasympsi}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ equivalent{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymequiv}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{2}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlbold {\isasymequiv}{\isasympsi}\ {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlbold {\isasymrightarrow}{\isasympsi}{\isacharparenright}\isactrlbold {\isasymand}{\isacharparenleft}{\isasympsi}\isactrlbold {\isasymrightarrow}{\isasymphi}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ diamond{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymdiamond}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymdiamond}{\isasymphi}\ {\isasymequiv}\ \isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isasymphi}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ exists{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymexists}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ da{\isacharparenright}\ of\isanewline
+\ \ \ \ P\ {\isasymphi}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymexists}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ F\ {\isasymphi}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymexists}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ F\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR\ dio{\isachardoublequoteclose}\ \isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ existsBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymexists}\ {\isasymphi}{\isachardoublequoteclose}%
+\isamarkupsection{Meta-Logic%
+}
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Our approach to rigorously distinguish between proper and improper language constructions 
+ and to explicitly maintain respective information is continued also at meta-level. For this 
+ we introduce three truth values \isa{tt},
+ \isa{ff} and \isa{err}, representing truth, falsity and error. These values can also 
+ be noted as \isa{{\isasymtop}}, \isa{{\isasymbottom}} and \isa{{\isacharasterisk}}. We could, of course, also introduce  
+ respective logical connectives for the meta-level, but in our applications so far (see below)
+ this was not yet relevant.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{datatype}\isamarkupfalse%
+\ mf\ {\isacharequal}\ tt\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymtop}{\isachardoublequoteclose}{\isacharparenright}\ {\isacharbar}\ ff\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymbottom}{\isachardoublequoteclose}{\isacharparenright}\ {\isacharbar}\ err\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharasterisk}{\isachardoublequoteclose}{\isacharparenright}%
+\begin{isamarkuptext}%
+Next we define the meta-logical notions of validity, satisfiability, 
+ countersatisfiability and invalidity for our embedded modal relational type theory. To support
+ concise formula representations in the remainder we introduce the following notations: \isa{{\isacharbrackleft}{\isasymphi}{\isacharbrackright}} 
+ (for \isa{{\isasymphi}} is valid), \isa{{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t} (\isa{{\isasymphi}} is satisfiability), \isa{{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t}
+ (\isa{{\isasymphi}} is countersatisfiability) and \isa{{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v} (\isa{{\isasymphi}} is invalid).%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ valid\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}mf{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharbrackleft}{\isacharunderscore}{\isacharbrackright}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ satisfiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}mf{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharbrackleft}{\isacharunderscore}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ countersatisfiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}mf{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharbrackleft}{\isacharunderscore}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ \ case\ {\isasymphi}\ of\ \isanewline
+\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ invalid\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}mf{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharbrackleft}{\isacharunderscore}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}%
+\isamarkupsection{Some Basic Tests%
+}
+\isamarkuptrue%
+%
+\isamarkupsubsection{Verifying Necessitation%
+}
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+The next two lemmata show that necessitation holds for arbitrary formulas 
+ and arbitrary propositional formulas. We present the lemma in both variants.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ necessitationF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}\ {\isasymlongrightarrow}\ {\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ necessitationP{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}\ {\isasymlongrightarrow}\ {\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsubsection{Modal Collapse is Countersatisfiable%
+}
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+The modelfinder Nitpick constructs a finite countermodel to the assertion
+  that modal collaps is valid. Nitpicks countermodel consists of four worlds i1, i2, i3 and i4.
+  Moreover, it defines  \isa{{\isasymphi}} to hold only in world i3 and it suggests i3 as the actual 
+  world in which to evaluate the conjecture formula. This countermodel is clearly not minimal.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ modalCollapseF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isacommand{nitpick}\isamarkupfalse%
 %
@@
 \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}isPropForm\ {\isacharless}R{\isadigit{1}}{\isasymbullet}a{\isachargreater}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharless}R{\isadigit{1}}{\isasymbullet}a{\isachargreater}\ {\isacharequal}\ X{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharless}a{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharbrackright}{\isachardoublequoteclose}\ \isacommand{nitpick}\isamarkupfalse%
+\ %
+\isamarkupcmt{Countermodel by Nitpick%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ modalCollapseP{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isacommand{nitpick}\isamarkupfalse%
 %
@@
 \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}isPropForm\ {\isacharless}a{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}isForm\ {\isacharless}a{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharless}a{\isasymcirc}R{\isadigit{1}}{\isachargreater}\ {\isacharequal}\ X{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharless}{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isasymbullet}a{\isachargreater}{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharless}{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isasymbullet}a{\isachargreater}\ {\isacharequal}\ X{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymnot}\ isWff\ {\isacharparenleft}{\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharless}{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}{\isasymbullet}a{\isachargreater}{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharless}{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}{\isasymbullet}a{\isachargreater}\ {\isacharequal}\ X{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}{\isachardot}R{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}R{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isacharless}R{\isadigit{1}}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isacharless}{\isachardot}R{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}{\isachardot}R{\isachardot}{\isachargreater}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymforall}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isacharless}{\isachardot}R{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}{\isachardot}R{\isachardot}{\isachargreater}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isamarkupsection{Are the priorities set correctly?%
-}
-\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymchi}{\isacharcomma}\ {\isasymequiv}\ {\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymchi}{\isacharcomma}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymchi}{\isacharcomma}\ {\isasymequiv}\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharparenleft}{\isacharcomma}{\isasympsi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymchi}{\isacharcomma}{\isacharparenright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}%
+\ %
+\isamarkupcmt{Countermodel by Nitpick%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+We also tried to prove the statement \isa{{\isacharbrackleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isacharequal}\ {\isasymtop}} with automated reasoners.
+ This was however not successful ... (check again and check why).%
+\end{isamarkuptext}%
+\isamarkuptrue%
+%
+\isamarkupsubsection{Verifying S5 Principles \label{sec:S5}%
+}
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+\isa{{\isasymbox}} could have been modeled by employing an equivalence relation \isa{r} in a 
+ guarding clause. This has been done in previous work. In a simpler, alternative approach we omitted 
+ this clause here (since all worlds are reachable from any world in an equivalence relation). The 
+ following lemmata, which check various conditions for S5,  ensure that we have indeed 
+ modeled S5 correctly.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}T{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}T{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}B{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}B{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}D{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}D{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}A{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}A{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}B{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}B{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{by}\isamarkupfalse%
+\ auto%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}C{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp%
 \endisatagproof
@@
 \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}\ {\isasymequiv}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}\ {\isasymequiv}\isactrlsup z\ {\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}\ {\isasymequiv}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymand}\isactrlsup z\ {\isacharparenleft}{\isacharcomma}{\isasympsi}{\isacharcomma}\ {\isasymequiv}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymand}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}%
+\ %
+\isamarkupcmt{Countermodel by Nitpick%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}C{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp%
 \endisatagproof
@@
 \isacommand{oops}\isamarkupfalse%
+\ %
+\isamarkupcmt{Countermodel by Nitpick%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}D{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}D{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsubsection{Relations between  Meta-Logical Notions%
+}
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}\ {\isasymlongleftrightarrow}\ {\isacharbrackleft}{\isasymphi}\isactrlsup P{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isacharequal}\ {\isasymbottom}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isacharequal}\ {\isasymtop}\ {\isasymlongleftrightarrow}\ {\isacharbrackleft}{\isasymphi}\isactrlsup P{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v\ {\isacharequal}\ {\isasymbottom}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}\ {\isasymlongleftrightarrow}\ {\isacharbrackleft}{\isasymphi}\isactrlsup F{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isacharequal}\ {\isasymbottom}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isacharequal}\ {\isasymtop}\ {\isasymlongleftrightarrow}\ {\isacharbrackleft}{\isasymphi}\isactrlsup F{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v\ {\isacharequal}\ {\isasymbottom}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+However, for terms we have%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup T{\isacharbrackright}\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup T{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup T{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup T{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsubsection{Testing for the Correct Propagation of Syntactical Category Information%
+}
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymexists}X{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup P{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup F{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup T{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup E{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymexists}X{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup F{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup P{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup T{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup E{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Most importantly, we have that the following language constructing is evaluated as erroneous at validity
+ level.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+This is also confirmed as follows in Isabelle: Isabelle simplifies the following expression
+ to \isa{dio\isactrlsup E\ {\isacharequal}\ X} (simply move the curse on \isa{simp} to see this).%
+\end{isamarkuptext}%
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Todo: ... select, adapt, and explain some of examples below ...%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymlparr}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymexists}X{\isachardot}\ {\isasymlparr}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+\ %
+\isamarkupcmt{Solution: \isa{{\isacharparenleft}{\isasymlambda}w{\isachardot}\ True{\isacharparenright}\ {\isacharequal}\ X}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymlparr}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}R{\isachardot}\ \isactrlbold {\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}R{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymforall}R{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsubsection{Are Priorities Defined Correctly?%
+}
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymchi}\isactrlsup P{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymchi}\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymchi}\isactrlsup P{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymchi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\ %
+\isamarkupcmt{Countermodel by Nitpick%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\ %
+\isamarkupcmt{Countermodel by Nitpick%
+}
 %
@@
 }
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+We introduce the distinguished 1-place relation constant: E (read: ‘being concrete’ or ‘concreteness’)%
+\end{isamarkuptext}%
 \isamarkuptrue%
@@
 \begin{isamarkuptext}%
-Distinguished 1-place relation constant: E! (read: ‘being concrete’ or ‘concreteness’)%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}ordinary{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}O\isactrlsup {\isacharbang}\ {\isasymequiv}\ {\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymdiamond}\isactrlsup r\ {\isacharless}{\isachardot}E{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-Being ordinary is being possibly concrete.%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}abstract{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}A\isactrlsup {\isacharbang}\ {\isasymequiv}\ {\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymnot}\isactrlsup z\ {\isasymdiamond}\isactrlsup r\ {\isacharless}{\isachardot}E{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-Being abstract is not possibly being concrete.%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}identity{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharequal}\isactrlsub e\isactrlsup z\ {\isasymequiv}\ \isanewline
-\ \ {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isacharless}O\isactrlsup {\isacharbang}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymand}\isactrlsup z\ {\isacharless}O\isactrlsup {\isacharbang}{\isasymbullet}{\isachardot}y{\isachardot}{\isachargreater}{\isacharparenright}\ {\isasymand}\isactrlsup z\ {\isasymbox}\isactrlsup r\ {\isacharparenleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharless}{\isachardot}F{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymequiv}\isactrlsup z\ {\isacharless}{\isachardot}F{\isachardot}{\isasymbullet}{\isachardot}y{\isachardot}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ z{\isacharunderscore}identityE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isacharparenright}{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}x\ {\isacharequal}\isactrlsub E\ y\ {\isasymequiv}\ {\isacharparenleft}Exe{\isadigit{2}}\ {\isacharequal}\isactrlsub e\isactrlsup z\ x\ y{\isacharparenright}{\isachardoublequoteclose}%
-\isamarkupsection{Further test examples%
-}
-\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymexists}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isacharparenleft}{\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}{\isachardot}R{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+Being ordinary is defined as being possibly concrete.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ ordinaryObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}O{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}O{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ \isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+Being abstract is is defined as not possibly being concrete.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ abstractObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}A{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}A{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ \isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+Identity \isa{{\isacharequal}\isactrlsub e} is defined as .... Subsequenty, the infix operator \isa{{\isacharequal}\isactrlsub E} is 
+ introduced.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ identity{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isacharequal}\isactrlsub e{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isacharequal}\isactrlsub e\ {\isasymequiv}\ \isanewline
+\ \ \isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ {\isacharparenleft}{\isasymlparr}O{\isacharbang}{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ {\isasymlparr}O{\isacharbang}{\isacharcomma}y\isactrlsup T{\isasymrparr}{\isacharparenright}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymforall}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isasymlparr}F\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymequiv}\ {\isasymlparr}F\isactrlsup T{\isacharcomma}y\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ identityE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isacharequal}\isactrlsub E{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}x\ \isactrlbold {\isacharequal}\isactrlsub E\ y\ {\isasymequiv}\ {\isasymlparr}\isactrlbold {\isacharequal}\isactrlsub e{\isacharcomma}x{\isacharcomma}y{\isasymrparr}{\isachardoublequoteclose}%
+\isamarkupsection{Further Test Examples%
+}
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Todo: ... select, adapt, and explain some of examples below%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ \isactrlbold {\isasymexists}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ \isactrlbold {\isasymforall}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}a\isactrlsup T{\isacharparenright}\ \isactrlbold {\isacharequal}\isactrlsub E\ {\isacharparenleft}a\isactrlsup T{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\ %
+\isamarkupcmt{Countermodel by Nitpick%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}O{\isacharbang}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\isactrlsup T{\isacharparenright}\ \isactrlbold {\isacharequal}\isactrlsub E\ {\isacharparenleft}a\isactrlsup T{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}F{\isachardot}\ {\isasymlparr}F\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymequiv}\ {\isasymlparr}F\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}O{\isacharbang}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}{\isacharparenleft}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isacharparenleft}x\isactrlsup T{\isacharparenright}\ \isactrlbold {\isacharequal}\isactrlsub E\ {\isacharparenleft}a\isactrlsup T{\isacharparenright}{\isacharparenright}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}F{\isachardot}\ {\isasymlbrace}a\isactrlsup T{\isacharcomma}F\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{by}\isamarkupfalse%
 \ auto%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymforall}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isacharparenleft}{\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}{\isachardot}R{\isachardot}{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isachardot}x{\isachardot}{\isasymcirc}R{\isadigit{1}}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\ \isacommand{nitpick}\isamarkupfalse%
-%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}a\ {\isacharequal}\isactrlsub E\ a{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\ \isacommand{nitpick}\isamarkupfalse%
-%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharless}O\isactrlsup {\isacharbang}{\isasymbullet}a{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ a\ {\isacharequal}\isactrlsub E\ a{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharless}{\isachardot}F{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}\ {\isasymequiv}\isactrlsup z\ {\isacharless}{\isachardot}F{\isachardot}{\isasymbullet}{\isachardot}x{\isachardot}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharless}O\isactrlsup {\isacharbang}{\isasymbullet}a{\isachargreater}\ {\isasymrightarrow}\isactrlsup z\ {\isacharless}{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isachardot}x{\isachardot}\ {\isacharequal}\isactrlsub E\ a{\isacharparenright}{\isasymbullet}a{\isachargreater}{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymexists}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharless}a{\isasymcirc}{\isachardot}F{\isachardot}{\isachargreater}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{by}\isamarkupfalse%
 \ auto%
@@
 \isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}isWff\ {\isacharcomma}{\isacharparenleft}{\isasymlambda}w{\isachardot}\ True{\isacharparenright}{\isacharcomma}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymexists}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharcomma}F{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{by}\isamarkupfalse%
 \ auto%
@@
 \endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymexists}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharsemicolon}F{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
-\ auto\isanewline
+%
+\isamarkupsection{Axioms%
+}
+\isamarkuptrue%
+%
+\isamarkupsubsection{Axioms for Negations and Conditionals%
+}
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymchi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymchi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isasympsi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymchi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasympsi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymchi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isasympsi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasympsi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsubsection{Axioms of Identity%
+}
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+todo%
+\end{isamarkuptext}%
+\isamarkuptrue%
+%
+\isamarkupsubsection{Axioms of Quantification%
+}
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+todo%
+\end{isamarkuptext}%
+\isamarkuptrue%
+%
+\isamarkupsubsection{Axioms of Actuality%
+}
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isasymA}{\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasympsi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isasymA}{\isacharparenleft}{\isasympsi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isasymA}{\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isasymA}{\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsubsection{Axioms of Necessity%
+}
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \ \ \isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \ \ \isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \ \ \ \ \ \ \isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+The following needs to be an axiom; it does not follow for free: it is possible that there 
+are contingently concrete individuals and it is possible that there are not:%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{axiomatization}\isamarkupfalse%
+\ \isakeyword{where}\isanewline
+\ \ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ {\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ {\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isamarkupsubsection{Axioms of Necessity and Actuality%
+}
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+\isanewline
+\isanewline
 %

### 2015-12-11 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
another improvement on syntax

@@
  \isa{{\isasymphi}} evaluates \isa{{\isasymphi}} wrt the fixed given world \isa{cw}. 
- The compound expression \isa{{\isasymA}\ {\isasymphi}} inherits its syntactical category  (\isa{Form} or
- \isa{PropForm}) from \isa{{\isasymphi}}. If the syntactical catagory of  \isa{{\isasymphi}} is 
- \isa{Error} or \isa{Term}, then the syntactical catagory of \isa{{\isasymA}\ {\isasymphi}} 
- is \isa{Error} and a dummy entity of appropriate type is returned. This illustrates the very 
+ The compound expression \isa{{\isasymA}\ {\isasymphi}} inherits its syntactical category  \isa{F} (formula) or
+ \isa{P} (propositional formula from \isa{{\isasymphi}}. If the syntactical catagory of  \isa{{\isasymphi}} is 
+ \isa{E} (error) or \isa{T} (term), then the syntactical catagory of \isa{{\isasymA}\ {\isasymphi}} 
+ is \isa{E} and a dummy entity of appropriate type is returned. This illustrates the very 
  idea of our explicit structure and constraints and this scheme will repeated below
@@
 \begin{isamarkuptext}%
-n-ary lambda abstraction \isa{{\isasymlambda}\isactrlsup {\isadigit{0}}{\isacharcomma}{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharcomma}{\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}{\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}}, for $n\geq 0$, is supported in the Principia
- Metaphysica only for propositional formulas. ... say more about \isa{{\isasymlambda}\isactrlsup {\isadigit{0}}} ... Their embedding is 
- straightforward: \isa{{\isasymlambda}\isactrlsup {\isadigit{0}}} is mapped to identity and \isa{{\isasymlambda}\isactrlsup {\isadigit{1}}{\isacharcomma}{\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}{\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}} are mapped to n-ary
- lambda abstractions, that is, \isa{{\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}} is e.g.
-mapped to \isa{{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}}.
+n-ary lambda abstraction \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}{\isacharcomma}\isactrlbold {\isasymlambda}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}\isactrlsup {\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}}, for $n\geq 0$, is supported in the Principia
+ Metaphysica only for propositional formulas. ... say more about \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}} ... Their embedding is 
+ straightforward: \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}} is mapped to identity and \isa{\isactrlbold {\isasymlambda}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}} are mapped to n-ary
+ lambda abstractions, that is, \isa{\isactrlbold {\isasymlambda}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} is mapped to \isa{{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} and \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}}
+ to \isa{{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}}.
  For pragmatical reasons we restrict ourselves here to the cases where $n\leq 0$.%
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ lam{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}{\isasymPhi}{\isacharparenright}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline
+\ lam{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline
 \ \ \ \ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}{\isasymlambda}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasymphi}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}{\isasymlambda}x{\isachardot}\ dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
 \isacommand{abbreviation}\isamarkupfalse%
-\ lam{\isadigit{1}}Binder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
+\ lam{\isadigit{1}}Binder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
 \isanewline
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ lam{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de\ de\ de{\isacharparenright}\ of\isanewline
+\ lam{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de\ de\ de{\isacharparenright}\ of\isanewline
 \ \ \ \ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}{\isasymlambda}x\ y\ z{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x\ y\ z{\isacharparenright}\ of\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasymphi}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}{\isasymlambda}x\ y\ z{\isachardot}\ dio{\isacharparenright}{\isachardoublequoteclose}%
@@
 %
-\begin{isamarkuptext}%
-We also tried to prove the statement \isa{{\isacharbrackleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isacharequal}\ {\isasymtop}} with automated reasoners.
- This was however not successful ... (check again and check why).%
-\end{isamarkuptext}%
-\isamarkuptrue%
-%
 \isamarkupsubsection{Verifying S5 Principles \label{sec:S5}%
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymlparr}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\ {\isachardoublequoteopen}{\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymexists}X{\isachardot}\ {\isasymlparr}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%
+\ {\isachardoublequoteopen}{\isasymexists}X{\isachardot}\ {\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymlparr}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
 \isadelimproof
@@
 \ simp\ \isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}x\ y{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}y\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
 %
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ ordinaryObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}O{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}O{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ \isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isachardoublequoteclose}%
+\ ordinaryObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}O{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}O{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}x{\isachardot}\ \isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isachardoublequoteclose}%
 \begin{isamarkuptext}%
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ abstractObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}A{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}A{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ \isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isachardoublequoteclose}%
+\ abstractObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}A{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}A{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}x{\isachardot}\ \isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isachardoublequoteclose}%
 \begin{isamarkuptext}%
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}O{\isacharbang}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}{\isacharparenleft}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{1}}x{\isachardot}\ {\isacharparenleft}x\isactrlsup T{\isacharparenright}\ \isactrlbold {\isacharequal}\isactrlsub E\ {\isacharparenleft}a\isactrlsup T{\isacharparenright}{\isacharparenright}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}O{\isacharbang}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}{\isacharparenleft}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isacharparenleft}x\isactrlsup T{\isacharparenright}\ \isactrlbold {\isacharequal}\isactrlsub E\ {\isacharparenleft}a\isactrlsup T{\isacharparenright}{\isacharparenright}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof

### 2015-12-11 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
further improvements: syntax, binder modified definition of identity relations

@@
  previous work \cite{J23,C40} is simple: modal logic formulas are identified with certain functional 
- type theory formulas of predicate type \isa{io}. Possible worlds are explicitly represented by 
+ type theory formulas of predicate type \isa{i{\isasymRightarrow}bool} (abbreviated as \isa{io} below). 
+ Possible worlds are explicitly represented by 
  terms of type  \isa{i}. A modal logic \isa{{\isasymphi}} formula holds for a world \isa{w} if and 
@@
 
- The challenge in this work is to appropriately 'restrict' this embedding for modal relational type theory.
+ The challenge here is to appropriately 'restrict' this embedding for modal relational type theory.
   \begin{figure}[t]
@@
 We start out with some type declarations and type abbreviations. 
- Our formalism explicitly encodes Kripke style semantics. Hence, we introduce a 
+ Our formalism explicitly encodes possible world semantics. Hence, we introduce a 
  distinguished type \isa{i} to represent the set of possible worlds. 
@@
 To explicitly model the syntactical restrictions of modal relational type theory we introduce a 
- datatype \isa{{\isacharprime}a\ opt} based on four constructors:
- \isa{ERR\ {\isacharprime}a} (identifies erroneous term constructions), \isa{P\ {\isacharprime}a} (identifies 
+ (polymorphic) datatype \isa{{\isacharprime}a\ opt} (where \isa{{\isacharprime}a} is a polymorphic variable in Isabelle) 
+ based on four constructors: \isa{ERR\ {\isacharprime}a} (identifies erroneous term constructions), \isa{P\ {\isacharprime}a} (identifies 
  propositional formulas), \isa{F\ {\isacharprime}a} (identifies  formulas), and \isa{T\ {\isacharprime}a} (identifies 
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ mkP{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup P{\isachardoublequoteclose}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup P\ {\isasymequiv}\ P\ {\isasymphi}{\isachardoublequoteclose}\ \isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ mkF{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup F{\isachardoublequoteclose}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup F\ {\isasymequiv}\ F\ {\isasymphi}{\isachardoublequoteclose}\ \isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ mkT{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup T{\isachardoublequoteclose}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup T\ {\isasymequiv}\ T\ {\isasymphi}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ mkE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup E{\isachardoublequoteclose}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup E\ {\isasymequiv}\ ERR\ {\isasymphi}{\isachardoublequoteclose}%
+\ mkP{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup P{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isadigit{0}}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup P\ {\isasymequiv}\ P\ {\isasymphi}{\isachardoublequoteclose}\ \isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ mkF{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup F{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isadigit{0}}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup F\ {\isasymequiv}\ F\ {\isasymphi}{\isachardoublequoteclose}\ \isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ mkT{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup T{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isadigit{0}}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup T\ {\isasymequiv}\ T\ {\isasymphi}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ mkE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup E{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isadigit{0}}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup E\ {\isasymequiv}\ ERR\ {\isasymphi}{\isachardoublequoteclose}%
 \begin{isamarkuptext}%
@@
  \isa{P} (propositional formula from \isa{{\isasymphi}}. If the syntactical catagory of  \isa{{\isasymphi}} is 
- \isa{E} (error) or \isa{T} (term), then the syntactical catagory of \isa{{\isasymA}\ {\isasymphi}} 
- is \isa{E} and a dummy entity of appropriate type is returned. This illustrates the very 
+ \isa{ERR} (error) or \isa{T} (term), then the syntactical catagory of \isa{{\isasymA}\ {\isasymphi}} 
+ is \isa{ERR} and a dummy entity of appropriate type is returned. This illustrates the very 
  idea of our explicit structure and constraints and this scheme will repeated below
@@
 
- Encoding \isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymPi}\isactrlsup {\isadigit{1}}} is noted here as \isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymcdot}{\isasymPi}\isactrlsup {\isadigit{1}}}.
+ Encoding \isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymPi}\isactrlsup {\isadigit{1}}} is noted here as \isa{{\isasymlbrace}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymrbrace}}.
  Encoding yields formulas and never propositional formulas. In the embedding encoding 
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ Enc{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}{\isasymlbrace}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrbrace}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlbrace}x{\isacharcomma}{\isasymPhi}{\isasymrbrace}\ {\isasymequiv}\ case\ {\isacharparenleft}x{\isacharcomma}{\isasymPhi}{\isacharparenright}\ of\ \isanewline
+\ Enc{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlbrace}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrbrace}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlbrace}x{\isacharcomma}{\isasymPhi}{\isasymrbrace}\ {\isasymequiv}\ case\ {\isacharparenleft}x{\isacharcomma}{\isasymPhi}{\isacharparenright}\ of\ \isanewline
 \ \ \ \ {\isacharparenleft}T{\isacharparenleft}y{\isacharparenright}{\isacharcomma}T{\isacharparenleft}Q{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
 \begin{isamarkuptext}%
-Exemplifying formulas \isa{{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{1}}} are noted here as \isa{{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymbullet}{\isasymkappa}\isactrlsub {\isadigit{1}}}.
+Exemplifying formulas \isa{{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{1}}} are noted here as \isa{{\isasymlparr}{\isasymPi}\isactrlsup {\isadigit{1}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymrparr}}.
  Exemplification yields propositional formulas and never formulas. In the embedding exemplification 
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ Exe{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isacharparenright}\ of\ \isanewline
+\ Exe{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isacharparenright}\ of\ \isanewline
 \ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ Exe{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharparenright}\ of\ \isanewline
+\ Exe{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharparenright}\ of\ \isanewline
 \ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{1}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{2}}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isadigit{1}}\ y{\isadigit{2}}{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
 \isacommand{abbreviation}\isamarkupfalse%
-\ Exe{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isacharparenright}\ of\ \isanewline
+\ Exe{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isacharparenright}\ of\ \isanewline
 \ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{1}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{2}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{3}}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isadigit{1}}\ y{\isadigit{2}}\ y{\isadigit{3}}{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ not{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymnot}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+\ not{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{5}}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{5}}{\isadigit{9}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
 \ \ \ \ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}{\isacharparenright}\ {\isacharbar}\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\ \ \isanewline
 \isacommand{abbreviation}\isamarkupfalse%
-\ implies{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymrightarrow}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{1}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymphi}{\isacharcomma}{\isasympsi}{\isacharparenright}\ of\ \isanewline
+\ implies{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymrightarrow}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{1}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymphi}{\isacharcomma}{\isasympsi}{\isacharparenright}\ of\ \isanewline
 \ \ \ \ {\isacharparenleft}F{\isacharparenleft}{\isasymalpha}{\isacharparenright}{\isacharcomma}F{\isacharparenleft}{\isasymbeta}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharparenleft}P{\isacharparenleft}{\isasymalpha}{\isacharparenright}{\isacharcomma}P{\isacharparenleft}{\isasymbeta}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ forall{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ da{\isacharparenright}\ of\isanewline
+\ forall{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ da{\isacharparenright}\ of\isanewline
 \ \ \ \ F{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
 \isacommand{abbreviation}\isamarkupfalse%
-\ forallBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymforall}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
+\ forallBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymforall}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
 %
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ box{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymbox}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymbox}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+\ box{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymbox}\ {\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{6}}{\isadigit{2}}{\isacharbrackright}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymbox}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
 \ \ \ \ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}v{\isachardot}\ {\isasympsi}\ v{\isacharparenright}\ {\isacharbar}\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}v{\isachardot}\ {\isasympsi}\ v{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
@@
  to \isa{{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}}.
- For pragmatical reasons we restrict ourselves here to the cases where $n\leq 0$.%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ lam{\isadigit{0}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+ For pragmatical reasons we restrict ourselves here to the cases where $n\leq 0$. Binder notation is
+ introduced for \isa{\isactrlbold {\isasymlambda}} (... unfortuntaley, I don't know yet how this can be achieved as well 
+ for \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}} ...)%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ lam{\isadigit{0}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
 \ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR\ dio{\isachardoublequoteclose}\ \ \isanewline
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ lam{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline
+\ lam{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline
 \ \ \ \ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}{\isasymlambda}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasymphi}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}{\isasymlambda}x{\isachardot}\ dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
 \isacommand{abbreviation}\isamarkupfalse%
-\ lam{\isadigit{1}}Binder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ lam{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de\ de{\isacharparenright}\ of\isanewline
+\ lamBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ lam{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de\ de{\isacharparenright}\ of\isanewline
 \ \ \ \ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x\ y{\isacharparenright}\ of\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasymphi}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ lam{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de\ de\ de{\isacharparenright}\ of\isanewline
+\ lam{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de\ de\ de{\isacharparenright}\ of\isanewline
 \ \ \ \ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}{\isasymlambda}x\ y\ z{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x\ y\ z{\isacharparenright}\ of\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasymphi}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}{\isasymlambda}x\ y\ z{\isachardot}\ dio{\isacharparenright}{\isachardoublequoteclose}%
@@
  \isa{{\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}}, is a propositional formula. In this case a term is returned and otherwise error 
- reported (for dummy entity \isa{de}).%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ that{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}e\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}{\isasymiota}{\isachardoublequoteclose}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymiota}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline
-\ \ \ \ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}THE\ x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ cw{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}de{\isacharparenright}{\isachardoublequoteclose}%
+ reported (for dummy entity \isa{de}). We again introduce binder notation.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ that{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}e\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymiota}{\isachardoublequoteclose}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymiota}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline
+\ \ \ \ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}THE\ x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ cw{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}de{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ thatBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}e\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}{\isasymiota}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymiota}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ {\isasymiota}\ {\isasymphi}{\isachardoublequoteclose}%
 \isamarkupsection{Further Logical Connectives%
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ conj{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymand}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{3}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlbold {\isasymand}{\isasympsi}\ {\isasymequiv}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isasymphi}\isactrlbold {\isasymrightarrow}\isactrlbold {\isasymnot}{\isasympsi}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ or{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymor}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{2}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlbold {\isasymor}{\isasympsi}\ {\isasymequiv}\ \isactrlbold {\isasymnot}{\isasymphi}\isactrlbold {\isasymrightarrow}{\isasympsi}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ equivalent{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymequiv}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{2}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlbold {\isasymequiv}{\isasympsi}\ {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlbold {\isasymrightarrow}{\isasympsi}{\isacharparenright}\isactrlbold {\isasymand}{\isacharparenleft}{\isasympsi}\isactrlbold {\isasymrightarrow}{\isasymphi}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ diamond{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymdiamond}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymdiamond}{\isasymphi}\ {\isasymequiv}\ \isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isasymphi}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ exists{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymexists}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ da{\isacharparenright}\ of\isanewline
+\ conj{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymand}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{3}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlbold {\isasymand}{\isasympsi}\ {\isasymequiv}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isasymphi}\isactrlbold {\isasymrightarrow}\isactrlbold {\isasymnot}{\isasympsi}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ or{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymor}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{2}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlbold {\isasymor}{\isasympsi}\ {\isasymequiv}\ \isactrlbold {\isasymnot}{\isasymphi}\isactrlbold {\isasymrightarrow}{\isasympsi}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ equivalent{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymequiv}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{1}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlbold {\isasymequiv}{\isasympsi}\ {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlbold {\isasymrightarrow}{\isasympsi}{\isacharparenright}\isactrlbold {\isasymand}{\isacharparenleft}{\isasympsi}\isactrlbold {\isasymrightarrow}{\isasymphi}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ diamond{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymdiamond}\ {\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{6}}{\isadigit{2}}{\isacharbrackright}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymdiamond}{\isasymphi}\ {\isasymequiv}\ \isactrlbold {\isasymnot}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymphi}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ exists{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymexists}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ da{\isacharparenright}\ of\isanewline
 \ \ \ \ P\ {\isasymphi}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymexists}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ F\ {\isasymphi}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymexists}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ F\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR\ dio{\isachardoublequoteclose}\ \isanewline
 \isacommand{abbreviation}\isamarkupfalse%
-\ existsBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymexists}\ {\isasymphi}{\isachardoublequoteclose}%
+\ existsBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymexists}\ {\isasymphi}{\isachardoublequoteclose}%
 \isamarkupsection{Meta-Logic%
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ valid\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}mf{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharbrackleft}{\isacharunderscore}{\isacharbrackright}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+\ valid\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}mf{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharbrackleft}{\isacharunderscore}{\isacharbrackright}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isacharbrackright}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
 \ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}\isanewline
 \isacommand{abbreviation}\isamarkupfalse%
-\ satisfiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}mf{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharbrackleft}{\isacharunderscore}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+\ satisfiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}mf{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharbrackleft}{\isacharunderscore}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isacharbrackright}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
 \ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}\isanewline
 \isacommand{abbreviation}\isamarkupfalse%
-\ countersatisfiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}mf{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharbrackleft}{\isacharunderscore}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ \ case\ {\isasymphi}\ of\ \isanewline
+\ countersatisfiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}mf{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharbrackleft}{\isacharunderscore}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isacharbrackright}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ \ case\ {\isasymphi}\ of\ \isanewline
 \ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}\isanewline
 \isacommand{abbreviation}\isamarkupfalse%
-\ invalid\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}mf{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharbrackleft}{\isacharunderscore}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+\ invalid\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}mf{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharbrackleft}{\isacharunderscore}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isacharbrackright}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
 \ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}%
@@
 \isacommand{lemma}\isamarkupfalse%
-\ necessitationF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}\ {\isasymlongrightarrow}\ {\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ necessitationP{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}\ {\isasymlongrightarrow}\ {\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ necessitationF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}\ {\isasymlongrightarrow}\ {\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ necessitationP{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}\ {\isasymlongrightarrow}\ {\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
   Moreover, it defines  \isa{{\isasymphi}} to hold only in world i3 and it suggests i3 as the actual 
-  world in which to evaluate the conjecture formula. This countermodel is clearly not minimal.%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ modalCollapseF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+  world in which to evaluate the conjecture formula. This countermodel is not minimal.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ modalCollapseF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ modalCollapseP{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ modalCollapseP{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isa{{\isasymbox}} could have been modeled by employing an equivalence relation \isa{r} in a 
- guarding clause. This has been done in previous work. In a simpler, alternative approach we omitted 
+ guarding clause. This has been done in previous work. In a simpler, alternative approach we omit 
  this clause here (since all worlds are reachable from any world in an equivalence relation). The 
  following lemmata, which check various conditions for S5,  ensure that we have indeed 
- modeled S5 correctly.%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ axiom{\isacharunderscore}T{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ axiom{\isacharunderscore}T{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ axiom{\isacharunderscore}B{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ axiom{\isacharunderscore}B{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ axiom{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+ obtain a correct modeling of S5.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}T{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}T{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}B{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}B{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ axiom{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ axiom{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ axiom{\isacharunderscore}D{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ axiom{\isacharunderscore}D{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ axiom{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ axiom{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ test{\isacharunderscore}A{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ test{\isacharunderscore}A{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ test{\isacharunderscore}B{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ axiom{\isacharunderscore}D{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}D{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ axiom{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}A{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}A{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}B{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ test{\isacharunderscore}B{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ test{\isacharunderscore}B{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ test{\isacharunderscore}C{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ test{\isacharunderscore}C{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ test{\isacharunderscore}C{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ test{\isacharunderscore}C{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ test{\isacharunderscore}D{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ test{\isacharunderscore}D{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ test{\isacharunderscore}D{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ test{\isacharunderscore}D{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymexists}X{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup P{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup F{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup T{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup E{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymexists}X{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup F{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup P{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup T{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup E{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\ {\isachardoublequoteopen}{\isasymexists}X{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X\isactrlsup P\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X\isactrlsup F{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X\isactrlsup T{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X\isactrlsup E{\isacharparenright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymexists}X{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ X\isactrlsup F\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ X\isactrlsup P{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ X\isactrlsup T{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ X\isactrlsup E{\isacharparenright}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymexists}X{\isachardot}\ {\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%
+\ {\isachardoublequoteopen}{\isasymexists}X{\isachardot}\ {\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X\isactrlsup P{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ {\isacharparenleft}X\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%
+\ {\isachardoublequoteopen}{\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X\isactrlsup P{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isanewline
+\isanewline
 \isacommand{lemma}\isamarkupfalse%
@@
 \endisadelimproof
+\isanewline
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ \isactrlbold {\isasymexists}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ \isactrlbold {\isasymforall}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
 %
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymchi}\isactrlsup P{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymchi}\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymchi}\isactrlsup P{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymchi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup P\ {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup P{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup P\ {\isasymequiv}\ {\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P\ \isactrlbold {\isasymequiv}\ {\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P\ \isactrlbold {\isasymequiv}\ {\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P\ \isactrlbold {\isasymequiv}\ {\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ ordinaryObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}O{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}O{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}x{\isachardot}\ \isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isachardoublequoteclose}%
+\ ordinaryObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}O{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}O{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}x{\isachardot}\ \isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isachardoublequoteclose}%
 \begin{isamarkuptext}%
@@
 \isacommand{abbreviation}\isamarkupfalse%
-\ abstractObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}A{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}A{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}x{\isachardot}\ \isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-Identity \isa{{\isacharequal}\isactrlsub e} is defined as .... Subsequenty, the infix operator \isa{{\isacharequal}\isactrlsub E} is 
- introduced.%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ identity{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}{\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isacharequal}\isactrlsub e{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isacharequal}\isactrlsub e\ {\isasymequiv}\ \isanewline
-\ \ \isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ {\isacharparenleft}{\isasymlparr}O{\isacharbang}{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ {\isasymlparr}O{\isacharbang}{\isacharcomma}y\isactrlsup T{\isasymrparr}{\isacharparenright}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymforall}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isasymlparr}F\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymequiv}\ {\isasymlparr}F\isactrlsup T{\isacharcomma}y\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ identityE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}{\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isacharequal}\isactrlsub E{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}x\ \isactrlbold {\isacharequal}\isactrlsub E\ y\ {\isasymequiv}\ {\isasymlparr}\isactrlbold {\isacharequal}\isactrlsub e{\isacharcomma}x{\isacharcomma}y{\isasymrparr}{\isachardoublequoteclose}%
-\isamarkupsection{Further Test Examples%
+\ abstractObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}A{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}A{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}x{\isachardot}\ \isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+Identity relations \isa{\isactrlbold {\isacharequal}\isactrlsub E} and \isa{\isactrlbold {\isacharequal}} are introduced.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{abbreviation}\isamarkupfalse%
+\ identityE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isacharequal}\isactrlsub E{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}x\ \isactrlbold {\isacharequal}\isactrlsub E\ y\ {\isasymequiv}\ {\isasymlparr}O{\isacharbang}{\isacharcomma}x{\isasymrparr}\ \isactrlbold {\isasymand}\ {\isasymlparr}O{\isacharbang}{\isacharcomma}y{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymforall}F{\isachardot}\ {\isasymlparr}F\isactrlsup T{\isacharcomma}x{\isasymrparr}\ \isactrlbold {\isasymequiv}\ {\isasymlparr}F\isactrlsup T{\isacharcomma}y{\isasymrparr}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isacommand{abbreviation}\isamarkupfalse%
+\ identity{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isacharequal}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}x\ \isactrlbold {\isacharequal}\ y\ {\isasymequiv}\ {\isacharparenleft}x\ \isactrlbold {\isacharequal}\isactrlsub E\ y{\isacharparenright}\ \isactrlbold {\isasymor}\ {\isacharparenleft}{\isasymlparr}A{\isacharbang}{\isacharcomma}x{\isasymrparr}\ \isactrlbold {\isasymand}\ {\isasymlparr}A{\isacharbang}{\isacharcomma}y{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymforall}F{\isachardot}\ {\isasymlbrace}x{\isacharcomma}F\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymequiv}\ {\isasymlbrace}y{\isacharcomma}F\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\isamarkupsubsection{Further Test Examples%
 }
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ \isactrlbold {\isasymexists}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ \isactrlbold {\isasymforall}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}a\isactrlsup T{\isacharparenright}\ \isactrlbold {\isacharequal}\isactrlsub E\ {\isacharparenleft}a\isactrlsup T{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ {\isachardoublequoteopen}{\isacharbrackleft}a\isactrlsup T\ \isactrlbold {\isacharequal}\isactrlsub E\ a\isactrlsup T{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}O{\isacharbang}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\isactrlsup T{\isacharparenright}\ \isactrlbold {\isacharequal}\isactrlsub E\ {\isacharparenleft}a\isactrlsup T{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}O{\isacharbang}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ a\isactrlsup T\ \isactrlbold {\isacharequal}\isactrlsub E\ a\isactrlsup T{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}O{\isacharbang}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}{\isacharparenleft}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isacharparenleft}x\isactrlsup T{\isacharparenright}\ \isactrlbold {\isacharequal}\isactrlsub E\ {\isacharparenleft}a\isactrlsup T{\isacharparenright}{\isacharparenright}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}O{\isacharbang}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ x\isactrlsup T\ \isactrlbold {\isacharequal}\isactrlsub E\ a\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}{\isasymphi}{\isachardot}\ {\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}{\isasymphi}{\isachardot}\ {\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}{\isasymphi}{\isachardot}\ {\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymchi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymchi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isasympsi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymchi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasympsi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymchi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isasympsi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasympsi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasympsi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasympsi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymnot}{\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymnot}{\isasympsi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isasymA}{\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasympsi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isasymA}{\isacharparenleft}{\isasympsi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ \isactrlbold {\isasymnot}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymequiv}\ \isactrlbold {\isasymnot}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isasymA}{\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isasymA}{\isacharparenleft}{\isasympsi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \ \ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ {\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ {\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+A brief check that this axiom is well-formed, i.e. does not return error%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ {\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ {\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isasymnoteq}\ {\isacharasterisk}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
 \isamarkupsubsection{Axioms of Necessity and Actuality%
@@
 \isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymequiv}\ {\isasymA}{\isacharparenleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymequiv}\ {\isasymA}{\isacharparenleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsubsection{Axioms for Descriptions%
+}
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+... here I still run into some problems, need to analyze why both
+ formulas result in errors, check carefully again definition of equality and description ...%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{4}}{\isacharunderscore}Inst{\isacharunderscore}{\isadigit{1}}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}x\isactrlsup T\ \isactrlbold {\isacharequal}\ {\isacharparenleft}{\isasymiota}\ x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymforall}\ z{\isachardot}\ {\isacharparenleft}{\isasymA}{\isasymlparr}R\isactrlsup T{\isacharcomma}z\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}z\isactrlsup T\ \isactrlbold {\isacharequal}\ x\isactrlsup T{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{4}}{\isacharunderscore}Inst{\isacharunderscore}{\isadigit{2}}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}x\isactrlsup T\ \isactrlbold {\isacharequal}\ {\isacharparenleft}{\isasymiota}\ x{\isachardot}\ {\isacharparenleft}{\isasymphi}{\isacharparenleft}x{\isacharparenright}{\isacharparenright}\isactrlsup T{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymforall}\ z{\isachardot}\ {\isacharparenleft}{\isasymA}{\isacharparenleft}{\isacharparenleft}{\isasymphi}{\isacharparenleft}z{\isacharparenright}{\isacharparenright}\isactrlsup T{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}z\isactrlsup T\ \isactrlbold {\isacharequal}\ x\isactrlsup T{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+\isanewline
 \isanewline

### 2015-12-14 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
further improvements, various

@@
   \caption{Grammar of Modal Relational Type Theory. \label{mmrt}
- Note that two kinds of (complex) formulas are introduced: ones that may have encoding subformulas and ones that don’t.
- The latter are designated as propositional formulas, the former ones simply as formulas. }
+  Note that two kinds of (complex) formulas are introduced: ones that may have encoding subformulas and 
+  ones that don’t. The latter are designated as propositional formulas, the former ones simply as formulas. }
   \end{figure}
@@
 \isamarkuptrue%
-\isacommand{typedecl}\isamarkupfalse%
+\ \isacommand{typedecl}\isamarkupfalse%
 \ i\isanewline
-\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
+\ \isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
 \ io\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}i\ {\isasymRightarrow}\ bool{\isacharparenright}{\isachardoublequoteclose}%
@@
 \isamarkuptrue%
-\isacommand{typedecl}\isamarkupfalse%
+\ \isacommand{typedecl}\isamarkupfalse%
 \ e%
@@
   (polymorphic) datatype \isa{{\isacharprime}a\ opt} (where \isa{{\isacharprime}a} is a polymorphic variable in Isabelle) 
- based on four constructors: \isa{ERR\ {\isacharprime}a} (identifies erroneous term constructions), \isa{P\ {\isacharprime}a} (identifies 
- propositional formulas), \isa{F\ {\isacharprime}a} (identifies  formulas), and \isa{T\ {\isacharprime}a} (identifies 
+  based on four constructors: \isa{ERR\ {\isacharprime}a} (identifies erroneous term constructions), \isa{P\ {\isacharprime}a} 
+  (identifies propositional formulas), \isa{F\ {\isacharprime}a} (identifies  formulas), and \isa{T\ {\isacharprime}a} (identifies 
   terms, such as lambda abstractions). The embeddings approach will be suitably adapted below so that 
@@
 \isamarkuptrue%
-\isacommand{datatype}\isamarkupfalse%
+\ \isacommand{datatype}\isamarkupfalse%
 \ {\isacharprime}a\ opt\ {\isacharequal}\ ERR\ {\isacharprime}a\ {\isacharbar}\ P\ {\isacharprime}a\ {\isacharbar}\ F\ {\isacharprime}a\ {\isacharbar}\ T\ {\isacharprime}a%
@@
 \isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ mkP{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup P{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isadigit{0}}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup P\ {\isasymequiv}\ P\ {\isasymphi}{\isachardoublequoteclose}\ \isanewline
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ mkF{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup F{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isadigit{0}}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup F\ {\isasymequiv}\ F\ {\isasymphi}{\isachardoublequoteclose}\ \isanewline
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ mkT{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup T{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isadigit{0}}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup T\ {\isasymequiv}\ T\ {\isasymphi}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ mkE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharunderscore}\isactrlsup E{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isadigit{0}}{\isadigit{9}}{\isacharbrackright}\ {\isadigit{1}}{\isadigit{1}}{\isadigit{0}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup E\ {\isasymequiv}\ ERR\ {\isasymphi}{\isachardoublequoteclose}%
@@
 Some language constructs in the theory of abstract types, e.g. the actuality operator  
- \isa{{\isasymA}} ("it is actually the case that"), refer to a (fixed) given world. To model such a 
+  \isa{\isactrlbold {\isasymA}} ("it is actually the case that"), refer to a (fixed) given world. To model such a 
   global world reference we introduce a
@@
 \isamarkuptrue%
-\isacommand{consts}\isamarkupfalse%
+\ \isacommand{consts}\isamarkupfalse%
 \ cw\ {\isacharcolon}{\isacharcolon}\ i\ \isanewline
-\isacommand{consts}\isamarkupfalse%
+\ \isacommand{consts}\isamarkupfalse%
 \ de{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isachardoublequoteclose}\ dio{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isachardoublequoteclose}\ da{\isacharcolon}{\isacharcolon}{\isacharprime}a%
@@
 \begin{isamarkuptext}%
-The actuality operator \isa{{\isasymA}} when applied to a formula or propositional formula 
+The actuality operator \isa{\isactrlbold {\isasymA}} when applied to a formula or propositional formula 
   \isa{{\isasymphi}} evaluates \isa{{\isasymphi}} wrt the fixed given world \isa{cw}. 
- The compound expression \isa{{\isasymA}\ {\isasymphi}} inherits its syntactical category  \isa{F} (formula) or
+  The compound expression \isa{\isactrlbold {\isasymA}{\isasymphi}} inherits its syntactical category  \isa{F} (formula) or
   \isa{P} (propositional formula from \isa{{\isasymphi}}. If the syntactical catagory of  \isa{{\isasymphi}} is 
- \isa{ERR} (error) or \isa{T} (term), then the syntactical catagory of \isa{{\isasymA}\ {\isasymphi}} 
+  \isa{ERR} (error) or \isa{T} (term), then the syntactical catagory of \isa{\isactrlbold {\isasymA}{\isasymphi}} 
   is \isa{ERR} and a dummy entity of appropriate type is returned. This illustrates the very 
@@
 \isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ {\isasymA}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt\ {\isasymRightarrow}\ io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymA}\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ Actual{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt\ {\isasymRightarrow}\ io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymA}\ {\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{6}}{\isadigit{4}}{\isacharbrackright}\ {\isadigit{6}}{\isadigit{5}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymA}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
 \ \ \ \ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasympsi}\ cw{\isacharparenright}\ {\isacharbar}\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasympsi}\ cw{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
@@
 \isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ Enc{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlbrace}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrbrace}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlbrace}x{\isacharcomma}{\isasymPhi}{\isasymrbrace}\ {\isasymequiv}\ case\ {\isacharparenleft}x{\isacharcomma}{\isasymPhi}{\isacharparenright}\ of\ \isanewline
@@
 \isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ Exe{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isacharparenright}\ of\ \isanewline
@@
 \isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ Exe{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharparenright}\ of\ \isanewline
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ Exe{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharparenright}\ of\ \isanewline
 \ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{1}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{2}}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isadigit{1}}\ y{\isadigit{2}}{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ Exe{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isacharparenright}\ of\ \isanewline
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ Exe{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \ \isanewline
+\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isacharparenright}\ of\ \isanewline
 \ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{1}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{2}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{3}}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isadigit{1}}\ y{\isadigit{2}}\ y{\isadigit{3}}{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
@@
 \isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ not{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{5}}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{5}}{\isadigit{9}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
 \ \ \ \ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}{\isacharparenright}\ {\isacharbar}\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\ \ \isanewline
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ implies{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymrightarrow}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{1}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymphi}{\isacharcomma}{\isasympsi}{\isacharparenright}\ of\ \isanewline
-\ \ \ \ {\isacharparenleft}F{\isacharparenleft}{\isasymalpha}{\isacharparenright}{\isacharcomma}F{\isacharparenleft}{\isasymbeta}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharparenleft}P{\isacharparenleft}{\isasymalpha}{\isacharparenright}{\isacharcomma}P{\isacharparenleft}{\isasymbeta}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
+\ \ \ \ {\isacharparenleft}P{\isacharparenleft}{\isasymalpha}{\isacharparenright}{\isacharcomma}P{\isacharparenleft}{\isasymbeta}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharparenleft}F{\isacharparenleft}{\isasymalpha}{\isacharparenright}{\isacharcomma}F{\isacharparenleft}{\isasymbeta}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\ {\isacharbar}\ \isanewline
+\ \ \ \ {\isacharparenleft}P{\isacharparenleft}{\isasymalpha}{\isacharparenright}{\isacharcomma}F{\isacharparenleft}{\isasymbeta}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharparenleft}F{\isacharparenleft}{\isasymalpha}{\isacharparenright}{\isacharcomma}P{\isacharparenleft}{\isasymbeta}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\ {\isacharbar}\ \isanewline
+\ \ \ \ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
 \begin{isamarkuptext}%
@@
 \isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ forall{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ da{\isacharparenright}\ of\isanewline
-\ \ \ \ F{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ forallBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymforall}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
-%
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ forall{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ da{\isacharparenright}\ of\isanewline
+\ \ \ \ F{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ \isanewline
+\ \ {\isacharbar}\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ forallBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymforall}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
+\isanewline
+\ %
 \isadelimproof
@@
 \isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ box{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymbox}\ {\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{6}}{\isadigit{2}}{\isacharbrackright}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymbox}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ box{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymbox}{\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{6}}{\isadigit{2}}{\isacharbrackright}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymbox}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
 \ \ \ \ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}v{\isachardot}\ {\isasympsi}\ v{\isacharparenright}\ {\isacharbar}\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}v{\isachardot}\ {\isasympsi}\ v{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
@@
 \isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ lam{\isadigit{0}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
@@
 \isanewline
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ lam{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline
 \ \ \ \ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}{\isasymlambda}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasymphi}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}{\isasymlambda}x{\isachardot}\ dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ lamBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ lamBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
+\isanewline
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ lam{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de\ de{\isacharparenright}\ of\isanewline
@@
 \isanewline
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ lam{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de\ de\ de{\isacharparenright}\ of\isanewline
@@
 The Principia Metaphysica supports rigid definite descriptions. Our definition maps
- \isa{{\isasymiota}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} to \isa{{\isacharparenleft}THE\ x{\isachardot}\ {\isasymphi}\ cw{\isacharparenright}}, that is Isabelle's inbuilt description operator THE
+  \isa{\isactrlbold {\isasymiota}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} to \isa{{\isacharparenleft}THE\ x{\isachardot}\ {\isasymphi}\ cw{\isacharparenright}}, that is Isabelle's inbuilt description operator THE
   is utilized and evaluation is rigidly carried out with respect to the current world \isa{cw}.
@@
 \isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ that{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}e\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymiota}{\isachardoublequoteclose}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymiota}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline
-\ \ \ \ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}THE\ x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ cw{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}de{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ thatBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}e\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}{\isasymiota}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymiota}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ {\isasymiota}\ {\isasymphi}{\isachardoublequoteclose}%
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ that{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}e\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymiota}{\isachardoublequoteclose}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymiota}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline
+\ \ \ \ F{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}THE\ x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ F\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ cw{\isacharparenright}\ {\isacharbar}\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}THE\ x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ cw{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}de{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ thatBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}e\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymiota}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymiota}x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymiota}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ \ \ {\isachardoublequoteopen}{\isasymlparr}\ F{\isadigit{1}}\isactrlsup T{\isacharcomma}{\isacharparenleft}\isactrlbold {\isasymiota}x{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}Q{\isadigit{1}}\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isasymrparr}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+\ \ %
+\isamarkupcmt{X is a propositional formula as intended%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
 \isamarkupsection{Further Logical Connectives%
@@
 \isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ conj{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymand}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{3}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlbold {\isasymand}{\isasympsi}\ {\isasymequiv}\ \isactrlbold {\isasymnot}{\isacharparenleft}{\isasymphi}\isactrlbold {\isasymrightarrow}\isactrlbold {\isasymnot}{\isasympsi}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ or{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymor}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{2}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlbold {\isasymor}{\isasympsi}\ {\isasymequiv}\ \isactrlbold {\isasymnot}{\isasymphi}\isactrlbold {\isasymrightarrow}{\isasympsi}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ equivalent{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isasymequiv}{\isachardoublequoteclose}\ {\isadigit{5}}{\isadigit{1}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymphi}\isactrlbold {\isasymequiv}{\isasympsi}\ {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlbold {\isasymrightarrow}{\isasympsi}{\isacharparenright}\isactrlbold {\isasymand}{\isacharparenleft}{\isasympsi}\isactrlbold {\isasymrightarrow}{\isasymphi}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ diamond{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymdiamond}\ {\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{6}}{\isadigit{2}}{\isacharbrackright}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymdiamond}{\isasymphi}\ {\isasymequiv}\ \isactrlbold {\isasymnot}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymphi}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ exists{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymexists}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ da{\isacharparenright}\ of\isanewline
-\ \ \ \ P\ {\isasymphi}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymexists}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ F\ {\isasymphi}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymexists}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ F\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR\ dio{\isachardoublequoteclose}\ \isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ existsBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymexists}\ {\isasymphi}{\isachardoublequoteclose}%
+\ \ \ \ P\ {\isasymphi}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymexists}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ \isanewline
+\ \ {\isacharbar}\ F\ {\isasymphi}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymexists}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ F\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR\ dio{\isachardoublequoteclose}\ \isanewline
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ existsBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymexists}{\isasymphi}{\isachardoublequoteclose}%
 \isamarkupsection{Meta-Logic%
@@
 \isamarkuptrue%
-\isacommand{datatype}\isamarkupfalse%
+\ \isacommand{datatype}\isamarkupfalse%
 \ mf\ {\isacharequal}\ tt\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymtop}{\isachardoublequoteclose}{\isacharparenright}\ {\isacharbar}\ ff\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymbottom}{\isachardoublequoteclose}{\isacharparenright}\ {\isacharbar}\ err\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharasterisk}{\isachardoublequoteclose}{\isacharparenright}%
@@
 \isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ valid\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}mf{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharbrackleft}{\isacharunderscore}{\isacharbrackright}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isacharbrackright}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
-\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
+\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ \isanewline
+\ \ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}\isanewline
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ satisfiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}mf{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharbrackleft}{\isacharunderscore}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isacharbrackright}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
-\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
+\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ \isanewline
+\ \ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}\isanewline
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ countersatisfiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}mf{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharbrackleft}{\isacharunderscore}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isacharbrackright}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ \ case\ {\isasymphi}\ of\ \isanewline
-\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
+\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ \isanewline
+\ \ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}\isanewline
+\ \isacommand{abbreviation}\isamarkupfalse%
 \ invalid\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}mf{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isacharbrackleft}{\isacharunderscore}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{1}}{\isacharbrackright}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
-\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}%
+\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ \isanewline
+\ \ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}%
 \isamarkupsection{Some Basic Tests%
@@
 \isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Question: What are the next two lemmata expected to return? So far they return truth. If that should
+  be disabled (in the definition of implication), the  we might run into a problem with the definition 
+  of \isa{x\ \isactrlbold {\isacharequal}\isactrlsub E\ y} below. Discuss.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
 %
@@
 \isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ necessitationF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}\ {\isasymlongrightarrow}\ {\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ necessitationP{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}\ {\isasymlongrightarrow}\ {\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ modalCollapseF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ modalCollapseP{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ axiom{\isacharunderscore}T{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ axiom{\isacharunderscore}T{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ axiom{\isacharunderscore}B{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ axiom{\isacharunderscore}B{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ axiom{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ axiom{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ axiom{\isacharunderscore}D{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ axiom{\isacharunderscore}D{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ axiom{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ axiom{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ test{\isacharunderscore}A{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ test{\isacharunderscore}A{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ test{\isacharunderscore}B{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ test{\isacharunderscore}B{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ test{\isacharunderscore}C{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ test{\isacharunderscore}C{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ test{\isacharunderscore}D{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ test{\isacharunderscore}D{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}\ {\isasymlongleftrightarrow}\ {\isacharbrackleft}{\isasymphi}\isactrlsup P{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isacharequal}\ {\isasymbottom}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isacharequal}\ {\isasymtop}\ {\isasymlongleftrightarrow}\ {\isacharbrackleft}{\isasymphi}\isactrlsup P{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v\ {\isacharequal}\ {\isasymbottom}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}\ {\isasymlongleftrightarrow}\ {\isacharbrackleft}{\isasymphi}\isactrlsup F{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isacharequal}\ {\isasymbottom}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isacharequal}\ {\isasymtop}\ {\isasymlongleftrightarrow}\ {\isacharbrackleft}{\isasymphi}\isactrlsup F{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v\ {\isacharequal}\ {\isasymbottom}{\isachardoublequoteclose}%
@@
 \begin{isamarkuptext}%
-However, for terms we have%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
+However, for terms we have:%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\ \isacommand{lemma}\isamarkupfalse%
 \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup T{\isacharbrackright}\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup T{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup T{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup T{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
@@
 \isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ {\isachardoublequoteopen}{\isasymexists}X{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X\isactrlsup P\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X\isactrlsup F{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X\isactrlsup T{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X\isactrlsup E{\isacharparenright}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ {\isachardoublequoteopen}{\isasymexists}X{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ X\isactrlsup F\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ X\isactrlsup P{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ X\isactrlsup T{\isacharparenright}\ {\isasymand}\ {\isasymnot}{\isacharparenleft}{\isasymexists}X{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ X\isactrlsup E{\isacharparenright}{\isachardoublequoteclose}%
@@
 \isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
@@
 %
-\begin{isamarkuptext}%
-Todo: ... select, adapt, and explain some of examples below ...%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isamarkupsubsection{Are Priorities Defined Correctly?%
+}
+\isamarkuptrue%
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup P\ {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup P{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup P\ {\isasymequiv}\ {\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\ %
+\isamarkupcmt{Countermodel by Nitpick%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P\ \isactrlbold {\isasymequiv}\ {\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P\ \isactrlbold {\isasymequiv}\ {\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P\ \isactrlbold {\isasymequiv}\ {\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\ %
+\isamarkupcmt{Countermodel by Nitpick%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsection{E!, O!, A! and =E%
+}
+\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+We introduce the distinguished 1-place relation constant: E (read: ‘being concrete’ or ‘concreteness’)%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\ \isacommand{consts}\isamarkupfalse%
+\ E{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+Being ordinary is defined as being possibly concrete.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ ordinaryObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}O{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}O{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}x{\isachardot}\ \isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isachardoublequoteclose}\isanewline
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}O{\isacharbang}\ {\isacharequal}\ X{\isachardoublequoteclose}%
 \isadelimproof
@@
 \ simp\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymexists}X{\isachardot}\ {\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X\isactrlsup P{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-\ %
-\isamarkupcmt{Solution: \isa{{\isacharparenleft}{\isasymlambda}w{\isachardot}\ True{\isacharparenright}\ {\isacharequal}\ X}%
-}
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X\isactrlsup P{\isachardoublequoteclose}%
+\ \ \ \ \ \ \ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isasymlambda}x\ w{\isachardot}\ Ex\ {\isacharparenleft}E\ x{\isacharparenright}{\isacharparenright}\isactrlsup T}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Being abstract is is defined as not possibly being concrete.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ abstractObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}A{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}A{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}x{\isachardot}\ \isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}A{\isacharbang}\ {\isacharequal}\ X{\isachardoublequoteclose}%
 \isadelimproof
@@
 \ simp\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\ \ \ \ \ \ \ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isasymlambda}x\ w{\isachardot}\ {\isasymforall}xa{\isachardot}\ {\isasymnot}\ E\ x\ xa{\isacharparenright}\isactrlsup T}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Identity relations \isa{\isactrlbold {\isacharequal}\isactrlsub E} and \isa{\isactrlbold {\isacharequal}} are introduced.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ identityE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isacharequal}\isactrlsub E{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}x\ \isactrlbold {\isacharequal}\isactrlsub E\ y\ {\isasymequiv}\ \isanewline
+\ \ \ \ {\isasymlparr}O{\isacharbang}{\isacharcomma}x{\isasymrparr}\ \isactrlbold {\isasymand}\ {\isasymlparr}O{\isacharbang}{\isacharcomma}y{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymforall}F{\isachardot}\ {\isasymlparr}F\isactrlsup T{\isacharcomma}x{\isasymrparr}\ \isactrlbold {\isasymequiv}\ {\isasymlparr}F\isactrlsup T{\isacharcomma}y{\isasymrparr}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}a\isactrlsup T\ \isactrlbold {\isacharequal}\isactrlsub E\ a\isactrlsup T\ {\isacharequal}\ X{\isachardoublequoteclose}%
 \isadelimproof
@@
 \ simp\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}R{\isachardot}\ \isactrlbold {\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\ \ \ \ \ \ %
+\isamarkupcmt{X is "\isa{{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymexists}x{\isachardot}\ E\ a\ x{\isacharparenright}\isactrlsup P}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsubsection{Identity on Individuals%
+}
+\isamarkuptrue%
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ identityI{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isacharequal}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}x\ \isactrlbold {\isacharequal}\ y\ {\isasymequiv}\ \isanewline
+\ \ \ \ x\ \isactrlbold {\isacharequal}\isactrlsub E\ y\ \isactrlbold {\isasymor}\ {\isacharparenleft}{\isasymlparr}A{\isacharbang}{\isacharcomma}x{\isasymrparr}\ \isactrlbold {\isasymand}\ {\isasymlparr}A{\isacharbang}{\isacharcomma}y{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymforall}F{\isachardot}\ {\isasymlbrace}x{\isacharcomma}F\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymequiv}\ {\isasymlbrace}y{\isacharcomma}F\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}a\isactrlsup T\ \isactrlbold {\isacharequal}\ a\isactrlsup T\ {\isacharequal}\ X{\isachardoublequoteclose}%
 \isadelimproof
@@
 \ simp\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isasymlambda}w{\isachardot}\ True{\isacharparenright}\isactrlsup F}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymlparr}A{\isacharbang}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ {\isasymlparr}A{\isacharbang}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymforall}F{\isachardot}\ {\isasymlbrace}a\isactrlsup T{\isacharcomma}F\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymequiv}\ {\isasymlbrace}a\isactrlsup T{\isacharcomma}F\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
 \isadelimproof
@@
 \ simp\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}x\ y{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}y\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\ \ \ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}x{\isachardot}\ {\isasymnot}\ E\ a\ x{\isacharparenright}\isactrlsup F}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymlparr}A{\isacharbang}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ {\isasymlparr}A{\isacharbang}{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
 \isadelimproof
@@
 \ simp\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}x{\isachardot}\ {\isasymnot}\ E\ a\ x{\isacharparenright}\isactrlsup P}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}\isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymforall}F{\isachardot}\ {\isasymlbrace}a\isactrlsup T{\isacharcomma}F\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymequiv}\ {\isasymlbrace}a\isactrlsup T{\isacharcomma}F\isactrlsup T{\isasymrbrace}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
 \isadelimproof
@@
 \ simp\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}R{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymforall}R{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isasymlambda}w{\isachardot}\ True{\isacharparenright}\isactrlsup F}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+As intended: the following two lambda-abstractions are not well-formed/eligible 
+  and their evaluation reports in ERR-terms.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ x\isactrlsup T\ \isactrlbold {\isacharequal}\ y\isactrlsup T{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
 \isadelimproof
@@
 \ simp\ \isacommand{oops}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ \isactrlbold {\isasymexists}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ \isactrlbold {\isasymforall}{\isacharparenleft}{\isasymlambda}R{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isamarkupsubsection{Are Priorities Defined Correctly?%
-}
-\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup P\ {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup P{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup P\ {\isasymequiv}\ {\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%
+\ \ \ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isasymlambda}x\ y{\isachardot}\ dio{\isacharparenright}\isactrlsup E}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymlambda}x{\isachardot}\ x\isactrlsup T\ \isactrlbold {\isacharequal}\ y\isactrlsup T{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+\ \ \ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isasymlambda}x{\isachardot}\ dio{\isacharparenright}\isactrlsup E}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isamarkupsubsection{Identitiy on Relations%
+}
+\isamarkuptrue%
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ identityRel{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}\ {\isacharparenleft}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isacharequal}\isactrlsup {\isadigit{1}}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isanewline
+\ \ \ \isakeyword{where}\ {\isachardoublequoteopen}F{\isadigit{1}}\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{1}}\ G{\isadigit{1}}\ {\isasymequiv}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}F{\isadigit{1}}{\isasymrbrace}\ \isactrlbold {\isasymequiv}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}G{\isadigit{1}}{\isasymrbrace}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ identityRel{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}\ {\isacharparenleft}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isacharequal}\isactrlsup {\isadigit{2}}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isanewline
+\ \ \ \isakeyword{where}\ {\isachardoublequoteopen}F{\isadigit{2}}\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{2}}\ G{\isadigit{2}}\ {\isasymequiv}\ \isactrlbold {\isasymforall}x{\isadigit{1}}{\isachardot}{\isacharparenleft}\ \ {\isacharparenleft}\isactrlbold {\isasymlambda}y{\isachardot}{\isasymlparr}F{\isadigit{2}}{\isacharcomma}y\isactrlsup T{\isacharcomma}x{\isadigit{1}}\isactrlsup T{\isasymrparr}{\isacharparenright}\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{1}}\ {\isacharparenleft}\isactrlbold {\isasymlambda}y{\isachardot}{\isasymlparr}G{\isadigit{2}}{\isacharcomma}y\isactrlsup T{\isacharcomma}x{\isadigit{1}}\isactrlsup T{\isasymrparr}{\isacharparenright}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymlambda}y{\isachardot}{\isasymlparr}F{\isadigit{2}}{\isacharcomma}x{\isadigit{1}}\isactrlsup T{\isacharcomma}y\isactrlsup T{\isasymrparr}{\isacharparenright}\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{1}}\ {\isacharparenleft}\isactrlbold {\isasymlambda}y{\isachardot}{\isasymlparr}G{\isadigit{2}}{\isacharcomma}x{\isadigit{1}}\isactrlsup T{\isacharcomma}y\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ identityRel{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}\ {\isacharparenleft}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isacharequal}\isactrlsup {\isadigit{3}}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isanewline
+\ \ \ \isakeyword{where}\ {\isachardoublequoteopen}F{\isadigit{3}}\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{3}}\ G{\isadigit{3}}\ {\isasymequiv}\ \isactrlbold {\isasymforall}x{\isadigit{1}}\ x{\isadigit{2}}{\isachardot}{\isacharparenleft}\ \ {\isacharparenleft}\isactrlbold {\isasymlambda}y{\isachardot}{\isasymlparr}F{\isadigit{3}}{\isacharcomma}y\isactrlsup T{\isacharcomma}x{\isadigit{1}}\isactrlsup T{\isacharcomma}x{\isadigit{2}}\isactrlsup T{\isasymrparr}{\isacharparenright}\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{1}}\ {\isacharparenleft}\isactrlbold {\isasymlambda}y{\isachardot}{\isasymlparr}G{\isadigit{3}}{\isacharcomma}y\isactrlsup T{\isacharcomma}x{\isadigit{1}}\isactrlsup T{\isacharcomma}x{\isadigit{2}}\isactrlsup T{\isasymrparr}{\isacharparenright}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymlambda}y{\isachardot}{\isasymlparr}F{\isadigit{3}}{\isacharcomma}x{\isadigit{1}}\isactrlsup T{\isacharcomma}y\isactrlsup T{\isacharcomma}x{\isadigit{2}}\isactrlsup T{\isasymrparr}{\isacharparenright}\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{1}}\ {\isacharparenleft}\isactrlbold {\isasymlambda}y{\isachardot}{\isasymlparr}G{\isadigit{3}}{\isacharcomma}x{\isadigit{1}}\isactrlsup T{\isacharcomma}y\isactrlsup T{\isacharcomma}x{\isadigit{2}}\isactrlsup T{\isasymrparr}{\isacharparenright}\isanewline
+\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymlambda}y{\isachardot}{\isasymlparr}F{\isadigit{3}}{\isacharcomma}x{\isadigit{1}}\isactrlsup T{\isacharcomma}x{\isadigit{2}}\isactrlsup T{\isacharcomma}y\isactrlsup T{\isasymrparr}{\isacharparenright}\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{1}}\ {\isacharparenleft}\isactrlbold {\isasymlambda}y{\isachardot}{\isasymlparr}G{\isadigit{3}}{\isacharcomma}x{\isadigit{1}}\isactrlsup T{\isacharcomma}x{\isadigit{2}}\isactrlsup T{\isacharcomma}y\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}F{\isadigit{1}}\isactrlsup T\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{1}}\ G{\isadigit{1}}\isactrlsup T\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+\ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}w\ x{\isachardot}\ {\isacharparenleft}F{\isadigit{1}}\ x\ w\ {\isasymlongrightarrow}\ G{\isadigit{1}}\ x\ w{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}G{\isadigit{1}}\ x\ w\ {\isasymlongrightarrow}\ F{\isadigit{1}}\ x\ w{\isacharparenright}{\isacharparenright}\isactrlsup F}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}F{\isadigit{2}}\isactrlsup T\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{2}}\ G{\isadigit{2}}\isactrlsup T\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+\ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isachardot}{\isachardot}{\isachardot}{\isacharparenright}\isactrlsup F}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}F{\isadigit{3}}\isactrlsup T\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{3}}\ G{\isadigit{3}}\isactrlsup T\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+\ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isachardot}{\isachardot}{\isachardot}{\isacharparenright}\isactrlsup F}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymlbrace}x\isactrlsup T{\isacharcomma}F{\isadigit{1}}\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymequiv}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}G{\isadigit{1}}\isactrlsup T{\isasymrbrace}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+\ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isachardot}{\isachardot}{\isachardot}{\isacharparenright}\isactrlsup F}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymlparr}F{\isadigit{1}}\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymequiv}\ {\isasymlparr}G{\isadigit{1}}\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+\ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isachardot}{\isachardot}{\isachardot}{\isacharparenright}\isactrlsup P}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \ \isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymlambda}y{\isachardot}{\isasymlparr}F{\isadigit{2}}\isactrlsup T{\isacharcomma}y\isactrlsup T{\isacharcomma}x{\isadigit{1}}\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+\ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isachardot}{\isachardot}{\isachardot}{\isacharparenright}\isactrlsup T}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \ \isanewline
+\isanewline
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ equalityRel{\isadigit{0}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isacharequal}\isactrlsup {\isadigit{0}}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isanewline
+\ \ \ \isakeyword{where}\ {\isachardoublequoteopen}F{\isadigit{0}}\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{0}}\ G{\isadigit{0}}\ {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymlambda}y\ {\isachardot}\ F{\isadigit{0}}{\isacharparenright}\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{1}}\ {\isacharparenleft}\isactrlbold {\isasymlambda}y{\isachardot}\ G{\isadigit{0}}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}F{\isadigit{1}}\isactrlsup T\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{1}}\ G{\isadigit{1}}\isactrlsup T\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+\ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymforall}w\ x{\isachardot}\ {\isacharparenleft}F{\isadigit{1}}\ x\ w\ {\isasymlongrightarrow}\ G{\isadigit{1}}\ x\ w{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}G{\isadigit{1}}\ x\ w\ {\isasymlongrightarrow}\ F{\isadigit{1}}\ x\ w{\isacharparenright}{\isacharparenright}\isactrlsup F}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+Some further tests:%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}a\isactrlsup T\ \isactrlbold {\isacharequal}\isactrlsub E\ a\isactrlsup T{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P\ \isactrlbold {\isasymequiv}\ {\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P\ \isactrlbold {\isasymequiv}\ {\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymand}\ {\isacharparenleft}{\isasympsi}\isactrlsup P\ \isactrlbold {\isasymequiv}\ {\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isasympsi}\isactrlsup P{\isacharparenright}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\ \isacommand{nitpick}\isamarkupfalse%
-%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\ %
-\isamarkupcmt{Countermodel by Nitpick%
-}
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isamarkupsection{E!, O!, A! and =E%
-}
-\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-We introduce the distinguished 1-place relation constant: E (read: ‘being concrete’ or ‘concreteness’)%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{consts}\isamarkupfalse%
-\ E{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-Being ordinary is defined as being possibly concrete.%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ ordinaryObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}O{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}O{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}x{\isachardot}\ \isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-Being abstract is is defined as not possibly being concrete.%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ abstractObject{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}A{\isacharbang}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}A{\isacharbang}\ {\isasymequiv}\ \isactrlbold {\isasymlambda}x{\isachardot}\ \isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymdiamond}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-Identity relations \isa{\isactrlbold {\isacharequal}\isactrlsub E} and \isa{\isactrlbold {\isacharequal}} are introduced.%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{abbreviation}\isamarkupfalse%
-\ identityE{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isacharequal}\isactrlsub E{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}x\ \isactrlbold {\isacharequal}\isactrlsub E\ y\ {\isasymequiv}\ {\isasymlparr}O{\isacharbang}{\isacharcomma}x{\isasymrparr}\ \isactrlbold {\isasymand}\ {\isasymlparr}O{\isacharbang}{\isacharcomma}y{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymforall}F{\isachardot}\ {\isasymlparr}F\isactrlsup T{\isacharcomma}x{\isasymrparr}\ \isactrlbold {\isasymequiv}\ {\isasymlparr}F\isactrlsup T{\isacharcomma}y{\isasymrparr}{\isacharparenright}{\isachardoublequoteclose}\isanewline
-\isanewline
-\isacommand{abbreviation}\isamarkupfalse%
-\ identity{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{infixl}\ {\isachardoublequoteopen}\isactrlbold {\isacharequal}{\isachardoublequoteclose}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isanewline
-\ \ \isakeyword{where}\ {\isachardoublequoteopen}x\ \isactrlbold {\isacharequal}\ y\ {\isasymequiv}\ {\isacharparenleft}x\ \isactrlbold {\isacharequal}\isactrlsub E\ y{\isacharparenright}\ \isactrlbold {\isasymor}\ {\isacharparenleft}{\isasymlparr}A{\isacharbang}{\isacharcomma}x{\isasymrparr}\ \isactrlbold {\isasymand}\ {\isasymlparr}A{\isacharbang}{\isacharcomma}y{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymbox}{\isacharparenleft}\isactrlbold {\isasymforall}F{\isachardot}\ {\isasymlbrace}x{\isacharcomma}F\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymequiv}\ {\isasymlbrace}y{\isacharcomma}F\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
-\isamarkupsubsection{Further Test Examples%
-}
-\isamarkuptrue%
-%
-\begin{isamarkuptext}%
-Todo: ... select, adapt, and explain some of examples below%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}a\isactrlsup T\ \isactrlbold {\isacharequal}\isactrlsub E\ a\isactrlsup T{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\ \isacommand{nitpick}\isamarkupfalse%
-%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{oops}\isamarkupfalse%
-\ %
-\isamarkupcmt{Countermodel by Nitpick%
-}
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}O{\isacharbang}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ a\isactrlsup T\ \isactrlbold {\isacharequal}\isactrlsub E\ a\isactrlsup T{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}F{\isachardot}\ {\isasymlparr}F\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymequiv}\ {\isasymlparr}F\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymlparr}O{\isacharbang}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ x\isactrlsup T\ \isactrlbold {\isacharequal}\isactrlsub E\ a\isactrlsup T{\isacharcomma}a\isactrlsup T{\isasymrparr}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}F{\isachardot}\ {\isasymlbrace}a\isactrlsup T{\isacharcomma}F\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}{\isasymphi}{\isachardot}\ {\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}{\isasymphi}{\isachardot}\ {\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasympsi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasympsi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasymchi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymnot}{\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymnot}{\isasympsi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ \isactrlbold {\isasymnot}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymequiv}\ \isactrlbold {\isasymnot}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isasymA}{\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isasymA}{\isacharparenleft}{\isasympsi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymA}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isasymA}{\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isasymA}{\isacharparenleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ \isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymA}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ \isactrlbold {\isasymnot}\isactrlbold {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymA}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymequiv}\ \isactrlbold {\isasymnot}\isactrlbold {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymA}{\isacharparenleft}{\isasympsi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasympsi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymA}{\isacharparenleft}{\isasympsi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymA}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ \isactrlbold {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymA}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ \isactrlbold {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymequiv}\ \isactrlbold {\isasymA}{\isacharparenleft}\isactrlbold {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymequiv}\ \isactrlbold {\isasymA}{\isacharparenleft}\isactrlbold {\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \ \ \ \ \ \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymbox}{\isacharparenleft}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \ \ \ \ \ \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ {\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}\isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymdiamond}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymphi}\isactrlsup P{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \ \ \ \ \ \ \ \ \ \isanewline
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ \isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymphi}\isactrlsup F{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
@@
 \isamarkuptrue%
-\isacommand{axiomatization}\isamarkupfalse%
+\ \isacommand{axiomatization}\isamarkupfalse%
 \ \isakeyword{where}\isanewline
-\ \ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ {\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ {\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ \ \ a{\isadigit{3}}{\isadigit{2}}{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ {\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ {\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \begin{isamarkuptext}%
@@
 \isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
+\ \isacommand{lemma}\isamarkupfalse%
 \ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ {\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ {\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isasymnoteq}\ {\isacharasterisk}{\isachardoublequoteclose}%
@@
 \endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}\isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ {\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}\isactrlbold {\isasymexists}x{\isachardot}\ {\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ \isactrlbold {\isasymdiamond}{\isacharparenleft}\isactrlbold {\isasymnot}{\isasymlparr}E\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+\ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isachardot}{\isachardot}{\isachardot}{\isacharparenright}\isactrlsup P}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
 %
@@
 \isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}{\isasymA}{\isacharparenleft}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymequiv}\ {\isasymA}{\isacharparenleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymequiv}\ {\isasymA}{\isacharparenleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ \isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymA}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}\isactrlbold {\isasymA}{\isasymphi}\isactrlsup P{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymA}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymrightarrow}\ \isactrlbold {\isasymbox}\isactrlbold {\isasymA}{\isasymphi}\isactrlsup F{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}P{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P\ \isactrlbold {\isasymequiv}\ \isactrlbold {\isasymA}{\isacharparenleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ a{\isadigit{3}}{\isadigit{3}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F\ \isactrlbold {\isasymequiv}\ \isactrlbold {\isasymA}{\isacharparenleft}\isactrlbold {\isasymbox}{\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \begin{isamarkuptext}%
-... here I still run into some problems, need to analyze why both
- formulas result in errors, check carefully again definition of equality and description ...%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{4}}{\isacharunderscore}Inst{\isacharunderscore}{\isadigit{1}}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}x\isactrlsup T\ \isactrlbold {\isacharequal}\ {\isacharparenleft}{\isasymiota}\ x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymforall}\ z{\isachardot}\ {\isacharparenleft}{\isasymA}{\isasymlparr}R\isactrlsup T{\isacharcomma}z\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}z\isactrlsup T\ \isactrlbold {\isacharequal}\ x\isactrlsup T{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-\isanewline
-\isacommand{lemma}\isamarkupfalse%
-\ a{\isadigit{3}}{\isadigit{4}}{\isacharunderscore}Inst{\isacharunderscore}{\isadigit{2}}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}x\isactrlsup T\ \isactrlbold {\isacharequal}\ {\isacharparenleft}{\isasymiota}\ x{\isachardot}\ {\isacharparenleft}{\isasymphi}{\isacharparenleft}x{\isacharparenright}{\isacharparenright}\isactrlsup T{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymforall}\ z{\isachardot}\ {\isacharparenleft}{\isasymA}{\isacharparenleft}{\isacharparenleft}{\isasymphi}{\isacharparenleft}z{\isacharparenright}{\isacharparenright}\isactrlsup T{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}z\isactrlsup T\ \isactrlbold {\isacharequal}\ x\isactrlsup T{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isacharasterisk}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
-\isanewline
-\isanewline
-\isanewline
+... here I still run into some problems, need to analyze why the simplifier gets stuck both
+  with both formulas ...%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}x\isactrlsup T\ \isactrlbold {\isacharequal}\ {\isacharparenleft}\isactrlbold {\isasymiota}x{\isachardot}{\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+\ \ \ \ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isachardot}{\isachardot}{\isachardot}{\isacharparenright}\isactrlsup F}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymforall}z{\isachardot}\ {\isacharparenleft}\isactrlbold {\isasymA}{\isacharparenleft}{\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}z\isactrlsup T\ \isactrlbold {\isacharequal}\ x\isactrlsup T{\isacharparenright}{\isacharparenright}{\isacharparenright}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+\ \ \ \ %
+\isamarkupcmt{X is \isa{{\isacharparenleft}{\isachardot}{\isachardot}{\isachardot}{\isacharparenright}\isactrlsup F}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+For the following two lemmata the simplifier does not get back.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\isatagproof
 %

### 2015-12-14 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
some text improvements

@@
   \begin{itemize} 
-  \item Can functional type theory, despite the problems as pointed by Zalta and Oppenheimer, 
+  \item Can functional type theory, despite the problems pointed at by Zalta and Oppenheimer, 
    be utilized to encode the Theory of Abstract Objects when following the embeddings approach?
-  \item How elegant and user-friendly is the resulting formalization? In other
-   words, to what extend can Isabelle's  user interface be facilitated to hide 
+  \item How elegant and user-friendly is the resulting formalization? 
+   To what extend can Isabelle's  user interface be facilitated to hide 
    unpleasant technicalities of the (extended) embedding from the user?
@@
   \item Can the reasoners eventually even contribute some new knowledge? 
+  \item Suggestions for improvements in Isabelle? Any particular problems detected in the course 
+  of the study?
   \ldots
@@
   Note that two kinds of (complex) formulas are introduced: ones that may have encoding subformulas and 
-  ones that don’t. The latter are designated as propositional formulas, the former ones simply as formulas. }
+  ones that do not. The latter are designated as propositional formulas, the former ones simply as formulas. }
   \end{figure}
@@
   for each language expression (in the embedded modal relational type theory) the respective datatype 
-  is identified and appropriately propagated. The encapsulated expressions (the polymorphic type \isa{{\isacharprime}a} 
-  will be instantiated below) realize the actual modeling of the logic embedding analogous 
+  is identified and appropriately propagated. The encapsulated expressions  
+  realize the actual modeling of the logic embedding analogous 
   to previous work for modal functional type theory.%
@@
 \begin{isamarkuptext}%
-Some language constructs in the theory of abstract types, e.g. the actuality operator  
+Some language constructs in the Principia Metaphysica, e.g. the actuality operator  
   \isa{\isactrlbold {\isasymA}} ("it is actually the case that"), refer to a (fixed) given world. To model such a 
@@
 Exemplifying formulas \isa{{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{1}}} are noted here as \isa{{\isasymlparr}{\isasymPi}\isactrlsup {\isadigit{1}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymrparr}}.
-  Exemplification yields propositional formulas and never formulas. In the embedding exemplification 
+  Exemplification yields propositional formulas. In the embedding exemplification 
   is identified with predicate application, just as encoding.%
@@
 \begin{isamarkuptext}%
-The Principia Metaphysica supports $n$-ary exemplification constructions. For pragmatical 
-  reasons we consider here the cases only for $n\leq 3$.%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\ \isacommand{abbreviation}\isamarkupfalse%
-\ Exe{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isanewline
+The Principia Metaphysica supports \isa{n}-ary exemplification constructions. For pragmatical 
+  reasons we consider here the cases only for \isa{n{\isasymle}{\isadigit{3}}}.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ Exe{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\isanewline
 \ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharparenright}\ of\ \isanewline
@@
 \ \isacommand{abbreviation}\isamarkupfalse%
-\ Exe{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \ \isanewline
+\ Exe{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isanewline
 \ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isacharparenright}\ of\ \isanewline
@@
 Formations with negation and implication are supported for both, formulas and propositional
-  formulas, and their embeddings are straightforward.%
-\end{isamarkuptext}%
-\isamarkuptrue%
-\ \isacommand{abbreviation}\isamarkupfalse%
-\ not{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ \ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{5}}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{5}}{\isadigit{9}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
+  formulas, and their embeddings are straightforward. In the case of implication the compound formula
+  is a propositional formula only of both subformulas are propositional formulas. If at one is a formula
+  and the other one a (propositional) formula, then the compound formula is a formula. In all other
+  cases an ERR-Formula is returned.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ not{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{5}}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{5}}{\isadigit{9}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymnot}\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline
 \ \ \ \ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}{\isacharparenright}\ {\isacharbar}\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymnot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\ \ \isanewline
@@
 \ \isacommand{abbreviation}\isamarkupfalse%
-\ forallBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymforall}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
+\ forallBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymforall}{\isasymphi}{\isachardoublequoteclose}\isanewline
 \isanewline
@@
   ease theorem proving. In Section \ref{sec:S5} we will actually demonstrate that the expected S5 properties
-  are validated by our modeling of \isa{\isactrlbold {\isasymbox}}.%
+  are validated by our modeling of \isa{\isactrlbold {\isasymbox}}.  \isa{\isactrlbold {\isasymbox}{\isasymphi}} is supported 
+  for formulas  and propositional formulas.%
 \end{isamarkuptext}%
@@
 n-ary lambda abstraction \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}{\isacharcomma}\isactrlbold {\isasymlambda}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}\isactrlsup {\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}}, for $n\geq 0$, is supported in the Principia
-  Metaphysica only for propositional formulas. ... say more about \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}} ... Their embedding is 
+  Metaphysica only over propositional formulas. ... say more about \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}} ... Their embedding is 
   straightforward: \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{0}}} is mapped to identity and \isa{\isactrlbold {\isasymlambda}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}} are mapped to n-ary
   lambda abstractions, that is, \isa{\isactrlbold {\isasymlambda}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} is mapped to \isa{{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} and \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}}
-  to \isa{{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}}.
-  For pragmatical reasons we restrict ourselves here to the cases where $n\leq 0$. Binder notation is
-  introduced for \isa{\isactrlbold {\isasymlambda}} (... unfortuntaley, I don't know yet how this can be achieved as well 
-  for \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}} ...)%
+  to \isa{{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}}, etc.
+  For pragmatical reasons we restrict ourselves here to the cases where $n\leq 3$. Binder notation is
+  introduced for \isa{\isactrlbold {\isasymlambda}} (... unfortuntaley, I don't know yet how binder notation can be 
+  achieved also for \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}} ...
+need to find out.).%
 \end{isamarkuptext}%
@@
 The Principia Metaphysica supports rigid definite descriptions. Our definition maps
-  \isa{\isactrlbold {\isasymiota}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} to \isa{{\isacharparenleft}THE\ x{\isachardot}\ {\isasymphi}\ cw{\isacharparenright}}, that is Isabelle's inbuilt description operator THE
+  \isa{\isactrlbold {\isasymiota}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} to \isa{{\isacharparenleft}THE\ x{\isachardot}\ {\isasymphi}\ cw{\isacharparenright}}, that is Isabelle's inbuilt definite description operator THE
   is utilized and evaluation is rigidly carried out with respect to the current world \isa{cw}.
-  Moreover, application of that is allowed only if the body of \isa{{\isasymPhi}}, computed by clause 
-  \isa{{\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}}, is a propositional formula. In this case a term is returned and otherwise error 
-  reported (for dummy entity \isa{de}). We again introduce binder notation.%
+  Moreover, application of \isa{\isactrlbold {\isasymiota}} to \isa{\isactrlbold {\isasymPhi}} is allowed only if the body of \isa{{\isasymPhi}}, 
+  computed by clause \isa{{\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}}, is a propositional formula. In this case a term is returned 
+  and otherwise an ERR-term is returned. We again introduce binder notation for \isa{\isactrlbold {\isasymiota}}.%
 \end{isamarkuptext}%
@@
   we introduce three truth values \isa{tt},
-  \isa{ff} and \isa{err}, representing truth, falsity and error. These values can also 
-  be noted as \isa{{\isasymtop}}, \isa{{\isasymbottom}} and \isa{{\isacharasterisk}}. We could, of course, also introduce  
-  respective logical connectives for the meta-level, but in our applications so far (see below)
+  \isa{ff} and \isa{err}, representing truth, falsity and error. These values aro also 
+  noted as \isa{{\isasymtop}}, \isa{{\isasymbottom}} and \isa{{\isacharasterisk}}. We could, of course, also introduce  
+  respective logical connectives for the meta-level, but in our applications (see below)
   this was not yet relevant.%
@@
   (for \isa{{\isasymphi}} is valid), \isa{{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t} (\isa{{\isasymphi}} is satisfiability), \isa{{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t}
-  (\isa{{\isasymphi}} is countersatisfiability) and \isa{{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v} (\isa{{\isasymphi}} is invalid).%
+  (\isa{{\isasymphi}} is countersatisfiability) and \isa{{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v} (\isa{{\isasymphi}} is invalid). Actually, so far 
+  we only use validity.%
 \end{isamarkuptext}%
@@
 Question: What are the next two lemmata expected to return? So far they return truth. If that should
-  be disabled (in the definition of implication), the  we might run into a problem with the definition 
-  of \isa{x\ \isactrlbold {\isacharequal}\isactrlsub E\ y} below. Discuss.%
+  be disabled (I guess that should then happen in the definition of implication), then we might run 
+  into a problem with the definition of \isa{x\ \isactrlbold {\isacharequal}\isactrlsub E\ y} below. Discuss.%
 \end{isamarkuptext}%
@@
 \begin{isamarkuptext}%
-The next two lemmata show that necessitation holds for arbitrary formulas 
+The next two lemmata show that neccessitation holds for arbitrary formulas 
   and arbitrary propositional formulas. We present the lemma in both variants.%
@@
 \isa{{\isasymbox}} could have been modeled by employing an equivalence relation \isa{r} in a 
-  guarding clause. This has been done in previous work. In a simpler, alternative approach we omit 
-  this clause here (since all worlds are reachable from any world in an equivalence relation). The 
-  following lemmata, which check various conditions for S5,  ensure that we have indeed 
+  guarding clause. This has been done in previous work. Our alternative, simpler definition of 
+  \isa{{\isasymbox}} above omits
+  this clause (since all worlds are reachable from any world in an equivalence relation). The 
+  following lemmata, which check various conditions for S5, confirm that we have indeed 
   obtain a correct modeling of S5.%
@@
 %
-\isamarkupsubsection{Testing for the Correct Propagation of Syntactical Category Information%
+\isamarkupsubsection{Testing the Propagation of Syntactical Category Information%
 }
@@
 \isamarkuptrue%
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isasymlparr}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharcomma}a\isactrlsup T{\isasymrparr}\ {\isacharequal}\ X{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+\ \ \ \ \ %
+\isamarkupcmt{X is \isa{dio\isactrlsup E}%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
 %

### 2015-12-14 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
exemplification and encoding are now primitive

@@
 \ \isacommand{consts}\isamarkupfalse%
-\ de{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isachardoublequoteclose}\ dio{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isachardoublequoteclose}\ da{\isacharcolon}{\isacharcolon}{\isacharprime}a%
+\ de{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isachardoublequoteclose}\ dio{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io{\isachardoublequoteclose}\ deio{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isasymRightarrow}io{\isachardoublequoteclose}\ da{\isacharcolon}{\isacharcolon}{\isacharprime}a%
 \isamarkupsection{Embedding of Modal Relational Type Theory%
@@
 \begin{isamarkuptext}%
-The Principia Metaphysica distinguishes between encoding and exemplifying, ... say more ...
+The Principia Metaphysica distinguishes between encoding \isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymPi}\isactrlsup {\isadigit{1}}} and 
+  exemplifying  \isa{{\isasymPi}\isactrlsup n{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isachardot}{\isachardot}{\isacharcomma}{\isasymkappa}\isactrlsub n}.
+...
+say more ...
+  Exemplification is supported here only for  \isa{{\isadigit{1}}{\isasymle}n{\isasymle}{\isadigit{3}}}.
 
-  Encoding \isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymPi}\isactrlsup {\isadigit{1}}} is noted here as \isa{{\isasymlbrace}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymrbrace}}.
-  Encoding yields formulas and never propositional formulas. In the embedding encoding 
-  is identified with predicate application.%
+  First we introduce the following primitive constants. These basic primitives are employed 
+  below in the definition of our type-raised (to \isa{{\isacharprime}a\ opt}-types) operations  
+  \isa{{\isasymlbrace}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymrbrace}} (for encoding) and  \isa{{\isasymlparr}{\isasymPi}\isactrlsup {\isadigit{1}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymrparr}}, \isa{{\isasymlparr}{\isasymPi}\isactrlsup {\isadigit{2}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{2}}{\isasymrparr}} and \isa{{\isasymlparr}{\isasymPi}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{2}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{3}}{\isasymrparr}}
+  (for exemplification).%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\ \isacommand{consts}\isamarkupfalse%
+\ enc{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}{\isasymRightarrow}io{\isachardoublequoteclose}\isanewline
+\ \isacommand{consts}\isamarkupfalse%
+\ exe{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}{\isasymRightarrow}e{\isasymRightarrow}io{\isachardoublequoteclose}\isanewline
+\ \isacommand{consts}\isamarkupfalse%
+\ exe{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isachardoublequoteclose}\ \isanewline
+\ \isacommand{consts}\isamarkupfalse%
+\ exe{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+Encoding \isa{{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymPi}\isactrlsup {\isadigit{1}}} is noted below as \isa{{\isasymlbrace}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isacharcomma}{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymrbrace}}.
+  Encoding yields formulas and never propositional formulas.%
 \end{isamarkuptext}%
@@
 \ Enc{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlbrace}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrbrace}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlbrace}x{\isacharcomma}{\isasymPhi}{\isasymrbrace}\ {\isasymequiv}\ case\ {\isacharparenleft}x{\isacharcomma}{\isasymPhi}{\isacharparenright}\ of\ \isanewline
-\ \ \ \ {\isacharparenleft}T{\isacharparenleft}y{\isacharparenright}{\isacharcomma}T{\isacharparenleft}Q{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
+\ \ \ \ {\isacharparenleft}T{\isacharparenleft}y{\isacharparenright}{\isacharcomma}T{\isacharparenleft}Q{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}enc\ y\ Q{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
 \begin{isamarkuptext}%
 Exemplifying formulas \isa{{\isasymPi}\isactrlsup {\isadigit{1}}{\isasymkappa}\isactrlsub {\isadigit{1}}} are noted here as \isa{{\isasymlparr}{\isasymPi}\isactrlsup {\isadigit{1}}{\isacharcomma}{\isasymkappa}\isactrlsub {\isadigit{1}}{\isasymrparr}}.
-  Exemplification yields propositional formulas. In the embedding exemplification 
-  is identified with predicate application, just as encoding.%
+  Exemplification yields propositional formulas.%
 \end{isamarkuptext}%
@@
 \ Exe{\isadigit{1}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isacharparenright}\ of\ \isanewline
-\ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
-\begin{isamarkuptext}%
-The Principia Metaphysica supports \isa{n}-ary exemplification constructions. For pragmatical 
-  reasons we consider here the cases only for \isa{n{\isasymle}{\isadigit{3}}}.%
+\ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}exe{\isadigit{1}}\ Q\ y{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
+\begin{isamarkuptext}%
+The Principia Metaphysica supports \isa{n}-ary exemplification constructions. 
+  We support the cases for \isa{{\isadigit{1}}{\isasymle}n{\isasymle}{\isadigit{3}}}.%
 \end{isamarkuptext}%
@@
 \ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharparenright}\ of\ \isanewline
-\ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{1}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{2}}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isadigit{1}}\ y{\isadigit{2}}{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{1}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{2}}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}exe{\isadigit{2}}\ Q\ y{\isadigit{1}}\ y{\isadigit{2}}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
 \ \isacommand{abbreviation}\isamarkupfalse%
@@
 \ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isacharparenright}\ of\ \isanewline
-\ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{1}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{2}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{3}}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isacharparenleft}Q\ y{\isadigit{1}}\ y{\isadigit{2}}\ y{\isadigit{3}}{\isacharparenright}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
+\ \ \ \ {\isacharparenleft}T{\isacharparenleft}Q{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{1}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{2}}{\isacharparenright}{\isacharcomma}T{\isacharparenleft}y{\isadigit{3}}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}exe{\isadigit{3}}\ Q\ y{\isadigit{1}}\ y{\isadigit{2}}\ y{\isadigit{3}}{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%
 \begin{isamarkuptext}%
@@
 \isanewline
-\ %
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
+\ \isacommand{lemma}\isamarkupfalse%
+\ binderTest{\isacharcolon}\ {\isachardoublequoteopen}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymphi}\ x{\isacharparenright}\ {\isacharequal}\ \isactrlbold {\isasymforall}{\isacharparenleft}{\isasymlambda}x{\isachardot}\ {\isasymphi}\ x{\isacharparenright}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{by}\isamarkupfalse%
+\ simp%
 \endisatagproof
@@
   to \isa{{\isacharparenleft}{\isasymlambda}xy{\isachardot}{\isasymphi}{\isacharparenright}}, etc.
-  For pragmatical reasons we restrict ourselves here to the cases where $n\leq 3$. Binder notation is
+  Similar to before, we support only the cases where $n\leq 3$. Binder notation is
   introduced for \isa{\isactrlbold {\isasymlambda}} (... unfortuntaley, I don't know yet how binder notation can be 
-  achieved also for \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}{\isacharcomma}{\isachardot}{\isachardot}{\isachardot}} ...
-need to find out.).%
+  achieved also for \isa{\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{2}}{\isacharcomma}\isactrlbold {\isasymlambda}\isactrlsup {\isadigit{3}}} ... need to find out.).%
 \end{isamarkuptext}%
@@
 \begin{isamarkuptext}%
-Question: What are the next two lemmata expected to return? So far they return truth. If that should
-  be disabled (I guess that should then happen in the definition of implication), then we might run 
-  into a problem with the definition of \isa{x\ \isactrlbold {\isacharequal}\isactrlsub E\ y} below. Discuss.%
+The next two statements are not theorems; Nitpick reports countermodels%
 \end{isamarkuptext}%
@@
 \isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
+\ simp%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\ %
+\isamarkupcmt{Countermodel by Nitpick%
+}
 %
@@
 \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\ \isacommand{nitpick}\isamarkupfalse%
+%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{oops}\isamarkupfalse%
+\ %
+\isamarkupcmt{Countermodel by Nitpick%
+}
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+%
+\begin{isamarkuptext}%
+However, the next two statements are of course valid.%
+\end{isamarkuptext}%
+\isamarkuptrue%
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{done}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{done}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
 %
@@
 \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}F{\isachardot}\ {\isasymlbrace}a\isactrlsup T{\isacharcomma}F\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\isadelimproof
+\ %
+\endisadelimproof
+%
+\isatagproof
+\isacommand{apply}\isamarkupfalse%
+\ simp\ \isacommand{oops}\isamarkupfalse%
+%
+\endisatagproof
+{\isafoldproof}%
+%
+\isadelimproof
+%
+\endisadelimproof
+\isanewline
+\isanewline
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}{\isasymphi}{\isachardot}\ {\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \isanewline
-\isanewline
-\ \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}{\isasymphi}{\isachardot}\ {\isasymphi}\isactrlsup P{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
+\ \isacommand{lemma}\isamarkupfalse%
+\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}{\isasymphi}{\isachardot}\ {\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
 \isadelimproof
@@
 \endisadelimproof
-\isanewline
-\ \isacommand{lemma}\isamarkupfalse%
-\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymexists}{\isasymphi}{\isachardot}\ {\isasymphi}\isactrlsup F{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
-\isadelimproof
-\ %
-\endisadelimproof
-%
-\isatagproof
-\isacommand{apply}\isamarkupfalse%
-\ simp\ \isacommand{by}\isamarkupfalse%
-\ auto%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
+%
+\isamarkupsubsection{Negation of Properties%
+}
+\isamarkuptrue%
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ notProp{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymsim}{\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{5}}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{5}}{\isadigit{9}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymsim}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isasymPhi}\ of\ \isanewline
+\ \ \ \ T{\isacharparenleft}{\isasymPsi}{\isacharparenright}\ {\isasymRightarrow}\ \isactrlbold {\isasymlambda}x{\isachardot}\isactrlbold {\isasymnot}{\isasymlparr}{\isasymPhi}{\isacharcomma}x\isactrlsup T{\isasymrparr}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}deio{\isacharparenright}{\isachardoublequoteclose}%
+\isamarkupsubsection{Individual Constant \isa{\isactrlbold a\isactrlsub V} and Function Term \isa{\isactrlbold a\isactrlsub G}%
+}
+\isamarkuptrue%
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ a{\isacharunderscore}V{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}e\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold a\isactrlsub V{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold a\isactrlsub V\ {\isasymequiv}\ \isactrlbold {\isasymiota}x{\isachardot}\ {\isacharparenleft}{\isasymlparr}A{\isacharbang}{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymforall}F{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}F\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}F\isactrlsup T\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{1}}\ F\isactrlsup T{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
+\isanewline
+\ \isacommand{abbreviation}\isamarkupfalse%
+\ a{\isacharunderscore}G{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold a\isactrlsub {\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{5}}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{5}}{\isadigit{9}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold a\isactrlsub G\ {\isasymequiv}\ \isactrlbold {\isasymiota}x{\isachardot}\ {\isacharparenleft}{\isasymlparr}A{\isacharbang}{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymforall}F{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}F\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymequiv}\ {\isacharparenleft}F\isactrlsup T\ \isactrlbold {\isacharequal}\isactrlsup {\isadigit{1}}\ G{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
 \isamarkupsection{Axioms%
@@
 \isamarkuptrue%
-%
-\isadelimproof
-%
-\endisadelimproof
-%
-\isatagproof
-%
-\endisatagproof
-{\isafoldproof}%
-%
-\isadelimproof
-%
-\endisadelimproof
 %

### 2016-03-01 FreeLogic/Freyd/runIsabelle.sh
added equality part of Scott's theory

@@ -1,0 +1,1 @@
+/Applications/Isabelle2016.app/Isabelle/bin/isabelle build -D .

### 2016-03-20 FreeLogic/Freyd/runIsabelle.sh
some modifications and improvements

@@ -1,1 +1,1 @@
-/Applications/Isabelle2016.app/Isabelle/bin/isabelle build -D .
+/Applications/Isabelle2015.app/Isabelle/bin/isabelle build -D .

### 2016-04-19 FreeLogic/2016-ICMS/runIsabelle.sh
ICMS extended abstract

@@ -1,1 +1,1 @@
-/Applications/Isabelle2015.app/Isabelle/bin/isabelle build -D .
+/Applications/Isabelle2016.app/Isabelle/bin/isabelle build -D .

### 2016-05-28 2016-AFP/runIsabelle.sh
Article for Archive of Formal Proofs added

@@ -1,0 +1,1 @@
+/Applications/Isabelle2014.app/Isabelle/bin/isabelle build -D .

### 2016-07-07 2016-AFP/runIsabelle.sh
update

@@ -1,1 +1,1 @@
-/Applications/Isabelle2014.app/Isabelle/bin/isabelle build -D .
+/Applications/Isabelle2016.app/Isabelle/bin/isabelle build -D .

### 2016-08-17 FreeLogic/2016-ArXiV/paper.tex
paper added

\documentclass{article}
\usepackage{graphicx}
\usepackage{color}
\usepackage{xcolor}

\title{On Foundational Axiomatic Systems for Category Theory}
\author{Christoph Benzm\"uller and Dana Scott}

\begin{document}
\maketitle

\begin{abstract}
Foundational axiomatic systems for category theory are studied. Our novel contributions include
(a) the detection of a previously undiscovered inconsistency in a well known system that has been around for decades, (b) the validation of an alternative system by the second author, and (c) the exploration of novel further alternatives. All of these results were supported by a significant amount of human-computer interaction, in which modern interactive and automated reasoning tools were fruitfully exploited.  
\end{abstract}

\section{Introduction}
The foundational  axiomatic system for category as proposed by Freyd and Scedrov in their 1990 textbook \cite{FreydScedrov90} is either inconsistent or it implies that all morphisms exist. We have detected this novel result by experiments with automated theorem provers.

An alternative foundational axiomatic systems for category theory has been proposed by the second author already in 1967. In a series of experiments in which automated reasoning tools have been exploited within the proof assistant Isabelle/HOL we have been able to formally validate this system. Moreover, by utilising the available reasoning tools in Isabelle/HOL we have been able to explore and validate interesting further alternatives. These novel alternatives form the core of our contribution.

At the conceptual level this paper exemplifies a new style of explorative mathematics which rests on a significant amount of human-machine interaction with integrated interactive-automated theorem proving technology. Many of the experiments we have conducted were such that the required reasoning was too tedious and time-consuming for humans to carry out with highest precision. It is here were cycles of formalisation and experimentation efforts in Isabelle/HOL provided significant support.

To enable our experiments we have exploited a semantical embedding of free logic in classical higher-order logic, which has recently been proposed \cite{ICMS16}.

This paper is structured as follows: \ldots

\section{The Issue with the Axiomatic System Freyd and Scedrov}
The following axiomatic system has been proposed by Freyd and Scedrov \cite{ICMS16}:

\begin{figure} \centering
\colorbox{black!20}{
\includegraphics[width=.6\textwidth]{./Images/FreydScedrov2.png}
}
\caption{(Inconsistent) Basic Definitions of Freyd and Scedrov}
\end{figure}

\begin{itemize}
\item First (incorrect) formalisation: \quad \quad \textcolor{red}{$x \approx y$} \quad := \quad
  \textcolor{blue}{$(E(x) \longleftrightarrow E(y)) \wedge x = y$}
\item Freyd/Scedrov want Kleene-Eq: \quad\textcolor{red}{$x \simeq y$} \quad := \quad  \textcolor{blue}{$(E(x) \vee E(y)) \longrightarrow (E(x) \wedge E(y) \wedge x = y)$}
\end{itemize}

\paragraph{1st Series of Experiments}
\textbf{Parameters:} \textcolor{red}{$\approx$}, at least one undefined map ($\star$), definite
description \\
\textbf{Results A:} Redundancies detected \hfill \textcolor{gray}{(in paper)} \\
\textbf{Results B:} Inconsistency detected \hfill \textcolor{gray}{(after paper writing)}

\paragraph{2nd Series of Experiments}
\textbf{Parameters:} \textcolor{red}{$\simeq$}, no $\star$ ($E$ maybe
empty), no definite
description \\
\textbf{Results C:} Consistent if all maps are defined \hfill \textcolor{gray}{(after paper writing)} \\
\textbf{Results D:} Inconsistent if undefined map(s) exist\hfill \textcolor{gray}{(after paper writing)}

\paragraph{3rd Series of Experiments}
\textbf{Parameters:} Scott's own axioms (\textbf{Identity
and Existence in Intuitionistic Logic}, 1977/79), uses 
non-reflexive equality in (A1) and Kleene Equality elsewhere, no $\star$ ($E$ maybe
empty), no definite
description 
\\
\textbf{Results E:} Consistent if all maps are defined \hfill \textcolor{gray}{(after paper writing)} \\
\textbf{Results F:} Still consistent if undefined map(s) exist\hfill \textcolor{gray}{(after paper writing)}

The latter paper also reported on 
earlier experiments on the system by Freyd and Scedrov. However, these experiments were based on a different notion of equality as assumed by Freyd and

\end{document}

### 2017-02-10 FreeLogic/2017-Journal/article.tex
added

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Exploring Axiom Systems for Category Theory%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
\subtitle{Utilizing a 
 Novel Approach to Automate Free Logic in HOL}

%\titlerunning{Short form of title}        % if too long for running head

\author{Christoph Benzmüller       \and
      Dana Scott 
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{F. Author \at
              first address \\
              Tel.: +123-45-678910\\
              Fax: +123-45-678910\\
              \email{fauthor@example.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           S. Author \at
              second address
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
  % Partiality and undefinedness are prominent challenges in various
  % areas of mathematics and computer science.  Unfortunately, however,
  % modern proof assistant system based on traditional classical or
  % intuitionistic logics provide rather inadequate support for these
  % challenge concepts.  Free logic offers a theoretically appealing
  % solution, but is has been considered as rather unsuited towards
  % practical utilisation.

  % The two main contributions of this article are: (i) A shallow
  % semantical embedding of free logic in classical higher-order logic
  % is presented; this embedding enables the application of higher-order
  % interactive and automated theorem provers (and their integrated
  % subprovers) for the formalisation and verification of free logic
  % theories.  (ii) This approach to automate free logic is exemplarily
  % employed in a selected domain of mathematics: Starting from a
  % generalization of the standard axioms for a monoid we present a
  % stepwise development of various, mutually equivalent foundational
  % axiom systems for category theory. As a side-effect of this work
  % some (minor) issue in a prominent category theory textbook have been
  % revealed.

  A shallow semantical embedding of free logic in classical
  higher-order logic is presented, which enables the off-the-shelf
  application of higher-order interactive and automated theorem
  provers (and their integrated subprovers) for the formalisation and
  verification of free logic theories.  
  Subsequently, this approach is exemplarily employed in a selected domain of
  mathematics: starting from a generalization of the standard axioms
  for a monoid we present a stepwise development of various, mutually
  equivalent foundational axiom systems for category theory. As a
  side-effect of this work some (minor) issue in a prominent category
  theory textbook has been revealed.

\keywords{Free Logic \and Classical Higher-Order Logic \and Category
  Theory \and Interactive and Automated Theorem Proving }
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}
Partiality and undefinedness are prominent challenges in various areas
of mathematics and computer science.  Unfortunately, however, modern
proof assistant systems and automated theorem provers based on
traditional classical or intuitionistic logics provide rather
inadequate support for these challenge concepts.  Free logic offers a
theoretically appealing solution, but is has been considered as rather
unsuited towards practical utilisation.

In this article we show how free logic can be
``implemented'' in any theorem proving system for classical
higher-order logic (HOL) \cite{B5}. The proposed solution employs a
semantic embedding of free (or inclusive logic) in HOL. We present an
exemplary implementation of this idea in the mathematical proof
assistant Isabelle/HOL \cite{NPW02}. Various state-of-the-art
first-order and higher-order automated theorem provers and model
finders are integrated (modulo suitable logic translations) with
Isabelle via the Sledgehammer tool \cite{Sledgehammer}, so that our
solution can be utilized, via Isabelle as foreground system, with a
whole range of other background reasoners. As a result we obtain an
elegant and powerful implementation of an interactive and automated
theorem proving (and model finding) system for free logic.

  The two main contributions of this article are: (i) A shallow
  semantical embedding of free logic in classical higher-order logic
  is presented; this embedding enables the application of higher-order
  interactive and automated theorem provers (and their integrated
  subprovers) for the formalisation and verification of free logic
  theories.  (ii) This approach to automate free logic is exemplarily
  employed in a selected domain of mathematics: Starting from a
  generalization of the standard axioms for a monoid we present a
  stepwise development of various, mutually equivalent foundational
  axiom systems for category theory. As a side-effect of this work
  some (minor) issue in a prominent category theory textbook have been
  revealed.

Partiality and undefinedness are core concepts in various areas of
mathematics.  Modern mathematical proof assistants and theorem proving
systems are often based on traditional classical or intuitionistic
logics and provide rather inadequate support for these challenge
concepts.  Free logic @{cite "sep-logic-free,scott67:exist"}, in
contrast, offers a theoretically and practically appealing
solution. Unfortunately, however, we are not aware of any implemented
and available theorem proving system for free logic.

In this extended abstract we show how free logic can be
``implemented'' in any theorem proving system for classical
higher-order logic (HOL) @{cite "B5"}. The proposed solution employs a
semantic embedding of free (or inclusive logic) in HOL. We present an
exemplary implementation of this idea in the mathematical proof
assistant Isabelle/HOL @{cite "NPW02"}. Various state-of-the-art
first-order and higher-order automated theorem provers and model
finders are integrated (modulo suitable logic translations) with
Isabelle via the Sledgehammer tool @{cite "Sledgehammer"}, so that our
solution can be utilized, via Isabelle as foreground system, with a
whole range of other background reasoners. As a result we obtain an
elegant and powerful implementation of an interactive and automated
theorem proving (and model finding) system for free logic.

To demonstrate the practical relevance of our new system, we present a
stepwise development of axiom systems for category theory by
generalizing the standard axioms for a monoid to a partial composition
operation. Our purpose is not to make or claim any contribution to
category theory but rather to show how formalizations involving the
kind of logic required (free logic) can be validated within modern
proof assistants.

A total of eight different axiom systems is studied. The systems I-VI are shown to 
be equivalent. The axiom system VII slightly modifies axiom system VI to obtain (modulo 
notational transformation) the set of axioms as proposed by  Freyd and Scedrov in their textbook
 ``Categories, Allegories'' @{cite "FreydScedrov90"}, published in 1990; 
see also Subsection \ref{subsec:FreydNotation} where we present their original system.
While the axiom systems I-VI are shown to be  consistent, a constricted inconsistency result is 
obtained for system VII (when encoded in free logic where free variables range over all 
objects): We can prove @{text "(∃x. ❙¬(E x)) ❙→ False"}, where @{text "E"} is the existence predicate. Read this as: If there 
are undefined objects, e.g. the value of an undefined composition @{text "x⋅y"}, then we have falsity.
By contraposition, all objects (and thus all compositions) must exist. But when we assume the latter,
then the axiom system VII essentially reduces categories to monoids.
We note that axiom system V, which avoids this problem, corresponds to a set of axioms proposed 
by Scott @{cite "Scott79"} in the 1970s. The problem can also be avoided by restricting the variables 
in axiom system VII to range only over existing objects and by postulating strictness conditions. 
This gives us axiom system VIII.

Our exploration has been significantly supported by series of experiments in which automated reasoning tools 
have been called from within the proof assistant Isabelle/HOL @{cite "Isabelle"} via the Sledgehammer 
tool @{cite "Sledgehammer"}. Moreover, we have obtained very useful feedback at various stages 
from the model finder Nitpick @{cite "Nitpick"} saving us from making several mistakes.

At the conceptual level this paper exemplifies a new style of explorative mathematics which rests 
on a significant amount of human-machine interaction with integrated interactive-auto\-ma\-ted 
theorem proving technology. The experiments we have conducted are such that the required 
reasoning is often too tedious and time-consuming for humans to be carried out repeatedly with 
highest level of precision. It is here where cycles of formalization and experimentation efforts in 
Isabelle/HOL provided  significant support. Moreover, the technical inconsistency issue for
axiom system VII was discovered by automated theorem provers, which further emphasises the added 
value of automated theorem proving in this area.

To enable our experiments we have exploited an embedding of free logic @{cite "Scott67"} 
in classical higher-order logic, which we have recently presented in a related paper @{cite "C57"}.

We also want to emphasize that this paper has been written entirely within the Isabelle 
framework by utilizing the Isabelle ``build'' tool; cf. @{cite "IsabelleManual2016"}, Section~2. 
It is thus an example of a formally verified mathematical document, where the PDF document as 
presented here has been generated directly from the verified source files mentioned above.
We also note that once the proofs have been mechanically checked, they are generally easy 
to find by hand using paper and pencil.

\section{Section title}
\label{sec:1}
Text with citations \cite{RefB} and \cite{RefJ}.
\subsection{Subsection title}
\label{sec:2}
as required. Don't forget to give each section
and subsection a unique label (see Sect.~\ref{sec:1}).
\paragraph{Paragraph headings} Use paragraph headings as needed.
\begin{equation}
a^2+b^2=c^2
\end{equation}

% For one-column wide figures use
\begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:1}       % Give a unique label
\end{figure}
%
% For two-column wide figures use
\begin{figure*}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[width=0.75\textwidth]{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:2}       % Give a unique label
\end{figure*}
%
% For tables use
\begin{table}
% table caption is above the table
\caption{Please write your table caption here}
\label{tab:1}       % Give a unique label
% For LaTeX tables use
\begin{tabular}{lll}
\hline\noalign{\smallskip}
first & second & third  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
number & number & number \\
number & number & number \\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
\bibliography{bibliography}   % name your BibTeX data base

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{RefJ}
% Format for Journal Reference
Author, Article title, Journal, Volume, page numbers (year)
% Format for books
\bibitem{RefB}
Author, Book title, page numbers. Publisher, place (year)
% etc
\end{thebibliography}

\end{document}
% end of file template.tex

### 2017-02-10 FreeLogic/2017-Journal/article.tex
added

@@
 
-\author{Christoph Benzmüller       \and
+\author{Christoph Benzm\"uller       \and
       Dana Scott 
@@
 
-In this article we show how free logic can be
+In the first part of this article (\S2 and \S3) we show how free logic can be
 ``implemented'' in any theorem proving system for classical
@@
 
-  The two main contributions of this article are: (i) A shallow
-  semantical embedding of free logic in classical higher-order logic
-  is presented; this embedding enables the application of higher-order
-  interactive and automated theorem provers (and their integrated
-  subprovers) for the formalisation and verification of free logic
-  theories.  (ii) This approach to automate free logic is exemplarily
-  employed in a selected domain of mathematics: Starting from a
-  generalization of the standard axioms for a monoid we present a
-  stepwise development of various, mutually equivalent foundational
-  axiom systems for category theory. As a side-effect of this work
-  some (minor) issue in a prominent category theory textbook have been
-  revealed.
+%   The two main contributions of this article are: (i) A shallow
+%   semantical embedding of free logic in classical higher-order logic
+%   is presented; this embedding enables the application of higher-order
+%   interactive and automated theorem provers (and their integrated
+%   subprovers) for the formalisation and verification of free logic
+%   theories.  (ii) This approach to automate free logic is exemplarily
+%   employed in a selected domain of mathematics: Starting from a
+%   generalization of the standard axioms for a monoid we present a
+%   stepwise development of various, mutually equivalent foundational
+%   axiom systems for category theory. As a side-effect of this work
+%   some (minor) issue in a prominent category theory textbook have been
+%   revealed.
 
-Partiality and undefinedness are core concepts in various areas of
-mathematics.  Modern mathematical proof assistants and theorem proving
-systems are often based on traditional classical or intuitionistic
-logics and provide rather inadequate support for these challenge
-concepts.  Free logic @{cite "sep-logic-free,scott67:exist"}, in
-contrast, offers a theoretically and practically appealing
-solution. Unfortunately, however, we are not aware of any implemented
-and available theorem proving system for free logic.
+% Partiality and undefinedness are core concepts in various areas of
+% mathematics.  Modern mathematical proof assistants and theorem proving
+% systems are often based on traditional classical or intuitionistic
+% logics and provide rather inadequate support for these challenge
+% concepts.  Free logic @{cite "sep-logic-free,scott67:exist"}, in
+% contrast, offers a theoretically and practically appealing
+% solution. Unfortunately, however, we are not aware of any implemented
+% and available theorem proving system for free logic.
 
-In this extended abstract we show how free logic can be
-``implemented'' in any theorem proving system for classical
-higher-order logic (HOL) @{cite "B5"}. The proposed solution employs a
-semantic embedding of free (or inclusive logic) in HOL. We present an
-exemplary implementation of this idea in the mathematical proof
-assistant Isabelle/HOL @{cite "NPW02"}. Various state-of-the-art
-first-order and higher-order automated theorem provers and model
-finders are integrated (modulo suitable logic translations) with
-Isabelle via the Sledgehammer tool @{cite "Sledgehammer"}, so that our
-solution can be utilized, via Isabelle as foreground system, with a
-whole range of other background reasoners. As a result we obtain an
-elegant and powerful implementation of an interactive and automated
-theorem proving (and model finding) system for free logic.
+% In this extended abstract we show how free logic can be
+% ``implemented'' in any theorem proving system for classical
+% higher-order logic (HOL) @{cite "B5"}. The proposed solution employs a
+% semantic embedding of free (or inclusive logic) in HOL. We present an
+% exemplary implementation of this idea in the mathematical proof
+% assistant Isabelle/HOL @{cite "NPW02"}. Various state-of-the-art
+% first-order and higher-order automated theorem provers and model
+% finders are integrated (modulo suitable logic translations) with
+% Isabelle via the Sledgehammer tool @{cite "Sledgehammer"}, so that our
+% solution can be utilized, via Isabelle as foreground system, with a
+% whole range of other background reasoners. As a result we obtain an
+% elegant and powerful implementation of an interactive and automated
+% theorem proving (and model finding) system for free logic.
 
-To demonstrate the practical relevance of our new system, we present a
-stepwise development of axiom systems for category theory by
-generalizing the standard axioms for a monoid to a partial composition
-operation. Our purpose is not to make or claim any contribution to
-category theory but rather to show how formalizations involving the
-kind of logic required (free logic) can be validated within modern
-proof assistants.
+To demonstrate the practical relevance of our new system, we present,
+in the second part of this article, a stepwise development of axiom
+systems for category theory by generalizing the standard axioms for a
+monoid to a partial composition operation. Our purpose is not to make
+or claim any contribution to category theory but rather to show how
+formalizations involving the kind of logic required (free logic) can
+be validated within modern proof assistants.
 
-A total of eight different axiom systems is studied. The systems I-VI are shown to 
-be equivalent. The axiom system VII slightly modifies axiom system VI to obtain (modulo 
-notational transformation) the set of axioms as proposed by  Freyd and Scedrov in their textbook
- ``Categories, Allegories'' @{cite "FreydScedrov90"}, published in 1990; 
-see also Subsection \ref{subsec:FreydNotation} where we present their original system.
-While the axiom systems I-VI are shown to be  consistent, a constricted inconsistency result is 
-obtained for system VII (when encoded in free logic where free variables range over all 
-objects): We can prove @{text "(∃x. ❙¬(E x)) ❙→ False"}, where @{text "E"} is the existence predicate. Read this as: If there 
-are undefined objects, e.g. the value of an undefined composition @{text "x⋅y"}, then we have falsity.
-By contraposition, all objects (and thus all compositions) must exist. But when we assume the latter,
-then the axiom system VII essentially reduces categories to monoids.
-We note that axiom system V, which avoids this problem, corresponds to a set of axioms proposed 
-by Scott @{cite "Scott79"} in the 1970s. The problem can also be avoided by restricting the variables 
-in axiom system VII to range only over existing objects and by postulating strictness conditions. 
-This gives us axiom system VIII.
+A total of eight different axiom systems is studied. The systems I-VI
+are shown to be equivalent. The axiom system VII slightly modifies
+axiom system VI to obtain (modulo notational transformation) the set
+of axioms as proposed by Freyd and Scedrov in their textbook
+``Categories, Allegories'' \cite{FreydScedrov90}, published in 1990;
+see also Subsection \ref{subsec:FreydNotation} where we present their
+original system.  While the axiom systems I-VI are shown to be
+consistent, a constricted inconsistency result is obtained for system
+VII (when encoded in free logic where free variables range over all
+objects): We can prove $\exists x. \neg(E x) \rightarrow False$, where
+$E$ is the existence predicate. Read this as: If there are undefined
+objects, e.g. the value of an undefined composition $x\cdot y$
+then we have falsity.  By contraposition, all objects (and thus all
+compositions) must exist. But when we assume the latter, then the
+axiom system VII essentially reduces categories to monoids.  We note
+that axiom system V, which avoids this problem, corresponds to a set
+of axioms proposed by Scott @{cite "Scott79"} in the 1970s. The
+problem can also be avoided by restricting the variables in axiom
+system VII to range only over existing objects and by postulating
+strictness conditions.  This gives us axiom system VIII.
 
@@
 
-To enable our experiments we have exploited an embedding of free logic @{cite "Scott67"} 
-in classical higher-order logic, which we have recently presented in a related paper @{cite "C57"}.
+The content of article is combines, extends and clarifies the
+contributions reported in two previous papers \cite{ICMS,ArXiv}.
 
-We also want to emphasize that this paper has been written entirely within the Isabelle 
-framework by utilizing the Isabelle ``build'' tool; cf. @{cite "IsabelleManual2016"}, Section~2. 
-It is thus an example of a formally verified mathematical document, where the PDF document as 
-presented here has been generated directly from the verified source files mentioned above.
-We also note that once the proofs have been mechanically checked, they are generally easy 
-to find by hand using paper and pencil.
+% To enable our experiments we have exploited an embedding of free logic @{cite "Scott67"} 
+% in classical higher-order logic, which we have recently presented in a related paper @{cite "C57"}.
+
+% We also want to emphasize that this paper has been written entirely within the Isabelle 
+% framework by utilizing the Isabelle ``build'' tool; cf. @{cite "IsabelleManual2016"}, Section~2. 
+% It is thus an example of a formally verified mathematical document, where the PDF document as 
+% presented here has been generated directly from the verified source files mentioned above.
+% We also note that once the proofs have been mechanically checked, they are generally easy 
+% to find by hand using paper and pencil.
+
+\section{Preliminaries}
+\label{sec:preliminaries}
+\subsection{Free Logic}
+Free logic \cite{Lambert60,Scottt} refers to a class of logic
+formalisms that are free of basic existence assumptions regarding the
+denotation of terms. Remember that terms in e.g. traditional classical
+and intuitionistic predicate logics always denote an object in a given
+(non-empty) domain $D$, which also serves as the domain of
+quantification, that is, the set of objects the existential and
+universal quantifiers of the logic range over. In free logic these
+basic assumption are abolished. Terms do still denote objects in a
+(non-empty) domain $D$, but a (possibly empty) set $E\subseteq D$ is
+added to characterize the subdomain of ``existing'' resp. ``defined''
+objects in $D$. Quantification, in contrast to traditional logics, now
+ranges over this set $E$ of existing/defined objects only. It is
+obvious how this helps to model undefideness and partiality:
+problematic terms, such as $1/0$, still denote, but they refer to
+undefined objects, that is, objects $d$ in $D\setminus E$ lying
+outside of the scope of quantification.
 
@@
 
-% Non-BibTeX users please use
-\begin{thebibliography}{}
-%
-% and use \bibitem to create references. Consult the Instructions
-% for authors for reference list style.
-%
-\bibitem{RefJ}
-% Format for Journal Reference
-Author, Article title, Journal, Volume, page numbers (year)
-% Format for books
-\bibitem{RefB}
-Author, Book title, page numbers. Publisher, place (year)
-% etc
-\end{thebibliography}
+% % Non-BibTeX users please use
+% \begin{thebibliography}{}
+% %
+% % and use \bibitem to create references. Consult the Instructions
+% % for authors for reference list style.
+% %
+% \bibitem{RefJ}
+% % Format for Journal Reference
+% Author, Article title, Journal, Volume, page numbers (year)
+% % Format for books
+% \bibitem{RefB}
+% Author, Book title, page numbers. Publisher, place (year)
+% % etc
+% \end{thebibliography}
 

### 2017-02-14 FreeLogic/2017-Journal/article.tex
update

@@
 %
-\usepackage{graphicx}
+\usepackage{graphicx,tikz}
 %
@@
 %
+
+\def\D{\mathbf{D}}
+\def\E{\mathbf{E}}
+
+\def\FFOL{\mathit{FFOL}}
+\def\V{\mathit{V}}
+\def\F{\mathit{F}}
+\def\P{\mathit{P}}
+\def\True{\mathit{True}}
+\def\False{\mathit{False}}
+
 \begin{document}
@@
 denotation of terms. Remember that terms in e.g. traditional classical
-and intuitionistic predicate logics always denote an object in a given
-(non-empty) domain $D$, which also serves as the domain of
+and intuitionistic predicate logics always denote an (existing) object
+in a given (non-empty) domain $\D$, which also serves as the domain of
 quantification, that is, the set of objects the existential and
@@
 basic assumption are abolished. Terms do still denote objects in a
-(non-empty) domain $D$, but a (possibly empty) set $E\subseteq D$ is
-added to characterize the subdomain of ``existing'' resp. ``defined''
-objects in $D$. Quantification, in contrast to traditional logics, now
-ranges over this set $E$ of existing/defined objects only. It is
-obvious how this helps to model undefideness and partiality:
-problematic terms, such as $1/0$, still denote, but they refer to
-undefined objects, that is, objects $d$ in $D\setminus E$ lying
-outside of the scope of quantification.
+(non-empty) domain $\D$, but a (possibly empty) set $\E\subseteq \D$ is
+chosen to characterize the subdomain of ``existing'' resp. ``defined''
+objects in $\D$. Quantification, in contrast to traditional logics, is
+now restricted to this set $\E$ of existing/defined objects only. It is
+obvious how this can be used to model undefideness and partiality:
+problematic terms, e.g. division by zero or improper definite
+descriptions, still denote, but they refer to undefined objects, that
+is, objects $d$ in $\D\setminus \E$ lying outside of the scope of
+quantification.
+
+The particular notion of free logic as exploited in the remainder of
+this article has been introduced by Scott \cite{scott67:_exist}.  A graphical
+illustration of this notion of free logic is presented in
+Fig.~\ref{fig1}. It
+employs a distinguished undefined object $\star$.  
+% Free logic (and inclusive logic) has been proposed as an alternative
+% to remedy these shortcomings. It distinguishes between a raw domain of
+% possibly non-existing objects ‹❙D› and a particular subdomain ‹❙E› of ‹❙D›,
+% containing only the ``existing'' entities. Free variables range over ‹❙D›
+% and quantified variables only over ‹❙E›. Each term denotes in ‹❙D› but not
+% necessarily in ‹❙E›. The particular notion of free logic as exploited below has been
+% introduced by Scott @{cite "scott67:_exist"}. A graphical 
+% illustration of this notion of free logic is presented in Fig.~\ref{fig1}.
+\begin{figure}
+\centering
+\newcommand\firstellipse{(2,-5) ellipse (6cm and 4cm)}
+\newcommand\secondellipse{(0,-5.3) ellipse (3.5cm and 2.5cm)}1
+\begin{tikzpicture}
+  \begin{scope}[fill opacity=1]
+    \fill[gray!40] \firstellipse;
+    \fill[gray!10] \secondellipse;
+  \end{scope}
+  \begin{scope}[very thick,font=\large]
+    \draw \firstellipse node[font=\normalsize\bfseries] at (-.5,-5) {\underline{\textbf{E}: existing objects}};
+    \draw \firstellipse node[font=\small] at (-.5,-5.5) {values of bound variables};
+    \draw \secondellipse node[font=\normalsize\bfseries] at (4.3,-2.5) {\underline{\textbf{D}: raw objects}};
+    \draw \secondellipse node[font=\small] at (4.3,-3) {values of free variables};
+  \end{scope}
+  \node[font=\normalsize\bfseries] at (6,-5) {$\star$};
+  \node[font=\normalsize\bfseries] at (6,-5.3) {undefined};
+\end{tikzpicture}
+\caption{Illustration of the Semantical Domains of Free Logic \label{fig1}}
+\end{figure}
+
+\begin{definition}[Syntax of $\FFOL$]
+  Given a denumerable set $\V$ of variable symbols, a denumerable set
+  $\F$ of $n$-ary function symbols ($n\geq 0$), and a denumerable set
+  $\P$ of $n$-ary predicate symbols ($n\geq 0$).
+
+  The terms and formulas of $\FFOL$ are formally defined as the
+  smallest sets such that:
+\begin{enumerate}
+\item each variable $x\in\V$ is a term of $\FFOL$, 
+\item given any $n$-ary ($n\geq 0$) function symbol $f\in\F$ and terms
+  $t_1,\ldots,t_n$ of $\FFOL$, then $f(t_1,\ldots,t_n)$ is a term of $\FFOL$, 
+\item given terms $t_1$ and $t_2$ of $\FFOL$, then $t_1 = t_2$ is an
+  (atomic) formula of $\FFOL$,
+\item given any $n$-ary ($n\geq 0$) predicate symbol $p\in\P$ and terms
+$t_1,\ldots,t_n$ of $\FFOL$, then $p(t_1,\ldots,t_n)$ is an (atomic)
+formula of $\FFOL$, 
+\item given formulas $r$ and $s$ of $\FFOL$, then $\neg r$, $r
+  \rightarrow s$ and $\forall x. r$ are (complex) formulas of $\FFOL$
+\item given a formulas $r$ of $\FFOL$, then $\ x. r$ is a
+  term of $\FFOL$ (definite  description).
+\end{enumerate}
+\end{definition}
+
+Further formulas of $\FFOL$  can be defined as usual.
+
+\begin{definition}[Dual-domain (positive) semantics of $\FFOL$]
+  A model structure for $\FFOL$ consists of a triple
+  $\langle D, E, I\rangle$, where $D$ is a non-empty raw domain of
+  objects, $E\subseteq D$ a possible empty set of ``existing''
+  resp. ``defined'' objects, and $I$ an Interpretation function
+  mapping 0-ary function symbols (constants) to objects $d\in E$, 
+ 0-ary predicate symbols (propositions) to $\True$ or $\False$, 
+  $n$-ary function symbols (for $n\geq 1$) to $n$-ary functions
+  $D \times \ldots \times D \longrightarrow D$ and $n$-ary predicate
+  symbols (for $n\geq 1$) to $n$-ary relations
+  $D \times \ldots \times D$.
+
+  Given an variable assignment $g: \V \longrightarrow D$, we
+  define the interpretation function $\|\cdot\|^{I,g}$ for terms and formulas of
+  $\FFOL$ as follows:
+\begin{enumerate}
+\item $\| x \|^{I,g} = g(x)$ for variable symbols $x$
+  $f\in\F$
+\item $\| c \|^{I,g} = I(c)$, where $c\in\F$ is an 0-ary function
+  symbol
+\item $\| f(t_1,\ldots,t_n)\|^{I,g} = I(f)(\| t_1 \|^{I,g},\ldots,\|
+  t_n \|^{I,g})$, where $f\in\F$ is an $n$-ary ($n\geq 1$) function symbol
+\item $\| p \|^{I,g} = I(p)$, where $p\in\F$ is an 0-ary predicate
+  symbol
+\item $\| t_1 = t_2 \|^{I,g} = \True$ iff $\| t_1 \|^{I,g} = \| t_2
+  \|^{I,g}$ (\footnote{Here we could e.g. require $\| t_1 \|^{I,g} \in E$ and
+  $\| t_2 \|^{I,g} \in E$ as an additional condition.}
+\item $\| p(t_1,\ldots,t_n) \|^{I,g} = \True$ iff $(\| t_1 \|^{I,g},\ldots,\|
+  t_n \|^{I,g}) \in I(p)$ for $n$-ary ($n\geq 1$) predicate symbols
+  $p\in\P$
+\item 
+\end{enumerate}
+\end{definition}
+
+\pagebreak
+\newpage
 

### 2017-02-21 FreeLogic/2017-Journal/article.tex
update

@@
 %
-\usepackage{graphicx,tikz}
+\usepackage{amsmath}
+\usepackage{xspace,stmaryrd,latexsym}
+\usepackage{graphicx,tikz,rotating}
 %
@@
 \def\False{\mathit{False}}
+\def\Impl{\rightarrow}
+\def\Descr{\rotatebox[origin=C]{180}{$\iota$}}
+%\def\Descr{\rotate[c]{180}{\iota}}
+
+% -----------------------------------------------
+
+\def\lambdot{\rule{0.6mm}{0.6mm}\hspace{0.4ex}} 
+\def\all#1{\forall #1\lambdot}
+\def\exi#1{\exists #1\lambdot}
+\def\lam#1{\lambda #1\lambdot}
+
+\def\modal#1{#1}
+\def\mfalse{\modal\bot}
+\def\mtrue{\modal\top}
+\def\mnot{\modal\neg\,}
+\def\mor{\,\modal\vee\,}
+\def\mand{\,\modal\wedge\,}
+\def\mimpl{\,\modal\supset\,}
+\def\miff{\,\modal\Leftrightarrow\,}
+\def\mball#1{\modal\Box_{#1}\,}
+\def\mdexi#1{\modal\Diamond_{#1}\,}
+\def\mall#1{\modal{\forall}{#1}\lambdot\,}
+\def\mexi#1{\modal{\exists}{#1}\lambdot\,}
+\def\mpi{\modal{\Pi}\,}
+\def\mvalid{\modal{\texttt{valid}}}
+
+\def\Metaeq{=}
+\def\bnormform#1{\left.#1\hspace*{-.4ex}\right\downarrow_\beta}
+\def\benormform#1{\left.#1\hspace*{-.4ex}\right\downarrow_{\beta\eta}}
+\def\Bnormform#1{\left.{#1}\hspace*{-.4ex}\right\downarrow_\beta}
+\def\Benormform#1{\left.{#1}\hspace*{-.4ex}\right\downarrow_{\beta\eta}}
+\def\ambnormform#1{{#1}\hspace*{-1.1ex}\downarrow_{\kern-.2em\scriptscriptstyle *}} % ``ambiguous'' normal form
+\def\eqb{\Metaeq_{\beta}}
+\def\eqe{\Metaeq_{\eta}}
+\def\eqbe{\Metaeq_{\beta\eta}}
+\def\convarrow{\rightarrow}
+
+\newcommand\entity[1]{\text{\textrm{#1}}}
+\def\QHL{\entity{QHL}}
+\def\QML{\entity{QML}}
+\def\NOM{\entity{NOM}}
+\def\SVAR{\entity{SVAR}}
+\def\CON{\entity{CON}}
+\def\FVAR{\entity{FVAR}}
+%\def\IC{\entity{IC}}
+\def\FSYM{\entity{FSYM}}
+\def\RSYM{\entity{RSYM}}
+\def\QHLSTT{\entity{QHLSTT}}
+\def\QMLSTT{\entity{QMLSTT}}
+\def\IV{\entity{IV}}
+\def\PV{\entity{PV}}
+\def\SYM{\entity{SYM}}
+\def\IVSTT{\entity{IVSTT}}
+\def\PVSTT{\entity{PVSTT}}
+\def\SYMSTT{\entity{SYMSTT}}
+\def\SSTT{\entity{SSTT}}
+\def\AR{\entity{AR}}
+\def\STT{\entity{STT}\xspace}
+
+\def\QKPIm{\entity{QK}\pi^-\xspace}
+\def\QKPI{\entity{QK}\pi\xspace}
+\def\QKPIp{\entity{QK}\pi^+\xspace}
+\def\QSFPIm{\entity{QS5}\pi^-\xspace}
+\def\QSFPI{\entity{QS5}\pi\xspace}
+\def\QSFPIp{\entity{QS5}\pi^+\xspace}
+
+\def\stt{\entity{STT}\xspace}
+\def\tt{\entity{STT}}
+\def\lm{\entity{MM}\xspace}
+\def\ipl{\entity{IPL}\xspace}
+\def\HOML{\entity{HOML}\xspace}
+\def\HOL{\entity{HOL}\xspace}
+
+\def\worldtype{\mu}
+\def\indtype{\iota}
+\def\mutype{\mu}
+\def\boola{\omicron}
+\def\boolb{\hat{\omicron}}
+
+\def\ar{\shortrightarrow}
+
+\newcommand\hol[1]{\boldsymbol{#1}}
+\newcommand\lift[1]{\lceil #1 \rceil}
+\newcommand\llift[1]{\dot{#1}}
+
+\newcommand{\imp}{\supset}
+\newcommand{\biimp}{\equiv}
+\newcommand{\allq}{\forall}
+\newcommand{\exq}{\exists}
+\newcommand{\seq}{\vdash}
+\newcommand{\nec}{\Box} % necessarily
+\newcommand{\pos}{\Diamond} % possibly
+\newcommand{\ess}[2]{#1 \ \mathit{ess.} \ #2}
+\newcommand{\NE}{\mathit{NE}}
 
@@
 
+The purpose of this article is not claim any novel results in category
+theory, but to demonstrate an elegant way to ``implement'' and utilise
+reasoning in free logic, and to present respective experiments.
+
 \keywords{Free Logic \and Classical Higher-Order Logic \and Category
@@
 
-In the first part of this article (\S2 and \S3) we show how free logic can be
-``implemented'' in any theorem proving system for classical
-higher-order logic (HOL) \cite{B5}. The proposed solution employs a
-semantic embedding of free (or inclusive logic) in HOL. We present an
-exemplary implementation of this idea in the mathematical proof
-assistant Isabelle/HOL \cite{NPW02}. Various state-of-the-art
+In the first part of this article (\S2 and \S3) we show how free logic
+can be elegantly ``implemented'' in any theorem proving system for
+classical higher-order logic (HOL) \cite{B5}. The proposed solution
+employs a semantic embedding of free (or inclusive logic) in HOL. We
+present an exemplary implementation of this idea in the mathematical
+proof assistant Isabelle/HOL \cite{NPW02}. Various state-of-the-art
 first-order and higher-order automated theorem provers and model
@@
 VII (when encoded in free logic where free variables range over all
-objects): We can prove $\exists x. \neg(E x) \rightarrow False$, where
+objects): We can prove $\exists x. \neg(E x) \Impl False$, where
 $E$ is the existence predicate. Read this as: If there are undefined
@@
 and intuitionistic predicate logics always denote an (existing) object
-in a given (non-empty) domain $\D$, which also serves as the domain of
-quantification, that is, the set of objects the existential and
-universal quantifiers of the logic range over. In free logic these
+in a given (non-empty) domain $\D$, and that $\D$ is also exactly the set the
+quantifiers range over. In free logic these
 basic assumption are abolished. Terms do still denote objects in a
@@
 chosen to characterize the subdomain of ``existing'' resp. ``defined''
-objects in $\D$. Quantification, in contrast to traditional logics, is
-now restricted to this set $\E$ of existing/defined objects only. It is
+objects in $\D$. Quantification is
+now restricted to set $\E$ of existing/defined objects only. It is
 obvious how this can be used to model undefideness and partiality:
@@
 The particular notion of free logic as exploited in the remainder of
-this article has been introduced by Scott \cite{scott67:_exist}.  A graphical
+this article has been introduced by Scott \cite{Scott67}.  A graphical
 illustration of this notion of free logic is presented in
@@
 
+We now formally introduce the syntax and semantics of free logic as
+assumed in the remainder of this article. We refer to this logic with $\FFOL$.
+
 \begin{definition}[Syntax of $\FFOL$]
-  Given a denumerable set $\V$ of variable symbols, a denumerable set
+  We start with a denumerable set $\V$ of variable symbols, a denumerable set
   $\F$ of $n$-ary function symbols ($n\geq 0$), and a denumerable set
@@
 \item given formulas $r$ and $s$ of $\FFOL$, then $\neg r$, $r
-  \rightarrow s$ and $\forall x. r$ are (complex) formulas of $\FFOL$
-\item given a formulas $r$ of $\FFOL$, then $\ x. r$ is a
-  term of $\FFOL$ (definite  description).
+  \Impl s$ and $\forall x. r$ are (compound) formulas of $\FFOL$
+\item given a formula $r$ of $\FFOL$, then $\Descr x. r$ is a
+  term of $\FFOL$ (definite  description)
 \end{enumerate}
@@
 
+Regarding the semantics different options may be considered. For
+example, instead of a possible empty set of existing objects $E$, we
+could postulate non-emptiness of $E$. We e.g. also have a choice when
+interpreting equations $t = t$ for undefined terms $t$; such equations
+could be mapped to $\True$ or $\False$. Different combinations of such
+choice points have been studied in the literature. Here we closely
+follow the logic of Scott \cite{Scott67}.
+
 \begin{definition}[Dual-domain (positive) semantics of $\FFOL$]
   A model structure for $\FFOL$ consists of a triple
-  $\langle D, E, I\rangle$, where $D$ is a non-empty raw domain of
+  $\langle D, E, I, \star\rangle$, where $D$ is a non-empty raw domain of
   objects, $E\subseteq D$ a possible empty set of ``existing''
-  resp. ``defined'' objects, and $I$ an Interpretation function
-  mapping 0-ary function symbols (constants) to objects $d\in E$, 
+  resp. ``defined'' objects, and $I$ an interpretation function
+  mapping 0-ary function symbols (constants) to defined objects $d\in E$, 
  0-ary predicate symbols (propositions) to $\True$ or $\False$, 
@@
   symbols (for $n\geq 1$) to $n$-ary relations
-  $D \times \ldots \times D$.
+  $D \times \ldots \times D$. Finally, $\star\in D\setminus E$ is a designated
+  (non-existing/undefined) object.
 
-  Given an variable assignment $g: \V \longrightarrow D$, we
+  Given a variable assignment $g: \V \longrightarrow D$, we
   define the interpretation function $\|\cdot\|^{I,g}$ for terms and formulas of
   $\FFOL$ as follows:
+\noindent
+\begin{description}
+\item{Terms}
 \begin{enumerate}
-\item $\| x \|^{I,g} = g(x)$ for variable symbols $x$
-  $f\in\F$
-\item $\| c \|^{I,g} = I(c)$, where $c\in\F$ is an 0-ary function
-  symbol
+\item $\| x \|^{I,g} = g(x)$ for variable symbols $x\in\F$
+\item $\| c \|^{I,g} = I(c)$, where $c\in\F$ is an 0-ary function symbol
 \item $\| f(t_1,\ldots,t_n)\|^{I,g} = I(f)(\| t_1 \|^{I,g},\ldots,\|
   t_n \|^{I,g})$, where $f\in\F$ is an $n$-ary ($n\geq 1$) function symbol
+\item $\| \Descr x. r \|^{I,g} = d \in E$, such that $\| r
+  \|^{I,g[d/x]} = \True$ and  $\| r
+  \|^{I,g[d'/x]} = \False$ for all $d'\not=d\in E$ (i.e. $d$ is the
+  unique existing object for which $r$ holds); if there is no
+  such $d\in E$, then $\| \Descr x. r \|^{I,g} = \star$
+\end{enumerate}
+
+\item{Formulas}
+\begin{enumerate}
 \item $\| p \|^{I,g} = I(p)$, where $p\in\F$ is an 0-ary predicate
@@
 \item $\| t_1 = t_2 \|^{I,g} = \True$ iff $\| t_1 \|^{I,g} = \| t_2
-  \|^{I,g}$ (\footnote{Here we could e.g. require $\| t_1 \|^{I,g} \in E$ and
-  $\| t_2 \|^{I,g} \in E$ as an additional condition.}
+  \|^{I,g}$ (this implies that equations such as $1/0 = 1/0$ are
+  evaluated to $\True$; however, we have alternative options do define
+  this case: e.g. we could
+  additionally require that $\| t_1 \|^{I,g} \in E$ and
+  $\| t_2 \|^{I,g} \in E$, in which case $1/0 = 1/0$ would be $\False$).
 \item $\| p(t_1,\ldots,t_n) \|^{I,g} = \True$ iff $(\| t_1 \|^{I,g},\ldots,\|
@@
   $p\in\P$
-\item 
+\item $\| \neg r \|^{I,g} = \True$ iff $\| r \|^{I,g} = \False$
+\item $\| r \Impl s \|^{I,g} = \True$ iff $\| r \|^{I,g} = \False$
+  or $\| s \|^{I,g} = \True$
+\item $\| \forall x. r  \|^{I,g} = \True$ iff for all $d \in E$ we
+  have $\|  r  \|^{I,g[d/x]} = \True$ (here $g[d/x]$ denotes the
+  variable assignment that is identical to $g$, except for variable
+  $x$, which is now mapped to object $d$)
+\end{enumerate}
+\end{description}
+
+\end{definition}
+
+\begin{definition}\label{homlvalid}
+  A formula $s_o$ is \emph{true} in model $M$ under assignment $g$ iff
+  $\|s_o\|^{M,g} = T$; this is also denoted as $M,g \models s_o$.  A
+  formula $s_o$ is called \emph{valid} in $M$, which is denoted as
+  $M \models s_o$, iff $M,g \models s_o$ for all assignments
+  $g$. Finally, a formula $s_o$ is called \emph{valid}, which we
+  denote by $\models s_o$, iff $s_o$ is valid for all $M$. Moreover,
+  we write $\Gamma\models \Delta$ (for sets of formulas $\Gamma$ and
+  $\Delta$) iff there is a model $M$ and an assignment $g$ such that
+  $M,g \models s_o$ for all $s_o\in \Gamma$ and $M,g \models t_o$ for
+  at least one $t_o\in \Delta$.
+\end{definition}
+
+\subsection{Classical higher-order logic}
+\HOL is easily obtained from \HOML by removing the modal operator
+$\Box$ from the grammar, and by dropping the set of possible worlds
+$W$ and the accessibility relation $R$ from the definition of a model.
+Nevertheless, we explicitly state the most relevant definitions for
+the particular notion of \HOL as employed in this paper. One reason is
+that we do want to carefully distinguish the \HOL and \HOML languages
+in the remainder (we use boldface fonts for \HOL and standard fonts
+for \HOML). There is also a subtle, but harmless, difference in the
+\HOL language as employed here  in comparison to the standard
+presentation: here three base types are employed, whereas
+usually only two base types are considered. The third base type plays
+a crucial role in our embedding of \HOML in \HOL.
+
+\begin{definition}\label{holtypes}
+  The set $\hol{T}$ of simple types freely generated from a set of
+  basic types $\{\hol{o}, \hol{\mu}, \hol{\iota}\}$ using the function type
+  constructor $\hol{\ar}$. $\hol{o}$ is the type of Booleans,
+  $\hol{\mu}$ is the type of individuals, and type
+  $\hol{\iota}$ is employed as the type of possible worlds below. As
+  before we may avoid parentheses.
+\end{definition}
+
+\begin{definition}\label{holgrammar}
+The grammar for higher-order logic $\HOL$ is:
+\begin{align*} 
+  \hol{s},\hol{t} \quad ::= \quad & \hol{p_\alpha} \mid \hol{X_\alpha} \mid \hol{(\lam{X_\alpha}
+  s_\beta)_{\alpha\ar\beta}} \mid \hol{(s_{\alpha\ar\beta}\, t_\alpha)_\beta} \mid  \hol{\neg_{o\ar o}\, s_o} \mid \\
+  & \hol{(({\vee_{o\ar o\ar o}}\,s_o)\,t_o)} \mid \hol{\forall_{(\alpha\ar
+    o)\ar o}(\lam{X_\alpha} s_o)} 
+\end{align*}
+where $\hol{\alpha},\hol{\beta}\in \hol{T}$. The text from
+Def.~\ref{homlgrammar} analogously applies, except that we do not
+consider the modal  connectives $\hol{\Box}$ and $\hol{\Diamond}$.
+\end{definition}
+
+The definitions for substitution (Def.~\ref{homlsubstitution}), $\beta$- and $\eta$-reduction (Def.~\ref{homlbetaeta}), frame (Def.~\ref{homlframe}), and assignment (Def.~\ref{homlassignment}) remain unchanged.
+
+\begin{definition}\label{holmodel}
+  A \emph{model} for \HOL is a tuple $\hol{M}=\hol{\langle D, I \rangle}$, where
+  $\hol{D}$ is a frame, and $\hol{I}$ is a family of typed interpretation
+  functions mapping constant symbols $\hol{p_\alpha}$ to appropriate
+  elements of $\hol{D_\alpha}$, called the \emph{denotation of $\hol{p_\alpha}$}
+  (the logical connectives $\hol{\neg}$, $\hol{\vee}$, and $\hol{\forall}$ are always
+  given the standard denotations, see below).  Moreover, we assume that the domains
+  $\hol{D_{\alpha\ar\alpha\ar o}}$ contain the respective identity relations.
+\end{definition}
+
+\begin{definition}\label{holvalue}
+  The \emph{value} $\hol{\| s_\alpha\|^{M,g}}$ of a \HOL term
+  $\hol{s_\alpha}$ on a model $\hol{M}=\hol{\langle D, I \rangle}$ under assignment $\hol{g}$ is an element $\hol{d}\in \hol{D_\alpha}$
+  defined in the following way:
+\begin{enumerate}
+\item $\hol{\|p_\alpha\|^{M,g}} = \hol{I(p_\alpha)}$ and $\hol{\|X_\alpha\|^{M,g}} = \hol{g(X_\alpha)}$
+\item $\hol{\|(s_{\alpha\ar\beta}\, t_\alpha)_\beta\|^{M,g}} = \hol{\|s_{\alpha\ar\beta}\|^{M,g}(\|t_\alpha\|^{M,g})}$
+\item $\hol{\|(\lam{X_\alpha}s_\beta)_{\alpha\ar\beta}\|^{M,g}} = $
+  the function $\hol{f}$ from $\hol{D_\alpha}$ to $\hol{D_\beta}$ such
+  that $\hol{f(d)} = \hol{\|s_\beta\|^{M,g[d/X_\alpha]}}$ for all
+  $\hol{d}\in \hol{D_\alpha}$
+\item $\hol{\|(\neg_{o\ar o}\, s_o)_o\|^{M,g}} = \hol{T}$ iff $\hol{\|s_o\|^{M,g}} = \hol{F}$
+\item $\hol{\|(({\vee_{o\ar o\ar o}}\,s_o)\,t_o)_o\|^{M,g}} =
+  \hol{T}$ iff\, $\hol{\|s_o\|^{M,g}} = \hol{T}$ or $\hol{\|t_o\|^{M,g}}
+  = \hol{T}$
+\item $\hol{\|(\forall_{(\alpha\ar o)\ar o}(\lam{X_\alpha}
+    s_o))_o\|^{M,g}} = \hol{T}$ iff for all $\hol{d}\in
+  \hol{D_\alpha}$ we have $\hol{\|s_o\|^{M,g[d/X_\alpha]}} = \hol{T}$
+%\item $\|(\Box_{o\ar o}\, s_o)_o\|^{M,g,w} = T$ iff for all $v \in W$ with $w R v$ we have  $\|s_o\|^{M,g,v}  = T$
 \end{enumerate}
 \end{definition}
+
+\begin{definition}\label{homlhenkinmodel}
+ A model $\hol{M}=\hol{\langle D, I \rangle}$ is called a
+ \emph{standard model} iff for all $\alpha,\beta\in T$ we have
+ $D_{\alpha\ar\beta} = \{ f \mid f : D_\alpha \longrightarrow D_\beta
+ \}$. In a \emph{Henkin model} function spaces are not necessarily
+ full. Instead it is only required that $D_{\alpha\ar\beta}
+ \subseteq \{ f \mid f : D_\alpha \longrightarrow D_\beta \}$ (for all
+ $\alpha,\beta\in T$) and that the valuation function 
+ $\|\cdot\|^{M,g}$ from above is total (i.e., every term denotes). Any standard model is obviously
+ also a Henkin model. We consider Henkin models in the remainder.
+\end{definition}
+
+\begin{definition}\label{homlvalid}
+A formula $s_o$ is \emph{true} in model $M$ 
+under assignment $g$ iff $\|s_o\|^{M,g} = T$; this is also denoted
+as $M,g \models s_o$.  A formula $s_o$ is called \emph{valid} in
+$M$, which is denoted as $M \models s_o$, iff $M,g \models s_o$ for all
+assignments $g$. Finally, a formula $s_o$ is called
+\emph{valid}, which we denote by $\models s_o$, iff $s_o$ is valid for
+all $M$. Moreover, we write $\Gamma\models \Delta$ (for sets of
+ formulas $\Gamma$ and $\Delta$) iff there is a model $M$ and an assignment $g$ such that  
+ $M,g \models s_o$ for all $s_o\in \Gamma$ and $M,g \models t_o$ for at least one $t_o\in \Delta$.
+\end{definition}
+
+% The definition for standard and Henkin models
+% (Def.~\ref{homlhenkinmodel}), and for truth in a model, validity,
+% etc. (Def.~\ref{homlvalid}) are adapted in the obvious way, and we use
+% the notation $\hol{M,g \models s_o}$, $\hol{\models s_o}$, and
+% $\hol{\Gamma \models \Delta}$. As for \HOML, we assume Henkin
+% semantics in the remainder.
+
+\section{Sound and Complete Embedding in HOL}
+Todo ... the embedding in Isabelle/HOL is depicted in 
+figure \ref{pic1}
+
+\begin{figure}[t]
+ \includegraphics[width=\textwidth]{EmbeddingPic}
+ \caption{Isabelle/HOL formalisation of $\FFOL$ in $\HOL$ \label{pic1}}
+\end{figure}
 

### 2017-03-23 FreeLogic/2017-Journal/article.tex
update

@@
 \usepackage{amsmath}
-\usepackage{xspace,stmaryrd,latexsym}
+\usepackage{xspace,stmaryrd,latexsym,url}
 \usepackage{graphicx,tikz,rotating}
+\usepackage[strings]{underscore}
+
 %
@@
 
-\def\D{\mathbf{D}}
-\def\E{\mathbf{E}}
+\def\D{\mathit{D}}
+\def\E{\mathit{E}}
 
@@
 
-\newcommand{\imp}{\supset}
-\newcommand{\biimp}{\equiv}
+\newcommand{\imp}{\longrightarrow}
+\newcommand{\limp}{\longleftarrow}
+\newcommand{\biimp}{\longleftrightarrow}
 \newcommand{\allq}{\forall}
@@
 
+\def\ti{i}
+\def\dom{\textit{dom \/}}
+\def\cod{\textit{cod \/}}
+\def\comp{\cdot}
+\def\kleq{\cong}
+\def\exid{\simeq}
+\def\ddef{:=}
+\def\id{\textit{I\/}}
+\def\ex{\E}
+
 \begin{document}
 
-\title{Exploring Axiom Systems for Category Theory%\thanks{Grants or other notes
-%about the article that should go on the front page should be
-%placed here. General acknowledgments should be placed at the end of the article.}
-}
-\subtitle{Utilizing a 
- Novel Approach to Automate Free Logic in HOL}
+\title{Automating Free Logic in HOL, with an Application in Category Theory\thanks{Mention DFG grants ...}}
+%\title{Free Logic and Axiom Systems for Category Theory in HOL\thanks{Mention DFG grants ...}}
+%\title{Embedding Free Logic and Axiom Systems for Category Theory in HOL\thanks{Mention DFG grants ...}}
+%\subtitle{(And an Exemplary Application in Category Theory)}
 
@@
 
-The purpose of this article is not claim any novel results in category
+The purpose of this article is not to claim any novel results in category
 theory, but to demonstrate an elegant way to ``implement'' and utilise
@@
 formalizations involving the kind of logic required (free logic) can
-be validated within modern proof assistants.
+be implemented and validated within modern proof assistants.
 
@@
 VII (when encoded in free logic where free variables range over all
-objects): We can prove $\exists x. \neg(E x) \Impl False$, where
-$E$ is the existence predicate. Read this as: If there are undefined
+objects): We can prove $\exists x. \neg(\ex x) \Impl False$, where
+$\ex$ is the existence predicate. Read this as: If there are undefined
 objects, e.g. the value of an undefined composition $x\cdot y$
@@
 that axiom system V, which avoids this problem, corresponds to a set
-of axioms proposed by Scott @{cite "Scott79"} in the 1970s. The
+of axioms proposed by Scott \cite{Scott79} in the 1970s. The
 problem can also be avoided by restricting the variables in axiom
@@
 
-Our exploration has been significantly supported by series of experiments in which automated reasoning tools 
-have been called from within the proof assistant Isabelle/HOL @{cite "Isabelle"} via the Sledgehammer 
-tool @{cite "Sledgehammer"}. Moreover, we have obtained very useful feedback at various stages 
-from the model finder Nitpick @{cite "Nitpick"} saving us from making several mistakes.
+Our exploration has been significantly supported by series of
+experiments in which automated reasoning tools have been called from
+within the proof assistant Isabelle/HOL via the
+Sledgehammer tool. Moreover, we have obtained
+very useful feedback at various stages from the model finder Nitpick
+\cite{Nitpick} saving us from making several mistakes.
 
-At the conceptual level this paper exemplifies a new style of explorative mathematics which rests 
-on a significant amount of human-machine interaction with integrated interactive-auto\-ma\-ted 
-theorem proving technology. The experiments we have conducted are such that the required 
-reasoning is often too tedious and time-consuming for humans to be carried out repeatedly with 
-highest level of precision. It is here where cycles of formalization and experimentation efforts in 
-Isabelle/HOL provided  significant support. Moreover, the technical inconsistency issue for
-axiom system VII was discovered by automated theorem provers, which further emphasises the added 
-value of automated theorem proving in this area.
+At the conceptual level this paper exemplifies a new style of
+explorative mathematics which rests on a significant amount of
+human-machine interaction with integrated interactive-auto\-ma\-ted
+theorem proving technology. The experiments we have conducted are such
+that the required reasoning is often too tedious and time-consuming
+for humans to be carried out repeatedly with highest level of
+precision. It is here where cycles of formalization and
+experimentation efforts in Isabelle/HOL provided significant
+support. Moreover, the technical inconsistency issue for axiom system
+VII was discovered by automated theorem provers, which further
+emphasises the added value of automated theorem proving in this area.
 
@@
 \subsection{Free Logic}
-Free logic \cite{Lambert60,Scottt} refers to a class of logic
+Free logic \cite{Lambert60,Scott67,lambert02:_free_logic} refers to a class of logic
 formalisms that are free of basic existence assumptions regarding the
@@
 basic assumption are abolished. Terms do still denote objects in a
-(non-empty) domain $\D$, but a (possibly empty) set $\E\subseteq \D$ is
+(non-empty) domain $\D$, but a (possibly empty) set $\ex\subseteq \D$ is
 chosen to characterize the subdomain of ``existing'' resp. ``defined''
 objects in $\D$. Quantification is
-now restricted to set $\E$ of existing/defined objects only. It is
+now restricted to set $\ex$ of existing/defined objects only. It is
 obvious how this can be used to model undefideness and partiality:
@@
 descriptions, still denote, but they refer to undefined objects, that
-is, objects $d$ in $\D\setminus \E$ lying outside of the scope of
+is, objects $d$ in $\D\setminus \ex$ lying outside of the scope of
 quantification.
@@
 The particular notion of free logic as exploited in the remainder of
-this article has been introduced by Scott \cite{Scott67}.  A graphical
+this article has been proposed by Scott \cite{Scott67}.  A graphical
 illustration of this notion of free logic is presented in
@@
   \begin{scope}[very thick,font=\large]
-    \draw \firstellipse node[font=\normalsize\bfseries] at (-.5,-5) {\underline{\textbf{E}: existing objects}};
+    \draw \firstellipse node[font=\normalsize\bfseries] at (-.5,-5) {\underline{\textbf{$\ex$}: existing objects}};
     \draw \firstellipse node[font=\small] at (-.5,-5.5) {values of bound variables};
@@
 
-  The terms and formulas of $\FFOL$ are formally defined as the
+  The \emph{terms and formulas of $\FFOL$} are formally defined as the
   smallest sets such that:
@@
 
-Further formulas of $\FFOL$  can be defined as usual.
+Further formulas of $\FFOL$, including various defined notions of
+equality, can be introduced as abbreviations.
 
-Regarding the semantics different options may be considered. For
-example, instead of a possible empty set of existing objects $E$, we
-could postulate non-emptiness of $E$. We e.g. also have a choice when
-interpreting equations $t = t$ for undefined terms $t$; such equations
-could be mapped to $\True$ or $\False$. Different combinations of such
-choice points have been studied in the literature. Here we closely
-follow the logic of Scott \cite{Scott67}.
+  \emph{Substitution} of a term $r$ for a variable $x$
+  in a term $s$ is denoted by $[r/x]s$.
 
-\begin{definition}[Dual-domain (positive) semantics of $\FFOL$]
-  A model structure for $\FFOL$ consists of a triple
-  $\langle D, E, I, \star\rangle$, where $D$ is a non-empty raw domain of
-  objects, $E\subseteq D$ a possible empty set of ``existing''
+A \emph{variable assignment} $g$ maps
+variables $x\in V$ to elements in $D$. $g[d/x]$ denotes the
+assignment that is identical to $g$, except for variable $x$, which is
+now mapped to $d$.
+
+Regarding the semantics different options have been proposed in the literature. For
+example, instead of a possible empty set of existing objects $\ex$, we
+could postulate non-emptiness of $\ex$. Here we closely
+follow the notion of free logic as proposed by Scott \cite{Scott67}.
+
+\begin{definition}[Dual-domain semantics of $\FFOL$]
+  A \emph{model structure for $\FFOL$} consists of a triple
+  $\langle D, \ex, I, \star\rangle$, where $D$ is a non-empty raw domain of
+  objects, $\ex\subseteq D$ a possible empty set of ``existing''
   resp. ``defined'' objects, and $I$ an interpretation function
-  mapping 0-ary function symbols (constants) to defined objects $d\in E$, 
+  mapping 0-ary function symbols (constants) to defined objects $d\in \ex$, 
  0-ary predicate symbols (propositions) to $\True$ or $\False$, 
@@
   symbols (for $n\geq 1$) to $n$-ary relations
-  $D \times \ldots \times D$. Finally, $\star\in D\setminus E$ is a designated
+  $D \times \ldots \times D$. Finally, $\star\in D\setminus \ex$ is a designated
   (non-existing/undefined) object.
 
-  Given a variable assignment $g: \V \longrightarrow D$, we
+  Given a variable assignment $g$, we
   define the interpretation function $\|\cdot\|^{I,g}$ for terms and formulas of
@@
 \begin{enumerate}
-\item $\| x \|^{I,g} = g(x)$ for variable symbols $x\in\F$
+\item $\| x \|^{I,g} = g(x)$ for variable symbols $x\in\V$
 \item $\| c \|^{I,g} = I(c)$, where $c\in\F$ is an 0-ary function symbol
@@
   t_n \|^{I,g})$, where $f\in\F$ is an $n$-ary ($n\geq 1$) function symbol
-\item $\| \Descr x. r \|^{I,g} = d \in E$, such that $\| r
+\item $\| \Descr x. r \|^{I,g} = d \in \ex$, such that $\| r
   \|^{I,g[d/x]} = \True$ and  $\| r
-  \|^{I,g[d'/x]} = \False$ for all $d'\not=d\in E$ (i.e. $d$ is the
+  \|^{I,g[d'/x]} = \False$ for all $d'\not=d\in \ex$ (i.e. $d$ is the
   unique existing object for which $r$ holds); if there is no
-  such $d\in E$, then $\| \Descr x. r \|^{I,g} = \star$
+  such $d\in \ex$, then $\| \Descr x. r \|^{I,g} = \star$
 \end{enumerate}
@@
 \item $\| t_1 = t_2 \|^{I,g} = \True$ iff $\| t_1 \|^{I,g} = \| t_2
-  \|^{I,g}$ (this implies that equations such as $1/0 = 1/0$ are
-  evaluated to $\True$; however, we have alternative options do define
-  this case: e.g. we could
-  additionally require that $\| t_1 \|^{I,g} \in E$ and
-  $\| t_2 \|^{I,g} \in E$, in which case $1/0 = 1/0$ would be $\False$).
+  \|^{I,g}$ (this basic notion of primitive equality on $D$ implies that equations such as $1/0 = 1/0$ are
+  evaluated to $\True$; later, in Section \ref{??}, we will
+  define and utilise further notions of equality, including \emph{Kleene equality}
+  and \emph{existing equality}).
 \item $\| p(t_1,\ldots,t_n) \|^{I,g} = \True$ iff $(\| t_1 \|^{I,g},\ldots,\|
@@
   or $\| s \|^{I,g} = \True$
-\item $\| \forall x. r  \|^{I,g} = \True$ iff for all $d \in E$ we
-  have $\|  r  \|^{I,g[d/x]} = \True$ (here $g[d/x]$ denotes the
-  variable assignment that is identical to $g$, except for variable
-  $x$, which is now mapped to object $d$)
+\item $\| \forall x. r  \|^{I,g} = \True$ iff for all $d \in \ex$ we
+  have $\|  r  \|^{I,g[d/x]} = \True$ % (here $g[d/x]$ denotes the
+  % variable assignment that is identical to $g$, except for variable
+  % $x$, which is now mapped to object $d$)
 \end{enumerate}
@@
 
-\subsection{Classical higher-order logic}
-\HOL is easily obtained from \HOML by removing the modal operator
-$\Box$ from the grammar, and by dropping the set of possible worlds
-$W$ and the accessibility relation $R$ from the definition of a model.
-Nevertheless, we explicitly state the most relevant definitions for
-the particular notion of \HOL as employed in this paper. One reason is
-that we do want to carefully distinguish the \HOL and \HOML languages
-in the remainder (we use boldface fonts for \HOL and standard fonts
-for \HOML). There is also a subtle, but harmless, difference in the
-\HOL language as employed here  in comparison to the standard
-presentation: here three base types are employed, whereas
-usually only two base types are considered. The third base type plays
-a crucial role in our embedding of \HOML in \HOL.
+\subsection{Classical Higher-Order Logic}
+Short introduction ... todo.
 
@@
   $\hol{\mu}$ is the type of individuals, and type
-  $\hol{\iota}$ is employed as the type of possible worlds below. As
-  before we may avoid parentheses.
+  $\hol{\iota}$ is employed as the type of possible worlds below. We
+  may avoid parentheses if the structure of a complex type is clear in context.
 \end{definition}
@@
 \begin{definition}\label{holgrammar}
-The grammar for higher-order logic $\HOL$ is:
+The language of higher-order logic $\HOL$ is defined by the following
+grammar:\footnote{Ednote: Maybe better to define this analagous to $\FFOL$.}
 \begin{align*} 
@@
 \end{align*}
-where $\hol{\alpha},\hol{\beta}\in \hol{T}$. The text from
-Def.~\ref{homlgrammar} analogously applies, except that we do not
-consider the modal  connectives $\hol{\Box}$ and $\hol{\Diamond}$.
+where $\hol{\alpha},\hol{\beta}\in \hol{T}$. $p_\alpha$ denotes typed constants and
+$X_\alpha$ typed variables (distinct from $p_\alpha$).  Complex typed
+terms are constructed via abstraction and application. The type of
+each term is given as a subscript.  Terms $s_o$ of type $o$ are called
+formulas.  The logical connectives of choice are
+$\hol{\neg_{o\ar o}}$, $\hol{\vee_{o\ar
+  o\ar o}}$, and $\hol{\forall_{(\alpha\ar
+  o)\ar o}}$ (for $\hol{\alpha\in T}$).  Type subscripts may be dropped if
+irrelevant or obvious. Similarly, parentheses may be avoided.  Binder
+notation $\hol{\all{X_\alpha} s_o}$ is used as shorthand for
+$\hol{\forall_{(\alpha\ar o)\ar o}
+(\lam{X_\alpha} s_o)}$, and infix notation $\hol{s \vee t}$ is employed
+instead of $\hol{((\vee s)\, t)}$. From the above connectives, other logical
+connectives, such as $\hol{\top}$, $\hol{\bot}$, $\hol{\wedge}$,
+$\hol{\supset}$, $\hol{\equiv}$ and $\hol{\exists}$, can be defined in the usual way.
 \end{definition}
 
-The definitions for substitution (Def.~\ref{homlsubstitution}), $\beta$- and $\eta$-reduction (Def.~\ref{homlbetaeta}), frame (Def.~\ref{homlframe}), and assignment (Def.~\ref{homlassignment}) remain unchanged.
+  \emph{Substitution} of a term $\hol{A_\alpha}$ for a variable $\hol{X_\alpha}$
+  in a term $\hol{B_\beta}$ is denoted by $\hol{[A/X]B}$.  Since we consider
+  $\hol{\alpha}$-conversion implicitly, we assume the bound variables of $\hol{B}$
+  avoid variable capture.
+
+%\begin{definition}\label{homlbetaeta} %\footnote{\textbf{Chris:} Is Def.4 needed at all?}
+  Two common relations on terms are given by $\hol{\beta}$-reduction and
+  $\hol{\eta}$-reduction.  A $\hol{\beta}$-redex has the form $\hol{(\lam{X}s)t}$ and
+  $\hol{\beta}$-reduces to $\hol{[t/X]s}$.  An $\hol{\eta}$-redex has the form
+  $\hol{(\lam{X}s X)}$ where variable $\hol{X}$ is not free in $\hol{s}$; it
+  $\hol{\eta}$-reduces to $\hol{s}$.  We write $\hol{s\eqb t}$ to mean $\hol{s}$ can be
+  converted to $\hol{t}$ by a series of $\hol{\beta}$-reductions and expansions.
+  Similarly, $\hol{s\eqbe t}$ means $\hol{s}$ can be converted to $\hol{t}$ using both
+  $\hol{\beta}$ and $\hol{\eta}$.  For each $\hol{s_\alpha\in \HOL}$ there is a unique
+  \emph{$\beta$-normal form} and a unique \emph{$\beta\eta$-normal
+    form}.
+% From this fact we know $s\eqb t$ ($s\eqbe t$) iff
+% $\Bnormform s\Metaeq\Bnormform t$
+% ($\Benormform s\Metaeq\Benormform t$).
+% The semantics of $\stt$ is well understood and thoroughly documented
+% in the literature \cite{Henkin50,Andrews72b,Andrews72a,BBK04}; our
+% summary below is adapted from Andrews~\cite{sep-type-theory-church}.
+%\end{definition}
+
+%\begin{definition}\label{homlassignment}
+A \emph{variable assignment} $g$ maps
+variables $\hol{X_\alpha}$ to elements in $\hol{D_\alpha}$. $\hol{g[d/W]}$ denotes the
+assignment that is identical to $\hol{g}$, except for variable $\hol{W}$, which is
+now mapped to $\hol{d}$.
+%\end{definition}
+
+\begin{definition}\label{homlframe}
+A \emph{frame} $\hol{D}$ is a collection $\hol{\{D_\alpha\}_{\alpha\in\entity{T}}}$
+of nonempty sets $\hol{D_\alpha}$, such that $\hol{D_o = \{T,F\}}$
+(for truth and falsehood).  The
+$\hol{D_{\alpha\ar\beta}}$ are collections of functions mapping
+$\hol{D_\alpha}$ into $\hol{D_\beta}$. 
+\end{definition}
 
@@
 under assignment $g$ iff $\|s_o\|^{M,g} = T$; this is also denoted
-as $M,g \models s_o$.  A formula $s_o$ is called \emph{valid} in
-$M$, which is denoted as $M \models s_o$, iff $M,g \models s_o$ for all
+as $M,g \models^\HOL s_o$.  A formula $s_o$ is called \emph{valid} in
+$M$, which is denoted as $M \models^\HOL s_o$, iff $M,g \models^\HOL s_o$ for all
 assignments $g$. Finally, a formula $s_o$ is called
-\emph{valid}, which we denote by $\models s_o$, iff $s_o$ is valid for
-all $M$. Moreover, we write $\Gamma\models \Delta$ (for sets of
+\emph{valid}, which we denote by $\models^\HOL s_o$, iff $s_o$ is valid for
+all $M$. Moreover, we write $\Gamma\models^\HOL \Delta$ (for sets of
  formulas $\Gamma$ and $\Delta$) iff there is a model $M$ and an assignment $g$ such that  
- $M,g \models s_o$ for all $s_o\in \Gamma$ and $M,g \models t_o$ for at least one $t_o\in \Delta$.
+ $M,g \models^\HOL s_o$ for all $s_o\in \Gamma$ and $M,g \models^\HOL t_o$ for at least one $t_o\in \Delta$.
 \end{definition}
@@
 
-\section{Sound and Complete Embedding in HOL}
+\section{Sound and Complete Embedding of $\FFOL$ in HOL}
 Todo ... the embedding in Isabelle/HOL is depicted in 
@@
 
-\pagebreak
-\newpage
+In this framework partial and total functions are modelled as follows: 
+A function $f$ is total if and only if for all $x$ we have $\ex x \imp \ex(f x)$ 
+For partial functions $f$ we may have some $x$ such that $\ex x$ but not
+ $\ex(f x)$. A function $f$ is strict  if  and only if for all $x$
+we have $\ex(f x) \imp \ex x$.
 
-\section{Section title}
-\label{sec:1}
-Text with citations \cite{RefB} and \cite{RefJ}.
-\subsection{Subsection title}
-\label{sec:2}
-as required. Don't forget to give each section
-and subsection a unique label (see Sect.~\ref{sec:1}).
-\paragraph{Paragraph headings} Use paragraph headings as needed.
-\begin{equation}
-a^2+b^2=c^2
-\end{equation}
+\section{Exploring Axioms Systems for Category Theory}
+In an exemplary theory exploration study, we have shown how Scott's
+\cite{Scott79} axiom system for category theory can be derived from a
+notion of partial monoids. These axioms systems are presented in Table \ref{axioms-sets-1}.
 
-% For one-column wide figures use
-\begin{figure}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics{example.eps}
-% figure caption is below the figure
-\caption{Please write your figure caption here}
-\label{fig:1}       % Give a unique label
-\end{figure}
-%
-% For two-column wide figures use
-\begin{figure*}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[width=0.75\textwidth]{example.eps}
-% figure caption is below the figure
-\caption{Please write your figure caption here}
-\label{fig:2}       % Give a unique label
-\end{figure*}
-%
-% For tables use
-\begin{table}
-% table caption is above the table
-\caption{Please write your table caption here}
-\label{tab:1}       % Give a unique label
-% For LaTeX tables use
-\begin{tabular}{lll}
-\hline\noalign{\smallskip}
-first & second & third  \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-number & number & number \\
-number & number & number \\
-\noalign{\smallskip}\hline
+The stepwise evolution has been described in
+\cite{R58}. Below we summarise these experiments.
+However, first we describe some basic modeling decisions for the
+technical encoding in Isabelle/HOL. The Isabelle/HOL sources of our experiments are
+available at \url{todo-sources}.
+
+\begin{table} \centering \normalsize
+\begin{tabular}{ll}
+\hline
+\\
+\multicolumn{2}{c}{Axioms Set I} \\
+%\hline
+\\
+ $S_{i}$ & $\ex(x \comp y) \imp (\ex x \wedge \ex y)$ \\
+ $E_{i}$ & $\ex(x \comp y) \limp (\ex x \wedge \ex y \wedge (\exists z. z \comp
+         z \cong z \wedge x \comp z \cong x \wedge z \comp y \cong y))$ \\
+ $A_{i}$ & $x\comp (y \comp z) \cong (x \comp y) \comp z$ \\
+ $C_{i}$ & $\forall y. \exists i.  \id i \wedge i \comp y \cong y$ \\
+ $D_{i}$ & $\forall x. \exists j.  \id j \wedge x \comp j \cong x$  \\
+\\
+\hline
+\\
+\multicolumn{2}{c}{Axioms Set II} \\
+%\hline
+\\
+$S_{ii}$ & $\ex(x \comp y) \imp (\ex x \wedge \ex y) \wedge (\ex (\dom x) \imp \ex
+        x) \wedge (\ex (\cod y) \imp \ex
+        y)$ \\
+ $E_{ii}$ & $\ex(x \comp y) \limp (\ex x \wedge \ex y \wedge (\exists z. z \comp
+         z \cong z \wedge x \comp z \cong x \wedge z \comp y \cong y))$ \\
+ $A_{ii}$ & $x\comp (y \comp z) \cong (x \comp y) \comp z$ \\
+ $C_{ii}$ & $\ex y \imp (\id(\cod y) \wedge (\cod y) \comp y \cong y)$ \\
+ $D_{ii}$ & $\ex x \imp (\id(\dom x) \wedge x \comp (\dom x) \cong x)$ \\
+\\
+\hline
+\\
+\multicolumn{2}{c}{Axioms Set III} \\
+%\hline
+\\
+$S_{iii}$ & $\ex(x \comp y) \imp (\ex x \wedge \ex y) \wedge (\ex (\dom x) \imp \ex
+        x) \wedge (\ex (\cod y) \imp \ex
+        y)$ \\
+ $E_{iii}$ & $\ex(x \comp y) \limp (\dom x \cong \cod y \wedge \ex (\cod y)))$ \\
+ $A_{iii}$ & $x\comp (y \comp z) \cong (x \comp y) \comp z$ \\
+ $C_{iii}$ & $\ex y \imp (\id(\cod y) \wedge (\cod y) \comp y \cong y)$ \\
+ $D_{iii}$ & $\ex x \imp (\id(\dom x) \wedge x \comp (\dom x) \cong x)$ \\
+\\
+\hline
+\\
+\multicolumn{2}{c}{Axioms Set IV} \\
+%\hline
+\\
+$S_{iv}$ & $\ex(x \comp y) \imp (\ex x \wedge \ex y) \wedge (\ex (\dom x) \imp \ex
+        x) \wedge (\ex (\cod y) \imp \ex
+        y)$ \\
+ $E_{iv}$ & $\ex(x \comp y) \biimp (\dom x \cong \cod y \wedge \ex (\cod y)))$ \\
+ $A_{iv}$ & $x\comp (y \comp z) \cong (x \comp y) \comp z$ \\
+ $C_{iv}$ & $(\cod y) \comp y \cong y$ \\
+ $D_{iv}$ & $x \comp (\dom x) \cong x$  \\
+\\
+\hline
+\\
+\multicolumn{2}{c}{Axioms Set V (Scott 79, \cite{Scott79})} \\
+%\hline
+\\
+$S1$ & $\ex (\dom x) \imp \ex x$ \\
+$S2$ & $\ex (\cod y) \imp \ex y$ \\
+$S3$ & $\ex(x \comp y) \biimp \dom x \simeq \cod y$ \\
+$S4$ & $x\comp (y \comp z) \cong (x \comp y) \comp z$ \\
+$S5$ & $(\cod y) \comp y \cong y$ \\
+$S6$ & $x \comp (\dom x) \cong x$  \\
+\\
+\hline
 \end{tabular}
+\caption{Stepwise evolution of Scott's \cite{Scott79} axiom
+  system for category theory from partial monoids. The axiom names are
+  motivated as follows: 
+  $S$ stands for strictness, $E$ for existence, $A$ for associativity, $C$ for
+  codomain, $D$ for Domain. The free variables $x$, $y$, $z$ range over
+  the raw domain $D$. The quantifiers in Axiom Sets I and II are
+  free logic quantifiers, that is, they range over the domain $E$ of
+  existing objects. \label{axioms-sets-1}}
 \end{table}
 
-%\begin{acknowledgements}
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-%\end{acknowledgements}
+\subsection{Modeling of basic concepts}
+Morphisms in the category are modeled as objects of type $\ti$. We introduce three partial functions, 
+$\dom$ (domain), $\cod$ (codomain), and $\comp$ (morphism composition). 
+Partiality of composition is handled exactly as expected: we generally may have 
+non-existing compositions $x\comp y$ (i.e. $\neg(\ex(x\comp y))$) for some existing  
+morphisms $x$ and $y$ (i.e. $\ex x$ and $\ex y$).
+
+For composition $\comp$ we assume set-theoretical composition here (i.e., functional 
+composition from right to left). This means that
+\[(\cod x) \comp (x \comp (\dom x)) \kleq x\] 
+and that 
+\[(x \comp y)a \kleq x(y a) \quad \text{when}\quad
+\dom x \exid \cod y\] 
+The equality symbol $\kleq$ denotes Kleene equality and it
+is defined as follows (where $=$ is identity on all objects, existing or non-existing, 
+of type $\ti$):
+\[x \kleq y \ddef (\ex x \vee \ex y) \imp x = y\]
+Existing identity $\simeq$ is defined as:
+\[x \simeq y \ddef \ex x \wedge \ex y \wedge  x = y\]
+
+$\cong$ is an equivalence relation. $\simeq$, in contrast, is only symmetric and transitive, and lacks 
+reflexivity. These observations are quickly confirmed by Isabelle.
+
+Next, we define the identity morphism predicate $\id$ as follows:
+
+abbreviation I where \[\id i \ddef (\forall x. \ex(i \comp x) \imp i \comp
+x \cong x) \wedge (\forall x. \ex(x \comp i) \imp x \comp i \cong x)\]
+
+This definition was suggested by an exercise in \cite{FreydScedrov90}
+on p.~4.  In earlier experiments we used a longer definition which can
+be proved equivalent on the basis of the other axioms. For monoids,
+where composition is total, $\id i$ means $i$ is a two-sided identity
+— and such are unique. For categories the property is much weaker.
+
+\subsection{Consistency}
+The model finder Nitpick confirms consistency for all of the axiom
+sets from Table \ref{axioms-sets-1}. For example, when asked to consider at least one defined and one undefined object, then
+Nitpick generates for all cases the following model (called $M_1$ in the remainder):
+$D=\{i_i,i_2\}$ and $E=\{i_1\}$;  $i_1\comp i_1$ is $i_1$,  and $i_2$
+in all other cases; $\cod$ and $\dom$ are identity on $D$. Without constraining the request, Nitpick
+generates an even simpler model (called $M_0$ in the remainder):
+$D=\{i_i\}$ and $E=\emptyset$; $i_1\comp i_1$ is $i_1$; $\cod$ and
+$\dom$ are identity on $D$. It is trivial to check that these models
+indeed confirm the consistency of all axiom sets from Table \ref{axioms-sets-1}.
+
+  % Constants:
+   % codomain = (λx. _)(i⇩1 := i⇩1)
+   %  op ⋅ = (λx. _)((i⇩1, i⇩1) := i⇩1)
+   %  domain = (λx. _)(i⇩1 := i⇩1)
+   %  E = (λx. _)(i⇩1 := False)
+
+  % Constants:
+  %   codomain = (λx. _)(i⇩1 := i⇩1, i⇩2 := i⇩2)
+  %   op ⋅ = (λx. _)((i⇩1, i⇩1) := i⇩1, (i⇩1, i⇩2) := i⇩2, (i⇩2, i⇩1) := i⇩2, (i⇩2, i⇩2) := i⇩2)
+  %   domain = (λx. _)(i⇩1 := i⇩1, i⇩2 := i⇩2)
+  %   E = (λx. _)(i⇩1 := True, i⇩2 := False)
+
+\subsection{Axioms Set I}
+ Axioms Set I is our most basic axiom set for category theory generalizing the 
+axioms for a monoid to a partial composition operation. Remember that a monoid is an 
+algebraic structure $(S,\circ)$, where $\circ$ is a binary operator on set $S$, 
+satisfying the following properties: 
+$$
+\begin{tabular}{ll}
+Closure: & $ \forall a,b \in S.\ a \circ b \in S$ \\
+Associativity: & $\forall a,b,c \in S.\ a \circ (b \circ c) = (a \circ b) \circ c$ \\
+Identity: & $\exists id_S \in S. \forall a\in S.\ id_S\circ a = a = a \circ id_S$
+\end{tabular}
+$$
+
+That is, a monoid is a semigroup with a two-sided identity element.
+
+Axioms Set I generalises the notion of a monoid by introducing a partial, strict binary 
+composition operation $\comp$. The existence of left and right identity elements is 
+addressed in the last two axioms. The notions of $\dom$ (Domain) and
+$\cod$ (Codomain)
+abstract from their common meaning in the context of sets. In category theory we
+work with just a single type of objects (the type $\ti$ of morphisms) and therefore 
+identity morphisms are employed to suitably characterize their
+meanings.
+
+We can prove that the $i$ in axiom $C_i$ and the $j$ in axiom $D_i$
+are unique. The proofs and the dependencies can be 
+   found automatically by Sledgehammer.
+$$  \forall y. \exists i. \id i \wedge i \comp y \cong y
+\wedge (\forall j.d(\id j \wedge j \comp y \cong y) \imp i \cong j)
+\quad 
+    (\text{by } A_i, C_i, S_i) $$
+$$ \forall x. \exists j. \id j \wedge x \comp j \cong x \wedge
+(\forall i. (\id i \wedge x \comp i \cong x) \imp j \cong i) \quad   
+    (\text{by }  A_i, D_i, S_i) $$
+
+However, the $i$ and $j$ need not be equal. Using existential
+variables $C$ and $D$, this can be encoded in
+   our formalization as follows: 
+ $$\exists C, D. (\forall y. \id (C y) \wedge (C y) \comp y \cong y)
+ \wedge (\forall x. \id (D x) \wedge x \comp (D x) \cong x) \wedge
+ D \not= C$$
+
+The model finder Nitpick confirms that this formula is satisfiable:
+e.g. choose domain $D=\{i_1,i_2\}$ and $E=\{i_2\}$; $i_2\comp i_2$ returns $i_2$,  and $i_1$
+in all other cases; variable $D$ is identity on domain $D$, but $C$ maps both
+$i_1$ and $i_2$ to $i_2$.
+
+\subsection{Axioms Set II}
+Axioms Set II is developed from Axioms Set I by Skolemization of the
+existentially quantified variables $i$ and $j$ in axioms $C_i$ and
+$D_i$. We can argue semantically that every model of Axioms Set I has
+such functions. Hence, we get a conservative extension of Axioms Set
+I. This could be done for any theory with an $\forall x. \exists i$.-axiom. The strictness axiom $S$ is extended, so
+that strictness is now also postulated for the new Skolem functions
+$\dom$ and $\cod$. Note that the values of Skolem functions
+outside $E$ can just be given by the identity function.
+
+The left-to-right direction of existence axiom $E_{ii}$ is implied. 
+  $$E(x \comp y) \imp (E x \wedge E y \wedge (\exists z. z \comp z
+  \cong z \wedge x \comp z \cong x \wedge z\comp y \cong y)) \quad
+  (\text{by } A_{ii}, C_{ii}, S_{ii})$$
+
+Axioms $C_{ii}$ and $D_{ii}$, together with $S_{ii}$, show that
+${\dom}$ and ${\cod}$ are total functions, as intended: 
+$$E x \imp E(\dom x) \quad (\text{by } D_{ii}, S_{ii})$$
+$$E x \imp E(\cod x) \quad (\text{by } C_{ii}, S_{ii}) $$
+
+The proofs are found by Sledgehammer and verified in Isabelle/HOL. Using Sledgehammer we have also
+shown that Axioms Set II implies Axioms Set I. Vice versa, Axioms Set I
+also implies Axioms Set II. This can easily 
+be shown by semantical means on the meta-level.
+
+\subsection{Remark on the Experiments}
+All proofs above and all proofs in the rest of this paper (unless
+stated otherwise) have been obtained fully automatically with the
+Sledgehammer tool in Isabelle/HOL. This tool interfaces to prominent
+first-order automated theorem provers such as CVC4 \cite{CVC4}, Z3
+\cite{Z3}, E \cite{E} and Spass \cite{Spass}.  Remotely, also
+  provers such as Vampire \cite{Vampire}, or the higher-order provers
+  Satallax \cite{Satallax} and LEO-II \cite{LEO} can be reached. For
+  example, to prove axiom $E_{iii}$ from Axioms Set II, we have called
+  Sledgehammer on all axioms of Axioms Set II. The provers then, via
+  Sledgehammer, suggested to call trusted/verified tools in
+  Isabelle/HOL with the exactly required dependencies they
+  detected. With the provided dependency information the trusted tools
+  in Isabelle/HOL were then able to reconstruct the external proofs on
+  their own.  This way we obtain a verification of our claims in
+  Isabelle/HOL, in which all the proofs have nevertheless been
+  contributed by automated theorem provers.
+
+\subsection{Axioms Set III}
+In Axioms Set III the existence  axiom  $E_{ii}$ from Axioms Set II  is simplified by taking advantage of 
+  the two new Skolem functions ${\dom}$ and $\cod$.
+
+The left-to-right direction of existence axiom $E_{iii}$ is implied.
+  $$E(x \comp y) \imp (\dom x \cong \cod y \wedge E(\cod y)) \quad  
+    (\text{by } A_{iii}, C_{iii}, D_{iii}, S_{iii})$$
+
+ Axioms Set II and Axioms Set III are equivalent; this has been
+ confirmed by the automated theorem provers and verified in Isabelle/HOL.
+
+\subsection{Axioms Set IV}
+Axioms Set IV simplifies the axioms $C_{iii}$ and  $D_{iii}$ . However, as it turned 
+ out, these simplifications also require the existence axiom $E_{iii}$ to be strengthened into
+ an equivalence.
+
+ Axioms Set III and Axioms Set IV are equivalent; this has been
+ confirmed by the automated theorem provers and verified in
+ Isabelle/HOL.
+
+\subsection{Axioms Set V}
+Axioms Set V has been proposed by Scott \cite{Scott79} in the 1970s. 
+This set of axioms is equivalent to the axiom set presented by Freyd
+and Scedrov in their textbook ``Categories, Allegories''
+\cite{FreydScedrov90}, when encoded in free logic, corrected/adapted
+and further simplified.  Their axiom set is technically flawed when
+encoded in our given context. This issue has been detected by
+automated theorem provers with the same technical infrastructure as
+employed so far. See Section\ref{sec-freyd-scedrov} for more
+details.
+
+ Axioms Set IV and Axioms Set V are equivalent; again, this has been
+ confirmed by the automated theorem provers and verified in
+ Isabelle/HOL.
+
+ \section{Assessment of the Axiom System by Freyd and
+   Scedrov} \label{sec-freyd-scedrov} In this section we study the
+ axioms set of Freyd and Scedrov from their textbook ``Categories,
+ Allegories'' \cite{FreydScedrov90}.  In Subsection
+ \ref{subsec-freyd-scedrov-1} we show, that their axioms set,
+ replicated in Table \ref{axioms-sets-2} as Axioms Set VI, becomes
+ inconsistent in our free logic setting if we assume non-existing
+ objects of type $i$, respectively, if we assume that the operations
+ are non-total.
+
+\begin{table} \centering \normalsize
+\begin{tabular}{ll}
+\hline
+\\
+\multicolumn{2}{c}{Axioms Set FS-I:  Freyd and Scedrov in original notation (with issues)} \\
+%\hline
+\\
+  $A1$ &  $\ex(x \circ y) \longleftarrow (x\Box \cong \Box y)$ \\ 
+  $A2a$ & $((\Box x)\Box) \cong \Box x$ \\ 
+  $A2b$ & $\Box (x\Box) \cong \Box x$ \\ 
+  $A3a$ & $(\Box x) \circ x \cong x$ \\ 
+  $A3b$ & $x \circ (x\Box) \cong x$ \\ 
+  $A4a$ & $\Box(x \circ y) \cong \Box(x \circ (\Box y))$ \\ 
+  $A4b$ & $(x \circ y)\Box \cong ((x\Box) \circ y)\Box$ \\ 
+  $A5$   & $x \circ (y \circ z) \cong  (x \circ y) \circ z$ \\
+\\
+\hline
+\\
+\multicolumn{2}{c}{Axioms Set FS-II: Freyd and Scedrov in our notation (with issues)} \\
+%\hline
+\\
+  $A1$  & $\ex (x \comp y) \longleftrightarrow \dom x \cong \cod y$ \\
+  $A2a$ & $\cod(\dom x) \cong \dom x$ \\  
+  $A2b$ & $\dom(\cod y) \cong cod y$ \\  
+  $A3a$  & $x \comp (\dom x) \cong x$ \\ 
+  $A3b$ & $(\cod y) \comp y \cong y$ \\
+  $A4a$ & $\dom(x \comp y) \cong \dom((\dom x) \comp y)$ \\ 
+  $A4b$ & $\cod(x \comp y) \cong \cod(x \comp (\cod y))$ \\ 
+  $A5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
+\\
+\hline
+\\
+\multicolumn{2}{c}{Axioms Set VI: Freyd and Scedrov in our notation
+  and corrected} \\
+%\hline
+\\
+  $A1'$  & $\ex (x \comp y) \longleftrightarrow \dom x \simeq\cod y$ \\
+  $A2a$ & $\cod(\dom x) \cong \dom x$ \\  
+  $A2b$ & $\dom(\cod y) \cong cod y$ \\  
+  $A3a$  & $x \comp (\dom x) \cong x$ \\ 
+  $A3b$ & $(\cod y) \comp y \cong y$ \\
+  $A4a$ & $\dom(x \comp y) \cong \dom((\dom x) \comp y)$ \\ 
+  $A4b$ & $\cod(x \comp y) \cong \cod(x \comp (\cod y))$ \\ 
+  $A5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
+\\
+\hline
+\end{tabular}
+\caption{The axioms set of Freyd and Scedrov in their and our
+  notation, together with a proposed correction.\label{axioms-sets-2}}
+\end{table}
+
+ Note, however, that the free variables in this first study range over
+ the existing and non-existing objects in domain $D$. One may argue,
+ that this is not the intention of Freyd and
+ Scedrov. Therefore, we add a second study in Subsection
+ \ref{subsec-freyd-scedrov-2}, in which we restrict the
+ variables to range only over existing objects in $E$. However, also in this case
+ the axiom system of Freyd and Scedrov remains unsatisfactory. Now it
+ turns out incomplete, 
+ since strictness conditions/axioms are required which are not mentioned in
+ the textbook.
+
+  Freyd and Scedrov employ a different notation for $\dom x$ and $\cod
+ x$. They denote these operations by $\Box x$ 
+  and $x\Box$. Moreover, they employ diagrammatic composition $(f \circ
+  g) x \cong g(f x)$ (functional composition from left to right) instead of the set-theoretic 
+  definition $(f \comp g) x \cong f(g x)$ (functional composition from right to left) used so far.
+  We leave it to the reader to verify that their Axioms
+  Set VI corresponds to Axioms
+  Set VII modulo an appropriate conversion of notation.\footnote{A recipe for 
+  this translation is as follows: (i) replace all $x \circ y$ by
+  $y \comp x$, (ii) rename the variables to get them again in alphabetical order,
+(iii) replace $\varphi\Box$ by $\cod \varphi$ and $\Box\varphi$  by $dom \varphi$, and finally
+(iv) replace $\cod y \cong \dom x$ (resp. $\cod y \simeq \dom x$) 
+   by $\dom x \cong \cod y$ (resp. $\dom x \simeq \cod y$).}
+
+\subsection{Constricted Inconsistency in Free Logic Setting} \label{subsec-freyd-scedrov-1}
+  A main difference in the system by Freyd and Scedrov to our Axiom
+  Set V from Table \ref{axioms-sets-1} concerns
+  axiom $S3$ respectively $A1$. Namely, instead of the non-reflexive
+  existing identity $\simeq$, they use Kleene 
+  equality $\cong$, cf. definition 1.11 on page 3 of \cite{FreydScedrov90}.\footnote{Def. 1.11 in Freyd 
+  Scedrov: ``The ordinary equality sign $=$ [i.e., our $\cong$] will be used in the
+  symmetric sense, to wit: if either side is defined then so is the other and they are equal. \ldots''} 
+  The difference seems minor, but in our free logic setting it has the effect to cause the mentioned
+  constricted inconsistency issue. This could perhaps be an oversight, or it could indicate
+  that Freyd and Scedrov actually mean the Axioms Set VIII below (where the variables in the axioms range 
+  over defined objects only). However, in Axioms Set VIII we had to (re-)introduce explicit 
+  strictness conditions to ensure equivalence to the Axiom Set V by
+  Scott.
+
+  The (constricted) inconsistency of Axioms Set FS-I, respectively
+  Axiom Set FS-II, from Table \ref{axioms-sets-2} has been 
+  detected first by the model finder Nitpick. When we asked Nitpick to
+  generate a model with at least one non-existing object, it claimed
+  that there is no such model. However, a model can still be
+  constructed if we do not make any assumptions about non-existing
+  objects. In fact, the model presented by Nitpick for this case
+  consists of a single, existing morphism.
+
+However, one can see directly that Axiom $A1$ is problematic
+as written: If $x$ and $y$ are undefined, then
+(presumably) $\dom x$ and $\cod y$ are undefined as
+well, and by the definition of Kleene equality, $\dom x \cong \cod
+  y$. $A1$ stipulates that $x \comp y$ should be defined in
+this case, which appears unintended.
+
+As we will demonstrate now, the consequences of this version of the axiom are
+even stronger. It implies that \emph{all} objects are defined,
+that is, composition (as well as $\dom$ and $\cod$) become total operations.
+The theory described by these axioms ``collapses'' to the theory of
+monoids: If all objects are defined, then one can conclude from $A1$ that 
+$\dom x \cong \dom y$ (resp.~$\dom x \cong \cod y$) and $\cod x \cong \cod y$), 
+and according to 1.14 of \cite{FreydScedrov90}, 
+the category reduces to a monoid provided that it is not empty.
+
+In fact, the automated theorem provers, via Sledgehammer, quickly
+prove falsity from Axioms Set FS-II (or FS-I) when assuming a 
+ non-existing object of type $i$:
+$$(\exists x. \neg E x) \imp False$$
+
+The provers identify the axioms $A1$,
+ $A2a$ and $A3a$ to cause the problem under this assumption. A
+ human-intuitive proof argument is as follows:
+
+ Let $a\in D$ be an undefined object, that is, assume $¬E a$.  By
+ instantiating axiom $A3a$ with $a$ we have $a \comp (\dom a) \cong a$.  From
+ this and definition of $\cong$ we know that $a \comp (\dom a)$ is not
+ defined. This is easy to see, since if $a \comp (\dom a)$ were defined, we
+ also had that $a$ is defined, which is not the case by assumption.
+  Hence, $\neg E (a \comp (\dom a)$.
+Next, we instantiate $A1$ with $a$ and $\dom a$ to obtain
+   $E(a \comp (\dom a)) \biimp \dom a \cong \cod(\dom a)$. Moreover,
+   by instantiating $A2a$ with $a$ we obtain $\cod(\dom a) \cong dom a$,
+   which we use (modulo symmetry and transitivity of $\cong$) to
+   rewrite the former result into 
+   $E(a \comp (\dom a)) \biimp \dom a \cong \dom a$. By reflexivity of
+   $\cong$ we thus get $E(a \comp (\dom a))$, i.e. that $a \comp
+   (\dom a)$ is defined, which contradicts $\neg E (a \comp (\dom
+   a)$. $\Box$
+
+As a corollary from the above constricted inconsistency result we get that all  must be
+defined: $\forall x. E x$
+
+% We also
+%  show
+%  that there is a simple fix to that issue, namely to replacement of
+%  the occurence of Kleene equality in one axiom by
+
+% We have modified the axioms of \cite{FreydScedrov90} by
+% replacing the original Kleene equality $\cong$ in their axiom $S3$ by
+% the non-reflexive, existing identity $\simeq$. Note that the modified
+% axiom $S3$ is equivalent to $E_{iv}$.\marginpar{Check again}
+
+%  this study we assume
+
+% However, this time we restrict 
+% the free variables in their system to range over existing objects only. By employing the free logic 
+% universal quantifier @{text "❙∀"} we thus modify Axiom Set VII as follows:
+
+\begin{table} \centering \normalsize
+\begin{tabular}{ll}
+\\
+\hline
+\\
+\multicolumn{2}{c}{Freyd and Scedrov in our notation (corrected and
+  reduced I)} \\
+%\hline
+\\
+  $B1'$  & $\ex (x \comp y) \longleftrightarrow \dom x \simeq\cod y$ \\
+  $B3a$  & $x \comp (\dom x) \cong x$ \\ 
+  $B3b$ & $(\cod y) \comp y \cong y$ \\
+  $B4a$ & $\dom(x \comp y) \cong \dom((\dom x) \comp y)$ \\ 
+  $B4b$ & $\cod(x \comp y) \cong \cod(x \comp (\cod y))$ \\ 
+  $B5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
+\\
+\hline
+\\
+\multicolumn{2}{c}{Freyd and Scedrov in our notation (corrected and
+  reduced II)} \\
+%\hline
+\\
+  $B1'$  & $\ex (x \comp y) \longleftrightarrow \dom x \simeq\cod y$ \\
+  $B2a$ & $\cod(\dom x) \cong \dom x$ \\  
+  $B2b$ & $\dom(\cod y) \cong cod y$ \\  
+  $B3a$  & $x \comp (\dom x) \cong x$ \\ 
+  $B3b$ & $(\cod y) \comp y \cong y$ \\
+  $B5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
+\\
+\hline
+\\
+\multicolumn{2}{c}{Freyd and Scedrov in our notation (corrected and
+  reduced III)} \\
+%\hline
+\\
+ $S^1_{v}$ & $\ex (\dom x) \imp \ex x$ \\
+  $S^2_{v}$ & $\ex (\cod y) \imp \ex y$ \\
+  $B1'$  & $\ex (x \comp y) \longleftrightarrow \dom x \simeq\cod y$ \\
+  $B3a$  & $x \comp (\dom x) \cong x$ \\ 
+  $B3b$ & $(\cod y) \comp y \cong y$ \\
+  $B5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
+\\
+\hline
+\end{tabular}
+\caption{Bla}
+\end{table}
+
+\subsection{Missing Strictness Axioms in Alternative Setting} \label{subsec-freyd-scedrov-2}
+
+\section{Conclusion}
+\ldots todo
+
+\begin{acknowledgements}
+DFG projects \ldots todo
+\end{acknowledgements}
 

### 2017-03-30 FreeLogic/2017-Journal/article.tex
update

@@
 
+\newcommand\map[1]{\hat{#1}}
 \newcommand\hol[1]{\boldsymbol{#1}}
@@
 
-The purpose of this article is not to claim any novel results in category
-theory, but to demonstrate an elegant way to ``implement'' and utilise
-reasoning in free logic, and to present respective experiments.
+  The purpose of this article is not to claim any novel results in
+  category theory, but to demonstrate an elegant way to ``implement''
+  and utilise interactive and automated reasoning in free logic, and
+  to present respective experiments.
 
@@
 objects in $\D$. Quantification is
-now restricted to set $\ex$ of existing/defined objects only. It is
-obvious how this can be used to model undefideness and partiality:
-problematic terms, e.g. division by zero or improper definite
-descriptions, still denote, but they refer to undefined objects, that
-is, objects $d$ in $\D\setminus \ex$ lying outside of the scope of
-quantification.
+now restricted to set $\ex$ of existing/defined objects only.
+
+It is obvious how this can be used to model undefideness and
+partiality: problematic terms, e.g. division by zero or improper
+definite descriptions, still denote, but they refer to undefined
+objects, that is, objects $d$ in $\D\setminus \ex$ lying outside of
+the scope of quantification.
+%In this framework partial and total functions are modelled as follows: 
+Moreover, a function $f$ is \emph{total} if and only if for all $x$ we have $\ex x \imp \ex(f x)$ 
+For \emph{partial} functions $f$ we may have some $x$ such that $\ex x$ but not
+$\ex(f x)$. A function $f$ is \emph{strict}  if  and only if for all $x$
+ we have $\ex(f x) \imp \ex x$.
 
@@
   resp. ``defined'' objects, and $I$ an interpretation function
-  mapping 0-ary function symbols (constants) to defined objects $d\in \ex$, 
- 0-ary predicate symbols (propositions) to $\True$ or $\False$, 
+  mapping $0$-ary function symbols (constants) to defined objects $d\in \ex$, 
+ $0$-ary predicate symbols (propositions) to $\True$ or $\False$, 
   $n$-ary function symbols (for $n\geq 1$) to $n$-ary functions
@@
 \item $\| x \|^{I,g} = g(x)$ for variable symbols $x\in\V$
-\item $\| c \|^{I,g} = I(c)$, where $c\in\F$ is an 0-ary function symbol
+\item $\| c \|^{I,g} = I(c)$, where $c\in\F$ is an $0$-ary function symbol
 \item $\| f(t_1,\ldots,t_n)\|^{I,g} = I(f)(\| t_1 \|^{I,g},\ldots,\|
@@
 \begin{enumerate}
-\item $\| p \|^{I,g} = I(p)$, where $p\in\F$ is an 0-ary predicate
+\item $\| q \|^{I,g} = I(q)$, where $q\in\P$ is an $0$-ary predicate
   symbol
@@
 \subsection{Classical Higher-Order Logic}
-Short introduction ... todo.
-
-\begin{definition}\label{holtypes}
+Simple type theory, also referred to as classical higher-order logic
+(HOL), is an expressive logic formalism that allows for higher-order
+quantification, that is quantification over arbitrary set and function
+variables.  It is based on the simply typed
+$\lambda$-calculus\footnote{ For a detailed discussion of typed
+  $\lambda$-calculi, we refer to the
+  literature~\cite{DBLP:books/daglib/0032840}.  }
+  %\footnote{
+    %Although \sys~actually supports a polymorphic typed $\lambda$-calculus
+    %we will
+    %stick here to the simply typed $\lambda$-calculus for a better understanding.}
+  and it has its origin in the work by
+  Church~\cite{DBLP:journals/jsyml/Church40}.
+
+\begin{definition}[Types]\label{holtypes}
   The set $\hol{T}$ of simple types freely generated from a set of
@@
 
-\begin{definition}\label{holgrammar}
+\begin{definition}[Syntax of $\HOL$]\label{holgrammar}
 The language of higher-order logic $\HOL$ is defined by the following
@@
   & \hol{(({\vee_{o\ar o\ar o}}\,s_o)\,t_o)} \mid \hol{\forall_{(\alpha\ar
-    o)\ar o}(\lam{X_\alpha} s_o)} 
+    o)\ar o}(\lam{X_\alpha} s_o)} \mid \hol{\Descr(\lam{X_\alpha} s_o)}
 \end{align*}
-where $\hol{\alpha},\hol{\beta}\in \hol{T}$. $p_\alpha$ denotes typed constants and
-$X_\alpha$ typed variables (distinct from $p_\alpha$).  Complex typed
+where $\hol{\alpha},\hol{\beta}\in \hol{T}$. $\hol{p_\alpha}$ denotes typed constants and
+$\hol{X_\alpha}$ typed variables (distinct from $\hol{p_\alpha}$).  Complex typed
 terms are constructed via abstraction and application. The type of
-each term is given as a subscript.  Terms $s_o$ of type $o$ are called
+each term is given as a subscript.  Terms $\hol{s_o}$ of type $\hol{o}$ are called
 formulas.  The logical connectives of choice are
 $\hol{\neg_{o\ar o}}$, $\hol{\vee_{o\ar
-  o\ar o}}$, and $\hol{\forall_{(\alpha\ar
-  o)\ar o}}$ (for $\hol{\alpha\in T}$).  Type subscripts may be dropped if
+  o\ar o}}$, $\hol{\forall_{(\alpha\ar
+  o)\ar o}}$ (for $\hol{\alpha\in T}$) and $\hol{\Descr_{(\alpha\ar
+  o)\ar \alpha}}$ (for $\hol{\alpha\in T}$).  Type subscripts may be dropped if
 irrelevant or obvious. Similarly, parentheses may be avoided.  Binder
-notation $\hol{\all{X_\alpha} s_o}$ is used as shorthand for
+notation $\hol{\all{X_\alpha} s_o}$ and $\hol{\Descr {X_\alpha} s_o}$ is used as shorthand for
 $\hol{\forall_{(\alpha\ar o)\ar o}
-(\lam{X_\alpha} s_o)}$, and infix notation $\hol{s \vee t}$ is employed
+(\lam{X_\alpha} s_o)}$ and $\hol{\Descr(\lam{X_\alpha} s_o)}$, and infix notation $\hol{s \vee t}$ is employed
 instead of $\hol{((\vee s)\, t)}$. From the above connectives, other logical
 connectives, such as $\hol{\top}$, $\hol{\bot}$, $\hol{\wedge}$,
-$\hol{\supset}$, $\hol{\equiv}$ and $\hol{\exists}$, can be defined in the usual way.
+$\hol{\Impl}$, $\hol{\equiv}$ and $\hol{\exists}$, can be defined in the usual way.
 \end{definition}
@@
   $\hol{\beta}$ and $\hol{\eta}$.  For each $\hol{s_\alpha\in \HOL}$ there is a unique
-  \emph{$\beta$-normal form} and a unique \emph{$\beta\eta$-normal
+  \emph{$\hol{\beta}$-normal form} and a unique \emph{$\hol{\beta\eta}$-normal
     form}.
@@
 %\begin{definition}\label{homlassignment}
-A \emph{variable assignment} $g$ maps
+A \emph{variable assignment} $\hol{g}$ maps
 variables $\hol{X_\alpha}$ to elements in $\hol{D_\alpha}$. $\hol{g[d/W]}$ denotes the
@@
   \hol{D_\alpha}$ we have $\hol{\|s_o\|^{M,g[d/X_\alpha]}} = \hol{T}$
+\item $\hol{\|(\Descr_{(\alpha\ar o)\ar \alpha}(\lam{X_\alpha}
+    s_o))_o\|^{M,g}} = \hol{d}$ if there exists a unique $\hol{d}\in \hol{D_{\alpha}}$ such that
+  $\hol{\|s_o\|^{M,g[d/X_\alpha]}} = \hol{T}$, 
+otherwise  $\hol{\|(\Descr_{(\alpha\ar o)\ar \alpha}(\lam{X_\alpha}
+    s_o))_o\|^{M,g}} = \hol{e}$ for an arbitrary element $\hol{e}\in \hol{D_{\alpha}}$
 %\item $\|(\Box_{o\ar o}\, s_o)_o\|^{M,g,w} = T$ iff for all $v \in W$ with $w R v$ we have  $\|s_o\|^{M,g,v}  = T$
@@
  A model $\hol{M}=\hol{\langle D, I \rangle}$ is called a
- \emph{standard model} iff for all $\alpha,\beta\in T$ we have
- $D_{\alpha\ar\beta} = \{ f \mid f : D_\alpha \longrightarrow D_\beta
- \}$. In a \emph{Henkin model} function spaces are not necessarily
- full. Instead it is only required that $D_{\alpha\ar\beta}
- \subseteq \{ f \mid f : D_\alpha \longrightarrow D_\beta \}$ (for all
- $\alpha,\beta\in T$) and that the valuation function 
- $\|\cdot\|^{M,g}$ from above is total (i.e., every term denotes). Any standard model is obviously
+ \emph{standard model} iff for all $\hol{\alpha,\beta}\in \hol{T}$ we have
+ $\hol{D_{\alpha\ar\beta}} = \{ f \mid f : \hol{D_\alpha} \longrightarrow \hol{D_\beta}\}$. In a \emph{Henkin model} function spaces are not necessarily
+ full. Instead it is only required that $\hol{D_{\alpha\ar\beta}}
+ \subseteq \{ f \mid f : \hol{D_\alpha} \longrightarrow \hol{D_\beta}\}$ (for all
+ $\hol{\alpha,\beta}\in \hol{T}$) and that the valuation function 
+ $\hol{\|\cdot\|^{M,g}}$ from above is total (i.e., every term denotes). Any standard model is obviously
  also a Henkin model. We consider Henkin models in the remainder.
@@
 \begin{definition}\label{homlvalid}
-A formula $s_o$ is \emph{true} in model $M$ 
-under assignment $g$ iff $\|s_o\|^{M,g} = T$; this is also denoted
-as $M,g \models^\HOL s_o$.  A formula $s_o$ is called \emph{valid} in
-$M$, which is denoted as $M \models^\HOL s_o$, iff $M,g \models^\HOL s_o$ for all
-assignments $g$. Finally, a formula $s_o$ is called
-\emph{valid}, which we denote by $\models^\HOL s_o$, iff $s_o$ is valid for
-all $M$. Moreover, we write $\Gamma\models^\HOL \Delta$ (for sets of
- formulas $\Gamma$ and $\Delta$) iff there is a model $M$ and an assignment $g$ such that  
- $M,g \models^\HOL s_o$ for all $s_o\in \Gamma$ and $M,g \models^\HOL t_o$ for at least one $t_o\in \Delta$.
+A formula $\hol{s_o}$ is \emph{true} in model $M$ 
+under assignment $\hol{g}$ iff $\hol{\|s_o\|^{M,g}} = \hol{T}$; this is also denoted
+as $\hol{M,g \models^\HOL s_o}$.  A formula $\hol{s_o}$ is called \emph{valid} in
+$\hol{M}$, which is denoted as $\hol{M \models^\HOL s_o}$, iff $\hol{M,g \models^\HOL s_o}$ for all
+assignments $\hol{g}$. Finally, a formula $\hol{s_o}$ is called
+\emph{valid}, which we denote by $\hol{\models^\HOL s_o}$, iff $\hol{s_o}$ is valid for
+all $\hol{M}$. Moreover, we write $\hol{\Gamma\models^\HOL \Delta}$ (for sets of
+ formulas $\hol{\Gamma}$ and $\hol{\Delta}$) iff there is a model $\hol{M}$ and an assignment $\hol{g}$ such that  
+ $\hol{M,g \models^\HOL s_o}$ for all $\hol{s_o}\in \hol{\Gamma}$ and $\hol{M,g \models^\HOL t_o}$ for at least one $\hol{t_o}\in \hol{\Delta}$.
 \end{definition}
@@
 
-\section{Sound and Complete Embedding of $\FFOL$ in HOL}
-Todo ... the embedding in Isabelle/HOL is depicted in 
-figure \ref{pic1}
-
-\begin{figure}[t]
+\begin{figure}[tp]
  \includegraphics[width=\textwidth]{EmbeddingPic}
@@
 
-In this framework partial and total functions are modelled as follows: 
-A function $f$ is total if and only if for all $x$ we have $\ex x \imp \ex(f x)$ 
-For partial functions $f$ we may have some $x$ such that $\ex x$ but not
- $\ex(f x)$. A function $f$ is strict  if  and only if for all $x$
-we have $\ex(f x) \imp \ex x$.
+\section{Shallow Semantical Embedding of $\FFOL$ in HOL}
+
+The existence predicate $E$ is realized in the embedding as a $\HOL$
+predicate $\hol{\ex}$ of type $\hol{ i\ar o}$; we assume that a
+respective constant symbol is given in the signature of \HOL.  The raw domain $\hol{D}$ is simply
+associated with the set of all objects of type $\hol{i}$, respectively
+with the universal
+predicate $\hol{\lambda X_i. T}$. Moreover, let
+constant symbol $\hol{\star}$ of type $i$ be in the signature of
+\HOL. We assume that $\hol{\|E \star\|^{M,g}=F}$ for all $\hol{M,g}$
+i.e. that the element denoted by $\hol{\star}$ is not an element of
+the domain of existing objects denoted by $\hol{\ex}$.
+
+\begin{definition}[Embedding of $\FFOL$ in \HOL]
+Given a formula $s \in \FFOL$. We map each language construct $s$ in the
+signature of $\FFOL$ to a corresponding term $\map{s}$ of \HOL. This
+mapping is defined as follows:
+
+\begin{tabular}{lcll}
+$\map{x}$    & := & $\hol{X_i}$ &for all $x\in \V$\\
+$\map{f(t^1,\ldots,t^n)}$    & := & $\hol{(f \map{t^1} \ldots \map{t^n})}$  \quad
+              & for all $n$-ary $f\in F$\\
+ & & &  $\hol{f}$ has type $\hol{\underbrace{{i \ar
+               \ldots  \ar i} \ar }_{n\geq o} i}$\\
+%$\map{p}$    & := & $\hol{p_o}$ & for all $0$-ary $p\in \P$\\
+$\map{s = t}$    & := & $\hol{\map{s} = \map{t}}$ \\
+$\map{p(t^1,\ldots,t^n)}$    & := & $\hol{(p \map{t^1} \ldots \map{t^n})}$  \quad
+             &  for all $n$-ary $p\in P$ \\ 
+   & & & $\hol{p}$ has type $\hol{\underbrace{{i \ar
+               \ldots  \ar i} \ar }_{n\geq o} o}$\\
+$\map{\neg \varphi}$ & := &  $\hol{\neg\map{\varphi}}$  \\
+$\map{\varphi \Impl \psi}$ & := &  $\hol{ \map{\varphi} \Impl \map{\psi}}$  \\
+$\map{\forall x. s}$ & := &  $\hol{\forall X_i. \ex
+                       X_i \Impl \map{s}}$   \\
+$\map{\Descr x. s}$ & := &  $\hol{\textbf{IfThenElse}}$ \\
+  & & \quad $\hol{(\exists x. \ex x \wedge \map{s} \wedge (\forall
+      y. (\ex y \wedge ((\lambda X_i. \map{s}) y)) \Impl y = x))}$ \\
+  & & \quad $\hol{ (\Descr  X_i. \map{s})}$ \\
+  & & \quad $\hol{\star}$  \\
+\end{tabular}
+where $\hol{\textbf{IfThenElse}}$ is an abbreviation for the term
+$\hol{\lam{S_o}\lam{X_i}\lam{Y_i}. \Descr Z_i. (S_o \wedge Z = X) \vee
+(\neg S_o \wedge Z
+= Y)}$.
+
+Further connectives can be introduced as usual: $r \vee  s := \neg r
+\Impl s$, $r \wedge  s := \neg (\neg r \vee \neg s)$, 
+\end{definition}
+
+Todo ... the embedding in Isabelle/HOL is depicted in 
+figure \ref{pic1}
+
+% In this framework partial and total functions are modelled as follows: 
+% A function $f$ is total if and only if for all $x$ we have $\ex x \imp \ex(f x)$ 
+% For partial functions $f$ we may have some $x$ such that $\ex x$ but not
+%  $\ex(f x)$. A function $f$ is strict  if  and only if for all $x$
+% we have $\ex(f x) \imp \ex x$.
 
@@
 
-The stepwise evolution has been described in
-\cite{R58}. Below we summarise these experiments.
-However, first we describe some basic modeling decisions for the
-technical encoding in Isabelle/HOL. The Isabelle/HOL sources of our experiments are
-available at \url{todo-sources}.
-
-\begin{table} \centering \normalsize
+The stepwise evolution has been described in \cite{R58}. Below we
+summarise these experiments.  However, first we describe some basic
+modeling decisions for the technical encoding in Isabelle/HOL. The
+Isabelle/HOL sources of our experiments are available at
+\url{todo-sources}. Note that in these sources we did add neither the
+definite description operator nor the designated undefined object
+$\star$, since both were not required in our experiments.
+
+\begin{table}[tp] \centering \normalsize
 \begin{tabular}{ll}

### 2017-04-26 FreeLogic/2017-Journal/article.tex
update

@@
 
+%\usepackage{authblk}
+
 %
@@
 
-\title{Automating Free Logic in HOL, with an Application in Category Theory\thanks{Mention DFG grants ...}}
+\title{Automating Free Logic in HOL, with an Application in Category Theory}
 %\title{Free Logic and Axiom Systems for Category Theory in HOL\thanks{Mention DFG grants ...}}
@@
 
-\author{Christoph Benzm\"uller       \and
-      Dana Scott 
+\author{Christoph Benzm\"uller  and Dana S. Scott}
+\institute{Christoph Benzm\"uller \at
+   University of Luxembourg, Luxembourg \& Freie Universit\"at Berlin, Berlin, Germany \\
+%   Stanford University, CSLI/Cordura Hall, Stanford, CA 94305-4115, U.S. \\
+   \email{c.benzmueller@gmail.com} \\
+% \\
+ %            \emph{Present address:} of F. Author  %  if needed
+Dana S. Scott \at
+Visiting Scholar at University of Califormia, Berkeley,  USA \\
+  \email{dana.scott@cs.cmu.edu}
 }
 
+\date{\today}                     %% if you don't need date to appear
+
+% \author{Christoph Benzm\"uller       \and
+%       Dana Scott 
+% }
+
 %\authorrunning{Short form of author list} % if too long for running head
 
-\institute{F. Author \at
-              first address \\
-              Tel.: +123-45-678910\\
-              Fax: +123-45-678910\\
-              \email{fauthor@example.com}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-           \and
-           S. Author \at
-              second address
-}
+% \institute{F. Author \at
+%               first address \\
+%               Tel.: +123-45-678910\\
+%               Fax: +123-45-678910\\
+%               \email{fauthor@example.com}           %  \\
+% %             \emph{Present address:} of F. Author  %  if needed
+%            \and
+%            S. Author \at
+%               second address
+% }
 
@@
   application of higher-order interactive and automated theorem
-  provers (and their integrated subprovers) for the formalisation and
+  provers for the formalisation and
   verification of free logic theories.  
@@
 
-To demonstrate the practical relevance of our new system, we present,
-in the second part of this article, a stepwise development of axiom
+To demonstrate the practical relevance of our new system, we present
+in \S4 a stepwise development of axioms
 systems for category theory by generalizing the standard axioms for a
@@
 formalizations involving the kind of logic required (free logic) can
-be implemented and validated within modern proof assistants.
-
-A total of eight different axiom systems is studied. The systems I-VI
-are shown to be equivalent. The axiom system VII slightly modifies
-axiom system VI to obtain (modulo notational transformation) the set
-of axioms as proposed by Freyd and Scedrov in their textbook
-``Categories, Allegories'' \cite{FreydScedrov90}, published in 1990;
-see also Subsection \ref{subsec:FreydNotation} where we present their
-original system.  While the axiom systems I-VI are shown to be
-consistent, a constricted inconsistency result is obtained for system
-VII (when encoded in free logic where free variables range over all
-objects): We can prove $\exists x. \neg(\ex x) \Impl False$, where
-$\ex$ is the existence predicate. Read this as: If there are undefined
-objects, e.g. the value of an undefined composition $x\cdot y$
-then we have falsity.  By contraposition, all objects (and thus all
-compositions) must exist. But when we assume the latter, then the
-axiom system VII essentially reduces categories to monoids.  We note
-that axiom system V, which avoids this problem, corresponds to a set
-of axioms proposed by Scott \cite{Scott79} in the 1970s. The
-problem can also be avoided by restricting the variables in axiom
-system VII to range only over existing objects and by postulating
-strictness conditions.  This gives us axiom system VIII.
+be implemented and validated within modern proof assistants such as
+Isabelle/HOL.  We also address the relation of our axioms systems to
+alternative proposals from the literature, including an axiom set
+proposed by Freyd and Scedrov in their textbook ``Categories,
+Allegories'' \cite{FreydScedrov90} for which we reveal a technical
+flaw: either all operations, e.g. morphism composition, are total or
+their axiom system is inconsistent. The repair for this problem is
+quite straightforward, however. The solution essentially corresponds
+to a set of axioms proposed by Scott \cite{Scott79} in the 1970s.
+
+% \marginpar{will rewrite this part}
+% A total of eight different axiom systems is studied. The systems I-VI
+% are shown to be equivalent. The axiom system VII slightly modifies
+% axiom system VI to obtain (modulo notational transformation) the set
+% of axioms as proposed by Freyd and Scedrov in their textbook
+% ``Categories, Allegories'' \cite{FreydScedrov90}, published in 1990;
+% see also Subsection \ref{subsec:FreydNotation} where we present their
+% original system.  While the axiom systems I-VI are shown to be
+% consistent, a constricted inconsistency result is obtained for system
+% VII (when encoded in free logic where free variables range over all
+% objects): We can prove $\exists x\lambdot \neg(\ex x) \Impl False$, where
+% $\ex$ is the existence predicate. Read this as: If there are undefined
+% objects, e.g. the value of an undefined composition $x\cdot y$
+% then we have falsity.  By contraposition, all objects (and thus all
+% compositions) must exist. But when we assume the latter, then the
+% axiom system VII essentially reduces categories to monoids.  We note
+% that axiom system V, which avoids this problem, corresponds to a set
+% of axioms proposed by Scott \cite{Scott79} in the 1970s. The
+% problem can also be avoided by restricting the variables in axiom
+% system VII to range only over existing objects and by postulating
+% strictness conditions.  This gives us axiom system VIII.
 
@@
 
-We now formally introduce the syntax and semantics of free logic as
+We now formally introduce the syntax and semantics of Scott's \cite{Scott67} free logic as
 assumed in the remainder of this article. We refer to this logic with $\FFOL$.
@@
 \item given formulas $r$ and $s$ of $\FFOL$, then $\neg r$, $r
-  \Impl s$ and $\forall x. r$ are (compound) formulas of $\FFOL$
-\item given a formula $r$ of $\FFOL$, then $\Descr x. r$ is a
+  \Impl s$ and $\forall x\lambdot r$ are (compound) formulas of $\FFOL$
+\item given a formula $r$ of $\FFOL$, then $\Descr x\lambdot r$ is a
   term of $\FFOL$ (definite  description)
@@
 \begin{definition}[Dual-domain semantics of $\FFOL$]
-  A \emph{model structure for $\FFOL$} consists of a triple
-  $\langle D, \ex, I, \star\rangle$, where $D$ is a non-empty raw domain of
+  A \emph{model structure for $\FFOL$} consists of a quadruple
+  $M = \langle D, \ex, I, \star\rangle$, where $D$ is a non-empty raw domain of
   objects, $\ex\subseteq D$ a possible empty set of ``existing''
@@
   Given a variable assignment $g$, we
-  define the interpretation function $\|\cdot\|^{I,g}$ for terms and formulas of
+  define the interpretation function $\|\cdot\|^{M,g}$ for terms and formulas of
   $\FFOL$ as follows:
@@
 \begin{enumerate}
-\item $\| x \|^{I,g} = g(x)$ for variable symbols $x\in\V$
-\item $\| c \|^{I,g} = I(c)$, where $c\in\F$ is an $0$-ary function symbol
-\item $\| f(t_1,\ldots,t_n)\|^{I,g} = I(f)(\| t_1 \|^{I,g},\ldots,\|
-  t_n \|^{I,g})$, where $f\in\F$ is an $n$-ary ($n\geq 1$) function symbol
-\item $\| \Descr x. r \|^{I,g} = d \in \ex$, such that $\| r
-  \|^{I,g[d/x]} = \True$ and  $\| r
-  \|^{I,g[d'/x]} = \False$ for all $d'\not=d\in \ex$ (i.e. $d$ is the
+\item $\| x \|^{M,g} = g(x)$ for variable symbols $x\in\V$
+\item $\| c \|^{M,g} = I(c)$, where $c\in\F$ is an $0$-ary function symbol
+\item $\| f(t_1,\ldots,t_n)\|^{M,g} = I(f)(\| t_1 \|^{M,g},\ldots,\|
+  t_n \|^{M,g})$, where $f\in\F$ is an $n$-ary ($n\geq 1$) function symbol
+\item $\| \Descr x\lambdot r \|^{M,g} = d \in \ex$, such that $\| r
+  \|^{M,g[d/x]} = \True$ and  $\| r
+  \|^{M,g[d'/x]} = \False$ for all $d'\not=d\in \ex$ (i.e. $d$ is the
   unique existing object for which $r$ holds); if there is no
-  such $d\in \ex$, then $\| \Descr x. r \|^{I,g} = \star$
+  such $d\in \ex$, then $\| \Descr x\lambdot r \|^{M,g} = \star$
 \end{enumerate}
@@
 \begin{enumerate}
-\item $\| q \|^{I,g} = I(q)$, where $q\in\P$ is an $0$-ary predicate
+\item $\| q \|^{M,g} = I(q)$, where $q\in\P$ is an $0$-ary predicate
   symbol
-\item $\| t_1 = t_2 \|^{I,g} = \True$ iff $\| t_1 \|^{I,g} = \| t_2
-  \|^{I,g}$ (this basic notion of primitive equality on $D$ implies that equations such as $1/0 = 1/0$ are
-  evaluated to $\True$; later, in Section \ref{??}, we will
+\item $\| t_1 = t_2 \|^{M,g} = \True$ iff $\| t_1 \|^{M,g} = \| t_2
+  \|^{M,g}$ (this basic notion of primitive equality on $D$ implies that equations such as $1/0 = 1/0$ are
+  evaluated to $\True$; later, in \S4, we will
   define and utilise further notions of equality, including \emph{Kleene equality}
   and \emph{existing equality}).
-\item $\| p(t_1,\ldots,t_n) \|^{I,g} = \True$ iff $(\| t_1 \|^{I,g},\ldots,\|
-  t_n \|^{I,g}) \in I(p)$ for $n$-ary ($n\geq 1$) predicate symbols
+\item $\| p(t_1,\ldots,t_n) \|^{M,g} = \True$ iff $(\| t_1 \|^{M,g},\ldots,\|
+  t_n \|^{M,g}) \in I(p)$ for $n$-ary ($n\geq 1$) predicate symbols
   $p\in\P$
-\item $\| \neg r \|^{I,g} = \True$ iff $\| r \|^{I,g} = \False$
-\item $\| r \Impl s \|^{I,g} = \True$ iff $\| r \|^{I,g} = \False$
-  or $\| s \|^{I,g} = \True$
-\item $\| \forall x. r  \|^{I,g} = \True$ iff for all $d \in \ex$ we
-  have $\|  r  \|^{I,g[d/x]} = \True$ % (here $g[d/x]$ denotes the
+\item $\| \neg r \|^{M,g} = \True$ iff $\| r \|^{M,g} = \False$
+\item $\| r \Impl s \|^{M,g} = \True$ iff $\| r \|^{M,g} = \False$
+  or $\| s \|^{M,g} = \True$
+\item $\| \forall x\lambdot r  \|^{M,g} = \True$ iff for all $d \in \ex$ we
+  have $\|  r  \|^{M,g[d/x]} = \True$ % (here $g[d/x]$ denotes the
   % variable assignment that is identical to $g$, except for variable
@@
 
-\begin{definition}\label{homlvalid}
+\begin{definition}[Validity]\label{ffollvalid}
   A formula $s_o$ is \emph{true} in model $M$ under assignment $g$ iff
-  $\|s_o\|^{M,g} = T$; this is also denoted as $M,g \models s_o$.  A
+  $\|s_o\|^{M,g} = T$; this is also denoted as $M,g \models^\FFOL s_o$.  A
   formula $s_o$ is called \emph{valid} in $M$, which is denoted as
-  $M \models s_o$, iff $M,g \models s_o$ for all assignments
+  $M \models^\FFOL s_o$, iff $M,g \models^\FFOL s_o$ for all assignments
   $g$. Finally, a formula $s_o$ is called \emph{valid}, which we
-  denote by $\models s_o$, iff $s_o$ is valid for all $M$. Moreover,
-  we write $\Gamma\models \Delta$ (for sets of formulas $\Gamma$ and
+  denote by $\models^\FFOL s_o$, iff $s_o$ is valid for all $M$. Moreover,
+  we write $\Gamma\models^\FFOL \Delta$ (for sets of formulas $\Gamma$ and
   $\Delta$) iff there is a model $M$ and an assignment $g$ such that
-  $M,g \models s_o$ for all $s_o\in \Gamma$ and $M,g \models t_o$ for
+  $M,g \models^\FFOL s_o$ for all $s_o\in \Gamma$ and $M,g \models^\FFOL t_o$ for
   at least one $t_o\in \Delta$.
@@
 \begin{definition}[Syntax of $\HOL$]\label{holgrammar}
-The language of higher-order logic $\HOL$ is defined by the following
-grammar:\footnote{Ednote: Maybe better to define this analagous to $\FFOL$.}
+The language of higher-order logic $\HOL$ with primitive equality and
+choice is defined by the following
+grammar:\footnote{It is well known that we could work with a much smaller set
+  of logical connectives, see e.g. \cite{Andrews02}. The choice here is motivated by the
+  signature supported in higher-order automated theorem provers such
+  as LEO-II \cite{LEO-II} and Leo-III \cite{Leo-III}.}
 \begin{align*} 
   \hol{s},\hol{t} \quad ::= \quad & \hol{p_\alpha} \mid \hol{X_\alpha} \mid \hol{(\lam{X_\alpha}
-  s_\beta)_{\alpha\ar\beta}} \mid \hol{(s_{\alpha\ar\beta}\, t_\alpha)_\beta} \mid  \hol{\neg_{o\ar o}\, s_o} \mid \\
+  s_\beta)_{\alpha\ar\beta}} \mid \hol{(s_{\alpha\ar\beta}\,
+                                    t_\alpha)_\beta} \mid
+                                    \hol{s_\alpha = t_\alpha} \mid
+                                    \hol{\neg_{o\ar o}\, s_o} \mid\\
   & \hol{(({\vee_{o\ar o\ar o}}\,s_o)\,t_o)} \mid \hol{\forall_{(\alpha\ar
@@
 irrelevant or obvious. Similarly, parentheses may be avoided.  Binder
-notation $\hol{\all{X_\alpha} s_o}$ and $\hol{\Descr {X_\alpha} s_o}$ is used as shorthand for
+notation $\hol{\all{X_\alpha} s_o}$ and $\hol{\Descr {X_\alpha}\lambdot s_o}$ is used as shorthand for
 $\hol{\forall_{(\alpha\ar o)\ar o}
@@
 connectives, such as $\hol{\top}$, $\hol{\bot}$, $\hol{\wedge}$,
-$\hol{\Impl}$, $\hol{\equiv}$ and $\hol{\exists}$, can be defined in the usual way.
+$\hol{\Impl}$, $\hol{\equiv}$ and $\hol{\exists}$, can be defined in
+the usual way. For example, $\hol{\Impl}$ can be defined as $\hol{\lam{X_o}\lam{Y_o}
+  \neg X \vee Y}$ and $\hol{\wedge}$ as $\hol{\lam{X_o}\lam{Y_o}
+  \neg (\neg X \vee \neg Y)}$.
 \end{definition}
@@
 
-\begin{definition}\label{homlframe}
+\begin{definition}[Frame for \HOL]\label{homlframe}
 A \emph{frame} $\hol{D}$ is a collection $\hol{\{D_\alpha\}_{\alpha\in\entity{T}}}$
-of nonempty sets $\hol{D_\alpha}$, such that $\hol{D_o = \{T,F\}}$
-(for truth and falsehood).  The
+of nonempty sets $\hol{D_\alpha}$, such that $\hol{D_o} = \{\True,\False\}$
+(where, as before, $\True$ and $\False$ denote truth and falsehood).  The
 $\hol{D_{\alpha\ar\beta}}$ are collections of functions mapping
@@
 
-\begin{definition}\label{holmodel}
+\begin{definition}[Model for \HOL]\label{holmodel}
   A \emph{model} for \HOL is a tuple $\hol{M}=\hol{\langle D, I \rangle}$, where
@@
 
-\begin{definition}\label{holvalue}
+\begin{definition}[Evaluation Function]\label{holvalue}
   The \emph{value} $\hol{\| s_\alpha\|^{M,g}}$ of a \HOL term
@@
   $\hol{d}\in \hol{D_\alpha}$
-\item $\hol{\|(\neg_{o\ar o}\, s_o)_o\|^{M,g}} = \hol{T}$ iff $\hol{\|s_o\|^{M,g}} = \hol{F}$
+\item $\hol{\|s_\alpha = t_\alpha\|^{M,g}} = {\True}$ iff $\hol{\|s_\alpha\|^{M,g}} = \hol{\|t_\alpha\|^{M,g}} $
+\item $\hol{\|(\neg_{o\ar o}\, s_o)_o\|^{M,g}} = {\True}$ iff $\hol{\|s_o\|^{M,g}} = {\False}$
 \item $\hol{\|(({\vee_{o\ar o\ar o}}\,s_o)\,t_o)_o\|^{M,g}} =
-  \hol{T}$ iff\, $\hol{\|s_o\|^{M,g}} = \hol{T}$ or $\hol{\|t_o\|^{M,g}}
-  = \hol{T}$
-\item $\hol{\|(\forall_{(\alpha\ar o)\ar o}(\lam{X_\alpha}
-    s_o))_o\|^{M,g}} = \hol{T}$ iff for all $\hol{d}\in
-  \hol{D_\alpha}$ we have $\hol{\|s_o\|^{M,g[d/X_\alpha]}} = \hol{T}$
+  {\True}$ iff\, $\hol{\|s_o\|^{M,g}} = {\True}$ or $\hol{\|t_o\|^{M,g}}
+  = {\True}$
+\item \sloppy $\hol{\|(\forall_{(\alpha\ar o)\ar o}(\lam{X_\alpha}
+    s_o))_o\|^{M,g}} = {\True}$ iff for all $\hol{d}\in
+  \hol{D_\alpha}$ we have $\hol{\|s_o\|^{M,g[d/X_\alpha]}} = {\False}$
 \item $\hol{\|(\Descr_{(\alpha\ar o)\ar \alpha}(\lam{X_\alpha}
     s_o))_o\|^{M,g}} = \hol{d}$ if there exists a unique $\hol{d}\in \hol{D_{\alpha}}$ such that
-  $\hol{\|s_o\|^{M,g[d/X_\alpha]}} = \hol{T}$, 
+  $\hol{\|s_o\|^{M,g[d/X_\alpha]}} = {\True}$, 
 otherwise  $\hol{\|(\Descr_{(\alpha\ar o)\ar \alpha}(\lam{X_\alpha}
@@
 
-\begin{definition}\label{homlhenkinmodel}
+\begin{definition}[Standard model and Henkin model]\label{homlhenkinmodel}
  A model $\hol{M}=\hol{\langle D, I \rangle}$ is called a
@@
 
-\begin{definition}\label{homlvalid}
+\begin{definition}[Validity]\label{homlvalid}
 A formula $\hol{s_o}$ is \emph{true} in model $M$ 
-under assignment $\hol{g}$ iff $\hol{\|s_o\|^{M,g}} = \hol{T}$; this is also denoted
+under assignment $\hol{g}$ iff $\hol{\|s_o\|^{M,g}} = {\True}$; this is also denoted
 as $\hol{M,g \models^\HOL s_o}$.  A formula $\hol{s_o}$ is called \emph{valid} in
@@
 
-\begin{figure}[tp]
- \includegraphics[width=\textwidth]{EmbeddingPic}
- \caption{Isabelle/HOL formalisation of $\FFOL$ in $\HOL$ \label{pic1}}
-\end{figure}
-
-\section{Shallow Semantical Embedding of $\FFOL$ in HOL}
-
-The existence predicate $E$ is realized in the embedding as a $\HOL$
-predicate $\hol{\ex}$ of type $\hol{ i\ar o}$; we assume that a
-respective constant symbol is given in the signature of \HOL.  The raw domain $\hol{D}$ is simply
-associated with the set of all objects of type $\hol{i}$, respectively
-with the universal
-predicate $\hol{\lambda X_i. T}$. Moreover, let
-constant symbol $\hol{\star}$ of type $i$ be in the signature of
-\HOL. We assume that $\hol{\|E \star\|^{M,g}=F}$ for all $\hol{M,g}$
-i.e. that the element denoted by $\hol{\star}$ is not an element of
-the domain of existing objects denoted by $\hol{\ex}$.
+\section{Shallow Semantical Embedding of $\FFOL$ in $\HOL$}
+We now present a shallow embedding of $\FFOL$ in $\HOL$ by identifying
+the language constructs of $\FFOL$ with corresponding terms of $\HOL$.
+In this embedding raw domains $D$ of a $\FFOL$ model structures are
+identified with the $\HOL$ domains $\hol{D_i}$.  The subdomain $E$ of
+existing objects is characterized in the embedding by a $\HOL$
+predicate $\hol{\ex}$ of type $\hol{ i\ar o}$. Hence, we assume in the
+remainder that a respective uninterpreted constant symbol $\hol{\ex}$
+is given in the signature of $\HOL$. Moreover, we assume that an
+uninterpreted constant symbol $\hol{\star}$ of type $i$ be in the
+signature of $\HOL$. We assume that $\hol{\|E \star\|^{M,g}=F}$ for
+all $\hol{M,g}$, i.e. that the element denoted by $\hol{\star}$ is not
+an element of the domain of existing objects denoted by $\hol{\ex}$.
 
 \begin{definition}[Embedding of $\FFOL$ in \HOL]
-Given a formula $s \in \FFOL$. We map each language construct $s$ in the
-signature of $\FFOL$ to a corresponding term $\map{s}$ of \HOL. This
+Given a formula $s \in \FFOL$. We map $s$ to a corresponding term $\map{s}$ of \HOL. This
 mapping is defined as follows:
 
+\noindent
 \begin{tabular}{lcll}
 $\map{x}$    & := & $\hol{X_i}$ &for all $x\in \V$\\
-$\map{f(t^1,\ldots,t^n)}$    & := & $\hol{(f \map{t^1} \ldots \map{t^n})}$  \quad
+$\map{f(t^1,\ldots,t^n)}$    & := & $(\map{f}\ \map{t^1} \ldots \map{t^n})$  \quad
               & for all $n$-ary $f\in F$\\
- & & &  $\hol{f}$ has type $\hol{\underbrace{{i \ar
-               \ldots  \ar i} \ar }_{n\geq o} i}$\\
+ & & &  where $\map{f}=\hol{f_{\underbrace{{i \ar
+               \ldots  \ar i} \ar }_{n\geq o} i}} \in \map{F}$\\
 %$\map{p}$    & := & $\hol{p_o}$ & for all $0$-ary $p\in \P$\\
-$\map{s = t}$    & := & $\hol{\map{s} = \map{t}}$ \\
-$\map{p(t^1,\ldots,t^n)}$    & := & $\hol{(p \map{t^1} \ldots \map{t^n})}$  \quad
+$\map{s = t}$    & := & $\map{s} \hol{=} \map{t}$ \\
+$\map{p(t^1,\ldots,t^n)}$    & := & $(\map{p}\ \map{t^1} \ldots \map{t^n})$  \quad
              &  for all $n$-ary $p\in P$ \\ 
-   & & & $\hol{p}$ has type $\hol{\underbrace{{i \ar
-               \ldots  \ar i} \ar }_{n\geq o} o}$\\
-$\map{\neg \varphi}$ & := &  $\hol{\neg\map{\varphi}}$  \\
-$\map{\varphi \Impl \psi}$ & := &  $\hol{ \map{\varphi} \Impl \map{\psi}}$  \\
-$\map{\forall x. s}$ & := &  $\hol{\forall X_i. \ex
-                       X_i \Impl \map{s}}$   \\
-$\map{\Descr x. s}$ & := &  $\hol{\textbf{IfThenElse}}$ \\
-  & & \quad $\hol{(\exists x. \ex x \wedge \map{s} \wedge (\forall
-      y. (\ex y \wedge ((\lambda X_i. \map{s}) y)) \Impl y = x))}$ \\
-  & & \quad $\hol{ (\Descr  X_i. \map{s})}$ \\
-  & & \quad $\hol{\star}$  \\
+   & & & where $\map{p}=\hol{p_{\underbrace{{i \ar
+               \ldots  \ar i} \ar }_{n\geq o} o}} \in \map{P}$\\
+
+$\map{\neg s}$ & := &  $\hol{\neg}\map{s}$  \\
+$\map{s \Impl r}$ & := &  $\map{s} \hol{\Impl} \map{r}$  \\
+$\map{\forall x\lambdot r}$ & := &  $\hol{\forall X_i\lambdot  \ex
+                       X_i\ \Impl}\ \map{r}$   \\
+$\map{\Descr x\lambdot r}$ & := &  $\hol{\textbf{IfThenElse}}$ \\
+  & & \multicolumn{2}{c}{\quad $\hol{(\exists X_i\lambdot \ex X \wedge} \map{r}\ \hol{\wedge (\forall
+      Y_i\lambdot (\ex Y \wedge ((\lam{X_i}} \map{r}) \hol{Y)) \Impl Y = X))}$} \\
+  & & \quad $\hol{(\Descr  X_i\lambdot}\map{r})$ \\
+  & & \quad $\hol{\star}$  \\[1em]
 \end{tabular}
 where $\hol{\textbf{IfThenElse}}$ is an abbreviation for the term
-$\hol{\lam{S_o}\lam{X_i}\lam{Y_i}. \Descr Z_i. (S_o \wedge Z = X) \vee
+$$\hol{\lam{S_o}\lam{X_i}\lam{Y_i} \Descr Z_i\lambdot (S_o \wedge Z = X) \vee
 (\neg S_o \wedge Z
-= Y)}$.
-
-Further connectives can be introduced as usual: $r \vee  s := \neg r
-\Impl s$, $r \wedge  s := \neg (\neg r \vee \neg s)$, 
+= Y)}$$
+
+% Further connectives can be introduced as usual, e.g. $r \vee  s := \neg r
+% \Impl s$, $r \wedge  s := \neg (\neg r \vee \neg s)$, 
 \end{definition}
 
-Todo ... the embedding in Isabelle/HOL is depicted in 
-figure \ref{pic1}
+The above mapping induces mappings from the sets $\map{V}$, $\map{F}$ and $\map{P}$
+of $\FFOL$ to corresponding variables (of type $i$), uninterpreted function
+symbols and uninterpreted predicate symbols in \HOL.
+
+To prove soundness and completeness\footnote{Similar soundness and completeness proofs for
+  shallow semantical embeddings have been presented in \cite{C37} and
+  \cite{J31}.} for the embedding, a
+mapping from $\FFOL$ models into Henkin models is
+employed.
+This mapping utilizes a mapping of $FFOL$ variable
+assignments $g$ into corresponding $\HOL$ variable assignments
+$\hol{g}$ (remember that $\FFOL$  domains $D$ are  identified with 
+\HOL domains $\hol{D_i}$, i.e. $\map{D} = \hol{D_i}$): Let $g$ be a variable assignment for
+  $\FFOL$.  Then $\map{g}:
+  \map{V}\mapsto \map{D}$ for $\HOL$ is defined such that
+  $\map{g}(X_i) = \map{g} \map{x} = g(x)$ 
+for all $\hol{X_i}\in \map{V}$. 
+Finally, $\map{g}$ is extended to an assignment for arbitrary
+variables $\hol{Y_\alpha} \notin \map{V}$  by choosing
+$\map{g}(\hol{Y_\alpha}) = \hol{d}\in \hol{D_\alpha}$ arbitrary (for
+all types $\alpha$).
+
+\begin{definition}[Henkin model $\map{M}$ for $\FFOL$ model $M$]\label{def:hm}
+Given a $\FFOL$ model $M = \langle D, \ex, I, \star\rangle$. The Henkin
+model $\map{M} = \hol{\langle \{D_\alpha\}_{\alpha \in {T}},I \rangle}$ for
+$M$ is defined as follows: 
+\begin{itemize}
+\item $\hol{D_i} = D$
+\item $\hol{D_o} = \{\True,\False\}$
+\item $\hol{D_{\alpha\ar\beta}}$ are
+chosen as (not necessarily full) sets of functions from
+$\hol{D_\alpha}$ to $\hol{D_\beta}$. Remember, however, that the
+choice of $\hol{D_{\alpha\ar\beta}}$ must always ensure that 
+the valuation function 
+ $\hol{\|\cdot\|^{\map{M},\map{g}}}$ remains total, i.e. that
+ all terms denote. In particular, it is required that $\hol{D_{i\ar
+     o}}$ contains the element $\hol{I \ex}$ as characterized below.
+\item Let $X^i_i = \map{x^i}$
+  for $x^i\in V$.  The interpretation function $\hol{I}$ of $\map{M}$
+  is chosen as follows:
+\begin{itemize}
+\item  $\hol{I \star_i} = \star \in D$
+\item  For all
+    $\hol{d} \in \hol{D_i} = \map{D}$ we have: $(\hol{I \ex_{i\ar o}})(\hol{d}) =
+    \hol{T}$  if and only if $\hol{d} \in E$. Note that this implies $(\hol{I \ex})(\hol{\star_i}) = \hol{F}$.
+\item \sloppy For all $\hol{f_{{\underbrace{{i \ar
+               \ldots  \ar i} \ar }_{n\geq o} i}}} = \map{f} \in \map{F}$ we
+       have: $(\hol{I} \hol{f})(\hol{d^1},\ldots,\hol{d^n}) = (I f)(\hol{d^1},\ldots,\hol{d^n})$ for
+       all $\hol{d^i}\in \hol{D_i} = \map{D}$ ($i=1,\ldots,n$ and
+       $n\geq 0$).
+\item \sloppy For all $\hol{p_{{\underbrace{{i \ar
+               \ldots  \ar i} \ar }_{n\geq o} 0}}} = \map{p} \in \map{P}$ we
+       have: $(\hol{I} \hol{p})(\hol{d^1},\ldots,\hol{d^n}) = \hol{T}$
+       if and only if $(\hol{d^1},\ldots,\hol{d^n}) \in (I p)$ for
+       all $\hol{d^i}\in \hol{D_i} = \map{D}$ ($i=1,\ldots,n$ and
+       $n\geq 0$).
+\item For all other constants $\hol{c_\alpha}$, choose $\hol{I
+    c_\alpha} \in \hol{D_\alpha}$ arbitrary.\footnote{In fact, it may be safely assumed that there are
+  no other constant symbols given, except for the symbols in
+  $\map{F}$ and $\map{P}$, the symbols $\hol{\ex_{i\ar o}}$  and $\hol{\star_{i}}$ and the logical connectives.}
+\end{itemize}
+\end{itemize}
+
+It is not hard to verify that ${H}^{M}$ is a Henkin model.\footnote{In
+  $\map{M}$ we have merely fixed $D_i=D$ and the interpretations of
+  $\ex$ and $\star$.  These
+  choices are not in conflict with any of the requirements regarding
+  frames and interpretations. The existence of a valuation function
+  ${V}$ for an HOL interpretation crucially depends on how sparse the
+  function spaces have been chosen in frame $\{D_\alpha\}_{\alpha \in
+    {T}}$. Andrews \cite{Andrews72b} discusses criteria that are sufficient
+  to ensure the existence of a valuation function; in
+  $\map{M}$) these requirements are met.}
+
+% worlds $S$, $D_\utype$ is chosen as the first-order domain $D$ (cf.\
+% definition of $\lfloor g^{i} \rfloor$), $D_\proptype$ is chosen as the
+% set of sets of possible worlds $Q$ (cf.\ definition of $\lfloor g^{p}
+% \rfloor$)\footnote{Sets are identified with their characteristic
+%   functions.}, and all other sets $D_{\alpha\typearrow\beta}$ are
+% chosen as (not necessarily full) sets of functions from $D_\alpha$ to
+% $D_\beta$.  For all $D_{\alpha\typearrow\beta}$ the rule that
+% every term must have a denotation must be obeyed, in particular, it is required that
+% $D_{u^n\typearrow\proptype}$,
+% $D_{i\typearrow\proptype\typearrow\proptype}$ and
+% $D_{i\typearrow\utype\typearrow o}$ contain the elements $I
+% k_{u^n\typearrow\proptype}$, $I
+% f_{i\typearrow\proptype\typearrow\proptype}$ and $I
+% \exInW_{i\typearrow\utype\typearrow o}$ as characterized next. Interpretation $I$ is constructed as follows:
+\end{definition}
+
+\begin{lemma}\label{lemma:1} \sloppy
+  Let $\map{M}$ be a Henkin model for $\FFOL$ model $M$. For all
+  terms and formulas $s\in \FFOL$ and variable assignments $g$ we have $\| s
+  \|^{M,g} = \| \map s \|^{\map M, \map g}$.
+
+% $M,g,s
+%   \models \delta \text{\ if and only if\ } {V}(\lfloor g \rfloor [s/S_\itype],
+%   \lfloor \delta \rfloor\, S_\itype)=T$.
+
+\begin{proof} 
+  The proof is by induction on the structure of $s$.
+
+  For $s=x\in V$ the claim follows from the definition of
+  $\map{g}$. For $s=c\in F$ where $c$ is $0$-ary we get the claim by
+  the choice of $\hol{I}$ in $\map M$, and for $s=f(t^1,\ldots,t^n)$
+  where $f\in F$ is $n$-ary ($n\geq 1$) we additionally need to apply
+  the induction hypothesis. The arguments for $s=p\in P$ where $p$ is
+  $0$-ary and for $s=p(t^1,\ldots,t^n)$ where $p\in P$ is $n$-ary
+  ($n\geq 1$) are similar.  The most complicated case is when
+  $s=\Descr x\lambdot r$. We here consider two cases. We either have
+  $\| r \|^{M,g[d/x]} = \True$ and $\| r \|^{M,g[d'/x]} = \False$ for
+  all $d'\not=d\in \ex$ (i.e. $d$ is the unique existing object for
+  which $r$ holds) or there is no such $d\in \ex$. In the first case
+  we have $\| \Descr x\lambdot r \|^{M,g} = d \in \ex$. By the
+  definition of the embedding $\map{\ }$, definition of $\map M$ and
+  $\map g$, induction hypothesis and a series of tedious evaluation
+  steps in \HOL we get
+  $\| \map{\Descr x\lambdot r} \|^{\map M, \map g} = \| \hol{\Descr
+    x\lambdot \map{r}} \|^{\map M, \map g} = d \in \ex$
+  (for the very same $d$ as above). In the second case we have
+  $\| \Descr x\lambdot r \|^{M,g} = \star$. Again we apply the
+  definition of the embedding $\map{\ }$, the definition of $\map M$
+  and $\map g$, induction hypothesis and a series of tedious
+  evaluation steps in \HOL to verify that
+  $\| \map{\Descr x\lambdot r} \|^{\map M, \map g} = \hol{\star} =
+  \star$. The remaining cases are similar (actually simpler) and left to the reader.
+\end{proof}
+\end{lemma}
+
+\begin{theorem}[Soundness and Completeness of the Embedding]\ \\
+For all formulas $s\in FFOL$ we have
+ $\models^\FFOL s \text{ if and only if }  \models^\HOL \map{s}$
+
+ \begin{proof} 
+ (Soundness, $\leftarrow$) The proof is by
+   contraposition. Assume $\not\models^\FFOL s$, i.e, there is a
+   $\FFOL$ model $M$ and an assignment $g$ such that
+   $\|s\|^{M,g}=\False$. By Lemma \ref{lemma:1} we have $\| \map s
+   \|^{\map M, \map g}=\False$. Hence, we get $\not\models^\HOL \map{s}$.
+
+ (Completeness, $\rightarrow$) The proof is again by
+    contraposition and analogous to above.
+\end{proof}
+\end{theorem}
 
@@
 % we have $\ex(f x) \imp \ex x$.
+
+%\pagebreak
+
+In the remainder of this article we present an application of our
+framework for the exploration of axioms systems in category theory. In
+this context description is not required and we hence omit it in our 
+theory. Figure \ref{pic1} shows the embedding of $\FFOL$ in $\HOL$,
+encoded in Isabelle/HOL, 
+that we have employed in our experiments. A related Isabelle/HOL
+encoding of the above theory with description has been presented and  discussed in
+\cite{ICMS}.
+
+\begin{figure}[htp]
+ \includegraphics[width=\textwidth]{EmbeddingPic}
+ \caption{Isabelle/HOL formalisation of $\FFOL$ (without description) in $\HOL$ \label{pic1}}
+\end{figure}
 
@@
 
-\begin{table}[tp] \centering \normalsize
+\begin{table}[htp] \centering \normalsize
 \begin{tabular}{ll}
@@
  $S_{i}$ & $\ex(x \comp y) \imp (\ex x \wedge \ex y)$ \\
- $E_{i}$ & $\ex(x \comp y) \limp (\ex x \wedge \ex y \wedge (\exists z. z \comp
+ $E_{i}$ & $\ex(x \comp y) \limp (\ex x \wedge \ex y \wedge (\exists z\lambdot z \comp
          z \cong z \wedge x \comp z \cong x \wedge z \comp y \cong y))$ \\
  $A_{i}$ & $x\comp (y \comp z) \cong (x \comp y) \comp z$ \\
- $C_{i}$ & $\forall y. \exists i.  \id i \wedge i \comp y \cong y$ \\
- $D_{i}$ & $\forall x. \exists j.  \id j \wedge x \comp j \cong x$  \\
+ $C_{i}$ & $\forall y\lambdot \exists i\lambdot  \id i \wedge i \comp y \cong y$ \\
+ $D_{i}$ & $\forall x\lambdot \exists j\lambdot  \id j \wedge x \comp j \cong x$  \\
 \\
@@
         y)$ \\
- $E_{ii}$ & $\ex(x \comp y) \limp (\ex x \wedge \ex y \wedge (\exists z. z \comp
+ $E_{ii}$ & $\ex(x \comp y) \limp (\ex x \wedge \ex y \wedge (\exists z\lambdot z \comp
          z \cong z \wedge x \comp z \cong x \wedge z \comp y \cong y))$ \\
@@
 
-abbreviation I where \[\id i \ddef (\forall x. \ex(i \comp x) \imp i \comp
-x \cong x) \wedge (\forall x. \ex(x \comp i) \imp x \comp i \cong x)\]
+abbreviation I where \[\id i \ddef (\forall x\lambdot \ex(i \comp x) \imp i \comp
+x \cong x) \wedge (\forall x\lambdot \ex(x \comp i) \imp x \comp i \cong x)\]
 
@@
 
-\subsection{Axioms Set I}
+\subsection{Axioms Sets I and II}
  Axioms Set I is our most basic axiom set for category theory generalizing the 
@@
 \begin{tabular}{ll}
-Closure: & $ \forall a,b \in S.\ a \circ b \in S$ \\
-Associativity: & $\forall a,b,c \in S.\ a \circ (b \circ c) = (a \circ b) \circ c$ \\
-Identity: & $\exists id_S \in S. \forall a\in S.\ id_S\circ a = a = a \circ id_S$
+Closure: & $ \forall a,b \in S\lambdot \ a \circ b \in S$ \\
+Associativity: & $\forall a,b,c \in S\lambdot\ a \circ (b \circ c) = (a \circ b) \circ c$ \\
+Identity: & $\exists id_S \in S\lambdot \forall a\in S\lambdot \ id_S\circ a = a = a \circ id_S$
 \end{tabular}
@@
    found automatically by Sledgehammer.
-$$  \forall y. \exists i. \id i \wedge i \comp y \cong y
-\wedge (\forall j.d(\id j \wedge j \comp y \cong y) \imp i \cong j)
+$$  \forall y\lambdot \exists i\lambdot \id i \wedge i \comp y \cong y
+\wedge (\forall j\lambdot d(\id j \wedge j \comp y \cong y) \imp i \cong j)
 \quad 
     (\text{by } A_i, C_i, S_i) $$
-$$ \forall x. \exists j. \id j \wedge x \comp j \cong x \wedge
-(\forall i. (\id i \wedge x \comp i \cong x) \imp j \cong i) \quad   
+$$ \forall x\lambdot \exists j\lambdot \id j \wedge x \comp j \cong x \wedge
+(\forall i\lambdot (\id i \wedge x \comp i \cong x) \imp j \cong i) \quad   
     (\text{by }  A_i, D_i, S_i) $$
@@
    our formalization as follows: 
- $$\exists C, D. (\forall y. \id (C y) \wedge (C y) \comp y \cong y)
- \wedge (\forall x. \id (D x) \wedge x \comp (D x) \cong x) \wedge
+ $$\exists C, D\lambdot (\forall y\lambdot \id (C y) \wedge (C y) \comp y \cong y)
+ \wedge (\forall x\lambdot \id (D x) \wedge x \comp (D x) \cong x) \wedge
  D \not= C$$
@@
 
-\subsection{Axioms Set II}
+%\subsection{Axioms Set II}
 Axioms Set II is developed from Axioms Set I by Skolemization of the
@@
 such functions. Hence, we get a conservative extension of Axioms Set
-I. This could be done for any theory with an $\forall x. \exists i$.-axiom. The strictness axiom $S$ is extended, so
+I. This could be done for any theory with an $\forall x\lambdot \exists i$.-axiom. The strictness axiom $S$ is extended, so
 that strictness is now also postulated for the new Skolem functions
@@
 The left-to-right direction of existence axiom $E_{ii}$ is implied. 
-  $$E(x \comp y) \imp (E x \wedge E y \wedge (\exists z. z \comp z
+  $$E(x \comp y) \imp (E x \wedge E y \wedge (\exists z\lambdot z \comp z
   \cong z \wedge x \comp z \cong x \wedge z\comp y \cong y)) \quad
@@
 
-\subsection{Axioms Set III}
+\subsection{Axioms Set III, IV and V} \marginpar{will improve presentation}
 In Axioms Set III the existence  axiom  $E_{ii}$ from Axioms Set II  is simplified by taking advantage of 
@@
 
-\subsection{Axioms Set IV}
+%\subsection{Axioms Set IV}
 Axioms Set IV simplifies the axioms $C_{iii}$ and  $D_{iii}$ . However, as it turned 
@@
 
-\subsection{Axioms Set V}
+%\subsection{Axioms Set V}
 Axioms Set V has been proposed by Scott \cite{Scott79} in the 1970s. 
@@
  non-existing object of type $i$:
-$$(\exists x. \neg E x) \imp False$$
+$$(\exists x\lambdot \neg E x) \imp False$$
 
@@
 As a corollary from the above constricted inconsistency result we get that all  must be
-defined: $\forall x. E x$
+defined: $\forall x\lambdot E x$
 
@@
 \begin{acknowledgements}
-DFG projects \ldots todo
+This work has been supported by the DFG Heisenberg fellowship (BE
+2501/9-2, \emph{, Towards Computational Metaphysics}) of the first
+author.
+
+We thank G{\"u}nter Rote, Lutz Schröder and and Emil Weydert for their
+valuable comments to earlier drafts of this article .
+
 \end{acknowledgements}

### 2017-04-27 FreeLogic/2017-Journal/article.tex
update

@@
 
-\title{Automating Free Logic in HOL, with an Application in Category Theory}
+\title{Automating Free Logic in HOL, with an Experimental Application in Category Theory}
 %\title{Free Logic and Axiom Systems for Category Theory in HOL\thanks{Mention DFG grants ...}}
@@
 Dana S. Scott \at
-Visiting Scholar at University of Califormia, Berkeley,  USA \\
+Visiting Scholar at University of California, Berkeley,  USA \\
   \email{dana.scott@cs.cmu.edu}
@@
   category theory, but to demonstrate an elegant way to ``implement''
-  and utilise interactive and automated reasoning in free logic, and
+  and utilize interactive and automated reasoning in free logic, and
   to present respective experiments.
@@
 traditional classical or intuitionistic logics provide rather
-inadequate support for these challenge concepts.  Free logic offers a
+inadequate support for these challenge concepts.  Free logic \cite{Lambert60,Scott67,lambert02:_free_logic,sep-logic-free} offers a
 theoretically appealing solution, but is has been considered as rather
@@
 classical higher-order logic (HOL) \cite{B5}. The proposed solution
-employs a semantic embedding of free (or inclusive logic) in HOL. We
+employs a semantic embedding of free in HOL. We
 present an exemplary implementation of this idea in the mathematical
@@
 be implemented and validated within modern proof assistants such as
-Isabelle/HOL.  We also address the relation of our axioms systems to
+Isabelle/HOL.  We also address the relation of our axiom systems to
 alternative proposals from the literature, including an axiom set
@@
 within the proof assistant Isabelle/HOL via the
-Sledgehammer tool. Moreover, we have obtained
+Sledgehammer tool \cite{Sledgehammer}. Moreover, we have obtained
 very useful feedback at various stages from the model finder Nitpick
@@
 VII was discovered by automated theorem provers, which further
-emphasises the added value of automated theorem proving in this area.
-
-The content of article is combines, extends and clarifies the
+emphasizes the added value of automated theorem proving in this area.
+
+The content of article is based on the 
 contributions reported in two previous papers \cite{ICMS,ArXiv}.
@@
 \subsection{Free Logic}
-Free logic \cite{Lambert60,Scott67,lambert02:_free_logic} refers to a class of logic
+Free logic (respectively
+inclusive logic) 
+\cite{Lambert60,Scott67,lambert02:_free_logic,sep-logic-free} refers to a class of logic
 formalisms that are free of basic existence assumptions regarding the
@@
 (non-empty) domain $\D$, but a (possibly empty) set $\ex\subseteq \D$ is
-chosen to characterize the subdomain of ``existing'' resp. ``defined''
+chosen to characterize the subdomain of ``\emph{existing}'' resp. ``\emph{defined}''
 objects in $\D$. Quantification is
@@
 %In this framework partial and total functions are modelled as follows: 
-Moreover, a function $f$ is \emph{total} if and only if for all $x$ we have $\ex x \imp \ex(f x)$ 
+Moreover, a function $f$ is \emph{total} if and only if for all $x$ we
+have $\ex x \imp \ex(f x)$.\footnote{The predication $\ex x$ represents that $x$ is a
+  member of $E$.}
 For \emph{partial} functions $f$ we may have some $x$ such that $\ex x$ but not
@@
 % illustration of this notion of free logic is presented in Fig.~\ref{fig1}.
+
 \begin{figure}
@@
 \newcommand\firstellipse{(2,-5) ellipse (6cm and 4cm)}
-\newcommand\secondellipse{(0,-5.3) ellipse (3.5cm and 2.5cm)}1
+\newcommand\secondellipse{(0,-5.3) ellipse (3.5cm and 2.5cm)}
+\resizebox{.9\textwidth}{!}{ 
 \begin{tikzpicture}
@@
 \end{tikzpicture}
+}
 \caption{Illustration of the Semantical Domains of Free Logic \label{fig1}}
@@
 
-We now formally introduce the syntax and semantics of Scott's \cite{Scott67} free logic as
+We formally introduce the syntax and semantics of free logic as
 assumed in the remainder of this article. We refer to this logic with $\FFOL$.
@@
 \item given formulas $r$ and $s$ of $\FFOL$, then $\neg r$, $r
-  \Impl s$ and $\forall x\lambdot r$ are (compound) formulas of $\FFOL$
+  \Impl s$ and $\forall x\lambdot r$ are (compound) formulas of
+  $\FFOL$, and
 \item given a formula $r$ of $\FFOL$, then $\Descr x\lambdot r$ is a
-  term of $\FFOL$ (definite  description)
+  term of $\FFOL$ (definite  description).
 \end{enumerate}
@@
 
-Further formulas of $\FFOL$, including various defined notions of
+Further terms and formulas of $\FFOL$, including various defined notions of
 equality, can be introduced as abbreviations.
 
-  \emph{Substitution} of a term $r$ for a variable $x$
-  in a term $s$ is denoted by $[r/x]s$.
+  % \emph{Substitution} of a term $r$ for a variable $x$
+  % in a term $s$ is denoted by $[r/x]s$.
 
@@
 example, instead of a possible empty set of existing objects $\ex$, we
-could postulate non-emptiness of $\ex$. Here we closely
+could postulate non-emptiness of $\ex$. 
+In fact, our approach below can be easily adapted for different variants of free and
+inclusive logic.
+Here we closely
 follow the notion of free logic as proposed by Scott \cite{Scott67}.
 
-\begin{definition}[Dual-domain semantics of $\FFOL$]
-  A \emph{model structure for $\FFOL$} consists of a quadruple
+\begin{definition}[Model of $\FFOL$]
+  A \emph{model (structure) for $\FFOL$} consists of a quadruple
   $M = \langle D, \ex, I, \star\rangle$, where $D$ is a non-empty raw domain of
-  objects, $\ex\subseteq D$ a possible empty set of ``existing''
-  resp. ``defined'' objects, and $I$ an interpretation function
+  objects, $\ex\subseteq D$ a possible empty set of existing/defined objects, and $I$ an interpretation function
   mapping $0$-ary function symbols (constants) to defined objects $d\in \ex$, 
@@
   symbols (for $n\geq 1$) to $n$-ary relations
-  $D \times \ldots \times D$. Finally, $\star\in D\setminus \ex$ is a designated
+  $D \times \ldots \times D$. $\True$ or $\False$ denote truth and
+  felshood respectively. Finally, $\star\in D\setminus \ex$ is a designated
   (non-existing/undefined) object. 
-
-  Given a variable assignment $g$, we
-  define the interpretation function $\|\cdot\|^{M,g}$ for terms and formulas of
-  $\FFOL$ as follows:
+\end{definition}
+
+\begin{definition}[Evaluation Function for $\FFOL$]
+  The \emph{value} $\| s \|^{M,g}$ of a term or formula $s\in\FFOL$
+  in a model $M=\langle D, \ex, I, \star\rangle$ under assignment $g$ 
+  defined in the following way:
 \noindent
@@
   such $d\in \ex$, then $\| \Descr x\lambdot r \|^{M,g} = \star$
+ \newcounter{enumTemp}
+ \setcounter{enumTemp}{\theenumi}
 \end{enumerate}
@@
 \begin{enumerate}
+\setcounter{enumi}{\theenumTemp}
 \item $\| q \|^{M,g} = I(q)$, where $q\in\P$ is an $0$-ary predicate
   symbol
-\item $\| t_1 = t_2 \|^{M,g} = \True$ iff $\| t_1 \|^{M,g} = \| t_2
-  \|^{M,g}$ (this basic notion of primitive equality on $D$ implies that equations such as $1/0 = 1/0$ are
+\item $\| t_1 = t_2 \|^{M,g} = \True$ if and only if $\| t_1 \|^{M,g} = \| t_2
+  \|^{M,g}$ (this basic notion of primitive equality on $D$ implies
+  that equations between ``undefined'' terms such as $1/0 = 1/0$ are
   evaluated to $\True$; later, in \S4, we will
-  define and utilise further notions of equality, including \emph{Kleene equality}
-  and \emph{existing equality}).
-\item $\| p(t_1,\ldots,t_n) \|^{M,g} = \True$ iff $(\| t_1 \|^{M,g},\ldots,\|
+  define and utilize further notions of equality, including \emph{Kleene equality}
+  and \emph{existing equality}, which behave differently).
+\item $\| p(t_1,\ldots,t_n) \|^{M,g} = \True$ if and only if $(\| t_1 \|^{M,g},\ldots,\|
   t_n \|^{M,g}) \in I(p)$ for $n$-ary ($n\geq 1$) predicate symbols
   $p\in\P$
-\item $\| \neg r \|^{M,g} = \True$ iff $\| r \|^{M,g} = \False$
-\item $\| r \Impl s \|^{M,g} = \True$ iff $\| r \|^{M,g} = \False$
+\item $\| \neg r \|^{M,g} = \True$ if and only if $\| r \|^{M,g} = \False$
+\item $\| r \Impl s \|^{M,g} = \True$ if and only if $\| r \|^{M,g} = \False$
   or $\| s \|^{M,g} = \True$
-\item $\| \forall x\lambdot r  \|^{M,g} = \True$ iff for all $d \in \ex$ we
+\item $\| \forall x\lambdot r  \|^{M,g} = \True$ if and only if for all $d \in \ex$ we
   have $\|  r  \|^{M,g[d/x]} = \True$ % (here $g[d/x]$ denotes the
@@
 \begin{definition}[Validity]\label{ffollvalid}
-  A formula $s_o$ is \emph{true} in model $M$ under assignment $g$ iff
+  A formula $s_o$ is \emph{true} in model $M$ under assignment $g$ if and only if
   $\|s_o\|^{M,g} = T$; this is also denoted as $M,g \models^\FFOL s_o$.  A
   formula $s_o$ is called \emph{valid} in $M$, which is denoted as
-  $M \models^\FFOL s_o$, iff $M,g \models^\FFOL s_o$ for all assignments
+  $M \models^\FFOL s_o$, if and only if $M,g \models^\FFOL s_o$ for all assignments
   $g$. Finally, a formula $s_o$ is called \emph{valid}, which we
-  denote by $\models^\FFOL s_o$, iff $s_o$ is valid for all $M$. Moreover,
-  we write $\Gamma\models^\FFOL \Delta$ (for sets of formulas $\Gamma$ and
-  $\Delta$) iff there is a model $M$ and an assignment $g$ such that
-  $M,g \models^\FFOL s_o$ for all $s_o\in \Gamma$ and $M,g \models^\FFOL t_o$ for
-  at least one $t_o\in \Delta$.
+  denote by $\models^\FFOL s_o$, if and only if $s_o$ is valid for all
+  $M$. 
+% Moreover,
+%   we write $\Gamma\models^\FFOL \Delta$ (for sets of formulas $\Gamma$ and
+%   $\Delta$) if and only if there is a model $M$ and an assignment $g$ such that
+%   $M,g \models^\FFOL s_o$ for all $s_o\in \Gamma$ and $M,g \models^\FFOL t_o$ for
+%   at least one $t_o\in \Delta$.
 \end{definition}
@@
 Simple type theory, also referred to as classical higher-order logic
-(HOL), is an expressive logic formalism that allows for higher-order
-quantification, that is quantification over arbitrary set and function
-variables.  It is based on the simply typed
-$\lambda$-calculus\footnote{ For a detailed discussion of typed
-  $\lambda$-calculi, we refer to the
-  literature~\cite{DBLP:books/daglib/0032840}.  }
+(HOL) \cite{AndrewsSEP}, is an expressive logic formalism which is based on the simply typed
+$\lambda$-calculus~\cite{barendregt13book}. 
   %\footnote{
@@
     %stick here to the simply typed $\lambda$-calculus for a better understanding.}
-  and it has its origin in the work by
-  Church~\cite{DBLP:journals/jsyml/Church40}.
+  HOL has its origin in the work by
+  Church~\cite{Church40}.
+
+For a detailed discussion of the syntax, semantics and automation
+of  HOL we refer to the literature (see e.g.
+\cite{AndrewsSEP,B5,J6} and the
+references therein). Below we introduce a variant of \HOL with primitive equality
+and description.
 
@@
   The set $\hol{T}$ of simple types freely generated from a set of
-  basic types $\{\hol{o}, \hol{\mu}, \hol{\iota}\}$ using the function type
-  constructor $\hol{\ar}$. $\hol{o}$ is the type of Booleans,
-  $\hol{\mu}$ is the type of individuals, and type
-  $\hol{\iota}$ is employed as the type of possible worlds below. We
+  basic types $\{\hol{o}, \hol{i}\}$ using the function type
+  constructor $\hol{\ar}$. $\hol{o}$ is the type of Booleans and 
+  $\hol{i}$ is the type of individuals. We
   may avoid parentheses if the structure of a complex type is clear in context.
@@
 The language of higher-order logic $\HOL$ with primitive equality and
-choice is defined by the following
+description is defined by the following
 grammar:\footnote{It is well known that we could work with a much smaller set
-  of logical connectives, see e.g. \cite{Andrews02}. The choice here is motivated by the
-  signature supported in higher-order automated theorem provers such
-  as LEO-II \cite{LEO-II} and Leo-III \cite{Leo-III}.}
+  of logical connectives, see e.g. \S1.4 of Andrews's overview
+  article~\cite{AndrewsSEP}. The choice here closely reflects the
+  set of primitive connectives as chosen in higher-order automated theorem provers such
+  as LEO-II \cite{LEO}, Leo-III \cite{Leo-III} and Satallax \cite{Satallax}.}
 \begin{align*} 
@@
 $\hol{\neg_{o\ar o}}$, $\hol{\vee_{o\ar
-  o\ar o}}$, $\hol{\forall_{(\alpha\ar
-  o)\ar o}}$ (for $\hol{\alpha\in T}$) and $\hol{\Descr_{(\alpha\ar
-  o)\ar \alpha}}$ (for $\hol{\alpha\in T}$).  Type subscripts may be dropped if
+  o\ar o}}$, $\hol{=_{\alpha\ar\alpha\ar  o}}$, $\hol{\forall_{(\alpha\ar
+  o)\ar o}}$ and $\hol{\Descr_{(\alpha\ar
+  o)\ar \alpha}}$ (where $\hol{\alpha\in T}$).  Type subscripts may be dropped if
 irrelevant or obvious. Similarly, parentheses may be avoided.  Binder
@@
 
-  \emph{Substitution} of a term $\hol{A_\alpha}$ for a variable $\hol{X_\alpha}$
-  in a term $\hol{B_\beta}$ is denoted by $\hol{[A/X]B}$.  Since we consider
-  $\hol{\alpha}$-conversion implicitly, we assume the bound variables of $\hol{B}$
-  avoid variable capture.
+We assume familiarity with $\lambda$-conversion (e.g. \emph{$\alpha$-renaming} and
+\emph{$\beta\eta$-reduction}) and \emph{$\beta\eta$-normal forms}~\cite{barendregt13book}.
+
+  % \emph{Substitution} of a term $\hol{A_\alpha}$ for a variable $\hol{X_\alpha}$
+  % in a term $\hol{B_\beta}$ is denoted by $\hol{[A/X]B}$.  Since we consider
+  % $\hol{\alpha}$-conversion implicitly, we assume the bound variables of $\hol{B}$
+  % avoid variable capture.
 
 %\begin{definition}\label{homlbetaeta} %\footnote{\textbf{Chris:} Is Def.4 needed at all?}
-  Two common relations on terms are given by $\hol{\beta}$-reduction and
-  $\hol{\eta}$-reduction.  A $\hol{\beta}$-redex has the form $\hol{(\lam{X}s)t}$ and
-  $\hol{\beta}$-reduces to $\hol{[t/X]s}$.  An $\hol{\eta}$-redex has the form
-  $\hol{(\lam{X}s X)}$ where variable $\hol{X}$ is not free in $\hol{s}$; it
-  $\hol{\eta}$-reduces to $\hol{s}$.  We write $\hol{s\eqb t}$ to mean $\hol{s}$ can be
-  converted to $\hol{t}$ by a series of $\hol{\beta}$-reductions and expansions.
-  Similarly, $\hol{s\eqbe t}$ means $\hol{s}$ can be converted to $\hol{t}$ using both
-  $\hol{\beta}$ and $\hol{\eta}$.  For each $\hol{s_\alpha\in \HOL}$ there is a unique
-  \emph{$\hol{\beta}$-normal form} and a unique \emph{$\hol{\beta\eta}$-normal
-    form}.
+  % Two common relations on terms are given by $\hol{\beta}$-reduction and
+  % $\hol{\eta}$-reduction.  A $\hol{\beta}$-redex has the form $\hol{(\lam{X}s)t}$ and
+  % $\hol{\beta}$-reduces to $\hol{[t/X]s}$.  An $\hol{\eta}$-redex has the form
+  % $\hol{(\lam{X}s X)}$ where variable $\hol{X}$ is not free in $\hol{s}$; it
+  % $\hol{\eta}$-reduces to $\hol{s}$.  We write $\hol{s\eqb t}$ to mean $\hol{s}$ can be
+  % converted to $\hol{t}$ by a series of $\hol{\beta}$-reductions and expansions.
+  % Similarly, $\hol{s\eqbe t}$ means $\hol{s}$ can be converted to $\hol{t}$ using both
+  % $\hol{\beta}$ and $\hol{\eta}$.  For each $\hol{s_\alpha\in \HOL}$ there is a unique
+  % \emph{$\hol{\beta}$-normal form} and a unique \emph{$\hol{\beta\eta}$-normal
+  %   form}.
 % From this fact we know $s\eqb t$ ($s\eqbe t$) iff
@@
 
-\begin{definition}[Evaluation Function]\label{holvalue}
+\begin{definition}[Evaluation Function for \HOL]\label{holvalue}
   The \emph{value} $\hol{\| s_\alpha\|^{M,g}}$ of a \HOL term
@@
 \begin{enumerate}
-\item $\hol{\|p_\alpha\|^{M,g}} = \hol{I(p_\alpha)}$ and $\hol{\|X_\alpha\|^{M,g}} = \hol{g(X_\alpha)}$
+\item $\hol{\|p_\alpha\|^{M,g}} = \hol{I(p_\alpha)}$ 
+\item $\hol{\|X_\alpha\|^{M,g}} = \hol{g(X_\alpha)}$
 \item $\hol{\|(s_{\alpha\ar\beta}\, t_\alpha)_\beta\|^{M,g}} = \hol{\|s_{\alpha\ar\beta}\|^{M,g}(\|t_\alpha\|^{M,g})}$
@@
   $\hol{d}\in \hol{D_\alpha}$
-\item $\hol{\|s_\alpha = t_\alpha\|^{M,g}} = {\True}$ iff $\hol{\|s_\alpha\|^{M,g}} = \hol{\|t_\alpha\|^{M,g}} $
-\item $\hol{\|(\neg_{o\ar o}\, s_o)_o\|^{M,g}} = {\True}$ iff $\hol{\|s_o\|^{M,g}} = {\False}$
+\item $\hol{\|s_\alpha = t_\alpha\|^{M,g}} = {\True}$ if and only if $\hol{\|s_\alpha\|^{M,g}} = \hol{\|t_\alpha\|^{M,g}} $
+\item $\hol{\|(\neg_{o\ar o}\, s_o)_o\|^{M,g}} = {\True}$ if and only if $\hol{\|s_o\|^{M,g}} = {\False}$
 \item $\hol{\|(({\vee_{o\ar o\ar o}}\,s_o)\,t_o)_o\|^{M,g}} =
-  {\True}$ iff\, $\hol{\|s_o\|^{M,g}} = {\True}$ or $\hol{\|t_o\|^{M,g}}
+  {\True}$ if and only if\, $\hol{\|s_o\|^{M,g}} = {\True}$ or $\hol{\|t_o\|^{M,g}}
   = {\True}$
 \item \sloppy $\hol{\|(\forall_{(\alpha\ar o)\ar o}(\lam{X_\alpha}
-    s_o))_o\|^{M,g}} = {\True}$ iff for all $\hol{d}\in
+    s_o))_o\|^{M,g}} = {\True}$ if and only if for all $\hol{d}\in
   \hol{D_\alpha}$ we have $\hol{\|s_o\|^{M,g[d/X_\alpha]}} = {\False}$
@@
 
-\begin{definition}[Standard model and Henkin model]\label{homlhenkinmodel}
+\begin{definition}[Standard and Henkin models]\label{homlhenkinmodel}
  A model $\hol{M}=\hol{\langle D, I \rangle}$ is called a
- \emph{standard model} iff for all $\hol{\alpha,\beta}\in \hol{T}$ we have
+ \emph{standard model} if and only if for all $\hol{\alpha,\beta}\in \hol{T}$ we have
  $\hol{D_{\alpha\ar\beta}} = \{ f \mid f : \hol{D_\alpha} \longrightarrow \hol{D_\beta}\}$. In a \emph{Henkin model} function spaces are not necessarily
@@
  $\hol{\|\cdot\|^{M,g}}$ from above is total (i.e., every term denotes). Any standard model is obviously
- also a Henkin model. We consider Henkin models in the remainder.
+ also a Henkin model. 
 \end{definition}
+
+We consider Henkin models in the remainder. For more details on Henkin
+semantics, its proof theory and examples of sound and complete calculi
+we refer to the literature (e.g. \cite{J6,J18}).
 
@@
 A formula $\hol{s_o}$ is \emph{true} in model $M$ 
-under assignment $\hol{g}$ iff $\hol{\|s_o\|^{M,g}} = {\True}$; this is also denoted
+under assignment $\hol{g}$ if and only if $\hol{\|s_o\|^{M,g}} = {\True}$; this is also denoted
 as $\hol{M,g \models^\HOL s_o}$.  A formula $\hol{s_o}$ is called \emph{valid} in
-$\hol{M}$, which is denoted as $\hol{M \models^\HOL s_o}$, iff $\hol{M,g \models^\HOL s_o}$ for all
+$\hol{M}$, which is denoted as $\hol{M \models^\HOL s_o}$, if and only if $\hol{M,g \models^\HOL s_o}$ for all
 assignments $\hol{g}$. Finally, a formula $\hol{s_o}$ is called
-\emph{valid}, which we denote by $\hol{\models^\HOL s_o}$, iff $\hol{s_o}$ is valid for
-all $\hol{M}$. Moreover, we write $\hol{\Gamma\models^\HOL \Delta}$ (for sets of
- formulas $\hol{\Gamma}$ and $\hol{\Delta}$) iff there is a model $\hol{M}$ and an assignment $\hol{g}$ such that  
- $\hol{M,g \models^\HOL s_o}$ for all $\hol{s_o}\in \hol{\Gamma}$ and $\hol{M,g \models^\HOL t_o}$ for at least one $\hol{t_o}\in \hol{\Delta}$.
+\emph{valid}, which we denote by $\hol{\models^\HOL s_o}$, if and only if $\hol{s_o}$ is valid for
+all $\hol{M}$. 
+% Moreover, we write $\hol{\Gamma\models^\HOL \Delta}$ (for sets of
+% formulas $\hol{\Gamma}$ and $\hol{\Delta}$) if and only if there is a model $\hol{M}$ and an assignment $\hol{g}$ such that  
+% $\hol{M,g \models^\HOL s_o}$ for all $\hol{s_o}\in \hol{\Gamma}$ and $\hol{M,g \models^\HOL t_o}$ for at least one $\hol{t_o}\in \hol{\Delta}$.
 \end{definition}
@@
 the language constructs of $\FFOL$ with corresponding terms of $\HOL$.
-In this embedding raw domains $D$ of a $\FFOL$ model structures are
-identified with the $\HOL$ domains $\hol{D_i}$.  The subdomain $E$ of
+In this embedding the raw domain $D$ of a $\FFOL$ model is
+identified with the domain of individuals $\hol{D_i}$ in a corresponding $\HOL$ model.  The subdomain $E$ of
 existing objects is characterized in the embedding by a $\HOL$
 predicate $\hol{\ex}$ of type $\hol{ i\ar o}$. Hence, we assume in the
-remainder that a respective uninterpreted constant symbol $\hol{\ex}$
+remainder that a respective uninterpreted constant symbol
+$\hol{\ex_{i\ar o}}$
 is given in the signature of $\HOL$. Moreover, we assume that an
-uninterpreted constant symbol $\hol{\star}$ of type $i$ be in the
-signature of $\HOL$. We assume that $\hol{\|E \star\|^{M,g}=F}$ for
-all $\hol{M,g}$, i.e. that the element denoted by $\hol{\star}$ is not
-an element of the domain of existing objects denoted by $\hol{\ex}$.
+uninterpreted constant symbol $\hol{\star}$ of type $\hol{i}$ be in the
+signature of $\HOL$. Finally, we assume that $\hol{\|E \star_i\|^{M,g}=F}$ for
+all $\hol{M,g}$, i.e. that the element denoted by $\hol{\star_i}$ is not
+an element of the domain of existing objects denoted by
+$\hol{\ex_{i\ar o}}$.
 
@@
 \noindent
+\resizebox{\textwidth}{!}{ 
 \begin{tabular}{lcll}
@@
 $\map{f(t^1,\ldots,t^n)}$    & := & $(\map{f}\ \map{t^1} \ldots \map{t^n})$  \quad
-              & for all $n$-ary $f\in F$\\
- & & &  where $\map{f}=\hol{f_{\underbrace{{i \ar
-               \ldots  \ar i} \ar }_{n\geq o} i}} \in \map{F}$\\
-%$\map{p}$    & := & $\hol{p_o}$ & for all $0$-ary $p\in \P$\\
+              & for all $n$-ary $f\in F$ ($n\geq 0$)\\
+  & & & where $\map{f} = \hol{f}$ is an uninterpreted \\
+   & & &  constant symbol of type ${\underbrace{{i \ar \ldots  \ar i} \ar }_{n\geq o} i}$ \\
 $\map{s = t}$    & := & $\map{s} \hol{=} \map{t}$ \\
 $\map{p(t^1,\ldots,t^n)}$    & := & $(\map{p}\ \map{t^1} \ldots \map{t^n})$  \quad
-             &  for all $n$-ary $p\in P$ \\ 
-   & & & where $\map{p}=\hol{p_{\underbrace{{i \ar
-               \ldots  \ar i} \ar }_{n\geq o} o}} \in \map{P}$\\
-
+             &  for all $n$-ary $p\in P$ ($n\geq 0$)\\ 
+   & & & where $\map{p} = \hol{p}$ is an uninterpreted \\
+   & & &  constant symbol  of type ${\underbrace{{i \ar \ldots  \ar i} \ar }_{n\geq o} o}$ \\
 $\map{\neg s}$ & := &  $\hol{\neg}\map{s}$  \\
@@
 $\map{\Descr x\lambdot r}$ & := &  $\hol{\textbf{IfThenElse}}$ \\
-  & & \multicolumn{2}{c}{\quad $\hol{(\exists X_i\lambdot \ex X \wedge} \map{r}\ \hol{\wedge (\forall
+  & & \multicolumn{2}{c}{\quad $\hol{(\exists X_i\lambdot \ex X
+      \wedge}\ \map{r} \hol{\wedge (\forall
       Y_i\lambdot (\ex Y \wedge ((\lam{X_i}} \map{r}) \hol{Y)) \Impl Y = X))}$} \\
@@
 \end{tabular}
+}
 where $\hol{\textbf{IfThenElse}}$ is an abbreviation for the term
@@
   \map{V}\mapsto \map{D}$ for $\HOL$ is defined such that
-  $\map{g}(X_i) = \map{g} \map{x} = g(x)$ 
+  $\map{g}(\hol{X_i}) = \map{g}(\map{x}) = g(x)$ 
 for all $\hol{X_i}\in \map{V}$. 
 Finally, $\map{g}$ is extended to an assignment for arbitrary
-variables $\hol{Y_\alpha} \notin \map{V}$  by choosing
-$\map{g}(\hol{Y_\alpha}) = \hol{d}\in \hol{D_\alpha}$ arbitrary (for
-all types $\alpha$).
+variables by choosing
+$\map{g}(\hol{Y_\alpha}) = \hol{d}\in \hol{D_\alpha}$ arbitrary 
+whenever $\hol{Y_\alpha} \notin \map{V}$.
 
@@
 \item $\hol{D_{\alpha\ar\beta}}$ are
-chosen as (not necessarily full) sets of functions from
+chosen as (not necessarily full) collections of functions from
 $\hol{D_\alpha}$ to $\hol{D_\beta}$. Remember, however, that the
 choice of $\hol{D_{\alpha\ar\beta}}$ must always ensure that 
-the valuation function 
- $\hol{\|\cdot\|^{\map{M},\map{g}}}$ remains total, i.e. that
+the evaluation function 
+ $\hol{\|\cdot\|^{\map{M},\map{g}}}$ below remains total, i.e. that
  all terms denote. In particular, it is required that $\hol{D_{i\ar
-     o}}$ contains the element $\hol{I \ex}$ as characterized below.
-\item Let $X^i_i = \map{x^i}$
-  for $x^i\in V$.  The interpretation function $\hol{I}$ of $\map{M}$
+     o}}$ contains the element $\hol{I \ex_{i\ar
+     o}}$ as characterized below.
+\item The interpretation function $\hol{I}$ of $\map{M}$
   is chosen as follows:
 \begin{itemize}
-\item  $\hol{I \star_i} = \star \in D$
+\item  $\hol{I \star_i} = \star \in \hol{D_i}$
 \item  For all
-    $\hol{d} \in \hol{D_i} = \map{D}$ we have: $(\hol{I \ex_{i\ar o}})(\hol{d}) =
-    \hol{T}$  if and only if $\hol{d} \in E$. Note that this implies $(\hol{I \ex})(\hol{\star_i}) = \hol{F}$.
-\item \sloppy For all $\hol{f_{{\underbrace{{i \ar
-               \ldots  \ar i} \ar }_{n\geq o} i}}} = \map{f} \in \map{F}$ we
+    $\hol{d} \in \hol{D_i}$ we have: $(\hol{I \ex_{i\ar o}})(\hol{d}) =
+    \hol{T}$  if and only if $\hol{d} \in E$. Note that this implies $(\hol{I \ex_{i\ar o}})(\hol{\star_i}) = \hol{F}$.
+\item \sloppy For all $\hol{f} = \map{f} \in \map{F}$ we
        have: $(\hol{I} \hol{f})(\hol{d^1},\ldots,\hol{d^n}) = (I f)(\hol{d^1},\ldots,\hol{d^n})$ for
-       all $\hol{d^i}\in \hol{D_i} = \map{D}$ ($i=1,\ldots,n$ and
+       all $\hol{d^i}\in \hol{D_i}$ ($i=1,\ldots,n$ and
        $n\geq 0$).
-\item \sloppy For all $\hol{p_{{\underbrace{{i \ar
-               \ldots  \ar i} \ar }_{n\geq o} 0}}} = \map{p} \in \map{P}$ we
+\item \sloppy For all $\hol{p} = \map{p} \in \map{P}$ we
        have: $(\hol{I} \hol{p})(\hol{d^1},\ldots,\hol{d^n}) = \hol{T}$
        if and only if $(\hol{d^1},\ldots,\hol{d^n}) \in (I p)$ for
-       all $\hol{d^i}\in \hol{D_i} = \map{D}$ ($i=1,\ldots,n$ and
+       all $\hol{d^i}\in \hol{D_i}$ ($i=1,\ldots,n$ and
        $n\geq 0$).
@@
     c_\alpha} \in \hol{D_\alpha}$ arbitrary.\footnote{In fact, it may be safely assumed that there are
-  no other constant symbols given, except for the symbols in
+  no other constant symbols given in a HOL signature, except for the symbols in
   $\map{F}$ and $\map{P}$, the symbols $\hol{\ex_{i\ar o}}$  and $\hol{\star_{i}}$ and the logical connectives.}
@@
 
-It is not hard to verify that ${H}^{M}$ is a Henkin model.\footnote{In
-  $\map{M}$ we have merely fixed $D_i=D$ and the interpretations of
-  $\ex$ and $\star$.  These
-  choices are not in conflict with any of the requirements regarding
+It is not hard to verify that $\map{M}$ is a Henkin
+model.\footnote{The fixings introduced in $\map{M}$
+  are not in conflict with any of the requirements regarding
   frames and interpretations. The existence of a valuation function
@@
   function spaces have been chosen in frame $\{D_\alpha\}_{\alpha \in
-    {T}}$. Andrews \cite{Andrews72b} discusses criteria that are sufficient
+    {T}}$. Andrews \cite{Andrews:gmae72} discusses criteria that are sufficient
   to ensure the existence of a valuation function; in
-  $\map{M}$) these requirements are met.}
+  $\map{M}$ these requirements are met.}
 
@@
   For $s=x\in V$ the claim follows from the definition of
-  $\map{g}$. For $s=c\in F$ where $c$ is $0$-ary we get the claim by
-  the choice of $\hol{I}$ in $\map M$, and for $s=f(t^1,\ldots,t^n)$
-  where $f\in F$ is $n$-ary ($n\geq 1$) we additionally need to apply
-  the induction hypothesis. The arguments for $s=p\in P$ where $p$ is
-  $0$-ary and for $s=p(t^1,\ldots,t^n)$ where $p\in P$ is $n$-ary
-  ($n\geq 1$) are similar.  The most complicated case is when
+  $\map{g}$. For $s=c\in F$, where $c$ is $0$-ary, we get the claim by
+  the choice of $\hol{I}$ in $\map M$, and for $s=f(t^1,\ldots,t^n)$,
+  where $f\in F$ is $n$-ary ($n\geq 1$), we additionally need to apply
+  the induction hypothesis. The arguments for $s=q\in P$, where $q$ is
+  $0$-ary, and for $s=p(t^1,\ldots,t^n)$, where $p\in P$ is $n$-ary
+  ($n\geq 1$), are similar.  The most complicated case is when
   $s=\Descr x\lambdot r$. We here consider two cases. We either have
+  $d \in E$ with
   $\| r \|^{M,g[d/x]} = \True$ and $\| r \|^{M,g[d'/x]} = \False$ for
   all $d'\not=d\in \ex$ (i.e. $d$ is the unique existing object for
-  which $r$ holds) or there is no such $d\in \ex$. In the first case
+  which $r$ holds) or there is no such $d\in \ex$. In the former case
   we have $\| \Descr x\lambdot r \|^{M,g} = d \in \ex$. By the
-  definition of the embedding $\map{\ }$, definition of $\map M$ and
-  $\map g$, induction hypothesis and a series of tedious evaluation
+  definition of the embedding $\map{\cdot}$, definition of $\map M$ and
+  $\map g$, $\lambda$-conversion, induction hypothesis and a series of tedious evaluation
   steps in \HOL we get
   $\| \map{\Descr x\lambdot r} \|^{\map M, \map g} = \| \hol{\Descr
-    x\lambdot \map{r}} \|^{\map M, \map g} = d \in \ex$
+    x\lambdot} \map{r} \|^{\map M, \map g} = d \in \ex$
   (for the very same $d$ as above). In the second case we have
   $\| \Descr x\lambdot r \|^{M,g} = \star$. Again we apply the
-  definition of the embedding $\map{\ }$, the definition of $\map M$
-  and $\map g$, induction hypothesis and a series of tedious
+  definition of the embedding $\map{\cdot}$, the definition of $\map M$
+  and $\map g$, $\lambda$-conversion, induction hypothesis and a series of tedious
   evaluation steps in \HOL to verify that
   $\| \map{\Descr x\lambdot r} \|^{\map M, \map g} = \hol{\star} =
-  \star$. The remaining cases are similar (actually simpler) and left to the reader.
+  \star$. The remaining cases are similar (actually simpler) and left
+  to the reader. $\Box$
 \end{proof}
@@
 For all formulas $s\in FFOL$ we have
- $\models^\FFOL s \text{ if and only if }  \models^\HOL \map{s}$
+ $\models^\FFOL s \text{ if and only if }  \models^\HOL \map{s}$.
 
@@
 
- (Completeness, $\rightarrow$) The proof is again by
-    contraposition and analogous to above.
+ (Completeness, $\rightarrow$) Analogous to above by contraposition
+ and Lemma \ref{lemma:1}.
 \end{proof}
@@
 
-In the remainder of this article we present an application of our
-framework for the exploration of axioms systems in category theory. In
-this context description is not required and we hence omit it in our 
-theory. Figure \ref{pic1} shows the embedding of $\FFOL$ in $\HOL$,
-encoded in Isabelle/HOL, 
-that we have employed in our experiments. A related Isabelle/HOL
-encoding of the above theory with description has been presented and  discussed in
-\cite{ICMS}.
+Properties of $\FFOL$ could now be experimentally explored with
+automated reasoning tools for $\HOL$. We have conducted such
+experiments in 
+an earlier paper \cite{ICMS}. These experiments confirm the
+illustrating examples discussed in Scott's paper \cite{Scott67}.
+
+\section{Exploring Axioms Systems for Category Theory}
+In an experimental theory exploration study, in which we utilized the
+free logic reasoning farmework from above, 
+we have shown how Scott's
+\cite{Scott79} axiom system for category theory can be derived from a
+notion of partial monoids. These axioms systems are presented in Table \ref{axioms-sets-1}.
+
+The stepwise evolution has been described in detail in\cite{ArXiv}. Below we
+summarize these experiments.  However, first we describe some basic
+modeling decisions for the technical encoding in Isabelle/HOL. The
+sources of our experiments, as discussed in \cite{ArXiv}, are available at
+\url{http://christoph-benzmueller.de/papers/2017-arXiv.zip}. Note that in these
+sources we did add neither the definite description operator nor the
+designated undefined object $\hol{\star}$, since both were not required in
+this particular application.
+
+Figure \ref{pic1} displays (parts of) the embedding of $\FFOL$ in
+$\HOL$, encoded in Isabelle/HOL, that we have employed in our
+experiments. A related Isabelle/HOL encoding of the above theory with
+description has been presented and discussed in
+\cite{ICMS}.\footnote{In the remainder of this article, and inline
+  with our text so far,  we present the formulas of
+  $\FFOL$ in non-boldface font. These formulas have been encoded in Isabelle/HOL using the
+  abbreviations as introduced in Fig.~\ref{pic1}. In the actual source
+  encoding, however, the usage of boldface and non-boldface is
+  (for technical reasons) reversed.}
 
@@
  \includegraphics[width=\textwidth]{EmbeddingPic}
- \caption{Isabelle/HOL formalisation of $\FFOL$ (without description) in $\HOL$ \label{pic1}}
+ \caption{Isabelle/HOL encoding of $\FFOL$ (without description)\label{pic1}}
 \end{figure}
-
-\section{Exploring Axioms Systems for Category Theory}
-In an exemplary theory exploration study, we have shown how Scott's
-\cite{Scott79} axiom system for category theory can be derived from a
-notion of partial monoids. These axioms systems are presented in Table \ref{axioms-sets-1}.
-
-The stepwise evolution has been described in \cite{R58}. Below we
-summarise these experiments.  However, first we describe some basic
-modeling decisions for the technical encoding in Isabelle/HOL. The
-Isabelle/HOL sources of our experiments are available at
-\url{todo-sources}. Note that in these sources we did add neither the
-definite description operator nor the designated undefined object
-$\star$, since both were not required in our experiments.
 
@@
   codomain, $D$ for Domain. The free variables $x$, $y$, $z$ range over
-  the raw domain $D$. The quantifiers in Axiom Sets I and II are
+  the raw domain $D$. The quantifiers in Axioms Sets I and II are
   free logic quantifiers, that is, they range over the domain $E$ of
@@
 \subsection{Modeling of basic concepts}
-Morphisms in the category are modeled as objects of type $\ti$. We introduce three partial functions, 
+Morphisms in the category are modeled as objects in $D$ (respectively,
+$\hol{D_i}$). We introduce three partial functions, 
 $\dom$ (domain), $\cod$ (codomain), and $\comp$ (morphism composition). 
@@
 $\cong$ is an equivalence relation. $\simeq$, in contrast, is only symmetric and transitive, and lacks 
-reflexivity. These observations are quickly confirmed by Isabelle.
+reflexivity. These observations are quickly confirmed by Sledgehammer
+in Isabelle.
 
@@
 
-abbreviation I where \[\id i \ddef (\forall x\lambdot \ex(i \comp x) \imp i \comp
+\[\id i \ddef (\forall x\lambdot \ex(i \comp x) \imp i \comp
 x \cong x) \wedge (\forall x\lambdot \ex(x \comp i) \imp x \comp i \cong x)\]
 
-This definition was suggested by an exercise in \cite{FreydScedrov90}
+This definition was suggested by an exercise in the textbook by Freyd
+and Scedrov \cite{FreydScedrov90}
 on p.~4.  In earlier experiments we used a longer definition which can
@@
 \subsection{Consistency}
-The model finder Nitpick confirms consistency for all of the axiom
+The model finder Nitpick confirms consistency for all of the axioms
 sets from Table \ref{axioms-sets-1}. For example, when asked to consider at least one defined and one undefined object, then
@@
 $\dom$ are identity on $D$. It is trivial to check that these models
-indeed confirm the consistency of all axiom sets from Table \ref{axioms-sets-1}.
+indeed confirm the consistency of all axioms sets from Table \ref{axioms-sets-1}.
 
@@
 \subsection{Axioms Sets I and II}
- Axioms Set I is our most basic axiom set for category theory generalizing the 
+ Axioms Set I is our most basic set of axioms for category theory generalizing the 
 axioms for a monoid to a partial composition operation. Remember that a monoid is an 
@@
 
-Axioms Set I generalises the notion of a monoid by introducing a partial, strict binary 
+Axioms Set I generalizes the notion of a monoid by introducing a partial, strict binary 
 composition operation $\comp$. The existence of left and right identity elements is 
@@
 abstract from their common meaning in the context of sets. In category theory we
-work with just a single type of objects (the type $\ti$ of morphisms) and therefore 
+work with just a single type of objects (the type $\hol{i}$ in our setting) and therefore 
 identity morphisms are employed to suitably characterize their
@@
    our formalization as follows: 
- $$\exists C, D\lambdot (\forall y\lambdot \id (C y) \wedge (C y) \comp y \cong y)
+ $$\exists C\lambdot \exists D\lambdot (\forall y\lambdot \id (C y) \wedge (C y) \comp y \cong y)
  \wedge (\forall x\lambdot \id (D x) \wedge x \comp (D x) \cong x) \wedge
@@
 such functions. Hence, we get a conservative extension of Axioms Set
-I. This could be done for any theory with an $\forall x\lambdot \exists i$.-axiom. The strictness axiom $S$ is extended, so
+I. This could be done for any theory with an ``$\forall x\lambdot \exists i\lambdot$''-axiom. The strictness axiom $S$ is extended, so
 that strictness is now also postulated for the new Skolem functions
-$\dom$ and $\cod$. Note that the values of Skolem functions
+$\dom$ and $cod$. Note that the values of Skolem functions
 outside $E$ can just be given by the identity function.
@@
 All proofs above and all proofs in the rest of this paper (unless
-stated otherwise) have been obtained fully automatically with the
+stated otherwise) have been obtained fully automatically in very
+reasonable time (typically just a few seconds) with the
 Sledgehammer tool in Isabelle/HOL. This tool interfaces to prominent
@@
   Isabelle/HOL, in which all the proofs have nevertheless been
-  contributed by automated theorem provers.
-
-\subsection{Axioms Set III, IV and V} \marginpar{will improve presentation}
+  contributed by automated theorem provers. However, there are still
+  a few calls of the \textsc{smt}-tactic contained in our document, 
+   which we are not entirely trivial to replace. In this sense, our
+   Isabelle/HOL verification is modulo the correctness of the \textsc{smt} solvers
+   CVC4 \cite{CVC4} and Z3 \cite{Z3}.
+
+\subsection{Axioms Set III, IV and V} 
 In Axioms Set III the existence  axiom  $E_{ii}$ from Axioms Set II  is simplified by taking advantage of 
-  the two new Skolem functions ${\dom}$ and $\cod$.
+  the two new Skolem functions ${\dom}$ and $cod$.
 
@@
 
- Axioms Set II and Axioms Set III are equivalent; this has been
- confirmed by the automated theorem provers and verified in Isabelle/HOL.
+ % Axioms Set II and Axioms Set III are equivalent; this has been
+ % confirmed by the automated theorem provers and verified in Isabelle/HOL.
 
 %\subsection{Axioms Set IV}
-Axioms Set IV simplifies the axioms $C_{iii}$ and  $D_{iii}$ . However, as it turned 
+Axioms Set IV simplifies the axioms $C_{iii}$ and  $D_{iii}$. However, as it turned 
  out, these simplifications also require the existence axiom $E_{iii}$ to be strengthened into
@@
 
- Axioms Set III and Axioms Set IV are equivalent; this has been
- confirmed by the automated theorem provers and verified in
- Isabelle/HOL.
+ % Axioms Set III and Axioms Set IV are equivalent; this has been
+ % confirmed by the automated theorem provers and verified in
+ % Isabelle/HOL.
 
@@
 Axioms Set V has been proposed by Scott \cite{Scott79} in the 1970s. 
-This set of axioms is equivalent to the axiom set presented by Freyd
+This set of axioms is equivalent to the axioms set presented by Freyd
 and Scedrov in their textbook ``Categories, Allegories''
 \cite{FreydScedrov90}, when encoded in free logic, corrected/adapted
-and further simplified.  Their axiom set is technically flawed when
+and further simplified.  Their axioms set is technically flawed when
 encoded in our given context. This issue has been detected by
 automated theorem provers with the same technical infrastructure as
-employed so far. See Section\ref{sec-freyd-scedrov} for more
+employed so far. See \S\ref{sec-freyd-scedrov} for more
 details.
 
- Axioms Set IV and Axioms Set V are equivalent; again, this has been
+ Axioms Sets II, III, IV and V are equivalent; this has been
+ automatically 
  confirmed by the automated theorem provers and verified in
@@
  axioms set of Freyd and Scedrov from their textbook ``Categories,
- Allegories'' \cite{FreydScedrov90}.  In Subsection
- \ref{subsec-freyd-scedrov-1} we show, that their axioms set,
- replicated in Table \ref{axioms-sets-2} as Axioms Set VI, becomes
+ Allegories'' \cite{FreydScedrov90}.  In \S\ref{subsec-freyd-scedrov-1} we show, that their axioms set,
+ replicated in Table \ref{axioms-sets-2} as Axioms Set FS-I, becomes
  inconsistent in our free logic setting if we assume non-existing
- objects of type $i$, respectively, if we assume that the operations
+ objects in $D$, respectively, if we assume that the operations
  are non-total.
@@
   $A2a$ & $\cod(\dom x) \cong \dom x$ \\  
-  $A2b$ & $\dom(\cod y) \cong cod y$ \\  
+  $A2b$ & $\dom(\cod y) \cong \cod y$ \\  
   $A3a$  & $x \comp (\dom x) \cong x$ \\ 
@@
  Note, however, that the free variables in this first study range over
- the existing and non-existing objects in domain $D$. One may argue,
+ the existing and non-existing objects in $D$. One may argue,
  that this is not the intention of Freyd and
- Scedrov. Therefore, we add a second study in Subsection
- \ref{subsec-freyd-scedrov-2}, in which we restrict the
+ Scedrov. Therefore, we add a second study in \S\ref{subsec-freyd-scedrov-2}, in which we restrict the
  variables to range only over existing objects in $E$. However, also in this case
@@
   We leave it to the reader to verify that their Axioms
-  Set VI corresponds to Axioms
-  Set VII modulo an appropriate conversion of notation.\footnote{A recipe for 
+  Set FS-I corresponds to Axioms
+  Set FS-II modulo an appropriate conversion of notation.\footnote{A recipe for 
   this translation is as follows: (i) replace all $x \circ y$ by
   $y \comp x$, (ii) rename the variables to get them again in alphabetical order,
-(iii) replace $\varphi\Box$ by $\cod \varphi$ and $\Box\varphi$  by $dom \varphi$, and finally
+(iii) replace $\varphi\Box$ by $\cod \varphi$ and $\Box\varphi$  by $\dom \varphi$, and finally
 (iv) replace $\cod y \cong \dom x$ (resp. $\cod y \simeq \dom x$) 
@@
 
-\subsection{Constricted Inconsistency in Free Logic Setting} \label{subsec-freyd-scedrov-1}
-  A main difference in the system by Freyd and Scedrov to our Axiom
-  Set V from Table \ref{axioms-sets-1} concerns
-  axiom $S3$ respectively $A1$. Namely, instead of the non-reflexive
-  existing identity $\simeq$, they use Kleene 
-  equality $\cong$, cf. definition 1.11 on page 3 of \cite{FreydScedrov90}.\footnote{Def. 1.11 in Freyd 
-  Scedrov: ``The ordinary equality sign $=$ [i.e., our $\cong$] will be used in the
-  symmetric sense, to wit: if either side is defined then so is the other and they are equal. \ldots''} 
-  The difference seems minor, but in our free logic setting it has the effect to cause the mentioned
-  constricted inconsistency issue. This could perhaps be an oversight, or it could indicate
-  that Freyd and Scedrov actually mean the Axioms Set VIII below (where the variables in the axioms range 
-  over defined objects only). However, in Axioms Set VIII we had to (re-)introduce explicit 
-  strictness conditions to ensure equivalence to the Axiom Set V by
-  Scott.
+ \subsection{Constricted Inconsistency in Free Logic
+   Setting} \label{subsec-freyd-scedrov-1} A main difference in the
+ system by Freyd and Scedrov to our Axioms Set V from Table
+ \ref{axioms-sets-1} concerns axiom $S3$ respectively $A1$. Namely,
+ instead of the non-reflexive existing identity $\simeq$, they use
+ Kleene equality $\cong$, cf. definition 1.11 on page 3 of their textbook
+ \cite{FreydScedrov90}.\footnote{Def. 1.11 in Freyd Scedrov: ``The
+   ordinary equality sign $=$ [i.e., our $\cong$] will be used in the
+   symmetric sense, to wit: if either side is defined then so is the
+   other and they are equal. \ldots''} The difference seems minor, but
+ in our free logic setting it has the effect to cause the mentioned
+ constricted inconsistency issue.\footnote{This could perhaps be an
+   oversight, or it could indicate that Freyd and Scedrov actually
+   mean the Axioms Set discussed in \S\ref{subsec-freyd-scedrov-2}
+   below.%  (where the variables in the axioms range over defined objects
+   % only). However, in this reading of the axioms of Freyd and Scedrov
+   % we had to (re-)introduce explicit strictness conditions to ensure
+   % equivalence to the Axioms Set V by Scott.
+ }
 
   The (constricted) inconsistency of Axioms Set FS-I, respectively
-  Axiom Set FS-II, from Table \ref{axioms-sets-2} has been 
+  Axioms Set FS-II, from Table \ref{axioms-sets-2} has been 
   detected first by the model finder Nitpick. When we asked Nitpick to
@@
 even stronger. It implies that \emph{all} objects are defined,
-that is, composition (as well as $\dom$ and $\cod$) become total operations.
+that is, composition (as well as $\dom$ and $cod$) become total operations.
 The theory described by these axioms ``collapses'' to the theory of
@@
 In fact, the automated theorem provers, via Sledgehammer, quickly
-prove falsity from Axioms Set FS-II (or FS-I) when assuming a 
+prove falsity from Axioms Sets FS-II and FS-I when assuming a 
  non-existing object of type $i$:
@@
  $A2a$ and $A3a$ to cause the problem under this assumption. A
- human-intuitive proof argument is as follows:
+ corresponding  human-intuitive proof argument is as follows:
 
@@
    $E(a \comp (\dom a)) \biimp \dom a \cong \cod(\dom a)$. Moreover,
-   by instantiating $A2a$ with $a$ we obtain $\cod(\dom a) \cong dom a$,
+   by instantiating $A2a$ with $a$ we obtain $\cod(\dom a) \cong \dom a$,
    which we use (modulo symmetry and transitivity of $\cong$) to
@@
 
-As a corollary from the above constricted inconsistency result we get that all  must be
-defined: $\forall x\lambdot E x$
+As a corollary from the above constricted inconsistency result we get
+that all morphisms (objects in $D$) must be
+defined: $\forall x\lambdot E x$.
 
@@
 
+Obviously Axioms Sets FS-I and FS-II are also redundant, and we have previously reported 
+on respective redundancies \cite{ICMS}.\footnote{The discussion in our releated
+  conference paper \cite{ICMS} was before the discovery of the above 
+constricted inconsistency issue, which tells us that the system (in our setting) can even be reduced 
+to axioms A1, A2a, and A3a (when we assume undefined objects).} For
+the corrected Axioms Set VI we still get redundancies. The different options to reduce this system are reported in
+Table~\ref{axioms-sets-3}.
+
+Attempts to remove axioms A1', A3a, A3b, and A5 from Axiom Set VI failed. Nitpick shows that they are independent.
+
+However, when assuming strictness of $\dom$ and $\cod$, the axioms
+A2a, A2b, A4a and A4b are all implied. Hence, under this 
+   assumptions, the reasoning tools quickly identify (A1' A3a A3b A5) as a minimal axiom 
+   set, which then exactly matches the Axioms Set V of Scott from Table~\ref{axioms-sets-1}.\footnote{This minimal set of axioms 
+   has also been mentioned by Freyd in a note \cite{Freyd16} and attributed to Martin Knopman. However, the proof
+   sketch presented there seems to fail when the adapted version of A1 (with $\simeq$) is employed.}
+
 \begin{table} \centering \normalsize
@@
 \\
-  $B1'$  & $\ex (x \comp y) \longleftrightarrow \dom x \simeq\cod y$ \\
-  $B3a$  & $x \comp (\dom x) \cong x$ \\ 
-  $B3b$ & $(\cod y) \comp y \cong y$ \\
-  $B4a$ & $\dom(x \comp y) \cong \dom((\dom x) \comp y)$ \\ 
-  $B4b$ & $\cod(x \comp y) \cong \cod(x \comp (\cod y))$ \\ 
-  $B5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
+  $A1'$  & $\ex (x \comp y) \longleftrightarrow \dom x \simeq\cod y$ \\
+  $A3a$  & $x \comp (\dom x) \cong x$ \\ 
+  $A3b$ & $(\cod y) \comp y \cong y$ \\
+  $A4a$ & $\dom(x \comp y) \cong \dom((\dom x) \comp y)$ \\ 
+  $A4b$ & $\cod(x \comp y) \cong \cod(x \comp (\cod y))$ \\ 
+  $A5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
 \\
@@
 \\
-  $B1'$  & $\ex (x \comp y) \longleftrightarrow \dom x \simeq\cod y$ \\
-  $B2a$ & $\cod(\dom x) \cong \dom x$ \\  
-  $B2b$ & $\dom(\cod y) \cong cod y$ \\  
-  $B3a$  & $x \comp (\dom x) \cong x$ \\ 
-  $B3b$ & $(\cod y) \comp y \cong y$ \\
-  $B5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
+  $A1'$  & $\ex (x \comp y) \longleftrightarrow \dom x \simeq\cod y$ \\
+  $A2a$ & $\cod(\dom x) \cong \dom x$ \\  
+  $A2b$ & $\dom(\cod y) \cong \cod y$ \\  
+  $A3a$  & $x \comp (\dom x) \cong x$ \\ 
+  $A3b$ & $(\cod y) \comp y \cong y$ \\
+  $A5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
 \\
@@
   $S^2_{v}$ & $\ex (\cod y) \imp \ex y$ \\
-  $B1'$  & $\ex (x \comp y) \longleftrightarrow \dom x \simeq\cod y$ \\
-  $B3a$  & $x \comp (\dom x) \cong x$ \\ 
-  $B3b$ & $(\cod y) \comp y \cong y$ \\
-  $B5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
+  $A1'$  & $\ex (x \comp y) \longleftrightarrow \dom x \simeq\cod y$ \\
+  $A3a$  & $x \comp (\dom x) \cong x$ \\ 
+  $A3b$ & $(\cod y) \comp y \cong y$ \\
+  $A5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
 \\
@@
 \end{tabular}
-\caption{Bla}
+\caption{Reduced variants of Axioms Set VI.\label{axioms-sets-3}}
 \end{table}
 
-\subsection{Missing Strictness Axioms in Alternative Setting} \label{subsec-freyd-scedrov-2}
-
-\section{Conclusion}
-\ldots todo
+\subsection{Missing Strictness Axioms in Alternative
+  Setting} \label{subsec-freyd-scedrov-2} We study the axiom system by
+Freyd and Scedrov once again. However, this time we restrict the free
+variables in their system to range over existing objects only. In the
+context of algebraic theories, it could be argued that this is the
+preferred reading of free variables.  By employing the free logic
+universal quantifier $\forall$, which realizes such a restriction, 
+we thus modify Axioms Set FS-II into
+Axioms-Set FS-III as displayed in Table~\ref{axioms-sets-3}.
+
+For Axioms Set FS-III the consistency checks with Nitpick succeeds,
+even if we assume undefined objects. However, this axioms set is
+obviously weaker than Axioms Set V from Table
+\ref{axioms-sets-1}. In fact, as has been shown by Nitpick, none of
+the axioms of this set are implied.  The situation changes when we
+explicitly postulate strictness of $\dom$, $\cod$ and $\comp$. Doing
+so we obtain Axioms Set FS-IV from Table \ref{axioms-sets-3}, which,
+as Nitpick confirms, is consistent even if we assume undefined
+objects. And the automated theorem provers via Sledgehammer confirm
+that Axioms Set FS-IV is equivalent to Axioms Set V, as
+intended. Unfortunately, however, respective strictness conditions are
+not mentioned in the textbook by Freyd and Scedrov.
+
+\begin{table} \centering \normalsize
+\begin{tabular}{ll}
+\hline
+\\
+\multicolumn{2}{c}{Axioms Set FS-III: Freyd and Scedrov in our notation (with issues)} \\
+%\hline
+\\
+  $B1$  & $\all{x}\all{y} \ex (x \comp y) \longleftrightarrow \dom x \cong \cod y$ \\
+  $B2a$ & $\all{x} \cod(\dom x) \cong \dom x$ \\  
+  $B2b$ & $\all{y} \dom(\cod y) \cong \cod y$ \\  
+  $B3a$  & $\all{x} x \comp (\dom x) \cong x$ \\ 
+  $B3b$ & $\all{y} (\cod y) \comp y \cong y$ \\
+  $B4a$ & $\all{x}\all{y} \dom(x \comp y) \cong \dom((\dom x) \comp y)$ \\ 
+  $B4b$ & $\all{x}\all{y} \cod(x \comp y) \cong \cod(x \comp (\cod y))$ \\ 
+  $B5$   & $\all{x}\all{y}\all{z} x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
+\\
+\hline
+\\
+\multicolumn{2}{c}{Axioms Set FS-IV: Freyd and Scedrov in our
+  notation (without issues)} \\
+%\hline
+\\
+ $B0a$ & $\ex (x \comp y) \longrightarrow  (\ex x \wedge \ex y)$ \\
+ $B0b$ & $\ex (\dom x)  \longrightarrow   \ex x$ \\
+ $B0b$ & $\ex (\cod x)  \longrightarrow   \ex x$ \\
+  $B1$  & $\all{x}\all{y} \ex (x \comp y) \longleftrightarrow \dom x \cong \cod y$ \\
+  $B2a$ & $\all{x} \cod(\dom x) \cong \dom x$ \\  
+  $B2b$ & $\all{y} \dom(\cod y) \cong \cod y$ \\  
+  $B3a$  & $\all{x} x \comp (\dom x) \cong x$ \\ 
+  $B3b$ & $\all{y} (\cod y) \comp y \cong y$ \\
+  $B4a$ & $\all{x}\all{y} \dom(x \comp y) \cong \dom((\dom x) \comp y)$ \\ 
+  $B4b$ & $\all{x}\all{y} \cod(x \comp y) \cong \cod(x \comp (\cod y))$ \\ 
+  $B5$   & $\all{x}\all{y}\all{z} x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
+\\
+\hline
+\end{tabular}
+\caption{The axioms set of Freyd and Scedrov in our
+  notation and with variable restriction to existing objects only.\label{axioms-sets-3}}
+\end{table}
+
+\section{Summary and Further Work}
+We have developed a new reasoning framework for free logic, and we
+have experimentally applied it for some first experiments in category
+theory.  We have demonstrated how modern proof assistants and theorem
+provers for classical higher-order logic may well support the
+reasoning in free logic. More concretely, we have applied our new free
+logic reasoning framework for the systematic exploration of axiom
+systems for category theory. Without tools support such experiments
+would be extremely tedious and error prone.
+In the course of our experiments, automated theorem provers 
+have revealed some (minor) issue in the textbook of Freyd and Scedrov \cite{FreydScedrov90},
+which we were able to correct. The correction essentially corresponds
+to the axiom system by Scott proposed earlier \cite{Scott67}.
+All our findings were achieved directly by or in
+close interaction with automated reasoning tools.
+
+% % Our free logic reasoning framework is publicly available for reuse:
+% Simply download Isabelle from https://isabelle.in.tum.de and
+% initialize it (respec- tively import) the file FreeFOL.thy from our
+% sources available at
+% www. christoph-benzmueller.de/papers/2016-ICMS.zip. Our category
+% theory experiments are contained in the file FreydScedrov.thy.
+
+Comparisons with other theorem provers for free logic are not possible at this stage, since we are not aware of any other existing systems.
+
+Further work includes the continuation of our formalization studies in
+category theory and the application of free logic to various other
+mathematical domains, including, for example,  projective geometry.
 
@@
 This work has been supported by the DFG Heisenberg fellowship (BE
-2501/9-2, \emph{, Towards Computational Metaphysics}) of the first
+2501/9-2, \emph{Towards Computational Metaphysics}) of the first
 author.
 
-We thank G{\"u}nter Rote, Lutz Schröder and and Emil Weydert for their
-valuable comments to earlier drafts of this article .
+We thank G{\"u}nter Rote, Lutz Schr\"oder and and Emil Weydert for their
+comments to \cite{ArXiv}, which together with \cite{ICMS} forms the
+basis for this article.
 

### 2017-04-29 FreeLogic/2017-Journal/article.tex
update

@@
 
-%\titlerunning{Short form of title}        % if too long for running head
+\titlerunning{Automating Free Logic in HOL}        % if too long for running head
 
@@
 classical higher-order logic (HOL) \cite{B5}. The proposed solution
-employs a semantic embedding of free in HOL. We
-present an exemplary implementation of this idea in the mathematical
-proof assistant Isabelle/HOL \cite{NPW02}. Various state-of-the-art
+employs a semantic embedding of free in HOL. We present, as an
+example, one implementation of this idea in the mathematical proof
+assistant Isabelle/HOL \cite{NPW02}. Various state-of-the-art
 first-order and higher-order automated theorem provers and model
@@
 
+The above results enable the employment of any theorem prover that
+supports $\HOL$ with definite description to reason with $\FFOL$,
+including TPTP THF \cite{J22} compliant systems such as Satallax,
+Nitpick, LEO-II and Leo-III. Alternatively, this theory can be encoded
+in interactive proof assistants, such as Isabelle/HOL. <
+  % \footnote{An example of respective abstract level proof
+  % tactics in the context of a semantical embedding of an
+  % hyperintensional higher-order modal logic in $\HOL$ can be found at:
+  % \url{https://github.com/ekpyron/TAO}; in this document a
+  % computer-formalization of Ed Zalta's Principia
+  % Logico-Metaphysica \url{https://mally.stanford.edu/principia.pdf} is presented.}
+
 Properties of $\FFOL$ could now be experimentally explored with
@@
 
-The stepwise evolution has been described in detail in\cite{ArXiv}. Below we
-summarize these experiments.  However, first we describe some basic
-modeling decisions for the technical encoding in Isabelle/HOL. The
-sources of our experiments, as discussed in \cite{ArXiv}, are available at
-\url{http://christoph-benzmueller.de/papers/2017-arXiv.zip}. Note that in these
-sources we did add neither the definite description operator nor the
-designated undefined object $\hol{\star}$, since both were not required in
-this particular application.
+The stepwise evolution has been described in detail
+in\cite{ArXiv}. Below we summarize these experiments.  However, first
+we describe some basic modeling decisions for the technical encoding
+in Isabelle/HOL. The sources of our experiments, as discussed in
+\cite{ArXiv}, are available at
+\url{http://christoph-benzmueller.de/papers/2017-arXiv.zip}. Note that
+in these sources we added neither the definite description operator
+nor the designated undefined object $\hol{\star}$, since both were not
+required in this particular application.
 
@@
 where composition is total, $\id i$ means $i$ is a two-sided identity
-— and such are unique. For categories the property is much weaker.
+--- and such are unique. For categories the property is much weaker.
 
@@
   a few calls of the \textsc{smt}-tactic contained in our document, 
-   which we are not entirely trivial to replace. In this sense, our
+   which we found are not entirely trivial to replace. In this sense, our
    Isabelle/HOL verification is modulo the correctness of the \textsc{smt} solvers
@@
 
+\begin{table} \centering \normalsize
+\begin{tabular}{ll}
+\\
+\hline
+\\
+\multicolumn{2}{c}{Freyd and Scedrov in our notation (corrected and
+  reduced I)} \\
+%\hline
+\\
+  $A1'$  & $\ex (x \comp y) \longleftrightarrow \dom x \simeq\cod y$ \\
+  $A3a$  & $x \comp (\dom x) \cong x$ \\ 
+  $A3b$ & $(\cod y) \comp y \cong y$ \\
+  $A4a$ & $\dom(x \comp y) \cong \dom((\dom x) \comp y)$ \\ 
+  $A4b$ & $\cod(x \comp y) \cong \cod(x \comp (\cod y))$ \\ 
+  $A5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
+\\
+\hline
+\\
+\multicolumn{2}{c}{Freyd and Scedrov in our notation (corrected and
+  reduced II)} \\
+%\hline
+\\
+  $A1'$  & $\ex (x \comp y) \longleftrightarrow \dom x \simeq\cod y$ \\
+  $A2a$ & $\cod(\dom x) \cong \dom x$ \\  
+  $A2b$ & $\dom(\cod y) \cong \cod y$ \\  
+  $A3a$  & $x \comp (\dom x) \cong x$ \\ 
+  $A3b$ & $(\cod y) \comp y \cong y$ \\
+  $A5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
+\\
+\hline
+\\
+\multicolumn{2}{c}{Freyd and Scedrov in our notation (corrected and
+  reduced III)} \\
+%\hline
+\\
+ $S^1_{v}$ & $\ex (\dom x) \imp \ex x$ \\
+  $S^2_{v}$ & $\ex (\cod y) \imp \ex y$ \\
+  $A1'$  & $\ex (x \comp y) \longleftrightarrow \dom x \simeq\cod y$ \\
+  $A3a$  & $x \comp (\dom x) \cong x$ \\ 
+  $A3b$ & $(\cod y) \comp y \cong y$ \\
+  $A5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
+\\
+\hline
+\end{tabular}
+\caption{Reduced variants of Axioms Set VI.\label{axioms-sets-3}}
+\end{table}
+
 Obviously Axioms Sets FS-I and FS-II are also redundant, and we have previously reported 
@@
    sketch presented there seems to fail when the adapted version of A1 (with $\simeq$) is employed.}
-
-\begin{table} \centering \normalsize
-\begin{tabular}{ll}
-\\
-\hline
-\\
-\multicolumn{2}{c}{Freyd and Scedrov in our notation (corrected and
-  reduced I)} \\
-%\hline
-\\
-  $A1'$  & $\ex (x \comp y) \longleftrightarrow \dom x \simeq\cod y$ \\
-  $A3a$  & $x \comp (\dom x) \cong x$ \\ 
-  $A3b$ & $(\cod y) \comp y \cong y$ \\
-  $A4a$ & $\dom(x \comp y) \cong \dom((\dom x) \comp y)$ \\ 
-  $A4b$ & $\cod(x \comp y) \cong \cod(x \comp (\cod y))$ \\ 
-  $A5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
-\\
-\hline
-\\
-\multicolumn{2}{c}{Freyd and Scedrov in our notation (corrected and
-  reduced II)} \\
-%\hline
-\\
-  $A1'$  & $\ex (x \comp y) \longleftrightarrow \dom x \simeq\cod y$ \\
-  $A2a$ & $\cod(\dom x) \cong \dom x$ \\  
-  $A2b$ & $\dom(\cod y) \cong \cod y$ \\  
-  $A3a$  & $x \comp (\dom x) \cong x$ \\ 
-  $A3b$ & $(\cod y) \comp y \cong y$ \\
-  $A5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
-\\
-\hline
-\\
-\multicolumn{2}{c}{Freyd and Scedrov in our notation (corrected and
-  reduced III)} \\
-%\hline
-\\
- $S^1_{v}$ & $\ex (\dom x) \imp \ex x$ \\
-  $S^2_{v}$ & $\ex (\cod y) \imp \ex y$ \\
-  $A1'$  & $\ex (x \comp y) \longleftrightarrow \dom x \simeq\cod y$ \\
-  $A3a$  & $x \comp (\dom x) \cong x$ \\ 
-  $A3b$ & $(\cod y) \comp y \cong y$ \\
-  $A5$   & $x \comp (y \comp z) \cong  (x \comp y) \comp z$   \\
-\\
-\hline
-\end{tabular}
-\caption{Reduced variants of Axioms Set VI.\label{axioms-sets-3}}
-\end{table}
-
-\subsection{Missing Strictness Axioms in Alternative
-  Setting} \label{subsec-freyd-scedrov-2} We study the axiom system by
-Freyd and Scedrov once again. However, this time we restrict the free
-variables in their system to range over existing objects only. In the
-context of algebraic theories, it could be argued that this is the
-preferred reading of free variables.  By employing the free logic
-universal quantifier $\forall$, which realizes such a restriction, 
-we thus modify Axioms Set FS-II into
-Axioms-Set FS-III as displayed in Table~\ref{axioms-sets-3}.
-
-For Axioms Set FS-III the consistency checks with Nitpick succeeds,
-even if we assume undefined objects. However, this axioms set is
-obviously weaker than Axioms Set V from Table
-\ref{axioms-sets-1}. In fact, as has been shown by Nitpick, none of
-the axioms of this set are implied.  The situation changes when we
-explicitly postulate strictness of $\dom$, $\cod$ and $\comp$. Doing
-so we obtain Axioms Set FS-IV from Table \ref{axioms-sets-3}, which,
-as Nitpick confirms, is consistent even if we assume undefined
-objects. And the automated theorem provers via Sledgehammer confirm
-that Axioms Set FS-IV is equivalent to Axioms Set V, as
-intended. Unfortunately, however, respective strictness conditions are
-not mentioned in the textbook by Freyd and Scedrov.
 
@@
 \caption{The axioms set of Freyd and Scedrov in our
-  notation and with variable restriction to existing objects only.\label{axioms-sets-3}}
+  notation and with variable restriction to existing objects only.\label{axioms-sets-4}}
 \end{table}
+
+\subsection{Missing Strictness Axioms in Alternative
+  Setting} \label{subsec-freyd-scedrov-2} We study the axiom system by
+Freyd and Scedrov once again. However, this time we restrict the free
+variables in their system to range over existing objects only. In the
+context of algebraic theories, it could be argued that this is the
+preferred reading of free variables.  By employing the free logic
+universal quantifier $\forall$, which realizes such a restriction, 
+we thus modify Axioms Set FS-II into
+Axioms-Set FS-III as displayed in Table~\ref{axioms-sets-4}.
+
+For Axioms Set FS-III the consistency checks with Nitpick succeeds,
+even if we assume undefined objects. However, this axioms set is
+obviously weaker than Axioms Set V from Table
+\ref{axioms-sets-1}. In fact, as has been shown by Nitpick, none of
+the axioms of this set are implied.  The situation changes when we
+explicitly postulate strictness of $\dom$, $\cod$ and $\comp$. Doing
+so we obtain Axioms Set FS-IV from Table \ref{axioms-sets-4}, which,
+as Nitpick confirms, is consistent even if we assume undefined
+objects. And the automated theorem provers via Sledgehammer confirm
+that Axioms Set FS-IV is equivalent to Axioms Set V, as
+intended. Unfortunately, however, respective strictness conditions are
+not mentioned in the textbook by Freyd and Scedrov.
 
@@
 logic reasoning framework for the systematic exploration of axiom
-systems for category theory. Without tools support such experiments
+systems for category theory. Without tools, support of such experiments
 would be extremely tedious and error prone.
@@
 mathematical domains, including, for example,  projective geometry.
+
+Moreover, abstract level proof tactics could be provided in proof
+assistants to support --- as an alternative to always unfolding the
+mapping from $\FFOL$ to $\HOL$ --- intuitive interaction (and even
+automation) in $\FFOL$ on top the semantical embedding.
 

### 2017-04-29 FreeLogic/2017-Journal/article.tex
update

@@
 $\HOL$, encoded in Isabelle/HOL, that we have employed in our
-experiments. A related Isabelle/HOL encoding of the above theory with
+experiments, as illustrated in Fig.~\ref{pic2}. A related Isabelle/HOL encoding of the above theory with
 description has been presented and discussed in
@@
 \begin{figure}[htp]
- \includegraphics[width=\textwidth]{EmbeddingPic}
+ \includegraphics[width=\textwidth]{FFOL-Pic1}
  \caption{Isabelle/HOL encoding of $\FFOL$ (without description)\label{pic1}}
+\end{figure}
+
+\begin{figure}[htp]
+ \includegraphics[width=\textwidth]{FFOL-Pic2}
+ \caption{Encoding of Axioms Set V in Isabelle/HOL using the
+   semantically embedded logic $\FFOL$ \label{pic2}}
 \end{figure}

### 2017-04-29 FreeLogic/2017-Journal/article.tex
update

--- 2017-04-29 FreeLogic/2017-Journal/article.tex
@@
 within the proof assistant Isabelle/HOL via the
-Sledgehammer tool \cite{Sledgehammer}. Moreover, we have obtained
+Sledgehammer tool. Moreover, we have obtained
 very useful feedback at various stages from the model finder Nitpick
@@
 $\HOL$, encoded in Isabelle/HOL, that we have employed in our
-experiments. A related Isabelle/HOL encoding of the above theory with
+experiments. Excerpts of these experiments are illustrated in Fig.~\ref{pic2}. A related Isabelle/HOL encoding of the above theory with
 description has been presented and discussed in
@@
 \begin{figure}[htp]
- \includegraphics[width=\textwidth]{EmbeddingPic}
+ \includegraphics[width=\textwidth]{FFOL-Pic1}
  \caption{Isabelle/HOL encoding of $\FFOL$ (without description)\label{pic1}}
+\end{figure}
+
+\begin{figure}[htp]
+ \includegraphics[width=\textwidth]{FFOL-Pic2}
+ \caption{Encoding of Axioms Set V in Isabelle/HOL utilizing the
+   embedded logic $\FFOL$ \label{pic2}}
 \end{figure}

### 2017-04-29 FreeLogic/2017-Journal/article.tex
update

@@
 
-\def\FFOL{\mathit{FFOL}}
+\def\FFOL{\entity{FFOL}\xspace}
 \def\V{\mathit{V}}
@@
 theoretically appealing solution, but is has been considered as rather
-unsuited towards practical utilisation.
+unsuited towards practical utilization.
 
@@
 very useful feedback at various stages from the model finder Nitpick
-\cite{Nitpick} saving us from making several mistakes.
+\cite{Nitpick}, saving us from making several mistakes.
 
@@
 references therein). Below we introduce a variant of \HOL with primitive equality
-and description.
+and definite description.
 
 \begin{definition}[Types]\label{holtypes}
-  The set $\hol{T}$ of simple types freely generated from a set of
+  The set $\hol{T}$ of simple types is freely generated from a set of
   basic types $\{\hol{o}, \hol{i}\}$ using the function type
@@
 \begin{definition}[Syntax of $\HOL$]\label{holgrammar}
-The language of higher-order logic $\HOL$ with primitive equality and
-description is defined by the following
+The terms of $\HOL$ with primitive equality and
+definite description are defined by the following
 grammar:\footnote{It is well known that we could work with a much smaller set
@@
 each term is given as a subscript.  Terms $\hol{s_o}$ of type $\hol{o}$ are called
-formulas.  The logical connectives of choice are
+\emph{formulas}.  The \emph{logical connectives} of choice are
 $\hol{\neg_{o\ar o}}$, $\hol{\vee_{o\ar
@@
 \begin{definition}[Model for \HOL]\label{holmodel}
-  A \emph{model} for \HOL is a tuple $\hol{M}=\hol{\langle D, I \rangle}$, where
+  A \emph{model (structure)} for \HOL is a tuple $\hol{M}=\hol{\langle D, I \rangle}$, where
   $\hol{D}$ is a frame, and $\hol{I}$ is a family of typed interpretation
@@
 \item $\hol{\|(\neg_{o\ar o}\, s_o)_o\|^{M,g}} = {\True}$ if and only if $\hol{\|s_o\|^{M,g}} = {\False}$
-\item $\hol{\|(({\vee_{o\ar o\ar o}}\,s_o)\,t_o)_o\|^{M,g}} =
+\item \sloppy $\hol{\|(({\vee_{o\ar o\ar o}}\,s_o)\,t_o)_o\|^{M,g}} =
   {\True}$ if and only if\, $\hol{\|s_o\|^{M,g}} = {\True}$ or $\hol{\|t_o\|^{M,g}}
@@
     s_o))_o\|^{M,g}} = {\True}$ if and only if for all $\hol{d}\in
-  \hol{D_\alpha}$ we have $\hol{\|s_o\|^{M,g[d/X_\alpha]}} = {\False}$
+  \hol{D_\alpha}$ we have $\hol{\|s_o\|^{M,g[d/X_\alpha]}} = {\True}$
 \item $\hol{\|(\Descr_{(\alpha\ar o)\ar \alpha}(\lam{X_\alpha}
@@
 an element of the domain of existing objects denoted by
-$\hol{\ex_{i\ar o}}$.
+$\hol{\ex_{i\ar o}}$ (technically this can be achieved by postulating
+a respective axiom).
 
@@
 of $\FFOL$ to corresponding variables (of type $i$), uninterpreted function
-symbols and uninterpreted predicate symbols in \HOL.
+symbols and uninterpreted predicate symbols in \HOL, respectively.
 
@@
 Nitpick, LEO-II and Leo-III. Alternatively, this theory can be encoded
-in interactive proof assistants, such as Isabelle/HOL. <
+in interactive proof assistants, such as Isabelle/HOL. 
   % \footnote{An example of respective abstract level proof
@@
 
-Properties of $\FFOL$ could now be experimentally explored with
+The different properties of $\FFOL$ could now be experimentally explored with
 automated reasoning tools for $\HOL$. We have conducted such
@@
 \section{Exploring Axioms Systems for Category Theory}
-In an experimental theory exploration study, in which we utilized the
-free logic reasoning farmework from above, 
+In an experimental theory exploration study, utilizing the
+free logic reasoning framework from above, 
 we have shown how Scott's
@@
 
-The stepwise evolution has been described in detail
-in\cite{ArXiv}. Below we summarize these experiments.  However, first
-we describe some basic modeling decisions for the technical encoding
-in Isabelle/HOL. The sources of our experiments, as discussed in
+The stepwise evolution has been described in detail in
+\cite{ArXiv}. Below we summarize these experiments.  However, first we
+describe some basic modeling decisions for the technical encoding in
+Isabelle/HOL.
+
+The sources of our experiments, as discussed in
 \cite{ArXiv}, are available at
@@
 nor the designated undefined object $\hol{\star}$, since both were not
-required in this particular application.
+required in this particular application. A related Isabelle/HOL
+encoding of the above theory with description has been presented and
+discussed in \cite{ICMS}.
 
@@
 $\HOL$, encoded in Isabelle/HOL, that we have employed in our
-experiments. Excerpts of these experiments are illustrated in Fig.~\ref{pic2}. A related Isabelle/HOL encoding of the above theory with
-description has been presented and discussed in
-\cite{ICMS}.\footnote{In the remainder of this article, and inline
+experiments.\footnote{In the remainder of this article, and inline
   with our text so far,  we present the formulas of
@@
   (for technical reasons) reversed.} 
+An excerpt of these experiments is shown in Fig.~\ref{pic2}.
 
@@
 $\hol{D_i}$). We introduce three partial functions, 
-$\dom$ (domain), $\cod$ (codomain), and $\comp$ (morphism composition). 
+$dom$ (domain), $cod$ (codomain), and $\comp$ (morphism composition). 
 Partiality of composition is handled exactly as expected: we generally may have 
@@
 $D=\{i_i,i_2\}$ and $E=\{i_1\}$;  $i_1\comp i_1$ is $i_1$,  and $i_2$
-in all other cases; $\cod$ and $\dom$ are identity on $D$. Without constraining the request, Nitpick
+in all other cases; $cod$ and $dom$ are identity on $D$. Without constraining the request, Nitpick
 generates an even simpler model (called $M_0$ in the remainder):
-$D=\{i_i\}$ and $E=\emptyset$; $i_1\comp i_1$ is $i_1$; $\cod$ and
-$\dom$ are identity on $D$. It is trivial to check that these models
+$D=\{i_i\}$ and $E=\emptyset$; $i_1\comp i_1$ is $i_1$; $cod$ and
+$dom$ are identity on $D$. It is trivial to check that these models
 indeed confirm the consistency of all axioms sets from Table \ref{axioms-sets-1}.
@@
 composition operation $\comp$. The existence of left and right identity elements is 
-addressed in the last two axioms. The notions of $\dom$ (Domain) and
-$\cod$ (Codomain)
+addressed in the last two axioms. The notions of $dom$ (domain) and
+$cod$ (codomain)
 abstract from their common meaning in the context of sets. In category theory we
@@
 that strictness is now also postulated for the new Skolem functions
-$\dom$ and $cod$. Note that the values of Skolem functions
+$dom$ and $cod$. Note that the values of Skolem functions
 outside $E$ can just be given by the identity function.
@@
   Isabelle/HOL with the exactly required dependencies they
-  detected. With the provided dependency information the trusted tools
+  detected, in this case $C_{ii}$, $D_{ii}$, $E_{ii}$ and $S_{ii}$. With the provided dependency information the trusted tools
   in Isabelle/HOL were then able to reconstruct the external proofs on
@@
 
-\subsection{Axioms Set III, IV and V} 
+\subsection{Axioms Sets III, IV and V} 
 In Axioms Set III the existence  axiom  $E_{ii}$ from Axioms Set II  is simplified by taking advantage of 
@@
  system by Freyd and Scedrov to our Axioms Set V from Table
- \ref{axioms-sets-1} concerns axiom $S3$ respectively $A1$. Namely,
+ \ref{axioms-sets-1} concerns axiom $S3$, respectively $A1$. Namely,
  instead of the non-reflexive existing identity $\simeq$, they use
@@
 even stronger. It implies that \emph{all} objects are defined,
-that is, composition (as well as $\dom$ and $cod$) become total operations.
+that is, composition (as well as $dom$ and $cod$) become total operations.
 The theory described by these axioms ``collapses'' to the theory of
@@
 prove falsity from Axioms Sets FS-II and FS-I when assuming a 
- non-existing object of type $i$:
+ non-existing object of type $\hol{i}$:
 $$(\exists x\lambdot \neg E x) \imp False$$
@@
 
-However, when assuming strictness of $\dom$ and $\cod$, the axioms
+However, when assuming strictness of $dom$ and $\cod$, the axioms
 A2a, A2b, A4a and A4b are all implied. Hence, under this 
@@
 
-For Axioms Set FS-III the consistency checks with Nitpick succeeds,
+For Axioms Set FS-III the consistency checks with Nitpick succeed,
 even if we assume undefined objects. However, this axioms set is
@@
 the axioms of this set are implied.  The situation changes when we
-explicitly postulate strictness of $\dom$, $\cod$ and $\comp$. Doing
+explicitly postulate strictness of $dom$, $cod$ and $\comp$. Doing
 so we obtain Axioms Set FS-IV from Table \ref{axioms-sets-4}, which,
@@
 
-Moreover, abstract level proof tactics could be provided in proof
-assistants to support --- as an alternative to always unfolding the
-mapping from $\FFOL$ to $\HOL$ --- intuitive interaction (and even
+Moreover, as an alternative to always unfolding the mapping from
+$\FFOL$ to $\HOL$, abstract level proof tactics could be provided
+e.g. in Isabelle/HOL to support intuitive interaction (and even
 automation) in $\FFOL$ on top the semantical embedding.

### 2018-09-11 FreeLogic/2018-AFP/AxiomaticCategoryTheory/output/document/root.tex
added

\documentclass[11pt,a4paper]{article}
\usepackage{isabelle,isabellesym}
\usepackage{authblk}
\usepackage{latexsym,amsmath}
\usepackage[margin=2cm]{geometry}

% further packages required for unusual symbols (see also
% isabellesym.sty), use only when needed

\usepackage{amssymb}
  %for \<leadsto>, \<box>, \<diamond>, \<sqsupset>, \<mho>, \<Join>,
  %\<lhd>, \<lesssim>, \<greatersim>, \<lessapprox>, \<greaterapprox>,
  %\<triangleq>, \<yen>, \<lozenge>

%\usepackage{eurosym}
  %for \<euro>

%\usepackage[only,bigsqcap]{stmaryrd}
  %for \<Sqinter>

%\usepackage{eufrak}
  %for \<AA> ... \<ZZ>, \<aa> ... \<zz> (also included in amssymb)

%\usepackage{textcomp}
  %for \<onequarter>, \<onehalf>, \<threequarters>, \<degree>, \<cent>,
  %\<currency>

% this should be the last package used
\usepackage{pdfsetup}

% urls in roman style, theory text in math-similar italics
\urlstyle{rm}
\isabellestyle{it}

% for uniform font size
%\renewcommand{\isastyle}{\isastyleminor}

\begin{document}

\title{Axiom Systems for Category Theory in Free Logic}
\author[1]{Christoph Benzm\"uller}
\author[2]{Dana S. Scott}
\affil[1]{University of Luxembourg, Luxembourg \& Freie Universit\"at Berlin, Germany}
\affil[2]{Visiting Scholar at University of Califormia, Berkeley,  USA}
\date{\today}                     %% if you don't need date to appear
\setcounter{Maxaffil}{0}
\renewcommand\Affilfont{\itshape\small}

\maketitle

\tableofcontents

% sane default for proof documents
\parindent 0pt\parskip 0.5ex

% generated text of all theories
\input{session}

% optional bibliography
\bibliographystyle{abbrv}
% \bibliography{root}

\begin{thebibliography}{1}

\bibitem{C57}
C.~Benzm{\"u}ller and D.~Scott.
\newblock Automating free logic in {Isabelle/HOL}.
\newblock In G.-M. Greuel, T.~Koch, P.~Paule, and A.~Sommese, editors, {\em
  Mathematical Software -- ICMS 2016, 5th International Congress, Proceedings},
  volume 9725 of {\em LNCS}, pages 43--50, Berlin, Germany, 2016. Springer.

\bibitem{C67}
C.~Benzm{\"u}ller and D.~Scott.
\newblock Some reflections on a computer-aided theory exploration study in
  category theory (extended abstract).
\newblock In T.~C. Hales, C.~Kaliszyk, S.~Schulz, and J.~Urban, editors, {\em
  3rd Conference on Artificial Intelligence and Theorem Proving (AITP 2018),
  Book of Abstracts}, 2018.

\bibitem{R58}
C.~Benzm{\"u}ller and D.~S. Scott.
\newblock Axiomatizing category theory in free logic.
\newblock Technical report, CoRR, 2016.
\newblock \url{http://arxiv.org/abs/1609.01493}.

\bibitem{FreydScedrov90}
P.~J. Freyd and A.~Scedrov.
\newblock {\em Categories, Allegories}.
\newblock North Holland, 1990.

\bibitem{MacLane48}
S.~McLane.
\newblock Groups, categories and duality.
\newblock {\em Proceedings of the National Academy of Sciences},
  34(6):263--267, 1948.

\bibitem{Scott79}
D.~Scott.
\newblock Identity and existence in intuitionistic logic.
\newblock In M.~Fourman, C.~Mulvey, and D.~Scott, editors, {\em Applications of
  Sheaves: Proceedings of the Research Symposium on Applications of Sheaf
  Theory to Logic, Algebra, and Analysis, Durham, July 9--21, 1977}, volume 752
  of {\em Lecture Notes in Mathematics}, pages 660--696. Springer Berlin
  Heidelberg, 1979.

\end{thebibliography}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2018-10-10 FreeLogic/2017-Journal/REVISED/article.tex
added

--- 2017-04-29 FreeLogic/2017-Journal/article.tex
@@
   verification of free logic theories.  
-  Subsequently, this approach is exemplarily employed in a selected domain of
-  mathematics: starting from a generalization of the standard axioms
+  Subsequently, this approach is applied to a selected domain of
+  mathematics:
+ starting from a generalization of the standard axioms
   for a monoid we present a stepwise development of various, mutually
@@
   and utilize interactive and automated reasoning in free logic, and
-  to present respective experiments.
+  to present illustrative experiments.
 
@@
 classical higher-order logic (HOL) \cite{B5}. The proposed solution
-employs a semantic embedding of free in HOL. We present, as an
+employs a semantic embedding of free logic in HOL. We present, as an
 example, one implementation of this idea in the mathematical proof
@@
 close interaction with automated reasoning tools. 
+Perhaps the lesson to be learned here is that, when working with partial functions,
+it is natural --- out of caution  --- to assume too much, and the automated reasoning
+tools, as we have shown here, can help find in what ways the axioms might be reduced or
+simplified.
 

### 2018-10-12 FreeLogic/2018-JAR/article.tex
modfied

--- 2018-10-10 FreeLogic/2017-Journal/REVISED/article.tex
@@
 
-\newcommand\map[1]{\hat{#1}}
+\newcommand\map[1]{\widehat{#1}}
 \newcommand\hol[1]{\boldsymbol{#1}}
@@
 
+\newtheorem{thm}{Theorem} 
+\newtheorem{defn}[thm]{Definition}
+\newtheorem{lem}[thm]{Lemma}
+
 \begin{document}
@@
 \institute{Christoph Benzm\"uller \at
-   University of Luxembourg, Luxembourg \& Freie Universit\"at Berlin, Berlin, Germany \\
+   Freie Universit\"at Berlin, Berlin, Germany \& University of Luxembourg, Luxembourg\\
 %   Stanford University, CSLI/Cordura Hall, Stanford, CA 94305-4115, U.S. \\
@@
 inadequate support for these challenge concepts.  Free logic \cite{Lambert60,Scott67,lambert02:_free_logic,sep-logic-free} offers a
-theoretically appealing solution, but is has been considered as rather
+theoretically appealing solution, but it has been considered as rather
 unsuited towards practical utilization.
@@
 employs a semantic embedding of free logic in HOL. We present, as an
-example, one implementation of this idea in the mathematical proof
+example, one implementation of this idea in the proof
 assistant Isabelle/HOL \cite{NPW02}. Various state-of-the-art
@@
 solution can be utilized, via Isabelle as foreground system, with a
-whole range of other background reasoners. As a result we obtain an
+whole range of other background reasoners, such as SMT solvers and
+first-order and higher-order automated theorem
+provers.\footnote{Cf.~\S\ref{sec-remarks-experiments} for further
+  information.} As a result we obtain an
 elegant and powerful implementation of an interactive and automated
@@
 quantifiers range over. In free logic these
-basic assumption are abolished. Terms do still denote objects in a
-(non-empty) domain $\D$, but a (possibly empty) set $\ex\subseteq \D$ is
+basic assumptions are abolished. Terms do still denote objects in a
+(non-empty) domain $\D$, but a (possibly empty) set $\ex\subset \D$ is
 chosen to characterize the subdomain of ``\emph{existing}'' resp. ``\emph{defined}''
@@
 Fig.~\ref{fig1}. It
-employs a distinguished undefined object $\star$.  
+employs a distinguished undefined object $\star$.\footnote{The $\star$
+  symbol is not to be confused with any other symbol in Isabelle/HOL.}
 % Free logic (and inclusive logic) has been proposed as an alternative
@@
 
-\begin{definition}[Syntax of $\FFOL$]
+\begin{defn}[Syntax of $\FFOL$]
   We start with a denumerable set $\V$ of variable symbols, a denumerable set
@@
 \end{enumerate}
-\end{definition}
+\end{defn}
 
@@
 
-\begin{definition}[Model of $\FFOL$]
+\begin{defn}[Model of $\FFOL$]
   A \emph{model (structure) for $\FFOL$} consists of a quadruple
   $M = \langle D, \ex, I, \star\rangle$, where $D$ is a non-empty raw domain of
-  objects, $\ex\subseteq D$ a possible empty set of existing/defined objects, and $I$ an interpretation function
+  objects, $\ex\subset D$ a possible empty set of existing/defined objects, and $I$ an interpretation function
   mapping $0$-ary function symbols (constants) to defined objects $d\in \ex$, 
@@
   (non-existing/undefined) object. 
-\end{definition}
-
-\begin{definition}[Evaluation Function for $\FFOL$]
+\end{defn}
+
+\begin{defn}[Evaluation Function for $\FFOL$]
   The \emph{value} $\| s \|^{M,g}$ of a term or formula $s\in\FFOL$
@@
 
-\end{definition}
-
-\begin{definition}[Validity]\label{ffollvalid}
+\end{defn}
+
+\begin{defn}[Validity]\label{ffollvalid}
   A formula $s_o$ is \emph{true} in model $M$ under assignment $g$ if and only if
-  $\|s_o\|^{M,g} = T$; this is also denoted as $M,g \models^\FFOL s_o$.  A
+  $\|s_o\|^{M,g} = True$; this is also denoted as $M,g \models^\FFOL s_o$.  A
   formula $s_o$ is called \emph{valid} in $M$, which is denoted as
@@
 %   at least one $t_o\in \Delta$.
-\end{definition}
+\end{defn}
 
@@
 
-\begin{definition}[Types]\label{holtypes}
+\begin{defn}[Types]\label{holtypes}
   The set $\hol{T}$ of simple types is freely generated from a set of
@@
   may avoid parentheses if the structure of a complex type is clear in context.
-\end{definition}
-
-\begin{definition}[Syntax of $\HOL$]\label{holgrammar}
+\end{defn}
+
+\begin{defn}[Syntax of $\HOL$]\label{holgrammar}
 The terms of $\HOL$ with primitive equality and
@@
   set of primitive connectives as chosen in higher-order automated theorem provers such
-  as LEO-II \cite{LEO}, Leo-III \cite{Leo-III} and Satallax \cite{Satallax}.}
+  as LEO-II \cite{LEO}, Leo-III \cite{Leo-III}, and Satallax \cite{Satallax}.}
 \begin{align*} 
@@
   \neg (\neg X \vee \neg Y)}$.
-\end{definition}
+\end{defn}
 
@@
 
-%\begin{definition}\label{homlbetaeta} %\footnote{\textbf{Chris:} Is Def.4 needed at all?}
+%\begin{defn}\label{homlbetaeta} %\footnote{\textbf{Chris:} Is Def.4 needed at all?}
   % Two common relations on terms are given by $\hol{\beta}$-reduction and
@@
 % summary below is adapted from Andrews~\cite{sep-type-theory-church}.
-%\end{definition}
-
-%\begin{definition}\label{homlassignment}
+%\end{defn}
+
+%\begin{defn}\label{homlassignment}
 A \emph{variable assignment} $\hol{g}$ maps
@@
 now mapped to $\hol{d}$.
-%\end{definition}
-
-\begin{definition}[Frame for \HOL]\label{homlframe}
+%\end{defn}
+
+\begin{defn}[Frame for \HOL]\label{homlframe}
 A \emph{frame} $\hol{D}$ is a collection $\hol{\{D_\alpha\}_{\alpha\in\entity{T}}}$
@@
 $\hol{D_\alpha}$ into $\hol{D_\beta}$. 
-\end{definition}
-
-\begin{definition}[Model for \HOL]\label{holmodel}
+\end{defn}
+
+\begin{defn}[Model for \HOL]\label{holmodel}
   A \emph{model (structure)} for \HOL is a tuple $\hol{M}=\hol{\langle D, I \rangle}$, where
@@
   $\hol{D_{\alpha\ar\alpha\ar o}}$ contain the respective identity relations.
-\end{definition}
-
-\begin{definition}[Evaluation Function for \HOL]\label{holvalue}
+\end{defn}
+
+\begin{defn}[Evaluation Function for \HOL]\label{holvalue}
   The \emph{value} $\hol{\| s_\alpha\|^{M,g}}$ of a \HOL term
@@
 \end{enumerate}
-\end{definition}
-
-\begin{definition}[Standard and Henkin models]\label{homlhenkinmodel}
+\end{defn}
+
+\begin{defn}[Standard and Henkin models]\label{homlhenkinmodel}
  A model $\hol{M}=\hol{\langle D, I \rangle}$ is called a
@@
  also a Henkin model. 
-\end{definition}
+\end{defn}
 
@@
 
-\begin{definition}[Validity]\label{homlvalid}
+\begin{defn}[Validity]\label{homlvalid}
 A formula $\hol{s_o}$ is \emph{true} in model $M$ 
@@
 % $\hol{M,g \models^\HOL s_o}$ for all $\hol{s_o}\in \hol{\Gamma}$ and $\hol{M,g \models^\HOL t_o}$ for at least one $\hol{t_o}\in \hol{\Delta}$.
-\end{definition}
+\end{defn}
 
@@
 is given in the signature of $\HOL$. Moreover, we assume that an
-uninterpreted constant symbol $\hol{\star}$ of type $\hol{i}$ be in the
+uninterpreted constant symbol $\hol{\star}$ of type $\hol{i}$ is in the
 signature of $\HOL$. Finally, we assume that $\hol{\|E \star_i\|^{M,g}=F}$ for
@@
 
-\begin{definition}[Embedding of $\FFOL$ in \HOL]
+\begin{defn}[Embedding of $\FFOL$ in \HOL]
 Given a formula $s \in \FFOL$. We map $s$ to a corresponding term $\map{s}$ of \HOL. This
@@
 % \Impl s$, $r \wedge  s := \neg (\neg r \vee \neg s)$, 
-\end{definition}
+\end{defn}
 
@@
 $\hol{g}$ (remember that $\FFOL$  domains $D$ are  identified with 
-\HOL domains $\hol{D_i}$, i.e. $\map{D} = \hol{D_i}$): Let $g$ be a variable assignment for
+\HOL domains $\hol{D_i}$, i.e. $\map{D} = \hol{D_i}$): let $g$ be a variable assignment for
   $\FFOL$.  Then $\map{g}:
@@
 
-\begin{definition}[Henkin model $\map{M}$ for $\FFOL$ model $M$]\label{def:hm}
+\begin{defn}[Henkin model $\map{M}$ for $\FFOL$ model $M$]\label{def:hm}
 Given a $\FFOL$ model $M = \langle D, \ex, I, \star\rangle$. The Henkin
@@
 % \exInW_{i\typearrow\utype\typearrow o}$ as characterized next. Interpretation $I$ is constructed as follows:
-\end{definition}
-
-\begin{lemma}\label{lemma:1} \sloppy
+\end{defn}
+
+\begin{lem}\label{lemma:1} \sloppy
   Let $\map{M}$ be a Henkin model for $\FFOL$ model $M$. For all
@@
   definition of the embedding $\map{\cdot}$, definition of $\map M$ and
-  $\map g$, $\lambda$-conversion, induction hypothesis and a series of tedious evaluation
+  $\map g$, $\lambda$-conversion, induction hypothesis and a series of evaluation
   steps in \HOL we get
@@
 \end{proof}
-\end{lemma}
-
-\begin{theorem}[Soundness and Completeness of the Embedding]\ \\
+\end{lem}
+
+\begin{thm}[Soundness and Completeness of the Embedding]\ \\
 For all formulas $s\in FFOL$ we have
@@
 \end{proof}
-\end{theorem}
+\end{thm}
 
@@
 Nitpick, LEO-II and Leo-III. Alternatively, this theory can be encoded
-in interactive proof assistants, such as Isabelle/HOL. 
+in interactive proof assistants such as Isabelle/HOL, which is the
+option we have chosen here. We thereby significantly benefit
+from the powerful proof automation means as provided in Isabelle/HOL,
+in particular, from the integrated model finder Nitpick, the SMT
+solvers CVC4~\cite{CVC4} and Z3~\cite{Z3}, and the first-order theorem
+provers E~\cite{E} and Spass~\cite{Spass}.
+
   % \footnote{An example of respective abstract level proof
@@
 
-The proofs are found by Sledgehammer and verified in Isabelle/HOL. Using Sledgehammer we have also
-shown that Axioms Set II implies Axioms Set I. Vice versa, Axioms Set I
-also implies Axioms Set II. This can easily 
-be shown by semantical means on the meta-level.
-
-\subsection{Remark on the Experiments}
+The proofs are found by the Sledgehammer tool and automatically
+reconstructed in Isabelle/HOL. Further information on these
+experiments are provided in \S\ref{sec-remarks-experiments}
+below. Using Sledgehammer we have also shown that Axioms Set II
+implies Axioms Set I. Vice versa, Axioms Set I also implies Axioms Set
+II. This can easily be shown by semantical means on the meta-level.
+
+\subsection{Remark on the Experiments}  \label{sec-remarks-experiments}
+\marginpar{Include remark on SMT calls and the SMT tactic (see Reviewer 1)}
+\marginpar{Include remark on Sledgehammer and how it works (see Reviewer 1)}
+
 All proofs above and all proofs in the rest of this paper (unless
@@
   Isabelle/HOL, in which all the proofs have nevertheless been
-  contributed by automated theorem provers. However, there are still
+  contributed by automated theorem provers.
+
+\marginpar{Remove this part? SMT is now called as an oracle.}
+  However, there are still
   a few calls of the \textsc{smt}-tactic contained in our document, 
@@
 
- Let $a\in D$ be an undefined object, that is, assume $¬E a$.  By
+ Let $a\in D$ be an undefined object, that is, assume $\neg E a$.  By
  instantiating axiom $A3a$ with $a$ we have $a \comp (\dom a) \cong a$.  From

### 2018-10-12 FreeLogic/2017-arXiv/runIsabelle.sh

@@ -1,1 +1,1 @@
-/Applications/Isabelle2016.app/Isabelle/bin/isabelle build -D .
+/Applications/Isabelle2017.app/Isabelle/bin/isabelle build -D .

### 2018-10-12 FreeLogic/2018-JAR/article.tex
modfied

@@
 
+\usepackage{cite}
+
 %\usepackage{authblk}
@@
 formalisms that are free of basic existence assumptions regarding the
-denotation of terms. Remember that terms in e.g. traditional classical
+denotation of terms.\footnote{Calculi for free logic are presented in \cite{sep-logic-free}; see also the references
+therein.} Remember that terms in e.g. traditional classical
 and intuitionistic predicate logics always denote an (existing) object
@@
 
-The sources of our experiments, as discussed in
-\cite{ArXiv}, are available at
-\url{http://christoph-benzmueller.de/papers/2017-arXiv.zip}. Note that
-in these sources we added neither the definite description operator
-nor the designated undefined object $\hol{\star}$, since both were not
-required in this particular application. A related Isabelle/HOL
-encoding of the above theory with description has been presented and
-discussed in \cite{ICMS}.
+The sources of our experiments as conducted here are available at
+\url{http://christoph-benzmueller.de/papers/2018-JAR-sources.zip}.
+These sources contain an embedding of full free logic in Isabelle/HOL,
+that is, with $\star$ and definite description
+(cf.~Fig.\ref{pic1}). In \cite{ArXiv}, $\star$ and definite
+description were still avoided; they are in fact not really 
+relevant for the conducted experiments.
+% Note that
+% in these sources we added neither the definite description operator
+% nor the designated undefined object $\hol{\star}$, since both were not
+% required in this particular application. A related Isabelle/HOL
+% encoding of the above theory with description has been presented and
+% discussed in \cite{ICMS}.
 
@@
  \includegraphics[width=\textwidth]{FFOL-Pic1}
- \caption{Isabelle/HOL encoding of $\FFOL$ (without description)\label{pic1}}
+ \caption{Isabelle/HOL encoding of $\FFOL$ (with $\star$ and definite description). \label{pic1}}
 \end{figure}
@@
  \caption{Encoding of Axioms Set V in Isabelle/HOL utilizing the
-   embedded logic $\FFOL$ \label{pic2}}
+   embedded logic $\FFOL$; Axioms Set V is proven equivalent to Axioms
+   Set IV. \label{pic2}}
 \end{figure}
@@
 \subsection{Remark on the Experiments}  \label{sec-remarks-experiments}
-\marginpar{Include remark on SMT calls and the SMT tactic (see Reviewer 1)}
-\marginpar{Include remark on Sledgehammer and how it works (see Reviewer 1)}
+% \marginpar{Include remark on SMT calls and the SMT tactic (see Reviewer 1)}
+% \marginpar{Include remark on Sledgehammer and how it works (see
+%   Reviewer 1)}
+% \marginpar{Add footnote on some issues with Sledgehammer, Z3 and Spass}
 
@@
 reasonable time (typically just a few seconds) with the
-Sledgehammer tool in Isabelle/HOL. This tool interfaces to prominent
+Sledgehammer tool in Isabelle/HOL (version Isabelle2017). This tool interfaces to prominent
 first-order automated theorem provers such as CVC4 \cite{CVC4}, Z3
@@
   Isabelle/HOL, in which all the proofs have nevertheless been
-  contributed by automated theorem provers.
-
-\marginpar{Remove this part? SMT is now called as an oracle.}
-  However, there are still
-  a few calls of the \textsc{smt}-tactic contained in our document, 
-   which we found are not entirely trivial to replace. In this sense, our
-   Isabelle/HOL verification is modulo the correctness of the \textsc{smt} solvers
-   CVC4 \cite{CVC4} and Z3 \cite{Z3}.
+  contributed by automated theorem provers. For further information on
+  the use and functioning of Sledgehammer we refer to the 
+  literature \cite{Sledgehammer,SledgehammerTutorial}.
+
+  In our experiments we have also made use of the Isabelle/HOL's
+  \textsc{smt} method, which ``translates the conjecture and any
+  user-supplied facts to the SMT solvers’ many-sorted first-order
+  logic, invokes a solver, and (depending on the solver) either trusts
+  the result or attempts to reconstruct the proof in Isabelle.''
+  (\cite[p.~5]{Sledgehammer}).\footnote{Technical remark: We have
+    selected CVC4 in our experiments as the default SMT solver, since
+    we did run into errors when working with Z3. These errors can
+    easily be reconstructed in the provided source files when
+    switching back to Z3 as default.}  For quite some time the use of the \textsc{smt}
+  method has been controversially discussed in the Isabelle/HOL
+  community. However, since about a year, the \textsc{smt} method is
+  now even eligible in submissions to the Archive of Formal
+  Proofs. For the work presented here this community internal discussion is 
+  of little relevance, since we could replace all uses of the\textsc{smt} method
+  by alternative proofs (which we avoid in order to keep
+  our formalisation concise).
+
+% \marginpar{Remove this part? SMT is now called as an oracle.}
+%   However, there are still
+%   a few calls of the \textsc{smt}-tactic contained in our document, 
+%    which we found are not entirely trivial to replace. In this sense, our
+%    Isabelle/HOL verification is modulo the correctness of the \textsc{smt} solvers
+%    CVC4 \cite{CVC4} and Z3 \cite{Z3}.
 
@@
 \\
-  $A1$ &  $\ex(x \circ y) \longleftarrow (x\Box \cong \Box y)$ \\ 
+  $A1$ &  $\ex(x \circ y) \longleftrightarrow (x\Box \cong \Box y)$ \\ 
   $A2a$ & $((\Box x)\Box) \cong \Box x$ \\ 
@@
   constructed if we do not make any assumptions about non-existing
-  objects. In fact, the model presented by Nitpick for this case
+  objects.\footnote{For this we have to inactivate the axiom
+    that postulates that $\star$ is an undefined/non-existing object.} In fact, the model presented by Nitpick for this case
   consists of a single, existing morphism.
@@
 
-Further work includes the continuation of our formalization studies in
+Further work includes the extension of our work towards an embedding of
+free higher-order logic, the continuation of our formalization studies in
 category theory and the application of free logic to various other
 mathematical domains, including, for example,  projective geometry.
+Regarding extensions towards free  higher-order logic some first steps
+have already been taken \cite{W56,makarenko16:_autom_logik_logik_stufe}.
 

### 2018-10-14 FreeLogic/2018-JAR/article.tex
corrections

@@
   equivalent foundational axiom systems for category theory. As a
-  side-effect of this work some (minor) issue in a prominent category
-  theory textbook has been revealed.
+  side-effect of this work some (minor) issues in a prominent category
+  theory textbook have been revealed.
 
@@
 For \emph{partial} functions $f$ we may have some $x$ such that $\ex x$ but not
-$\ex(f x)$. A function $f$ is \emph{strict}  if  and only if for all $x$
+$\ex(f x)$. A function $f$ is called \emph{strict}  if  and only if
+for all $x\in \D$
  we have $\ex(f x) \imp \ex x$.
 
-The particular notion of free logic as exploited in the remainder of
-this article has been proposed by Scott \cite{Scott67}.  A graphical
+The particular version of free logic as exploited in the remainder of
+this article was proposed by Scott \cite{Scott67}.  A graphical
 illustration of this notion of free logic is presented in
@@
 
-We formally introduce the syntax and semantics of free logic as
-assumed in the remainder of this article. We refer to this logic with $\FFOL$.
+We next  formally introduce the syntax and semantics of free logic as
+to be used in the remainder of this article. We refer to this logic as
+$\FFOL$.
 
@@
     %stick here to the simply typed $\lambda$-calculus for a better understanding.}
-  HOL has its origin in the work by
+  HOL has its origin in the work of
   Church~\cite{Church40}.
@@
 references therein). Below we introduce a variant of \HOL with primitive equality
-and definite description.
+and definite descriptions.
 
@@
 an earlier paper \cite{ICMS}. These experiments confirm the
-illustrating examples discussed in Scott's paper \cite{Scott67}.
+illustrative examples discussed in Scott's paper \cite{Scott67}.
 
 \section{Exploring Axioms Systems for Category Theory}
-In an experimental theory exploration study, utilizing the
+In an experimental theory-exploration study, utilizing the
 free logic reasoning framework from above, 
@@
   Proofs. For the work presented here this community internal discussion is 
-  of little relevance, since we could replace all uses of the\textsc{smt} method
+  of little relevance, since we could replace all uses of the \textsc{smt} method
   by alternative proofs (which we avoid in order to keep
@@
 \multicolumn{2}{c}{Axioms Set VI: Freyd and Scedrov in our notation
-  and corrected} \\
+(corrected)} \\
 %\hline
@@
 
-Further work includes the extension of our work towards an embedding of
-free higher-order logic, the continuation of our formalization studies in
-category theory and the application of free logic to various other
-mathematical domains, including, for example,  projective geometry.
-Regarding extensions towards free  higher-order logic some first steps
-have already been taken \cite{W56,makarenko16:_autom_logik_logik_stufe}.
+Further work includes the extension of our work towards an embedding
+of free higher-order logic, the continuation of our formalization
+studies in category theory (especially extensions of the theory
+involving functors) and the application of free logic to
+various other mathematical domains, including, for example, projective
+geometry.  Regarding extensions towards free higher-order logic some
+first steps have already been taken
+\cite{W56,makarenko16:_autom_logik_logik_stufe}, and a recent
+continuation of our formalisation studies \cite{J39} now also includes 
+an early axiom system for category theory by Saunders MacLane
+\cite{maclane48:_group}.
 

### 2018-10-14 FreeLogic/2018-JAR/article.tex
added

@@
   $D \times \ldots \times D$. $\True$ or $\False$ denote truth and
-  felshood respectively. Finally, $\star\in D\setminus \ex$ is a designated
+  falsehood respectively. Finally, $\star\in D\setminus \ex$ is a designated
   (non-existing/undefined) object. 
@@
 
-\begin{defn}[Evaluation Function for $\FFOL$]
+\begin{defn}[Evaluation Function for $\FFOL$] \sloppy
   The \emph{value} $\| s \|^{M,g}$ of a term or formula $s\in\FFOL$
@@
 
-We assume familiarity with $\lambda$-conversion (e.g. \emph{$\alpha$-renaming} and
+\sloppy We assume familiarity with $\lambda$-conversion (e.g. \emph{$\alpha$-renaming} and
 \emph{$\beta\eta$-reduction}) and \emph{$\beta\eta$-normal forms}~\cite{barendregt13book}.
@@
 
-\begin{defn}[Henkin model $\map{M}$ for $\FFOL$ model $M$]\label{def:hm}
+\begin{defn}[Henkin model $\map{M}$ for $\FFOL$ model
+  $M$]\label{def:hm} \sloppy
 Given a $\FFOL$ model $M = \langle D, \ex, I, \star\rangle$. The Henkin
@@
 \hline
-\\
+\\[-.8em]
 \multicolumn{2}{c}{Axioms Set I} \\
@@
 \hline
-\\
+\\[-.8em]
 \multicolumn{2}{c}{Axioms Set II} \\
@@
 \hline
-\\
+\\[-.8em]
 \multicolumn{2}{c}{Axioms Set III} \\
@@
 \hline
-\\
+\\[-.8em]
 \multicolumn{2}{c}{Axioms Set IV} \\
@@
 \hline
-\\
+\\[-.8em]
 \multicolumn{2}{c}{Axioms Set V (Scott 79, \cite{Scott79})} \\

### 2018-11-23 FreeLogic/2018-JAR/article.tex
update

@@
 
-\author{Christoph Benzm\"uller  and Dana S. Scott}
+\author{Christoph Benzm\"uller\thanks{Benzmüller received funding from the German National Research
+  Foundation DFG under Heisenberg grant \emph{Towards Computational
+    Metaphysics} (BE 2501/9-2) and from VolkswagenStiftung under grant
+  Consistent Rational Argumentation in Politics (CRAP).}  and Dana S. Scott}
 \institute{Christoph Benzm\"uller \at
@@
   $n$-ary function symbols (for $n\geq 1$) to $n$-ary functions
-  $D \times \ldots \times D \longrightarrow D$ and $n$-ary predicate
+  $D \times \dotsb \times D \longrightarrow D$ and $n$-ary predicate
   symbols (for $n\geq 1$) to $n$-ary relations
-  $D \times \ldots \times D$. $\True$ or $\False$ denote truth and
+  $D \times \dotsb \times D$. $\True$ or $\False$ denote truth and
   falsehood respectively. Finally, $\star\in D\setminus \ex$ is a designated
@@
 that is, with $\star$ and definite description
-(cf.~Fig.\ref{pic1}). In \cite{ArXiv}, $\star$ and definite
+(cf.~Fig.~\ref{pic1}). In \cite{ArXiv}, $\star$ and definite
 description were still avoided; they are in fact not really 
@@
 The model finder Nitpick confirms consistency for all of the axioms
-sets from Table \ref{axioms-sets-1}. For example, when asked to consider at least one defined and one undefined object, then
+sets from Table~\ref{axioms-sets-1}. For example, when asked to consider at least one defined and one undefined object, then
 Nitpick generates for all cases the following model (called $M_1$ in the remainder):
@@
 $dom$ are identity on $D$. It is trivial to check that these models
-indeed confirm the consistency of all axioms sets from Table \ref{axioms-sets-1}.
+indeed confirm the consistency of all axioms sets from Table~\ref{axioms-sets-1}.
 
@@
   the result or attempts to reconstruct the proof in Isabelle.''
-  (\cite[p.~5]{Sledgehammer}).\footnote{Technical remark: We have
+  \cite[p.~5]{Sledgehammer}.\footnote{Technical remark: We have
     selected CVC4 in our experiments as the default SMT solver, since
@@
     easily be reconstructed in the provided source files when
-    switching back to Z3 as default.}  For quite some time the use of the \textsc{smt}
-  method has been controversially discussed in the Isabelle/HOL
-  community. However, since about a year, the \textsc{smt} method is
-  now even eligible in submissions to the Archive of Formal
-  Proofs. For the work presented here this community internal discussion is 
-  of little relevance, since we could replace all uses of the \textsc{smt} method
-  by alternative proofs (which we avoid in order to keep
-  our formalisation concise).
+    switching back to Z3 as default.}  For quite some time the use of
+  the \textsc{smt} method has been controversially discussed in the
+  Isabelle/HOL community, and there is in fact a significant difference
+  between using the \textsc{smt} method in combination with Z3 or with
+  CVC4, as we prefer. When setting the solver to CVC4, the contributed
+  proofs are accepted and being trusted without replaying them in the
+  Isabelle kernel. Proofs contributed by Z3, in contrast, are never
+  trusted and always replayed in Isabelle's kernel. For the work
+  presented here this community internal discussion is of minor
+  relevance, so that we decided to continue working with CVC4 in order
+  to keep our formalisation concise and also because CVC4
+  performed surprisingly well in our experiments.\footnote{An expert
+    reviewer of this article, to whom we are very grateful, provided
+    alternative proofs which can be
+    fully replayed in the kernel of Isabelle.}
 
@@
  axioms set of Freyd and Scedrov from their textbook ``Categories,
- Allegories'' \cite{FreydScedrov90}.  In \S\ref{subsec-freyd-scedrov-1} we show, that their axioms set,
- replicated in Table \ref{axioms-sets-2} as Axioms Set FS-I, becomes
+ Allegories'' \cite{FreydScedrov90}.  In \S\ref{subsec-freyd-scedrov-1} we show that their axioms set,
+ replicated in Table~\ref{axioms-sets-2} as Axioms Set FS-I, becomes
  inconsistent in our free logic setting if we assume non-existing
@@
    Setting} \label{subsec-freyd-scedrov-1} A main difference in the
- system by Freyd and Scedrov to our Axioms Set V from Table
- \ref{axioms-sets-1} concerns axiom $S3$, respectively $A1$. Namely,
+ system by Freyd and Scedrov to our Axioms Set V from Table~\ref{axioms-sets-1} concerns axiom $S3$, respectively $A1$. Namely,
  instead of the non-reflexive existing identity $\simeq$, they use
@@
   The (constricted) inconsistency of Axioms Set FS-I, respectively
-  Axioms Set FS-II, from Table \ref{axioms-sets-2} has been 
+  Axioms Set FS-II, from Table~\ref{axioms-sets-2} has been 
   detected first by the model finder Nitpick. When we asked Nitpick to
@@
 even if we assume undefined objects. However, this axioms set is
-obviously weaker than Axioms Set V from Table
-\ref{axioms-sets-1}. In fact, as has been shown by Nitpick, none of
+obviously weaker than Axioms Set V from Table~\ref{axioms-sets-1}. In fact, as has been shown by Nitpick, none of
 the axioms of this set are implied.  The situation changes when we
 explicitly postulate strictness of $dom$, $cod$ and $\comp$. Doing
-so we obtain Axioms Set FS-IV from Table \ref{axioms-sets-4}, which,
+so we obtain Axioms Set FS-IV from Table~\ref{axioms-sets-4}, which,
 as Nitpick confirms, is consistent even if we assume undefined
@@
 \begin{acknowledgements}
-This work has been supported by the DFG Heisenberg fellowship (BE
-2501/9-2, \emph{Towards Computational Metaphysics}) of the first
-author.
-
  We thank G{\"u}nter Rote, Lutz Schr\"oder and and Emil Weydert for their
@@
 
+We also want to express our gratitude to the reviewers of this
+article.  Their fruitful feedback definitely helped to improve the
+final version.
 \end{acknowledgements}

### 2018-12-17 FreeLogic/2018-JAR/article.tex
update

@@
 %\bibliographystyle{spphys}       % APS-like style for physics
-\bibliography{bibliography}   % name your BibTeX data base
-
-% % Non-BibTeX users please use
-% \begin{thebibliography}{}
-% %
-% % and use \bibitem to create references. Consult the Instructions
-% % for authors for reference list style.
-% %
-% \bibitem{RefJ}
-% % Format for Journal Reference
-% Author, Article title, Journal, Volume, page numbers (year)
-% % Format for books
-% \bibitem{RefB}
-% Author, Book title, page numbers. Publisher, place (year)
-% % etc
-% \end{thebibliography}
+%\bibliography{bibliography}   % name your BibTeX data base
+
+\begin{thebibliography}{10}
+\providecommand{\url}[1]{{#1}}
+\providecommand{\urlprefix}{URL }
+\expandafter\ifx\csname urlstyle\endcsname\relax
+  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
+  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
+  \urlstyle{rm}\Url}\fi
+
+\bibitem{Andrews:gmae72}
+Andrews, P.: General models and extensionality.
+\newblock Journal of Symbolic Logic \textbf{37}(2), 395--397 (1972)
+
+\bibitem{AndrewsSEP}
+Andrews, P.: Church's type theory.
+\newblock In: E.~Zalta (ed.) The Stanford Encyclopedia of Philosophy, spring
+  2014 edn. (2014)
+
+\bibitem{barendregt13book}
+Barendregt, H., Dekkers, W., Statman, R.: Lambda Calculus with Types.
+\newblock Perspectives in Logic. Cambridge University Press (2013)
+
+\bibitem{C37}
+Benzm{\"u}ller, C.: Automating quantified conditional logics in {HOL}.
+\newblock In: F.~Rossi (ed.) Proc. of IJCAI-23. Beijing, China (2013)
+
+\bibitem{J31}
+Benzm{\"u}ller, C.: Cut-elimination for quantified conditional logic.
+\newblock Journal of Philosophical Logic  (2016)
+
+\bibitem{J6}
+Benzm{\"u}ller, C., Brown, C., Kohlhase, M.: Higher-order semantics and
+  extensionality.
+\newblock Journal of Symbolic Logic \textbf{69}(4), 1027--1088 (2004)
+
+\bibitem{J18}
+Benzm{\"u}ller, C., Brown, C., Kohlhase, M.: Cut-simulation and
+  impredicativity.
+\newblock Logical Methods in Computer Science \textbf{5}(1:6), 1--21 (2009)
+
+\bibitem{B5}
+Benzm{\"u}ller, C., Miller, D.: Automation of higher-order logic.
+\newblock In: J.~Siekmann, D.~Gabbay, J.~Woods (eds.) Handbook of the History
+  of Logic, Volume 9 --- Logic and Computation. Elsevier (2014)
+
+\bibitem{ICMS}
+Benzm{\"u}ller, C., Scott, D.: Automating free logic in {Isabelle/HOL}.
+\newblock In: G.M. Greuel, T.~Koch, P.~Paule, A.~Sommese (eds.) Mathematical
+  Software -- ICMS 2016, 5th International Congress, Proceedings, \emph{LNCS},
+  vol. 9725, pp. 43--50. Springer, Berlin, Germany (2016)
+
+\bibitem{ArXiv}
+Benzm{\"{u}}ller, C., Scott, D.S.: Axiomatizing category theory in free logic.
+\newblock CoRR \textbf{abs/1609.01493} (2016)
+
+\bibitem{J39}
+Benzm\"uller, C., Scott, D.S.: Axiom systems for category theory in free logic.
+\newblock Archive of Formal Proofs  (2018).
+\newblock
+  \urlprefix\url{https://www.isa-afp.org/entries/AxiomaticCategoryTheory.html}
+
+\bibitem{Leo-III}
+Benzm{\"u}ller, C., Steen, A., Wisniewski, M.: {Leo-III} version 1.1 (system
+  description).
+\newblock In: T.~Eiter, D.~Sands (eds.) Logic for Programming, Artificial
+  Intelligence, and Reasoning (LPAR) --- Short Papers, Kalpa Puplications.
+  EasyChair, Maun, Botswana (2017).
+\newblock To appear
+
+\bibitem{LEO}
+Benzm{\"{u}}ller, C., Sultana, N., Paulson, L.C., Theiss, F.: The higher-order
+  prover {Leo-II}.
+\newblock Journal of Automated Reasoning \textbf{55}(4), 389--404 (2015)
+
+\bibitem{SledgehammerTutorial}
+Blanchette, J.C.: {Hammering Away -- A User’s Guide to Sledgehammer for
+  Isabelle/HOL}.
+\newblock Institut f{\"u}r Informatik, Technische Universit{\"a}t M{\"u}nchen
+  (2018).
+\newblock \urlprefix\url{https://isabelle.in.tum.de/doc/sledgehammer.pdf}.
+\newblock With contributions from Lawrence C. Paulson
+
+\bibitem{Sledgehammer}
+Blanchette, J.C., B\"ohme, S., Paulson, L.C.: Extending {Sledgehammer} with
+  {SMT} solvers.
+\newblock Journal of Automated Reasoning \textbf{51}(1), 109--128 (2013)
+
+\bibitem{Nitpick}
+Blanchette, J.C., Nipkow, T.: Nitpick: {A} counterexample generator for
+  higher-order logic based on a relational model finder.
+\newblock In: M.~Kaufmann, L.C. Paulson (eds.) Interactive Theorem Proving,
+  First International Conference, {ITP} 2010, Edinburgh, UK, July 11-14, 2010.
+  Proceedings, \emph{Lecture Notes in Computer Science}, vol. 6172, pp.
+  131--146. Springer (2010)
+
+\bibitem{Spass}
+Blanchette, J.C., Popescu, A., Wand, D., Weidenbach, C.: {More {SPASS} with
+  Isabelle -- Superposition with Hard Sorts and Configurable Simplification}.
+\newblock In: L.~Beringer, A.P. Felty (eds.) Interactive Theorem Proving -
+  Third International Conference, {ITP} 2012, Princeton, NJ, USA, August 13-15,
+  2012. Proceedings, \emph{Lecture Notes in Computer Science}, vol. 7406, pp.
+  345--360. Springer (2012)
+
+\bibitem{Satallax}
+Brown, C.E.: Satallax: An automatic higher-order prover.
+\newblock In: B.~Gramlich, D.~Miller, U.~Sattler (eds.) Automated Reasoning -
+  6th International Joint Conference, {IJCAR} 2012, Manchester, UK, June 26-29,
+  2012. Proceedings, \emph{Lecture Notes in Computer Science}, vol. 7364, pp.
+  111--117. Springer (2012)
+
+\bibitem{Church40}
+Church, A.: A formulation of the simple theory of types.
+\newblock Journal of Symbolic Logic \textbf{5}, 56--68 (1940)
+
+\bibitem{CVC4}
+Deters, M., Reynolds, A., King, T., Barrett, C.W., Tinelli, C.: A tour of
+  {CVC4:} {How} it works, and how to use it.
+\newblock In: K.~Claessen, V.~Kuncak (eds.) Formal Methods in Computer-Aided
+  Design, {FMCAD} 2014, Lausanne, Switzerland, October 21-24, 2014, p.~7.
+  {IEEE} (2014)
+
+\bibitem{Freyd16}
+Freyd, P.: {Amplifications, Diminutions, Subscorings for Categories,
+  Allegories} (2016).
+\newblock University of Pennsylvania. Unpublished. Available at
+  \url{https://www.math.upenn.edu/~pjf/amplifications.pdf}; (accessed in
+  {August} 2016)
+
+\bibitem{FreydScedrov90}
+Freyd, P., Scedrov, A.: Categories, Allegories.
+\newblock North Holland (1990)
+
+\bibitem{Vampire}
+Kov{\'{a}}cs, L., Voronkov, A.: {First-Order Theorem Proving and Vampire}.
+\newblock In: N.~Sharygina, H.~Veith (eds.) Computer Aided Verification - 25th
+  International Conference, {CAV} 2013, Saint Petersburg, Russia, July 13-19,
+  2013. Proceedings, \emph{Lecture Notes in Computer Science}, vol. 8044, pp.
+  1--35. Springer (2013)
+
+\bibitem{Lambert60}
+Lambert, K.: The definition of e(xistence)! in free logic.
+\newblock In: Abstracts: The International Congress for Logic, Methodology and
+  Philosophy of Science. Stanford: Stanford University Press (1960)
+
+\bibitem{lambert02:_free_logic}
+Lambert, K.: Free Logic: Selected Essays.
+\newblock Cambridge: Cambridge University Press (2002)
+
+\bibitem{maclane48:_group}
+MacLane, S.: Groups, categories and duality.
+\newblock Proceedings of the National Academy of Sciences \textbf{34}(6),
+  263--267 (1948)
+
+\bibitem{makarenko16:_autom_logik_logik_stufe}
+Makarenko, I.: Automatisierung von freier logik in logik h{\"o}herer stufe
+  (2016).
+\newblock Bachelorarbeit, Institut f{\"u}r Informatik, Freie Universit{\"a}t
+  Berlin
+
+\bibitem{Z3}
+de~Moura, L.M., Bj{\o}rner, N.: {Z3: An Efficient {SMT} Solver}.
+\newblock In: C.R. Ramakrishnan, J.~Rehof (eds.) Tools and Algorithms for the
+  Construction and Analysis of Systems, 14th International Conference, {TACAS}
+  2008, Held as Part of the Joint European Conferences on Theory and Practice
+  of Software, {ETAPS} 2008, Budapest, Hungary, March 29-April 6, 2008.
+  Proceedings, \emph{Lecture Notes in Computer Science}, vol. 4963, pp.
+  337--340. Springer (2008)
+
+\bibitem{NPW02}
+Nipkow, T., Paulson, L.C., Wenzel, M.: {Isabelle/HOL: A Proof Assistant for
+  Higher-Order Logic}.
+\newblock No. 2283 in LNCS. Springer (2002)
+
+\bibitem{sep-logic-free}
+Nolt, J.: Free logic.
+\newblock In: E.N. Zalta (ed.) The Stanford Encyclopedia of Philosophy, winter
+  2014 edn. (2014)
+
+\bibitem{E}
+Schulz, S.: System description: {E} 1.8.
+\newblock In: K.L. McMillan, A.~Middeldorp, A.~Voronkov (eds.) Logic for
+  Programming, Artificial Intelligence, and Reasoning - 19th International
+  Conference, LPAR-19, Stellenbosch, South Africa, December 14-19, 2013.
+  Proceedings, \emph{Lecture Notes in Computer Science}, vol. 8312, pp.
+  735--743. Springer (2013).
+\newblock \doi{10.1007/978-3-642-45221-5}.
+\newblock \urlprefix\url{http://dx.doi.org/10.1007/978-3-642-45221-5}
+
+\bibitem{Scott67}
+Scott, D.: Existence and description in formal logic.
+\newblock In: R.~Schoenman (ed.) Bertrand Russell: Philosopher of the Century,
+  pp. 181--200. George Allen \& Unwin, London (1967).
+\newblock (Reprinted with additions in: Philosophical Application of Free
+  Logic, edited by K. Lambert. Oxford Universitry Press, 1991, pp. 28 - 48)
+
+\bibitem{Scott79}
+Scott, D.: Identity and existence in intuitionistic logic.
+\newblock In: M.~Fourman, C.~Mulvey, D.~Scott (eds.) Applications of Sheaves:
+  Proceedings of the Research Symposium on Applications of Sheaf Theory to
+  Logic, Algebra, and Analysis, Durham, July 9--21, 1977, \emph{Lecture Notes
+  in Mathematics}, vol. 752, pp. 660--696. Springer Berlin Heidelberg (1979)
+
+\bibitem{J22}
+Sutcliffe, G., Benzm{\"u}ller, C.: Automated reasoning in higher-order logic
+  using the {TPTP THF} infrastructure.
+\newblock Journal of Formalized Reasoning \textbf{3}(1), 1--27 (2010)
+
+\bibitem{W56}
+Wisniewski, M., Steen, A., Benzm\"uller, C.: {TPTP} and beyond: Representation
+  of quantified non-classical logics.
+\newblock In: C.~Benzm{\"u}ller, J.~Otten (eds.) ARQNL 2016. Automated
+  Reasoning in Quantified Non-Classical Logics, vol. 1770, pp. 51--65. CEUR
+  Workshop Proceedings, http://ceur-ws.org (2016)
+
+\end{thebibliography}
 

### 2018-12-17 FreeLogic/2018-JAR/article.tex
update

@@
     Metaphysics} (BE 2501/9-2) and from VolkswagenStiftung under grant
-  Consistent Rational Argumentation in Politics (CRAP).}  and Dana S. Scott}
+  \emph{Consistent Rational Argumentation in Politics} (CRAP).}  and Dana S. Scott}
 \institute{Christoph Benzm\"uller \at
@@
   & \hol{(({\vee_{o\ar o\ar o}}\,s_o)\,t_o)} \mid \hol{\forall_{(\alpha\ar
-    o)\ar o}(\lam{X_\alpha} s_o)} \mid \hol{\Descr(\lam{X_\alpha} s_o)}
+    o)\ar o}(\lam{X_\alpha} s_o)} \mid \hol{\Descr_{(\alpha\ar
+  o)\ar \alpha}(\lam{X_\alpha} s_o)}
 \end{align*}
@@
 notation $\hol{\all{X_\alpha} s_o}$ and $\hol{\Descr {X_\alpha}\lambdot s_o}$ is used as shorthand for
-$\hol{\forall_{(\alpha\ar o)\ar o}
+$\hol{\forall 
 (\lam{X_\alpha} s_o)}$ and $\hol{\Descr(\lam{X_\alpha} s_o)}$, and infix notation $\hol{s \vee t}$ is employed
@@
 $$  \forall y\lambdot \exists i\lambdot \id i \wedge i \comp y \cong y
-\wedge (\forall j\lambdot d(\id j \wedge j \comp y \cong y) \imp i \cong j)
+\wedge (\forall j\lambdot (\id j \wedge j \comp y \cong y) \imp i \cong j)
 \quad 
@@
 monoids: If all objects are defined, then one can conclude from $A1$ that 
-$\dom x \cong \dom y$ (resp.~$\dom x \cong \cod y$) and $\cod x \cong \cod y$), 
+$\dom x \cong \dom y$ (resp.~$\dom x \cong \cod y$ and $\cod x \cong \cod y$), 
 and according to 1.14 of \cite{FreydScedrov90}, 
@@
  also had that $a$ is defined, which is not the case by assumption.
-  Hence, $\neg E (a \comp (\dom a)$.
+  Hence, $\neg E (a \comp (\dom a))$.
 Next, we instantiate $A1$ with $a$ and $\dom a$ to obtain
@@
    (\dom a)$ is defined, which contradicts $\neg E (a \comp (\dom
-   a)$. $\Box$
+   a))$. $\Box$
 
@@
 \bibitem{makarenko16:_autom_logik_logik_stufe}
-Makarenko, I.: Automatisierung von freier logik in logik h{\"o}herer stufe
+Makarenko, I.: Automatisierung von Freier Logik in Logik h{\"o}herer Stufe
   (2016).
